### 2014-11-23 abstract.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

\newpage
\doublespacing

\begin{center}
ABSTRACT\\
\addcontentsline{toc}{section}{ABSTRACT}

\yourtitle \\
\yourname \\
\number\year\\
\end{center}

\par
Nearly every large organization on Earth is involved in software development at some level.  Some organizations
specialize in software development while other organizations only participate in software development out of
necessity. In both cases, the performance of the software development matters.  Organizations collect
vast amounts of data relating to software development.  What do the organizations do with that data? 
That is the problem.  Many organizations fail to do anything meaningful with the data.

Another problem is knowing what data to collect.  There are many options, but certain data is more important than
others.  What data should a software development organization collect?

This paper plans to answer that question and present a framework to gather the 
right information and provide a score for an organization that
produces software.  The score is not to be comparative between organizations, but to be comparative for a specific
organization over time.

The primary goal of this work is to provide a general framework for what a software development organization
should measure and how to report on those measurements.  The focus is scoring of the entire
organization and not just the development efforts.  The secondary goal of this work is to provide
a software implementation of that framework.

\end{document}

### 2014-11-23 acknowledgements.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

\newpage

\begin{center}
ACKNOWLEDGEMENTS\\
~\\
\end{center}

I would like to acknowledge the generous support I received from my family. Thank you
to Emily for providing encouragement and the final push to get me to eventually finish.
Thank you to Ainsley, Porter, Trey, and Ryker for always providing a smile.

I would also like to acknowledge numerous other people for providing
guidance and support during the process.
I will only use first names, but you know who you are. Thank you to: Jess, Chris, Clay, 
Bob, Todd, Leslie, Mike, and Ralph.

\end{document}

### 2014-11-23 appendices.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

\newpage
%% numbers following sections with A, B, C..
\appendix
\label{appendix}
\begin{center}
APPENDIX\\
~\\
\end{center}
\addcontentsline{toc}{section}{APPENDIX}

%%\section{Example Graphics}

%%\begin{figure}[h!]
%%\scriptsize
%%$$
%%\begin{array}{cc}
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
%%(a) & (b) \\
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
%%(c) & (d) \\
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
%%(e) & (f) \\
%%\end{array}
%%$$
%%\caption{A graphic in the appendix}
%%\end{figure}

%% Prints all figures and tables on the page and begins a new page
%% http://www.astro.rug.nl/~kuijken/latex.html
%%\clearpage

\section{Case Study Source Code} 
\label{app:case}

\subsection{R Code - Quality} 
\scriptsize{
\begin{lstlisting}[language=R]
# Load the Quality data.
setAs("character","myDate", function(from) as.Date(from, format="%m/%d/%Y") )
setClass('myDate')

quality_data <- read.csv('quality_data_clean.csv', 
        colClasses=c('factor','myDate','myDate','numeric','numeric',
        'numeric','numeric','numeric','numeric','numeric') )
str(quality_data)
head(quality_data)
summary(quality_data)

# Get data prior to 2013
old_quality_data = quality_data[quality_data$MONTH_DT <= as.Date('2013-12-31') ,]
str(old_quality_data)
pairs(old_quality_data[,c('TOTAL_TIX','EST_DEV_RES_HRS')] )

# Separate out large (>1000 hours) and small projects
large_quality_data = old_quality_data[old_quality_data$EST_DEV_RES_HRS >= 1000,]
str(large_quality_data)
largefit <- lm(TOTAL_TIX ~ EST_DEV_RES_HRS + DFTS_CNT_SIT + DFTS_CNT_UAT , 
        data=large_quality_data)
summary(largefit)
largefit_sigma = summary(largefit)$sigma
pairs(large_quality_data[,c('EST_DEV_RES_HRS','DFTS_CNT_SIT',
        'DFTS_CNT_UAT','TOTAL_TIX')])

small_quality_data = 
        old_quality_data[old_quality_data$EST_DEV_RES_HRS < 1000 
            && old_quality_data$APP != 'App 86' ,]
str(small_quality_data)
smallfit <- lm(TOTAL_TIX ~ EST_DEV_RES_HRS + DFTS_CNT_SIT + DFTS_CNT_UAT , 
        data=small_quality_data)
summary(smallfit)
smallfit_sigma = summary(smallfit)$sigma
pairs(small_quality_data[,c('EST_DEV_RES_HRS','DFTS_CNT_SIT',
        'DFTS_CNT_UAT','TOTAL_TIX')])

# predict new data  
new_large_quality_data = 
        quality_data[quality_data$MONTH_DT > as.Date('2013-12-31') 
            & quality_data$MONTH_DT < as.Date('2014-12-31') 
            & quality_data$EST_DEV_RES_HRS >= 1000,]
new_small_quality_data = 
        quality_data[quality_data$MONTH_DT > as.Date('2013-12-31') 
        & quality_data$MONTH_DT < as.Date('2014-12-31') 
        & quality_data$EST_DEV_RES_HRS < 1000,]
new_large_quality_data$PREDICTION = 
        predict(largefit, newdata=new_large_quality_data)
new_large_quality_data$SCORE = 
        (new_large_quality_data$PREDICTION - new_large_quality_data$TOTAL_TIX)
        / (6 * summary(largefit)$sigma)
new_large_quality_data[,c('APP','MONTH_DT','TOTAL_TIX','PREDICTION', 'SCORE')]

new_small_quality_data$PREDICTION = predict(smallfit, newdata=new_small_quality_data)
new_small_quality_data$SCORE = 
        (new_small_quality_data$PREDICTION - new_small_quality_data$TOTAL_TIX)
        / (6 * summary(smallfit)$sigma)
new_small_quality_data[,c('APP','MONTH_DT','TOTAL_TIX','PREDICTION', 'SCORE')]

#Combine new data  
new_quality_data = rbind(new_large_quality_data, new_small_quality_data)
str(new_quality_data)
summary(new_quality_data)

aggregate(SCORE ~ MONTH_DT, new_quality_data, mean)

# TODO include
# numerical summary stats, graphical summaries,
# dist of variables(hist used for guidance), associations among variables
\end{lstlisting}}

\end{document}

### 2014-11-23 paper_10_intro.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

\newpage
\pagenumbering{arabic}
\setcounter{tocdepth}{2}

% see this for  guidance https://www.cs.purdue.edu/homes/dec/essay.dissertation.html
\section{Introduction}

Software is becoming a vital part of companies. In 2011 Marc Andreessen, co-founder of the venture capital firm Andreessen-Horowitz,
famously claimed, ``Software is Eating The World'' \cite{Andreessen2001}. His argument was for the ever increasing importance of software
in all organizations big and small regardless of the industry.  With this important declaration, the production of new software is
going to be critical.  Just as important will be the effective measurement of how this software is produced.

The goal of this work is to provide a basis of what data should be collected by a software development organization, and how that data
should be used to formulate a single number representing the software development score of an organization. A framework to 
achieve the score will be presented.  The  score
is not to be comparative between organizations, but to rather form a historical baseline for a specific organization.  Also, a software
system to collect, calculate, and report the score will be presented.

\subsection{Background}

Throughout the history of software development, many values have been collected and used to measure the effectiveness of software development. 
Many metrics have been used in the past and are still being used.  A metric can be defined as the science of indirect measurement.
The following are some examples of metrics that can be collected about source code:
\begin{itemize}
\item SLOC - The number of Source Lines of Code 
\item NOM - The Number of Methods per class
\item Complexity - A numerical measure of the code complexity, some common examples are McCabe \cite{McCabe1976} and Halstead \cite{Halstead1977}
\item Design - The amount of coupling and cohesion present in the software code
\item Source Code Analysis - Tools that determine whether code adheres to specified set of rules. Common examples are PMD and findbugs.
\end{itemize}

However, the metrics on source code only explain part of the software development lifecycle.  
Most of the effort has been placed on measuring just the computer code and not the entire organization.  Software
development involves more than just source code.

\subsection{Previous Software Engineering Scoring Attempts}

Sextant is a visualization tool for Java source code \cite{Winter2013}.  Sextant provides a graphical representation of the information related 
to a software system.  The tool provides the capability to provide custom rules which are specific to the domain or application.  However,
Sextant only provides metrics and analysis of the software code.  It provides no information regarding the rest of the 
software development lifecycle.  Also, the primary output of Sextant is visual graphs.  While these graphs do provide
useful information, they do not provide a single number to determine the performance of the software.

\textit{Software process mining} \cite{Rubin2007} provides
an algorithm and information for measuring a software engineering process from
the Software Configuration Management (SCM). Software process mining does provide a method for tracking all 
documentation that can be placed in SCM, not just source code.  The technique creates process models 
to understand the process of developing software and code. It is less focused on the output and results,
but it is more focused on conformance to a process or understanding the process. Once again, a single number is not produced.

One example of scoring software development is presented by Jones \cite{Jones2012}. The methodology looks
for the presence of various techniques used in software engineering.  The methodology provides a score based upon the 
productivity and quality increase of the technique being evaluated.  A couple example techniques are: 
automated source code analysis and continuous integration.  The end result is a score in range $[-10,10]$. 
While the single number score is nice, it does not account for the entirety of the software development lifecycle.

Much work has been done to determine metrics for source code, in fact 
entire books have been written on the topic of software metrics \cite{Jones1996, Putnam2013}. Yet, 
organizations still struggle to measure the production of software.
Little work exists
for scoring the entire software development organization.

\end{document}

### 2014-11-23 paper_20_sdo.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

\section{A Software Development Organization (SDO)}
A \textit{Software Development Organization} is any organization or subset of an organization that is responsible
for the creation, deployment, and maintenance of software.  Many times a software development organization
is a company that produces software.  Other times, a software development organization is contained
within the Information Technology department of a larger organization. Some of the job roles
with an SDO are: software engineer, system administrator, software quality analyst,
programmer, database administrator, and documentation specialist.

\subsection{What is Software?}
Numerous definitions can be found for the term \textit{software}.
Software is more than just computer programs. According to Ian Sommerville \cite{Sommerville2001}, 
"Software is not just the programs but also all associated documentation and configuration data which is needed to make these programs operate correctly."
This is the definition used for the remainder of this work.

\subsection{The Software Development Lifecycle}
    For this question, I choose to rewrite that section of the proposal.  This was
    my favorite question. It forced me to go look back into the history of
    software development.

    The discipline of software engineering has created a workflow for developing
    software.  
    This workflow is called the \textit{Software Development Life Cycle (SDLC)}.
    SDLC can be defined as \cite{Ruparelia2010}:
    \begin{quote}
     [...] a conceptual framework or process that considers the structure of the stages
     involved in the development of an application from its initial feasibility study
     through to its deployment in the field and maintenance.
    \end{quote}
    While the SDLC states what needs to be done, there are numerous models 
    that formalize exactly how to perform the SDLC.  The models contain
    steps that are commonly referred to as a phases. A few of the popular
    models are described below.

    \subsubsection{Waterfall}
        The waterfall model is the oldest and most influential of the SDLC models. 
        It was first presented at a Navy Mathematical Computing Advisory Panel in 1956
        by Herb Benington \cite{Benington1987}. Figure \ref{fig:benington} shows
        the model Benington outlined for producing large software systems.  
        In 1970, Benington's model was modified by Royce \cite{Royce1987}.  Royce
        produced an updated version of the diagram seen in Figure \ref{fig:royce}
        which provides some loops to go back to a previous phase in the workflow.

        \begin{figure}
            \centering
            \includegraphics[scale=.5]{benington_waterfall.PNG}
            \caption[Benington's original diagram for producing large software systems]
                    {Benington's original diagram for producing large software 
                        systems, adapted from \cite{Benington1987}}
            \label{fig:benington}
        \end{figure}%
        \begin{figure}
            \centering
            \includegraphics[scale=.5]{royce_waterfall.PNG}
            \caption[Royce's version of the waterfall model]
                {Royce's version of the waterfall model for producing software 
                        systems, adapted from \cite{Royce1987}}
            \label{fig:royce}
        \end{figure}

        The modern version of the waterfall model specifies that each phase needs 
        to be entirely completed before moving
        onto the next phase.  Some small amount of overlap is permitted and looping 
        occurs but both actions are discouraged and should be limited.  
        A modern diagram of the waterfall model can be seen in Figure \ref{fig:waterfall}.
        \begin{figure}[here]
            \centering
            \includegraphics[scale=.6]{waterfall.png}
            \caption[Modern Waterfall]
                {Modern Waterfall Diagram, adapted from \cite{Hibbs2009} }
            \label{fig:waterfall}
        \end{figure}

        Waterfall has some excellent features such as: simple to understand,
        easy to plan, and well-defined phases. However, waterfall lacks
        the flexibility required of many software systems built today
        \cite{Maheshwari2012}.  Due to the fact the phases are so sequential,
        it makes changes during the life cycle difficult and expensive if 
        not impossible. Therefore, other models of SDLC have been created
        to address the lack of flexibility of the waterfall model. Notice,
        the other models are  adaptations of waterfall.

    \subsubsection{Spiral}

        The spiral model for software development was presented by Boehm in 1986
        \cite{Boehm1986, Boehm1988}. 
        The goal of the spiral mode of software development is very risk-driven.
        A software project will start with many small and quick iterations. 
        Each iteration will cover the following 4 basic steps. 
        \begin{enumerate}
            \item Determine Objectives
            \item Identify Risks
            \item Develop and Test
            \item Plan Next Iteration
        \end{enumerate}
        This model allows software to be built over a series of iterations
        without risking too much time or effort in any single iteration.
        Sprial requires a very adaptive management approach
        as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
        It can also be difficult to identify risks that will occur in future
        iterations.
        Figure \ref{fig:spiral} provides a bit more detail on the iterations
        and the overall process. 
        \begin{figure}[here]
            \centering
            \includegraphics[scale=.5]{spiral_model.png}
            \caption[Spiral SDLC Model]{Spiral SDLC Model \cite{Boehm2000} }
            \label{fig:spiral}
        \end{figure}

    \subsubsection{Agile}
        Agile software development has arisen due to the inability
        of the waterfall and other models to adjust to changes during the 
        development cycle.  
        Agile software development is a group of SDLC models that operate
        under the influence of the following four key principles \cite{Beck2001}.
        \begin{enumerate}
            \item Individuals and interactions over processes and tools
            \item Working software over comprehensive documentation
            \item Customer collaboration over contract negotiation
            \item Responding to change over following a plan
        \end{enumerate}
        Agile does not specify an implementation, but
        some specific models of agile SDLC are:
        eXtreme Programming, Scrum, Lean, Kanban and others 
        \cite{Moniruzzaman2013, Hibbs2009}.  Agile models 
        are very popular in many of today's software development
        organizations because the models work well for dynamic
        quickly changing applications such as web-based applications.

    \subsubsection{SDLC Commonalities}
        Even with the large number of SDLC models currently being used by different SDOs,
        there is still some commonalities among the models.  The 
        commonalities can be tied back to the steps of waterfall.  All of the models
        exhibit, to some degree, the following phases. The only major difference is 
        the scope, size, and duration of each phase.  For example, the spiral
        model spends less time in each phase.  The agile models produce less
        documentation and focus more on the Implemenation phase. Here are
        the common phases in nearly all SDLC models:
        \begin{description}
            \item[1. Requirements] \hfill \\ The first phase is involved 
                with defining what the software must do.  Each piece of 
                functionality is considered a requirement.  
            \item[2. Design] \hfill \\ Before writing any code, the 
                necessary infrastructure and involved software systems
                must be identified. This phase can serve as a roadmap for the 
                remaining phases. If done properly, this phase can greatly 
                help the later phases.
            \item[3. Implementation] \hfill \\ Often the only phase of the SDLC 
                that is measured, this is the phase where the actual computer
                code is written.
            \item[4. Testing] \hfill \\ This phase validates the expected 
                functionality.  Also, testing attempts to discover unexpected
                side affects of the software.
            \item[5. Deployment and Maintenance] \hfill \\ All software must 
                be correctly deployed and maintained.  This phase is the 
                most expensive and lengthy phase of the software
                development lifecycle.
        \end{description}

\subsection{What is Software Engineering?}
    \textit{Software Engineering} as a term dates back to the 
    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013}. Over the 
    years many definitions have been provided.  IEEE provides a definition that encompasses many of the
    other definitions.  IEEE defines software engineering as, 
    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
    \cite{Ieee1990}.

    Software engineering has struggled to determine the correct projects to complete \cite{DeMarco2009}.
    Software projects are typically behind schedule and over budget. Organizations need a better
    technique to understand the past performance so they can better predict the future performance.

\subsection{Terminology}

\begin{description}
    \item[SIT]   (Systems Integration Testing) - The initial step of testing
        after the development phase of the SDLC.  This is typically 
        performed by members of the SDO.  It is validation that all the
        software components function together as expected.
    \item[UAT]   (User Acceptance Testing) - The final step of testing
        when a select few members of the user group are invited to
        validate the software system. Once validation has occured for
        UAT, the software system is ready to proceed to production
    \item[PROD]  (Production) - The software has been released to the final audience.
    \item[defect] Whenever the output of software does not meet expectations.  It is important to mention that even though defects are typically 
            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.
\end{description}

%\subsection{Data-Driven Software Engineering}
%Data Driven Software Engineering not Data Driven Software Development

%Check these book \cite{Jones2009, Jones1996, Lee2003}. This might be similar
%to process mining \cite{vanderAalst2012}.

\end{document}

### 2014-11-23 paper_30_measure.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

% new section
\section{Data Driven Software Engineering}

Performance indicators can be crucial measurements
within any business setting, and an SDO is no exception. Many
SDOs struggle to determine the correct indicators to track and
how to track them.  
The differences between the indicators will be explored and
possible measures for each indicator in an SDO will be
presented.  The 4 different types of indicators are.
\begin{enumerate}
  \item RI (Result Indicator)
  \item KRI (Key Result Indicator)
  \item PI (Performance Indicator)
  \item KPI (Key Performance Indicator)
\end{enumerate}

More information on the indicators can be found
in chapter 1 of \cite{parmenter2010}
as well as \cite{florac1999,kaplan1992,letier2013}.

\subsection{Result Indicators for Software Departments}
    This section will cover the potential result indicators for an SDO.

\subsection{Performance Indicators for Software Departments}
    This section will cover the potential performance indicators for an SDO.

\subsection{Balanced Scorecard}

A common technique for organization to measure themselves is a balanced scorecard.
A \textit{balanced scorecard} must contain the following
characteristics.
\begin{itemize}
  \item Financial 
  \item Customer Focus
  \item Environment/Community
  \item Internal Process
  \item Employee Satisfaction
  \item Learning and Growth
\end{itemize}

Balanced scorecards are great for displaying the important information about
and organization.  However, a balanced scorecard does not specify what
exactly needs to be tracked.  It is also not specific to an SDO and 
it does produce a single number.

%This info comes from \cite{parmenter2010}.

%\subsection{Possible data points for Level %of Effort}

%\begin{description}
%    \item[Actual Development Hours] Actual Hours Spent on development
%    \item[Estimated Development Hours]  Initial Hours estimated for a project, this will commonly be different from the actual development hours
%    \item[Source Lines Of Code (SLOC)]  This is count of the total number of lines of source code
%    \item[Modified Lines Of Code] This is a count of the number of modified lines of source code. This number is a sum of the deleted, added, and modified lines of source code.
%end{description}

According to Putnam and Myers in \cite{Putnam2013}, the 5 core measurements for managing software
projects are:

\begin{enumerate}
    \item \textbf{Quantity of function} usually measured in terms of size (such as source lines of code or function points), that ultimately execute on the computer
    \item \textbf{Productivity} as expressed in terms of the functionality produced for the time and effort expended
    \item \textbf{Time} the duration of the project in calendar months
    \item \textbf{Effort} the amount of work expended in person-months
    \item \textbf{Reliability} as expressed in terms of defect rate (or its reciprocal, mean time to defect)
\end{enumerate}
However, these measurements don't focus on the entire SDO. They say nothing about the availablity of the software infrastructure or the satisfaction of the users.

\begin{description}
  \item[Time] This measurement can be hours, days, weeks, or months.  the time increment does not matter as long as it is consistent.
  \item[Effort] This measurement is person-months, person-weeks, or person-days.
  \item[Quality] This measurement is the defect rate (defects per time period).
  \item[Amount of Work] This measurement has the same units as Effort above. 
  \item[Process Productivity] look into this a bit further
  \item[Function Points] find a definition and a comparison with story points
  \item[Story Points] Look in some agile book
\end{description}

Chapter 7 of \cite{Putnam2013} contains some equations to calculate and relate
these measures. Those equations will be studied and evaluated.

Antolic in \cite{Antolic2008} demostrates some ways to measure KPIs for the  software development process.

\subsection{Measuring Other Aspects of an SDO}

It is important to note that software departments do not just
develop software.  The department has many other duties
including: deploying software, installing server hardware/software,
writing documentation, surveying users, and other things.

\subsection{Combining The Measures to Form MPI}

How can the PIs, RIs, KRIs, and KPIs be combined to form a single
value called an MPI (Master Performance Indicator)?  The field
of sports analytics also has numerous techniques for combining
multiple indicators to produce a single number \cite{Cervone2014}.

\end{document}

### 2014-11-23 paper_40_mpi.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

\section{MPI}

Software development organizations struggle to measure overall performance.  The Master Performance Indicator (MPI) is an algorithm to provide a single number score for the performance of a software development organization. It works by statistically analyzing the past performance of the organization and using that information to score an organization on current and future performance.  MPI focuses on the following elements of a software development organization: \textit{requirements},  \textit{quality},  \textit{on-schedule},  \textit{availability}, and  \textit{satisfaction}. MPI is not meant to be comparative between organizations, but to measure the amount of increase or decrease a single organization exhibits.
It is possible the concept could be expanded beyond just software development organizations or the previously stated elements.

Here are the attributes of the MPI scoring.
            \begin{itemize}
                \item The range of scores must have equal values above and below 0
                \item The minimum score must equate to the worst possible performance, however that is defined
                \item Similarily, the maximum score must equate to the best possible performance.  
                \item A score of 0 must be average (or expected) performance
                \item All individual elements must have the same scoring range
            \end{itemize}

            As long as those 5 features are met, the range can be anything.  The range of $[-1,1]$ was chosen because it is easy to scale to a different range such as $[-10,10]$ or $[-100,100]$.  It maybe makes sense to use variables for the range.  The formulas are designed to fall in the range $[-1,1]$.  Thus scaling can be applied to obtain values in any appropriate range.

\subsection{Quality}
Quality is arguably the most important part of software development.  Poor quality means time, money, and resources are spent 
fixing the quality.  One of the key indicators of software quality is defects.  Thus, it is important
to measure the number of defects associated with a software release.  The following is an algorithm to calculate
the quality score of software being released.

\begin{displaymath}
   S_{1_i} = \left\{
     \begin{array}{lr}
       \text{where } f \geq d_i & : \left[ \frac{f - d_i}{f} \right] \\
       \text{where } d_i > f  & : \left[ \frac{f-d_i }{6\sigma} \right]
     \end{array}
   \right]
\end{displaymath}

\[
    S_{1} = \frac{\sum^n_{i=1} S_{1_i}}{n}
\]
\begin{itemize}
\item $n$ is the number of apps
\item $d_i$ is the actual defects
\item $f(h_i)$ is the function to predict defects based upon hours and other aspects of software development
\item $6\sigma$ 6 times an estimate of the standard deviation of the population using function $f$ above
\end{itemize}

Here are the columns of the data.

\begin{longtable}{@{}l rr rr}
% pairs: absolute number (percentage)

\toprule%
 \centering%
 {\bfseries Column Name}
 & {\bfseries Data Type}
 &  \\

\cmidrule[0.4pt](r{0.125em}){1-1}%
\cmidrule[0.4pt](lr{0.125em}){2-2}%
\cmidrule[0.4pt](l{0.125em}){3-3}%
% \midrule
\endhead

Application ID & String (factor) & Required \\
\myrowcolour%
Frequency Date & Date & Required \\
Development Hours & Integer & Required \\
\myrowcolour%
Testing Hours & Integer & Optional \\ 
Defects in SIT & Integer & Optional \\ 
\myrowcolour%
Defects in UAT & Integer  & Optional \\ 
Defects in PROD & Integer  & Required \\

\bottomrule

\caption{Quality - Inputs}
\label{tab:quality}
\end{longtable}

There are 2 parts here.  First the system needs to be loaded with this data.  Hopefully,
a file with this data will exist going back a few months or years.  It is also important
to note that the data load must be optional if an organization does not have existing
data.  Second, every release (month/year) a new file will be upload with new information
about the most recent release.

Here is the problem for loading the data:
Given a data file with the above columns, can a regression model be automatically found
that fits the data?  The regression model will serve as the "target" for future 
releases.  Here is a list of possible things to automate to get a good model.
\begin{itemize}
\item Linear Regression
\item Stepwise Regression
\item Ridge Regression for suspected multicolinearity
\item Removal of outliers
\end{itemize}

\subsection{Satisfaction}
The satisfaction of the customer is also very important.  The following is an algorithm to calculate the satisfaction of software.
\[
    S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
\]

\begin{itemize}
\item $a_{i j}$ answer to question $j$ for app $i$
\item $m$ number of questions
\item $n$ number of apps
\item $min$ minimum score for a question
\item $max$ maximum score for a question
\end{itemize}

\begin{longtable}{@{}l rr rr}
% pairs: absolute number (percentage)

\toprule%
 \centering%
 {\bfseries Column Name}
 & {\bfseries Data Type}
 &  \\

\cmidrule[0.4pt](r{0.125em}){1-1}%
\cmidrule[0.4pt](lr{0.125em}){2-2}%
\cmidrule[0.4pt](l{0.125em}){3-3}%
% \midrule
\endhead

Question ID & String  & Required \\
\myrowcolour%
Question Text & String  & Optional \\
Application ID & String & Required \\
\myrowcolour%
Frequency Date & Date & Required \\
Response & Integer between min and max  & Required \\
\myrowcolour%
Response Date & Date & Optional \\

\bottomrule

\caption{Satisfaction - Inputs}
\label{tab:satisfaction}
\end{longtable}

\subsection{Availability}
All the new requirements and great quality do not matter if the software is not available.  
The following algorithm will calculate the score of software availability.
\begin{displaymath}
   S_{3_i} = \left\{
     \begin{array}{lr}
       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
     \end{array}
   \right.
\end{displaymath} 
\[
    S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
\]

\begin{itemize}
\item $A_{a_i}$ actual availability for app i
\item $A_{e_i}$ expected availability for app i
\end{itemize}

\begin{longtable}{@{}l rr rr}
% pairs: absolute number (percentage)

\toprule%
 \centering%
 {\bfseries Column Name}
 & {\bfseries Data Type}
 &  \\

\cmidrule[0.4pt](r{0.125em}){1-1}%
\cmidrule[0.4pt](lr{0.125em}){2-2}%
\cmidrule[0.4pt](l{0.125em}){3-3}%
% \midrule
\endhead

Application ID & String  & Required \\
\myrowcolour%
Frequency Date & Date & Required \\
Uptime & Float & Optional \\
\myrowcolour%
Scheduled Downtime & Float & Optional \\
Unscheduled Downtime & Float  & Optional \\
\myrowcolour%
Percent Uptime & Float & Required \\
Expected Percent Uptime & Float & Required \\

\bottomrule

\caption{Availability - Inputs}
\label{tab:avail}
\end{longtable}

\subsection{On-Schedule}
Delivery of software in a timely manner is important.  Therefore, it is critical to know whether software was released early, late, or on-time.  
The best possible score should be achieved
            when meeting the estimated date exactly.  The maximum score
            should come from the best estimate.  Then given historical
            release data, it is easy to determine an 
            average $\Delta$ between the actual and the estimated.  
            Finishing a project within that $\Delta$ should result 
            in a positive score.  Outside the $\Delta$ results in
            negative scores.  For example, a project releasing
            one day early or one day late would receive the same score
            because in both cases the estimate was missed by one day.

The exact algorithm here is yet to be determined.

%The score can be accomplished with the following 
%algorithm.
%\[
%    S_4 = \frac{\sum^n_{i=1} \left( C_{a_i} - C_{e_i} \right)}{n}
%\]
%\begin{itemize}
%\item $C_a$ actual number of days for application $i$
%\item $C_e$ estimated number of days for application $i$
%\end{itemize}

\begin{longtable}{@{}l rr rr}
% pairs: absolute number (percentage)

\toprule%
 \centering%
 {\bfseries Column Name}
 & {\bfseries Data Type}
 &  \\

\cmidrule[0.4pt](r{0.125em}){1-1}%
\cmidrule[0.4pt](lr{0.125em}){2-2}%
\cmidrule[0.4pt](l{0.125em}){3-3}%
% \midrule
\endhead

Application ID & String  & Required \\
\myrowcolour%
Frequency Date & Date & Required \\
Scheduled Finish Date & Date & Required \\
\myrowcolour%
Actual Start Date & Date  & Required \\
Actual Finish Date & Date  & Required \\

\bottomrule

\caption{On-Schedule - Inputs}
\label{tab:sched}
\end{longtable}

\subsection{Requirements}
Requirements are desired new features or enhancements to a software product.  It is important to know how many requirements
were scheduled to be completed versus how many actually got completed.  
\[
    S_5 = \frac{\sum^n_{i=1}\left( R_{a_i} - R_{e_i} \right)}{n}
\]
\begin{itemize}
\item $R_a$ actual requirements completed for application $i$
\item $R_e$ expected requirements completed for application $i$
\end{itemize}

\begin{longtable}{@{}l rr rr}
% pairs: absolute number (percentage)

\toprule%
 \centering%
 {\bfseries Column Name}
 & {\bfseries Data Type}
 &  \\

\cmidrule[0.4pt](r{0.125em}){1-1}%
\cmidrule[0.4pt](lr{0.125em}){2-2}%
\cmidrule[0.4pt](l{0.125em}){3-3}%
% \midrule
\endhead

Application ID & String  & Required \\
\myrowcolour%
Frequency Date & Date & Required \\
Requirements Scheduled & Integer & Required \\
\myrowcolour%
Actual Requirements Released & Integer  & Required \\

\bottomrule

\caption{Requirements - Inputs}
\label{tab:req}
\end{longtable}

\subsection{Final MPI Score}
One complete overall score cannot be successful without including information from various aspects of the software development organization.  Therefore, the previous results
are combined to provide one overall score.

\[
    MPI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
\]

\end{document}

### 2014-11-23 paper_50_sdlc-ae.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

% All about the SDLC Analytic Engine
\section{SDLC Analytic Engine}

In order for an SDO to properly track the elements of MPI, a data storage system should be available to store the appropriate data.   This storage system will be named the SDLC Analytic Engine (SDLC-AE). Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.

The SDLC-AE would make gamification of the SDLC attainable.  Prior attempts
at gamification of the SDLC focus only on the development phase \cite{Dubois2013} \cite{Snipes2013}.

\begin{figure}[ht]
\includegraphics[scale=.7]{sdlc-ae.png}
\caption{SDLC Analytic Engine}
\label{fig:sdlc-ae}
\end{figure}

\subsection{Database Structure}
   All the data necessary to compute MPI needs to be stored in a database.  This section will 
   layout the structure of tables and relationships necessary to the store all the data
   within a relational database such as MySQL or PostgreSQL.  Eventually,
   database diagrams and SQL scripts will be provided in the section.

\subsection{Queries}
    The section will provide the necessary SQL queries to obtain the correct data
    needed to compute the individual elements of MPI.

\subsection{Computations}
    This section will provide R scripts to calculate each individual score and the overall 
    MPI score. The scripts will need to be run every time the data is updated and the MPI
    score needs to be recalculated.

\begin{comment}
    \subsection{Estimation}

    \begin{itemize}
    \item Change to Database Structure  
    \item Modify Database Data    
    \item Create a New Database, number of new databases  
    \item Server Configuration Changes Required   
    \item New Servers Required   
    \item Number of Team Members Involved  
    \item Number of (sub)Systems Involved  
    \item Estimation Date
    \item Number of Days Allowed
    \item List of Other Attributes
    \item Number of Screens Involved 
    \item Actual Value (hours, days, dollars) 
    \end{itemize}

    Estimated Dev Hours - The number of development hours estimated for a project, this is just developer hours
    Estimated Doc Hours - The number of documentation hours estimated for a project
    Estimated Test Hours - The number of testing hours estimated for a project
    Estimated Deployment Hours - The number of estimated hours required to deploy the project

    \subsection{Requirements}
    List of: 
    \begin{description}
      \item[Title] 
      \item[Descrition]
      \item[author]
      \item[projectID]
      \item[date]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{Maintenance (Defects)}
    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[description]
      \item[date Entered]
      \item[Date fixed]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{Testing}

    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[title]
      \item[description]
      \item[author]
      \item[Date Started]
      \item[Date Executed]
      \item[Status (Pending, pass, fail)]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

    \subsection{Development}

    List of Coding Tasks:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[List of Files]
      \item[author]
      \item[Date Started]
      \item[Completion Date]
      \item[Number of Unit Tests]
      \item[Lines of Code]
      \item[Others] See \cite{Jones2009, Jones2012, Rubin2007, Snipes2013}
    \end{description}

    \subsection{Implementation}

    List of:
    \begin{description}
      \item[Project] 
      \item[Release]
      \item[date Entered]
      \item[Date Scheduled]
      \item[Date Executed]
      \item[Ordering/Prerequisites]
      \item[Comments] list of \\
      \begin{description}
        \item[date]
        \item[comment Text]
        \item[author]
      \end{description}
    \end{description}

\end{comment}

\end{document}

### 2014-11-23 paper_60_tooling.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

% new section
\section{Tooling}

\subsection{SDLC Dashboard}
This maybe needs a name: Project MPI????  The goal of this project is to provide a tool that
given the 5 files will be able to provide a score for the software department.  It should run 
as a web application.

This section will provide information to install and run a tool for calculating MPI for an organization.
\subsubsection{Introduction}
\subsubsection{Overview}
\subsubsection{Installation}
\subsubsection{Database}
maybe MongoDB, maybe PostgreSQL/MySQL
\subsubsection{Webserver}
The software can either run standalone on cloud-hosted platform such as Heroku.  Try using Play Framework 2 with Authenticate.

\subsection{SDLC-AE}

\end{document}

### 2014-11-23 paper_70_case-study.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

% new section
\section{Case Study: Scoring an SDO of a Large Financial Institution}

Data has been collected from the software development processes of
an SDO within a large financial institution.
The data collection was from 2008 to present. This section will provide the analysis performed and the MPI scores of that data. The data is incomplete but that is realistic of most oganizations.  Currently, the data
consists of availability, quality, and schedule.  Satisfaction and Requirements are being obtained. An example of the initial analysis is included in \cref{app:case}.

%These are notes

%Application(app) - a software system or a collection of other apps, for example: Wystar is an application but it is a collection of other apps namely WyConnect, WyBatch ...
%Project - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
%Release - A collection of projects being put in production on a specified date

%The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.

%1. Identify the Work/Task/Project
%  1. Get Initial Idea
%  2. Obtain Details
%2. Estimate
%  1. Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
%  2. Obtain Approval 
%  3. Quit or Go Forward
%3. Write BRD
%  1. Identify the Requirements
%  2. Detail the Requirements
%4. Write FSD
%  1. Find System Integrations
%  2. Identify Functional Specs
%  3. Detail the Functional Specs
%5. Development of all the tasks in FSD
%  1. Identify the Coding Tasks
%  2. Write the Code/Develop the solution
%  3. Write the Unit Tests
%6. Test
%  1. Create Test Plans and Cases
%  2. Run Test Plans and Cases
%7. Deployment
%  1. Create Deployment Steps
%  2. Run Deployment Steps
%8. Maintenance
%  1. Capture Bugs
%  2. Survey Users
% end of notes

\end{document}

### 2014-11-23 paper_80_conclusion.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

% new section
\section{Conclusions}

There are many metrics that can be used to evaluate a Software Development Organization (SDO). 
Knowing which metrics to use and what they all mean can be a daunting task.  MPI is a
proposed solution to the difficulty of measuring an SDO.

Upon completion, this work shall identify:
\begin{itemize}
    \item Define \textbf{What} characteristics should be measured for an SDO
    \item Define \textbf{How} to measure those characteristics
    \item Map the relationship or lack of relationship with a Balanced Scorecard
    \item Create a Framework to store the necessary data for MPI
    \item Outline a Process to generate the MPI score
    \item Provide an example MPI score with real data
\end{itemize}

An entire software development organization (SDO) needs to be measured and analyzed properly, not just the development portion. This document has provided an overview of what indicators need to be measured for an SDO, and how those indicators can be combined to form a single number indicating the performance score of a software development organization.  Also, a framework to store this data was discussed.

\end{document}

### 2014-11-23 quotes.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

\newpage

% moves everything to the bottom of the page :-)
\vspace*{\fill}

\begin{flushleft}
\textit{``What you have here is small data.''}
\end{flushleft}

\begin{flushright}
Clay Campbell
\end{flushright}

\vspace{1in}

\begin{flushleft}
\textit{``Every day, three times per second, we produce the equivalent of the amount of data that the Library of Congress has in its entire print collection, right? But most of it is like cat videos on YouTube or 13-year-olds exchanging text messages about the next Twilight movie.''}
\end{flushleft}

\begin{flushright}
Nate Silver
\end{flushright}

\end{document}

### 2014-11-23 signature.tex
Initial ShareLaTeX Import

\documentclass[SDSUThesis.tex]{subfiles} 
\begin{document}

\begin{center}
\yourtitle
\vspace{0.5in}
\end{center}

\par This thesis is approved as a creditable and independent investigation by a candidate for the Master's of Science degree and is acceptable for meeting the thesis requirements for this degree.  Acceptance of this thesis does not imply that the conclusions reached by the candidate are necessarily the conclusions of the major department.

\vspace{1.5in}

\singlespacing

\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
\hspace*{230bp}\youradvisor\\
\hspace*{\fill}Thesis Advisor \hspace*{97bp}Date

\vspace{1in}

\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
\hspace*{230bp}\departmenthead\\
\hspace*{\fill}Head, Math and Statistics \hspace*{40bp}Date

\end{document}

### 2014-11-23 signature.tex
updates to signature page and bibliography
a few more updates to the signature page

@@
 
-\par This thesis is approved as a creditable and independent investigation by a candidate for the Master's of Science degree and is acceptable for meeting the thesis requirements for this degree.
-Acceptance of this thesis does not imply that the conclusions reached by the candidate are necessarily the conclusions of the major department.
+\par This dissertation is approved as a creditable and independent investigation by a 
+candidate for the Doctor of Philosophy degree and is acceptable for 
+meeting the dissertation requirements for this degree. Acceptance of this does not imply 
+that the conclusions reached by the candidates are necessarily the conclusions of the 
+major department.
 
@@
 \hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
-\hspace*{230bp}\youradvisor\\
-\hspace*{\fill}Thesis Advisor \hspace*{97bp}Date
+\hspace*{194bp}\youradvisor\\
+\hspace*{\fill}Dissertation Advisor \hspace*{47bp}Date
 
@@
 \hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
-\hspace*{230bp}\departmenthead\\
+\hspace*{194bp}\departmenthead\\
 \hspace*{\fill}Head, Math and Statistics \hspace*{40bp}Date
 
+\vspace{1in}
+
+\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
+\hspace*{194bp}Dean, Graduate School \hspace*{54bp}Date
 \end{document}

### 2014-11-25 paper_20_sdo.tex
moved images to their own directory
capitalize titles and rearrange  sections

@@
 
-\section{A Software Development Organization (SDO)}
+\section{A SOFTWARE DEVELOPMENT ORGANIZATION (SDO)}
 A \textit{Software Development Organization} is any organization or subset of an organization that is responsible
@@
 
-\subsection{What is Software?}
+\subsection{WHAT IS SOFTWARE?}
 Numerous definitions can be found for the term \textit{software}.
@@
 
-\subsection{The Software Development Lifecycle}
+\subsection{THE SOFTWARE DEVELOPMENT LIFECYCLE}
     For this question, I choose to rewrite that section of the proposal.  This was
@@
 
-    \subsubsection{Waterfall}
+    \subsubsection{WATERFALL}
         The waterfall model is the oldest and most influential of the SDLC models. 
@@
             \centering
-            \includegraphics[scale=.5]{benington_waterfall.PNG}
+            \includegraphics[scale=.5]{images/benington_waterfall.PNG}
             \caption[Benington's original diagram for producing large software systems]
@@
             \centering
-            \includegraphics[scale=.5]{royce_waterfall.PNG}
+            \includegraphics[scale=.5]{images/royce_waterfall.PNG}
             \caption[Royce's version of the waterfall model]
@@
             \centering
-            \includegraphics[scale=.6]{waterfall.png}
+            \includegraphics[scale=.6]{images/waterfall.png}
             \caption[Modern Waterfall]
@@
 
-    \subsubsection{Spiral}
+    \subsubsection{SPIRAL}
 
@@
             \centering
-            \includegraphics[scale=.5]{spiral_model.png}
+            \includegraphics[scale=.5]{images/spiral_model.png}
             \caption[Spiral SDLC Model]{Spiral SDLC Model \cite{Boehm2000} }
@@
 
-    \subsubsection{Agile}
+    \subsubsection{AGILE}
         Agile software development has arisen due to the inability
@@
 
-    \subsubsection{SDLC Commonalities}
+    \subsubsection{SDLC COMMONALITIES}
         Even with the large number of SDLC models currently being used by different SDOs,
@@
 
-\subsection{What is Software Engineering?}
+\subsection{WHAT IS SOFTWARE ENGINEERING?}
     \textit{Software Engineering} as a term dates back to the 
@@
 
-\subsection{Terminology}
+\subsection{TERMINOLOGY}
 

### 2014-11-25 paper_30_measure.tex
capitalize titles and rearrange  sections

@@
 % new section
-\section{Data Driven Software Engineering}
+\section{DATA DRIVEN SOFTWARE ENGINEERING}
 
@@
 
-\subsection{Result Indicators for Software Departments}
+\subsection{RESULT INDICATORS FOR SDOs}
     This section will cover the potential result indicators for an SDO.
 
-\subsection{Performance Indicators for Software Departments}
+\subsection{PERFORMANCE INDICATORS FOR SDOs}
     This section will cover the potential performance indicators for an SDO.
 
-\subsection{Balanced Scorecard}
+\subsection{BALANCED SCORECARD}
 
@@
 
-\subsection{Measuring Other Aspects of an SDO}
+\subsection{MEASURING OTHER ASPECTS OF AN SDO}
 
@@
 
-\subsection{Combining The Measures to Form MPI}
+\subsection{COMBINING THE MEASURES TO FORM MPI}
 

### 2014-11-25 paper_40_mpi.tex
capitalize titles and rearrange  sections

@@
 
-\section{MPI}
+\section{ELEMENTS OF MPI}
 
@@
 
-\subsection{Quality}
+\subsection{AVAILABILITY}
+All the new requirements and great quality do not matter if the software is not available.  
+The following algorithm will calculate the score of software availability.
+\begin{displaymath}
+   S_{3_i} = \left\{
+     \begin{array}{lr}
+       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
+       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
+     \end{array}
+   \right.
+\end{displaymath} 
+\[
+    S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
+\]
+
+\begin{itemize}
+\item $A_{a_i}$ actual availability for app i
+\item $A_{e_i}$ expected availability for app i
+\end{itemize}
+
+\begin{longtable}{@{}l rr rr}
+% pairs: absolute number (percentage)
+
+\toprule%
+ \centering%
+ {\bfseries Column Name}
+ & {\bfseries Data Type}
+ &  \\
+
+\cmidrule[0.4pt](r{0.125em}){1-1}%
+\cmidrule[0.4pt](lr{0.125em}){2-2}%
+\cmidrule[0.4pt](l{0.125em}){3-3}%
+% \midrule
+\endhead
+
+Application ID & String  & Required \\
+\myrowcolour%
+Frequency Date & Date & Required \\
+Uptime & Float & Optional \\
+\myrowcolour%
+Scheduled Downtime & Float & Optional \\
+Unscheduled Downtime & Float  & Optional \\
+\myrowcolour%
+Percent Uptime & Float & Required \\
+Expected Percent Uptime & Float & Required \\
+
+\bottomrule
+
+\caption{Availability - Inputs}
+\label{tab:avail}
+\end{longtable}
+
+\subsection{QUALITY}
 Quality is arguably the most important part of software development.  Poor quality means time, money, and resources are spent 
@@
 
-\subsection{Satisfaction}
+\subsection{SATISFACTION}
 The satisfaction of the customer is also very important.  The following is an algorithm to calculate the satisfaction of software.
@@
 \item $a_{i j}$ answer to question $j$ for app $i$
-\item $m$ number of questions
+\item $m$ number of questions with equal weights
 \item $n$ number of apps
@@
 
-\subsection{Availability}
-All the new requirements and great quality do not matter if the software is not available.  
-The following algorithm will calculate the score of software availability.
-\begin{displaymath}
-   S_{3_i} = \left\{
-     \begin{array}{lr}
-       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
-       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
-     \end{array}
-   \right.
-\end{displaymath} 
-\[
-    S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
-\]
-
-\begin{itemize}
-\item $A_{a_i}$ actual availability for app i
-\item $A_{e_i}$ expected availability for app i
-\end{itemize}
-
-\begin{longtable}{@{}l rr rr}
-% pairs: absolute number (percentage)
-
-\toprule%
- \centering%
- {\bfseries Column Name}
- & {\bfseries Data Type}
- &  \\
-
-\cmidrule[0.4pt](r{0.125em}){1-1}%
-\cmidrule[0.4pt](lr{0.125em}){2-2}%
-\cmidrule[0.4pt](l{0.125em}){3-3}%
-% \midrule
-\endhead
-
-Application ID & String  & Required \\
-\myrowcolour%
-Frequency Date & Date & Required \\
-Uptime & Float & Optional \\
-\myrowcolour%
-Scheduled Downtime & Float & Optional \\
-Unscheduled Downtime & Float  & Optional \\
-\myrowcolour%
-Percent Uptime & Float & Required \\
-Expected Percent Uptime & Float & Required \\
-
-\bottomrule
-
-\caption{Availability - Inputs}
-\label{tab:avail}
-\end{longtable}
-
-\subsection{On-Schedule}
+\subsection{SCHEDULE}
 Delivery of software in a timely manner is important.  Therefore, it is critical to know whether software was released early, late, or on-time.  
@@
 Frequency Date & Date & Required \\
+Scheduled Start Date & Date & Required \\
+\myrowcolour%
 Scheduled Finish Date & Date & Required \\
+Actual Start Date & Date  & Required \\
 \myrowcolour%
-Actual Start Date & Date  & Required \\
 Actual Finish Date & Date  & Required \\
@@
 
-\caption{On-Schedule - Inputs}
+\caption{Schedule - Inputs}
 \label{tab:sched}
@@
 
-\subsection{Requirements}
+\subsection{REQUIREMENTS}
 Requirements are desired new features or enhancements to a software product.  It is important to know how many requirements
@@
 
-\subsection{Final MPI Score}
+\subsection{FINAL MPI SCORE}
 One complete overall score cannot be successful without including information from various aspects of the software development organization.  Therefore, the previous results

### 2014-11-25 paper_50_sdlc-ae.tex
moved images to their own directory
capitalize titles and rearrange  sections

@@
 % All about the SDLC Analytic Engine
-\section{SDLC Analytic Engine}
+\section{SDLC ANALYTIC ENGINE}
 
@@
 \begin{figure}[ht]
-\includegraphics[scale=.7]{sdlc-ae.png}
+\includegraphics[scale=.7]{images/sdlc-ae.png}
 \caption{SDLC Analytic Engine}
@@
 
-\subsection{Database Structure}
+\subsection{DATABASE STRUCTURE}
    All the data necessary to compute MPI needs to be stored in a database.  This section will 
@@
 
-\subsection{Queries}
+\subsection{QUERIES}
     The section will provide the necessary SQL queries to obtain the correct data
@@
 
-\subsection{Computations}
+\subsection{COMPUTATIONS}
     This section will provide R scripts to calculate each individual score and the overall 

### 2014-11-25 paper_60_tooling.tex
capitalize titles and rearrange  sections

@@
 % new section
-\section{Tooling}
+\section{TOOLING}
 
-\subsection{SDLC Dashboard}
+\subsection{SDLC DASHBOARD}
 This maybe needs a name: Project MPI????  The goal of this project is to provide a tool that
@@
 This section will provide information to install and run a tool for calculating MPI for an organization.
-\subsubsection{Introduction}
-\subsubsection{Overview}
-\subsubsection{Installation}
-\subsubsection{Database}
+\subsubsection{INTRODUCTION}
+\subsubsection{OVERVIEW}
+\subsubsection{INSTALLATION}
+\subsubsection{DATABASE}
 maybe MongoDB, maybe PostgreSQL/MySQL
-\subsubsection{Webserver}
+\subsubsection{WEBSERVER}
 The software can either run standalone on cloud-hosted platform such as Heroku.  Try using Play Framework 2 with Authenticate.
 
-\subsection{SDLC-AE}
-
 \end{document}

### 2014-12-13 paper_20_sdo.tex
adding some new references

@@
     \textit{Software Engineering} as a term dates back to the 
-    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013}. Over the 
+    1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
     years many definitions have been provided.  IEEE provides a definition that encompasses many of the
@@
             both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.
+
+            ``
+                A software defect is a bug or error that causes
+                software to either stop operating or to produce
+                invalid or unacceptable results.
+            '' as quoted from
+            \cite{Jones2009}.  Also in here is the 4 severity levels.  Also, current defect removal is only about 85\% and this value should be increased to about 95\%. 
 \end{description}

### 2014-12-13 paper_40_mpi.tex
adding some new references

@@
 
-The exact algorithm here is yet to be determined.
+\section{Schedule Adherence}
+    \subsection{Overview}
+        Delivery of software in a timely manner is an essential part of being a 
+        successful SDO.  Being able to meet scheduled deadlines is a sign of accurate
+        estimation and planning.  Drastically missing deadlines is a sign of an SDO
+        with a process that needs refinement.  Studies have shown that 
+        software projects exceed the estimates by an average of
+        30\% \cite{Jorgensen2014}.  Thus it is important to score SDOs on accurate
+        schedule adherence. Without tracking and measuring schedule adherence, it will
+        not improve.
+
+        The score is based upon the historical deviance of estimates for
+        projects.  The top score of
+        100 will be obtained when the schedule is met exactly.  A historical average 
+        of deviance of schedule will be used to determine an appropriate range
+        of schedule adherence.  A schedule that occurs within that range will be awarded
+        a score of 0 or above, with less deviance being awarded more points.  Schedules
+        that do not fall within the range of deviance will be awarded negative scores, 
+        with a greater deviance resulting in a lower score all the way to -100 which means
+        the package took twice as long as expected or more.
+        For example, a package that takes more than twice as long to deliver than
+        estimated will receive a score of -100.
+
+    \newpage
+    \subsection{Formula}
+
+    The formula for schedule is based upon past performance.  Of the 422 projects
+    scheduled since June 2013, only 45 projects had an estimated start date, estimated
+    finish date and an actual finish date.  Of those 45 projects; 20 finished exactly on time,
+    9 finished early and 16 finished late.
+
+    The first step of the formula is finding the percentage the schedules were missed for 
+    historical projects.  The calculation treats over- and under-estimating the schedule
+    the same.  The same penalty is applied in both cases.  For example, being 15\% late
+    will result in the same score as being 15\% early. Perform this calculation
+    only for projects that did not exactly meet the estimated finish date.
+
+        \begin{displaymath}
+            \Delta_i = \left| \frac{F_{a_i} - F_{s_i}}{ F_{s_i} - B_{s_i} + 1} \right|
+        \end{displaymath}
+
+        Find the average of the $\Delta_i$'s.  This is the average percent of a missed
+        schedule.  
+        \begin{displaymath}
+           \bar{\Delta}  = \frac{\sum^n_{i=1}\Delta_i}{n}
+        \end{displaymath}
+
+        \textit{The formula for schedule is then a percentage above or below the $\Delta$.  
+        The number is calculated for each project, and then averaged to form the schedule score.}
+
+        After the $\bar{\Delta}$ is calculated, the following formulas are used to create the schedule scores
+        for each project and then the averaged schedule score.
+
+        \begin{displaymath}
+           S_{4_i} = \left\{
+             \begin{array}{lr}
+                \text{where } \Delta_i \geq 1 & : -1 \times 100 \\
+               \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \times 100  \\
+               \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \times 100
+             \end{array}
+           \right] \text{   , calculate schedule score for each project $i$}
+        \end{displaymath}
+
+        \[
+            S_{4} = \frac{\sum^n_{i=1} S_{4_i}}{n} \text{   , average the schedule scores}
+        \]
+        \begin{itemize}
+            \item $n$ is the number of projects
+            \item $F_{a_i}$ the actual finish date of project i
+            \item $F_{s_i}$ the scheduled finish date of project i
+            \item $B_{s_i}$ the scheduled beginning date of project i
+            \item $\Delta_i$ the percent the schedule was missed
+            \item $\bar{\Delta}$ is the average percent RT misses schedules, $\approx 26$
+            \item $S_{4_i}$ is the schedule score for project $i$
+        \end{itemize}
+
+    \subsection{Example Calculation}
+    \subsection{Data and Calculations}
+    \subsubsection{Obtain the Data}
+    \subsubsection{Run the Calculations}
+    \subsection{Past Performance}
+    \subsection{Process for the Future}
 

### 2014-12-16 paper_30_measure.tex
adding material that had been removed for the proposal

@@
 
-% new section
 \section{DATA DRIVEN SOFTWARE ENGINEERING}
@@
 
-%This info comes from \cite{parmenter2010}.
+This info comes from \cite{parmenter2010}.
 
-%\subsection{Possible data points for Level %of Effort}
+\subsection{Possible data points for Level of Effort}
 
-%\begin{description}
-%    \item[Actual Development Hours] Actual Hours Spent on development
-%    \item[Estimated Development Hours]  Initial Hours estimated for a project, this will commonly be different from the actual development hours
-%    \item[Source Lines Of Code (SLOC)]  This is count of the total number of lines of source code
-%    \item[Modified Lines Of Code] This is a count of the number of modified lines of source code. This number is a sum of the deleted, added, and modified lines of source code.
-%end{description}
+\begin{description}
+    \item[Actual Development Hours] Actual Hours Spent on development
+    \item[Estimated Development Hours]  Initial Hours estimated for a project, this will commonly be different from the actual development hours
+    \item[Source Lines Of Code (SLOC)]  This is count of the total number of lines of source code
+    \item[Modified Lines Of Code] This is a count of the number of modified lines of source code. This number is a sum of the deleted, added, and modified lines of source code.
+\end{description}
 

### 2014-12-16 paper_70_case-study.tex
capitalize titles and rearrange  sections
adding material that had been removed for the proposal

@@
 % new section
-\section{Case Study: Scoring an SDO of a Large Financial Institution}
+\section{CASE STUDY: SCORING AN SDO OF A LARGE FINANCIAL INSTITUTION}
 
@@
 
-%These are notes
+These are notes
 
-%Application(app) - a software system or a collection of other apps, for example: Wystar is an application but it is a collection of other apps namely WyConnect, WyBatch ...
-%Project - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
-%Release - A collection of projects being put in production on a specified date
+Application(app) - a software system or a collection of other apps, for example: Wystar is an application but it is a collection of other apps namely WyConnect, WyBatch ...
+Project - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
+Release - A collection of projects being put in production on a specified date
 
-%The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.
+The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.
 
-%1. Identify the Work/Task/Project
-%  1. Get Initial Idea
-%  2. Obtain Details
-%2. Estimate
-%  1. Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
-%  2. Obtain Approval 
-%  3. Quit or Go Forward
-%3. Write BRD
-%  1. Identify the Requirements
-%  2. Detail the Requirements
-%4. Write FSD
-%  1. Find System Integrations
-%  2. Identify Functional Specs
-%  3. Detail the Functional Specs
-%5. Development of all the tasks in FSD
-%  1. Identify the Coding Tasks
-%  2. Write the Code/Develop the solution
-%  3. Write the Unit Tests
-%6. Test
-%  1. Create Test Plans and Cases
-%  2. Run Test Plans and Cases
-%7. Deployment
-%  1. Create Deployment Steps
-%  2. Run Deployment Steps
-%8. Maintenance
-%  1. Capture Bugs
-%  2. Survey Users
-% end of notes
+1. Identify the Work/Task/Project
+  1. Get Initial Idea
+  2. Obtain Details
+2. Estimate
+  1. Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
+  2. Obtain Approval 
+  3. Quit or Go Forward
+3. Write BRD
+  1. Identify the Requirements
+  2. Detail the Requirements
+4. Write FSD
+  1. Find System Integrations
+  2. Identify Functional Specs
+  3. Detail the Functional Specs
+5. Development of all the tasks in FSD
+  1. Identify the Coding Tasks
+  2. Write the Code/Develop the solution
+  3. Write the Unit Tests
+6. Test
+  1. Create Test Plans and Cases
+  2. Run Test Plans and Cases
+7. Deployment
+  1. Create Deployment Steps
+  2. Run Deployment Steps
+8. Maintenance
+  1. Capture Bugs
+  2. Survey Users
+ end of notes
 

### 2014-12-19 paper_10_intro.tex
capitalize titles and rearrange  sections
adding some new references
fixed Schedule chapter problem starting to work on SEMAT section

@@
 % see this for  guidance https://www.cs.purdue.edu/homes/dec/essay.dissertation.html
-\section{Introduction}
+\section{INTRODUCTION}
 
@@
 
-\subsection{Background}
+\subsection{BACKGROUND}
 
@@
 
-\subsection{Previous Software Engineering Scoring Attempts}
+\subsection{PREVIOUS SOFTWARE SCORING ATTEMPTS }
 
@@
 
+Quality is tested in \cite{Miguel2014}
+
+See also \cite{Buse2010}.
+
+\subsubsection{SEMAT}
+
+SEMAT is being dubbed as the ``new software engineering'' \cite{Jacobson2014}.
+Three parts to the kernel:
+\begin{itemize}
+\item Measurement
+\item Categorization
+\item Competencies
+\end{itemize}
+
+The seven dimensions:
+\begin{itemize}
+\item Opportunity
+\item Stakeholders
+\item Requirements
+\item Software Systems
+\item Work
+\item Team
+\item Way of Working
+\end{itemize}
+
+\subsection{ORGANIZATION OF THE WORK}
+
+The remainder of this dissertation is divided into 5 chapters.  The next chapter provides
+an overview of software, software development lifecycles, software engineering, and software
+development organizations.  Chapter 3 introduces what is meant by the term data-driven
+software engineering. Chapter 4 then provides an explanation of the Master Performance 
+Indicator (MPI).  It will present the essential elements for calculating the MPI, as well
+as the formulas, frameworks, and data necessary to produce the MPI. Chapter 5 provides
+a technological framework for generating and storing the current and historical MPI values.
+Chapter 6 demostrates how MPI can be implemented in a software development portion of 
+a large financial institution.  Chapter 7 concludes the dissertation with a summary
+of the results and some possible future directions for further enhancements.
+
 \end{document}

### 2014-12-19 paper_40_mpi.tex
fixed Schedule chapter problem starting to work on SEMAT section

@@
 \subsection{SCHEDULE}
-Delivery of software in a timely manner is important.  Therefore, it is critical to know whether software was released early, late, or on-time.  
-The best possible score should be achieved
-            when meeting the estimated date exactly.  The maximum score
-            should come from the best estimate.  Then given historical
-            release data, it is easy to determine an 
-            average $\Delta$ between the actual and the estimated.  
-            Finishing a project within that $\Delta$ should result 
-            in a positive score.  Outside the $\Delta$ results in
-            negative scores.  For example, a project releasing
-            one day early or one day late would receive the same score
-            because in both cases the estimate was missed by one day.
 
-\section{Schedule Adherence}
-    \subsection{Overview}
+    \subsubsection{Overview}
         Delivery of software in a timely manner is an essential part of being a 
@@
 
-    \newpage
-    \subsection{Formula}
+    \subsubsection{Formula}
 
@@
 
-    \subsection{Example Calculation}
-    \subsection{Data and Calculations}
-    \subsubsection{Obtain the Data}
-    \subsubsection{Run the Calculations}
-    \subsection{Past Performance}
-    \subsection{Process for the Future}
+    \subsubsection{Example Calculation}
+    \subsubsection{Data and Calculations}
+    \subsubsection{Past Performance}
+    \subsubsection{Process for the Future}
+
+    \subsubsection{ALTERNATE APPROACH}
+    The best possible score should be achieved
+            when meeting the estimated date exactly.  The maximum score
+            should come from the best estimate.  Then given historical
+            release data, it is easy to determine an 
+            average $\Delta$ between the actual and the estimated.  
+            Finishing a project within that $\Delta$ should result 
+            in a positive score.  Outside the $\Delta$ results in
+            negative scores.  For example, a project releasing
+            one day early or one day late would receive the same score
+            because in both cases the estimate was missed by one day.
 

### 2014-12-22 paper_10_intro.tex
note for CMMI and cocomo
add CMMI and Cocomo II and SEMAT details

@@
 
+\subsection{CMMI}
+The Capability Maturity Model Integration (CMMI) is one of the most widely acknowledged models for process 
+improvement in software development.  CMMI offers a generic guideline and appraisal program for process 
+improvement.  It was created and is administered by the Software Engineering Institute at
+Carnegie Mellon University. While the CMMI is not specific to software development,
+it is often applied in software development settings.
+CMMI certification is required for many United States Government and Department of Defense contracts.
+
+CMMI-Dev is a modification of the CMMI specific to the development activities applied to products
+and services \cite{CMMI}.  The practices covered in CMMI-Dev include project management, 
+systems engineering, hardware engineering, process management, software engineering, and 
+other maintenance processes.  Five maturity levels are specified, and they include the 
+existence of a number of process areas.  The 5 maturity levels and the process areas are
+specified as follows.
+
+\subsubsection{CMMI MATURITY LEVEL 1 - INITIAL}
+    A maturity level 1 organization consists of a adhoc and chaotic processes.  While working
+    products are still produced, the results are often over budget and behind schedule.  A level
+    1 organization will also have difficulties repeating a process with the same degree of 
+    success.  These organizations typically rely on the heroic efforts of certain individuals.
+
+\subsubsection{CMMI MATURITY LEVEL 2 - MANAGED}
+    A maturity level 2 organization has a policy for planning and executing processes.  
+    The processes are controlled, monitored, reviewed, and enforced.  The practices are even
+    maintained in times of stress.  The following process areas should be present at maturity
+    level 2.
+    \begin{description}
+        \item Configuration Management (CM)
+        \item Measurement and Analysis (MA)
+        \item Project Monitoring and Control (PMC)
+        \item Project Planning (PP)
+        \item Process and Product Quality Assurance (PPQA)
+        \item Requirements Management (REQM)
+        \item Supplier Agreement Management (SAM)
+    \end{description}
+
+\subsubsection{CMMI MATURITY LEVEL 3 - DEFINED}
+    A maturity level 3 organization has well-understood processes that are described in 
+    standards, tools, procedures, and methods.  The organization has standard processes
+    that are reviewed and improved over time.  The major differentiators between level 2 
+    and level 3 is the existence of standards and process descriptions. 
+    A level 2 organization will have
+    processes that are inconsistent across projects.  A level 3 organization will tailor
+    a standard process for each project.  Also, level 3 processes are described with 
+    much more rigor.  In addition to the process areas found in level 2, 
+    the following process areas should be present at maturity level 3.
+    \begin{itemize}
+        \item Decision Analysis and Resolution (DAR)
+        \item Integrated Project Management (IPM)
+        \item Organizational Process Definition (OPD)
+        \item Organizational Process Focus (OPF)
+        \item Organizational Training (OT)
+        \item Product Integration (PI)
+        \item Requirements Development (RD)
+        \item Risk Management (RSKM)
+        \item Technical Solution (TS)
+        \item Validation (VAL)
+        \item Verification (VER)
+    \end{itemize}
+
+\subsubsection{CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED}
+    A maturity level 4 organization has quantitative measures for quality and process performance. 
+    The measures are based upon customer needs, end users, and process implementers.  The quality
+    and process performance are understood mathematically and managed throughout the life of a project.
+    Level 4 is characterized by the predictability of the process performance. In addition to
+    the process areas found in level 2 and 3, the following additional process areas should be present
+    at maturity level 4.
+    \begin{itemize}
+        \item Organizational Process Performance (OPP)
+        \item Quantitative Project Management (QPM)
+    \end{itemize}
+\subsubsection{CMMI MATURITY LEVEL 5 - OPTIMIZING} 
+    The final and pinnacle level of CMMI maturity is level 5.  A maturity level 5 organization
+    continually improves processes based upon quantitative measures.  The major distinction from 
+    level 4 is the constant focus on improving and managing organizational performance.  A maturity level
+    5 organization has well-documented standard processes that are tracked and enforced as well as
+    a focus on continual improvement of the processes based upon 
+    quantitative measures.  In addition to the process areas of the previous maturity levels, maturity
+    level 5 should contain the following process areas.
+    \begin{itemize}
+        \item Causal Analysis and Resolution (CAR)
+        \item Organizational Performance Management (OPM)
+    \end{itemize}
+
+        \begin{figure}[here]
+            \centering
+            \includegraphics[scale=.7]{images/cmmi.png}
+            \caption[Characteristics of CMMI]{Characteristics of CMMI, image adapted from  \cite{Godfrey} }
+            \label{fig:cmmi}
+        \end{figure}
+
+A visual description of the CMMI maturity levels can be seen in Figure \ref{fig:cmmi}.  
+While CMMI-Dev does provide an excellent framework for improving a process.  It
+is wholely focused on process improvement.  It does not provide guidelines
+for evaluating the final product.  
+Also, it does not provide a specify mechanism for evaluating
+or scoring the progression through the maturity levels.  
+An indicator is still needed to quantify the overall performance of an organization, not
+just the compliance to standard processes.
+
+\subsection{COCOMO}
+    Constructive Cost Model (COCOMO) is a software cost estimation model created
+    by Boehm \cite{Boehm1981}.  It combines future project characteristics
+    with historical project data to create a regression model to estimate the 
+    cost of a software project.  The original version developed in 1981 was
+    focused on mainframe and batch processing.  An unpdated version, named
+    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
+    development practices such as desktop development, off the shelf components,
+    and code reuse.  COCOMO provides a nice algorithm for making decisions
+    regarding building or buying software products.  It does not provide 
+    an algorithms to review past performance of estimates and modify the
+    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
+    but it only provides an estimate and not an evaluation of the actual
+    performance.
+
 \subsection{PREVIOUS SOFTWARE SCORING ATTEMPTS }
@@
 
+\subsubsection{SOFTWARE QUALITY}
 Quality is tested in \cite{Miguel2014}
 
+\subsubsection{SOFTWARE ANALYTICS}
 See also \cite{Buse2010}.
@@
 
-SEMAT is being dubbed as the ``new software engineering'' \cite{Jacobson2014}.
-Three parts to the kernel:
-\begin{itemize}
-\item Measurement
-\item Categorization
-\item Competencies
-\end{itemize}
-
-The seven dimensions:
-\begin{itemize}
+    Software Engineering Method and Theory (SEMAT) is claiming to be the ``new software engineering'' 
+    \cite{Jacobson2014}.  The authors rightfully claim that software engineering lacks
+    an underlying theoretical foundation found in other engineering disciplines.  This lack of theory
+    has led software engineering to not be engineering, but rather a craft.  The goal of 
+    SEMAT is to merge the craftsmanship and engineering to provide a foundation for software
+    engineering.  The primary initiative of SEMAT has been the creation of a kernel for 
+    software engineering.  The kernel is the minimal set of things common to all software development
+    endeavours. The three parts to the kernel are:
+    \begin{description}
+        \item[Measurement] - There must exist a means to determine the health and progress of an endeavour
+        \item[Categorization]-  The activities must progress through categories during an endeavour
+        \item[Competencies] - Specific competencies will be required for completing activities
+    \end{description}
+    The kernel defines alphas, which are seven dimensions with
+    specific states for measuring progress. 
+    The seven dimensions are: 
+    \begin{enumerate}
         \item Opportunity
@@
         \item Way of Working
-\end{itemize}
+    \end{enumerate}
+
+    Although SEMAT is very promising, the development is not yet complete.  Adoption is
+    limited so the technique has not been validated on many
+    actual software engineering endeavours.  Although SEMAT does include a part for
+    measurement of progress, it does not specify how the measurement is to be 
+    performed.
 

### 2014-12-24 paper_30_measure.tex
fixed Schedule chapter problem starting to work on SEMAT section
adding book how to measure anything
descriptions for indicators

@@
 
-\section{DATA DRIVEN SOFTWARE ENGINEERING}
+\section{DATA-DRIVEN SOFTWARE ENGINEERING}
+
+Anything can be measured \cite{Hubbard2010}.
+
+Data Driven Software Engineering not Data Driven Software Development
 
@@
 possible measures for each indicator in an SDO will be
-presented.  The 4 different types of indicators are.
-\begin{enumerate}
-  \item RI (Result Indicator)
-  \item KRI (Key Result Indicator)
-  \item PI (Performance Indicator)
-  \item KPI (Key Performance Indicator)
-\end{enumerate}
+presented.  The 4 different types of indicators are:
+\begin{description}
+  \item[RI (Result Indicator)] - what has been done
+  \item[KRI (Key Result Indicator)] - how you have done
+  \item[PI (Performance Indicator)] - what to do
+  \item[KPI (Key Performance Indicator)] - what to do to dramatically increase performance
+\end{description}
 

### 2014-12-27 paper_10_intro.tex
added software dev analytics
updates to intro

@@
 for the presence of various techniques used in software engineering.  The methodology provides a score based upon the 
-productivity and quality increase of the technique being evaluated.  A couple example techniques are: 
+productivity and quality increase of the technique being evaluated.  Points are positive or negative based upon the 
+presense of various techniques. A couple example techniques are: 
 automated source code analysis and continuous integration.  The end result is a score in range $[-10,10]$. 
-While the single number score is nice, it does not account for the entirety of the software development lifecycle.
+While the result is a single number score, it does not account for the entirety of the software development lifecycle.
 
@@
 \subsubsection{SOFTWARE ANALYTICS}
-See also \cite{Buse2010}.
+See also \cite{Buse2010}.  There is a subsection named
+software development analytics \cite{Menzies2012}.
 
@@
 
+    So it has been shown, there exist many attempts to 
+    evaluate portions of the a software development 
+    organization.  None of the the attempts provide
+    a single number score for the entirety of the 
+    organization.  Most of the techniques focus on
+    specific portions of the software development 
+    lifecycle, namely the development portion.
+
 \subsection{ORGANIZATION OF THE WORK}

### 2014-12-30 paper_10_intro.tex
software analytics
continuing work on lit review

@@
 
-\subsection{COCOMO}
-    Constructive Cost Model (COCOMO) is a software cost estimation model created
-    by Boehm \cite{Boehm1981}.  It combines future project characteristics
-    with historical project data to create a regression model to estimate the 
-    cost of a software project.  The original version developed in 1981 was
-    focused on mainframe and batch processing.  An unpdated version, named
-    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
-    development practices such as desktop development, off the shelf components,
-    and code reuse.  COCOMO provides a nice algorithm for making decisions
-    regarding building or buying software products.  It does not provide 
-    an algorithms to review past performance of estimates and modify the
-    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
-    but it only provides an estimate and not an evaluation of the actual
-    performance.
-
-\subsection{PREVIOUS SOFTWARE SCORING ATTEMPTS }
+\subsection{PREVIOUS SOFTWARE EVALUATION ATTEMPTS }
 
@@
 \subsubsection{SOFTWARE ANALYTICS}
-See also \cite{Buse2010}.  There is a subsection named
-software development analytics \cite{Menzies2012}.
+What is software analytics?
+See also \cite{Buse2010}.
+
+\textit{Software Development Analytics} is a subfield of software analytics 
+\cite{Menzies2012}.  It focuses on the analytics of the development of software, not
+the overall performance of the software.
+
+\cite{Marcus2010}
+
+\subsubsection{COCOMO}  
+    Constructive Cost Model (COCOMO) is a software cost estimation model created
+    by Boehm \cite{Boehm1981}.  It combines future project characteristics
+    with historical project data to create a regression model to estimate the 
+    cost of a software project.  The original version developed in 1981 was
+    focused on mainframe and batch processing.  An unpdated version, named
+    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
+    development practices such as desktop development, off the shelf components,
+    and code reuse.  COCOMO provides a nice algorithm for making decisions
+    regarding building or buying software products.  It does not provide 
+    an algorithms to review past performance of estimates and modify the
+    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
+    but it only provides an estimate and not an evaluation of the actual
+    performance.
 

### 2014-12-30 paper_20_sdo.tex
adding material that had been removed for the proposal
fixed Schedule chapter problem starting to work on SEMAT section
continuing work on lit review

@@
         quickly changing applications such as web-based applications.
+        Startups have largely adopted the Lean methodology for its
+        ability to identify a minimum viable product\footnote{
+        A \textit{minimum viable product} is a reduced version of software
+        that contains only the bare minimum functionality required to meet
+        the requirements.}
+        and reduce the time to market \cite{Giardino2014}.
 
@@
 
-%\subsection{Data-Driven Software Engineering}
-%Data Driven Software Engineering not Data Driven Software Development
-
-%Check these book \cite{Jones2009, Jones1996, Lee2003}. This might be similar
-%to process mining \cite{vanderAalst2012}.
+Check these book \cite{Jones2009, Jones1996, Lee2003}. This might be similar
+to process mining \cite{vanderAalst2012}.
 

### 2014-12-31 paper_10_intro.tex
adding more papers

@@
 What is software analytics?
-See also \cite{Buse2010}.
+
+Some of the measurements focus specifically on the source code; analyzing the 
+complexity, size, and coupling \cite{Tosi2012}.
+
+Letier and Fitzgerald discuss how to choose the correct tools and techniques to analyze
+software data \cite{Letier2013}.  A goal model is produced that matches the data analysis methods
+with the goals of the software stakeholders.  Again, the method does not focus
+on analysis of development of software.
 
@@
 the overall performance of the software.
+
+See also \cite{Buse2010}.
 

### 2014-12-31 paper_30_measure.tex
adding some capitol letters to the section headers
adding more papers

@@
 in chapter 1 of \cite{parmenter2010}
-as well as \cite{florac1999,kaplan1992,letier2013}.
+as well as \cite{florac1999,kaplan1992}.
 
@@
 
-\subsection{Possible data points for Level of Effort}
+\subsection{POSSIBLE DATA POINTS FOR LEVEL OF EFFORT}
 

### 2014-12-31 paper_10_intro.tex
added PROMISE Data repo

@@
 
+Software development produces many value pieces of datum that can be analyzed
+\cite{Marcus2010}. Just a few of the pieces of datum are:
+email communication, bugs, fixes, source code, version control system histories,
+process information, and test data.  Examples of this type of data
+can be found in the PROMISE Data Repository \cite{promise12}.
+
 See also \cite{Buse2010}.
-
-\cite{Marcus2010}
 

### 2014-12-31 paper_10_intro.tex
adding some more papers

@@
 \subsubsection{SOFTWARE QUALITY}
-Quality is tested in \cite{Miguel2014}
+Quality is tested in \cite{Miguel2014} and a stack of other papers
 
 \subsubsection{SOFTWARE ANALYTICS}
-What is software analytics?
+One area of research that is focusing on the evaluation of software development organizations
+is \textit{software analytics}.  It is less focused o evaluation
+and more so on analysis of software data.  The goal of software analytics is to extract insights
+from software artifacts to aide practioners in making better decisions regarding software
+development \cite{Zhang2013}.  The main focus areas of software analytics are:
+\begin{description}
+    \item[User Experience] - How can the software enable the user to more easily or quickly 
+        accomplish the task at hand?
+    \item[Quality] - How can the number of problems with the software be decreased?
+    \item[Development Productivity] - How can the processes or tools be modified to increase 
+        the rate at which software is produced? 
+\end{description}
+
+Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
+analytics must address:
+\begin{enumerate}
+    \item ``How much better is my model performing than a naive strategy, such as guessing [\ldots]?''
+    \item ``How practically significant are the results?''
+    \item ``How sensitive are the results to small changes in one or more of the inputs?''
+\end{enumerate}
+These are 3 important questions that should be addressed when presenting any results in
+software analytics.
 

### 2014-12-31 paper_20_sdo.tex
adding some more papers

@@
     years many definitions have been provided.  IEEE provides a definition that encompasses many of the
-    other definitions.  IEEE defines software engineering as, 
+    other definitions.  IEEE ISO610.12 defines software engineering as, 
     ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''

### 2015-01-01 paper_10_intro.tex
adding some data mining for software engineering data
updating some history of software analytics

@@
 \subsubsection{SOFTWARE ANALYTICS}
+The application of data mining techniques to software engineering can be traced back to the
+late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.
+
 One area of research that is focusing on the evaluation of software development organizations
-is \textit{software analytics}.  It is less focused o evaluation
-and more so on analysis of software data.  The goal of software analytics is to extract insights
+is \textit{software analytics}.  It is less focused on evaluation
+and more so on all sorts of analysis of software data.  Early forms of 
+software analytics were methods of data mining applied to software engineering data
+\cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. The term software intelligence was 
+used \cite{Hassan2010}, but
+the term software analytics has become the common term for referring to the topic \cite{Zhang2011}.
+The goal of software analytics is to extract insights
 from software artifacts to aide practioners in making better decisions regarding software
@@
 
-See also \cite{Buse2010}.
+See also \cite{Buse2010} and then \cite{Buse2012} begins to discuss the 
+information that is needed to properly perform software development analytics.
 

### 2015-01-02 paper_10_intro.tex
lots more references added

@@
 from software artifacts to aide practioners in making better decisions regarding software
-development \cite{Zhang2013}.  The main focus areas of software analytics are:
+development \cite{Zhang2013}.  The three main focus areas of software analytics are:
 \begin{description}
@@
 information that is needed to properly perform software development analytics.
+
+%%%%%% a brief outline
+the use can be traced back to late 1990s, then techniques of data mining were applied to 
+software engineering data
+
+Then it became known as software analytics
+desc software analytics
+
+then describe software dev analytics
+
+then describe how all this analysis requires data, so determining the correct data is important \cite{Buse2012}
+In order to store the data, tools are needed \cite{Czerwonka2013,Zhang2013} not east to create the right tools \cite{Spraragen2005}
+
+then discuss how gamification is an obvious next step \cite{Dubois2013, Jain2013}
+
+the discuss software quality \cite{Jones2013,Boehm2001,Faizan2012,Miguel2014}
 

### 2015-01-02 paper_10_intro.tex
reorganize the introduction

@@
 
-Software is becoming a vital part of companies. In 2011 Marc Andreessen, co-founder of the venture capital firm Andreessen-Horowitz,
-famously claimed, ``Software is Eating The World'' \cite{Andreessen2001}. His argument was for the ever increasing importance of software
-in all organizations big and small regardless of the industry.  With this important declaration, the production of new software is
-going to be critical.  Just as important will be the effective measurement of how this software is produced.
+    Software is becoming a vital part of companies. In 2011 Marc Andreessen, 
+    co-founder of the venture capital firm Andreessen-Horowitz,
+    famously claimed, ``Software is Eating The World'' \cite{Andreessen2001}. 
+    His argument was for the ever increasing importance of software
+    in all organizations big and small regardless of the industry.  With 
+    this important declaration, the production of new software is
+    going to be critical.  Just as important will be the effective 
+    measurement of how this software is produced.
 
-The goal of this work is to provide a basis of what data should be collected by a software development organization, and how that data
-should be used to formulate a single number representing the software development score of an organization. A framework to 
+    The goal of this work is to provide a basis of what data should 
+    be collected by a software development organization, and how that data
+    should be used to formulate a single number representing the 
+    software development score of an organization. A framework to 
     achieve the score will be presented.  The  score
-is not to be comparative between organizations, but to rather form a historical baseline for a specific organization.  Also, a software
+    is not to be comparative between organizations, but to 
+    rather form a historical baseline for a specific organization.  Also, a software
     system to collect, calculate, and report the score will be presented.
@@
 
-Throughout the history of software development, many values have been collected and used to measure the effectiveness of software development. 
-Many metrics have been used in the past and are still being used.  A metric can be defined as the science of indirect measurement.
-The following are some examples of metrics that can be collected about source code:
+    Throughout the history of software development, many values have been 
+    collected and used to measure the effectiveness of software development. 
+    Many metrics have been used in the past and are still being used.  
+    A metric can be defined as the science of indirect measurement.
+    The following are some examples of metrics that can be collected 
+    about source code:
     \begin{itemize}
@@
         \item NOM - The Number of Methods per class
-\item Complexity - A numerical measure of the code complexity, some common examples are McCabe \cite{McCabe1976} and Halstead \cite{Halstead1977}
-\item Design - The amount of coupling and cohesion present in the software code
-\item Source Code Analysis - Tools that determine whether code adheres to specified set of rules. Common examples are PMD and findbugs.
+        \item Complexity - A numerical measure of the code complexity,
+            some common examples are McCabe \cite{McCabe1976} and 
+            Halstead \cite{Halstead1977}
+        \item Design - The amount of coupling and cohesion present 
+        in the software code
+        \item Source Code Analysis - Tools that determine whether 
+        code adheres to specified set of rules. Common 
+        examples are PMD and findbugs.
     \end{itemize}
 
-However, the metrics on source code only explain part of the software development lifecycle.  
-Most of the effort has been placed on measuring just the computer code and not the entire organization.  Software
+    However, the metrics on source code only explain part of the 
+    software development lifecycle.  
+    Most of the effort has been placed on measuring just the 
+    computer code and not the entire organization.  Software
     development involves more than just source code.
 
-\subsection{CMMI}
-The Capability Maturity Model Integration (CMMI) is one of the most widely acknowledged models for process 
-improvement in software development.  CMMI offers a generic guideline and appraisal program for process 
+\subsection{OVERVIEW}
+
+    What is the goal? how will it help?  Expand on the thesis statement here
+    score the overall organization
+    produce a single a number score
+    don't focus too heavily on the source code
+
+\subsection{PREVIOUS SOFTWARE EVALUATION METHODS}
+
+While much work has been done in t
+
+\subsubsection{CMMI}
+    The Capability Maturity Model Integration (CMMI) is one of the most 
+    widely acknowledged models for process 
+    improvement in software development.  CMMI offers a generic guideline 
+    and appraisal program for process 
     improvement.  It was created and is administered by the Software Engineering Institute at
@@
     it is often applied in software development settings.
-CMMI certification is required for many United States Government and Department of Defense contracts.
+    CMMI certification is required for many United States Government 
+    and Department of Defense contracts.
 
@@
 
-\subsubsection{CMMI MATURITY LEVEL 1 - INITIAL}
+    \begin{description}
+        \item[CMMI MATURITY LEVEL 1 - INITIAL]
             A maturity level 1 organization consists of a adhoc and chaotic processes.  While working
@@
 
-\subsubsection{CMMI MATURITY LEVEL 2 - MANAGED}
+        \item[CMMI MATURITY LEVEL 2 - MANAGED]
             A maturity level 2 organization has a policy for planning and executing processes.  
@@
             level 2.
-    \begin{description}
+            \begin{itemize}
                 \item Configuration Management (CM)
@@
                 \item Supplier Agreement Management (SAM)
-    \end{description}
+            \end{itemize}
 
-\subsubsection{CMMI MATURITY LEVEL 3 - DEFINED}
+        \item[CMMI MATURITY LEVEL 3 - DEFINED]
             A maturity level 3 organization has well-understood processes that are described in 
@@
 
-\subsubsection{CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED}
+        \item[CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED]
             A maturity level 4 organization has quantitative measures for quality and process performance. 
-    The measures are based upon customer needs, end users, and process implementers.  The quality
-    and process performance are understood mathematically and managed throughout the life of a project.
-    Level 4 is characterized by the predictability of the process performance. In addition to
-    the process areas found in level 2 and 3, the following additional process areas should be present
+            The measures are based upon customer needs, end users, and process implementers.  
+            The quality
+            and process performance are understood mathematically and managed 
+            throughout the life of a project.
+            Level 4 is characterized by the predictability of the process performance. 
+            In addition to
+            the process areas found in level 2 and 3, the following additional 
+            process areas should be present
             at maturity level 4.
@@
             \end{itemize}
-\subsubsection{CMMI MATURITY LEVEL 5 - OPTIMIZING} 
-    The final and pinnacle level of CMMI maturity is level 5.  A maturity level 5 organization
-    continually improves processes based upon quantitative measures.  The major distinction from 
-    level 4 is the constant focus on improving and managing organizational performance.  A maturity level
-    5 organization has well-documented standard processes that are tracked and enforced as well as
+
+        \item[CMMI MATURITY LEVEL 5 - OPTIMIZING]
+            The final and pinnacle level of CMMI maturity is level 5.  
+            A maturity level 5 organization
+            continually improves processes based upon quantitative measures.  
+            The major distinction from 
+            level 4 is the constant focus on improving and managing 
+            organizational performance.  A maturity level
+            5 organization has well-documented standard processes that are 
+            tracked and enforced as well as
             a focus on continual improvement of the processes based upon 
-    quantitative measures.  In addition to the process areas of the previous maturity levels, maturity
+            quantitative measures.  In addition to the process areas of the 
+            previous maturity levels, maturity
             level 5 should contain the following process areas.
@@
             \end{itemize}
+    \end{description}
 
@@
 
-\subsection{PREVIOUS SOFTWARE EVALUATION ATTEMPTS }
+\subsubsection{COCOMO}  
+    Constructive Cost Model (COCOMO) is a software cost estimation model created
+    by Boehm \cite{Boehm1981}.  It combines future project characteristics
+    with historical project data to create a regression model to estimate the 
+    cost of a software project.  The original version developed in 1981 was
+    focused on mainframe and batch processing.  An unpdated version, named
+    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
+    development practices such as desktop development, off the shelf components,
+    and code reuse.  COCOMO provides a nice algorithm for making decisions
+    regarding building or buying software products.  It does not provide 
+    an algorithms to review past performance of estimates and modify the
+    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
+    but it only provides an estimate and not an evaluation of the actual
+    performance.
+
+\subsubsection{SEMAT}
+
+    Software Engineering Method and Theory (SEMAT) is claiming to be the ``new software engineering'' 
+    \cite{Jacobson2014}.  The authors rightfully claim that software engineering lacks
+    an underlying theoretical foundation found in other engineering disciplines.  This lack of theory
+    has led software engineering to not be engineering, but rather a craft.  The goal of 
+    SEMAT is to merge the craftsmanship and engineering to provide a foundation for software
+    engineering.  The primary initiative of SEMAT has been the creation of a kernel for 
+    software engineering.  The kernel is the minimal set of things common to all software development
+    endeavours. The three parts to the kernel are:
+    \begin{description}
+        \item[Measurement] - There must exist a means to determine the health and progress of an endeavour
+        \item[Categorization]-  The activities must progress through categories during an endeavour
+        \item[Competencies] - Specific competencies will be required for completing activities
+    \end{description}
+    The kernel defines alphas, which are seven dimensions with
+    specific states for measuring progress. 
+    The seven dimensions are: 
+    \begin{enumerate}
+        \item Opportunity
+        \item Stakeholders
+        \item Requirements
+        \item Software Systems
+        \item Work
+        \item Team
+        \item Way of Working
+    \end{enumerate}
+
+    Although SEMAT is very promising, the development is not yet complete.  Adoption is
+    limited so the technique has not been validated on many
+    actual software engineering endeavours.  Although SEMAT does include a part for
+    measurement of progress, it does not specify how the measurement is to be 
+    performed.
 
@@
 
-\subsubsection{COCOMO}  
-    Constructive Cost Model (COCOMO) is a software cost estimation model created
-    by Boehm \cite{Boehm1981}.  It combines future project characteristics
-    with historical project data to create a regression model to estimate the 
-    cost of a software project.  The original version developed in 1981 was
-    focused on mainframe and batch processing.  An unpdated version, named
-    COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
-    development practices such as desktop development, off the shelf components,
-    and code reuse.  COCOMO provides a nice algorithm for making decisions
-    regarding building or buying software products.  It does not provide 
-    an algorithms to review past performance of estimates and modify the
-    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
-    but it only provides an estimate and not an evaluation of the actual
-    performance.
-
-\subsubsection{SEMAT}
-
-    Software Engineering Method and Theory (SEMAT) is claiming to be the ``new software engineering'' 
-    \cite{Jacobson2014}.  The authors rightfully claim that software engineering lacks
-    an underlying theoretical foundation found in other engineering disciplines.  This lack of theory
-    has led software engineering to not be engineering, but rather a craft.  The goal of 
-    SEMAT is to merge the craftsmanship and engineering to provide a foundation for software
-    engineering.  The primary initiative of SEMAT has been the creation of a kernel for 
-    software engineering.  The kernel is the minimal set of things common to all software development
-    endeavours. The three parts to the kernel are:
-    \begin{description}
-        \item[Measurement] - There must exist a means to determine the health and progress of an endeavour
-        \item[Categorization]-  The activities must progress through categories during an endeavour
-        \item[Competencies] - Specific competencies will be required for completing activities
-    \end{description}
-    The kernel defines alphas, which are seven dimensions with
-    specific states for measuring progress. 
-    The seven dimensions are: 
-    \begin{enumerate}
-        \item Opportunity
-        \item Stakeholders
-        \item Requirements
-        \item Software Systems
-        \item Work
-        \item Team
-        \item Way of Working
-    \end{enumerate}
-
-    Although SEMAT is very promising, the development is not yet complete.  Adoption is
-    limited so the technique has not been validated on many
-    actual software engineering endeavours.  Although SEMAT does include a part for
-    measurement of progress, it does not specify how the measurement is to be 
-    performed.
-
     So it has been shown, there exist many attempts to 

### 2015-01-03 paper_10_intro.tex
most of the lit review is complete

@@
     collected and used to measure the effectiveness of software development.
-    Many metrics have been used in the past and are still being used.  
-    A metric can be defined as the science of indirect measurement.
-    The following are some examples of metrics that can be collected 
-    about source code:
-    \begin{itemize}
-        \item SLOC - The number of Source Lines of Code 
-        \item NOM - The Number of Methods per class
-        \item Complexity - A numerical measure of the code complexity,
-            some common examples are McCabe \cite{McCabe1976} and 
-            Halstead \cite{Halstead1977}
-        \item Design - The amount of coupling and cohesion present 
-        in the software code
-        \item Source Code Analysis - Tools that determine whether 
-        code adheres to specified set of rules. Common 
-        examples are PMD and findbugs.
-    \end{itemize}
-
-    However, the metrics on source code only explain part of the 
-    software development lifecycle.  
-    Most of the effort has been placed on measuring just the 
-    computer code and not the entire organization.  Software
-    development involves more than just source code.
 
@@
 
-\subsection{PREVIOUS SOFTWARE EVALUATION METHODS}
-
-While much work has been done in t
-
-\subsubsection{CMMI}
+\subsection{CMMI}
     The Capability Maturity Model Integration (CMMI) is one of the most 
@@
     and appraisal program for process 
-    improvement.  It was created and is administered by the Software Engineering Institute at
+    improvement.  It was created and is administered by the 
+    Software Engineering Institute at
     Carnegie Mellon University. While the CMMI is not specific to software development,
@@
 
-    CMMI-Dev is a modification of the CMMI specific to the development activities applied to products
-    and services \cite{CMMI}.  The practices covered in CMMI-Dev include project management, 
-    systems engineering, hardware engineering, process management, software engineering, and 
-    other maintenance processes.  Five maturity levels are specified, and they include the 
-    existence of a number of process areas.  The 5 maturity levels and the process areas are
-    specified as follows.
+    CMMI-Dev is a modification of the CMMI specific to the 
+    development activities applied to products
+    and services \cite{CMMI}.  The practices covered in 
+    CMMI-Dev include project management, 
+    systems engineering, hardware engineering, process 
+    management, software engineering, and 
+    other maintenance processes.  Five maturity levels are 
+    specified, and they include the 
+    existence of a number of process areas.  The 5 maturity 
+    levels and the process areas are specified as follows.
 
@@
         \item[CMMI MATURITY LEVEL 1 - INITIAL]
-            A maturity level 1 organization consists of a adhoc and chaotic processes.  While working
-            products are still produced, the results are often over budget and behind schedule.  A level
-            1 organization will also have difficulties repeating a process with the same degree of 
-            success.  These organizations typically rely on the heroic efforts of certain individuals.
+            A maturity level 1 organization consists of an
+                adhoc and chaotic processes.  While working
+                products are still produced, the results are 
+                often over budget and behind schedule.  A level
+                1 organization will also have difficulties 
+                repeating a process with the same degree of 
+                success.  These organizations typically rely 
+                on the heroic efforts of certain individuals.
 
         \item[CMMI MATURITY LEVEL 2 - MANAGED]
-            A maturity level 2 organization has a policy for planning and executing processes.  
-            The processes are controlled, monitored, reviewed, and enforced.  The practices are even
-            maintained in times of stress.  The following process areas should be present at maturity
+            A maturity level 2 organization has a policy for 
+            planning and executing processes.  
+            The processes are controlled, monitored, 
+            reviewed, and enforced.  The practices are even
+            maintained in times of stress.  The following 
+            process areas should be present at maturity
             level 2.
@@
         \item[CMMI MATURITY LEVEL 3 - DEFINED]
-            A maturity level 3 organization has well-understood processes that are described in 
-            standards, tools, procedures, and methods.  The organization has standard processes
-            that are reviewed and improved over time.  The major differentiators between level 2 
+            A maturity level 3 organization has well-understood 
+            processes that are described in 
+            standards, tools, procedures, and methods.  The 
+            organization has standard processes
+            that are reviewed and improved over time.  The 
+            major differentiators between level 2 
             and level 3 is the existence of standards and process descriptions. 
             A level 2 organization will have
-            processes that are inconsistent across projects.  A level 3 organization will tailor
-            a standard process for each project.  Also, level 3 processes are described with 
+            processes that are inconsistent across projects.  
+            A level 3 organization will tailor
+            a standard process for each project.  Also, 
+            level 3 processes are described with 
             much more rigor.  In addition to the process areas found in level 2, 
@@
         \item[CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED]
-            A maturity level 4 organization has quantitative measures for quality and process performance. 
-            The measures are based upon customer needs, end users, and process implementers.  
+            A maturity level 4 organization has quantitative 
+            measures for quality and process performance. 
+            The measures are based upon customer needs, 
+            end users, and process implementers.  
             The quality
@@
 
-    \begin{figure}[here]
+    \begin{figure}[ht]
         \centering
         \includegraphics[scale=.7]{images/cmmi.png}
-        \caption[Characteristics of CMMI]{Characteristics of CMMI, image adapted from  \cite{Godfrey} }
+        \caption[Characteristics of CMMI]{Characteristics of CMMI, 
+            image adapted from  \cite{Godfrey} }
         \label{fig:cmmi}
@@
     or scoring the progression through the maturity levels.  
-    An indicator is still needed to quantify the overall performance of an organization, not
+    An indicator is still needed to quantify the overall 
+    performance of an organization, not
     just the compliance to standard processes.
 
-\subsubsection{COCOMO}  
+\subsection{PREVIOUS SOFTWARE EVALUATION WORK}
+
+    An example of scoring software development is presented by 
+    Jones \cite{Jones2012}. The methodology looks
+    for the presence of various techniques used in software engineering.  
+    The methodology provides a score based upon the 
+    productivity and quality increase of the technique being evaluated.  
+    Points are positive or negative based upon the 
+    presense of various techniques. A couple example techniques are: 
+    automated source code analysis and continuous integration.  The end 
+    result is a score in range $[-10,10]$. 
+    While the result is a single number score, it does not account for the 
+    entirety of the software development lifecycle.
+
     Constructive Cost Model (COCOMO) is a software cost estimation model created
@@
     an algorithms to review past performance of estimates and modify the
-    algorithm accordingly.  COCOMO II can be a useful tool for an SDO,
+    algorithm accordingly.  COCOMO II can be a useful tool for 
+    estimating the time and costs within an SDO,
     but it only provides an estimate and not an evaluation of the actual
@@
 
+    Sextant is a visualization tool for Java source code \cite{Winter2013}.  
+    Sextant provides a graphical representation of the information related 
+    to a software system.  The tool provides the capability to provide 
+    custom rules which are specific to the domain or application.  However,
+    Sextant only provides metrics and analysis of the software code.  
+    It provides no information regarding the rest of the 
+    software development lifecycle.  Also, the primary output of Sextant 
+    is visual graphs.  While these graphs do provide
+    useful information, they do not provide a single number 
+    to determine the performance of the software.
+
+    Another promising research area is \textit{process mining}.
+    As stated by Wil van der Aalst \cite{vanderAalst2011}, 
+    ``The idea of process mining is to discover, monitor
+    and improve real
+    processes (i.e., not assumed processes) by extracting knowledge from event logs
+    readily available in today's systems.''  Creating software involves
+    a vast amount of processes.  Numerous logs of raw data are collected.  
+    One application of process mining in the area of software development
+    was an algorithm and information for measuring a software engineering process from
+    the Software Configuration Management (SCM) \cite{Rubin2007}.
+    The technique creates process models 
+    to understand the process of developing software and code. 
+    It is less focused on the output and results,
+    but it is more focused on adherence to a specified process.
+
+    Process mining has also been applied to decision making regarding software 
+    upgrades \cite{Genuchten2014}.  Historic and current logs can be 
+    processed and evaluated.
+    Then small pilot groups can be offered the upgrade, and the new logs will 
+    be processed and evaluated. Thus, process mining can be beneficial for new 
+    software implementation.  More research needs to be done applying
+    process mining to the other process involved with software development,
+    such as other documentation, testing, and implementation.
+
+    Although process mining can be useful for analyzing software
+    development data, it has not yet been applied to the entirety 
+    of a software development organization. It also does not
+    focus on the results of the organization.  It focuses
+    on process conformance, which can be very important, so it
+    is limited in the ability to evaluate the entire organization.
+
+    Much work has been done to determine metrics for source code, in fact 
+    entire books have been written on the topic of software 
+    metrics \cite{Jones1996, Putnam2013}. Yet, 
+    organizations still struggle to measure the production of software.
+    Little work exists
+    for scoring the entire software development organization.
+
 \subsubsection{SEMAT}
 
-    Software Engineering Method and Theory (SEMAT) is claiming to be the ``new software engineering'' 
-    \cite{Jacobson2014}.  The authors rightfully claim that software engineering lacks
-    an underlying theoretical foundation found in other engineering disciplines.  This lack of theory
-    has led software engineering to not be engineering, but rather a craft.  The goal of 
-    SEMAT is to merge the craftsmanship and engineering to provide a foundation for software
-    engineering.  The primary initiative of SEMAT has been the creation of a kernel for 
-    software engineering.  The kernel is the minimal set of things common to all software development
+    Software Engineering Method and Theory (SEMAT) is claiming to 
+    be the ``new software engineering'' 
+    \cite{Jacobson2014}.  The authors rightfully claim that 
+    software engineering lacks
+    an underlying theoretical foundation found in other 
+    engineering disciplines.  This lack of theory
+    has led software engineering to not be engineering, but 
+    rather a craft.  The goal of 
+    SEMAT is to merge the craftsmanship and engineering to 
+    provide a foundation for software
+    engineering.  The primary initiative of SEMAT 
+    has been the creation of a kernel for 
+    software engineering.  The kernel is the minimal set 
+    of things common to all software development
     endeavours. The three parts to the kernel are:
     \begin{description}
-        \item[Measurement] - There must exist a means to determine the health and progress of an endeavour
-        \item[Categorization]-  The activities must progress through categories during an endeavour
-        \item[Competencies] - Specific competencies will be required for completing activities
+        \item[Measurement] - There must exist a means to 
+            determine the health and progress of an endeavour
+        \item[Categorization]-  The activities must progress 
+            through categories during an endeavour
+        \item[Competencies] - Specific competencies will 
+            be required for completing activities
     \end{description}
+
     The kernel defines alphas, which are seven dimensions with
@@
 
-Sextant is a visualization tool for Java source code \cite{Winter2013}.  Sextant provides a graphical representation of the information related 
-to a software system.  The tool provides the capability to provide custom rules which are specific to the domain or application.  However,
-Sextant only provides metrics and analysis of the software code.  It provides no information regarding the rest of the 
-software development lifecycle.  Also, the primary output of Sextant is visual graphs.  While these graphs do provide
-useful information, they do not provide a single number to determine the performance of the software.
+\subsubsection{SOFTWARE QUALITY}
 
-\textit{Software process mining} \cite{Rubin2007} provides
-an algorithm and information for measuring a software engineering process from
-the Software Configuration Management (SCM). Software process mining does provide a method for tracking all 
-documentation that can be placed in SCM, not just source code.  The technique creates process models 
-to understand the process of developing software and code. It is less focused on the output and results,
-but it is more focused on conformance to a process or understanding the process. Once again, a single number is not produced.
+    Software quality is one of the most well studied aspects
+    of software development.  Most of the work focuses on
+    either the problems with the software or the source code.
+    Quality and the number of problems with the software
+    are inversely related, more problems means lower quality. 
+    Quality is easy to measure, but 
+    that measurement is usually very software specific.  It is easy
+    to find that some software has $X$ number of problems, but
+    it is nearly impossible to determine whether the quality
+    of that software is better or worse than some other software
+    with $X$ defects.  One piece of software can be 
+    larger\footnote{Saying a piece of software is larger can be a 
+    rather arbitrary statement.  Does that mean the software requires 
+    more computing time, has more lines of code, more documentation, 
+    more hours spent on development, or some other arbitrary measure.}
+    or more complex.  Thus, finding a value for quality is easier 
+    than interpreting that value.  Not matter the interpretation,
+    the goal is to release the number of problems with the software.
+    Top 10 lists have been created for techniques to remove problems
+    from software \cite{Boehm2001}.  
+    A number of different techniques or best practices
+    for preventing defects have 
+    been proposed \cite{Faizan2012}.  These are all strategies to identify
+    or remove the problems before the software is completed and released
+    to users.
 
-One example of scoring software development is presented by Jones \cite{Jones2012}. The methodology looks
-for the presence of various techniques used in software engineering.  The methodology provides a score based upon the 
-productivity and quality increase of the technique being evaluated.  Points are positive or negative based upon the 
-presense of various techniques. A couple example techniques are: 
-automated source code analysis and continuous integration.  The end result is a score in range $[-10,10]$. 
-While the result is a single number score, it does not account for the entirety of the software development lifecycle.
+    Another aspect of software quality is the complexity of the 
+    source code.  More complex code results in more maintenance efforts and
+    more chances for problems. A couple of numerical measures for the 
+    complexity of source code have been created.  The most common examples
+    are McCabe \cite{McCabe1976} and Halstead \cite{Halstead1977}.
+    However, the measures on source code only explain part of the 
+    software development lifecycle.
 
-Much work has been done to determine metrics for source code, in fact 
-entire books have been written on the topic of software metrics \cite{Jones1996, Putnam2013}. Yet, 
-organizations still struggle to measure the production of software.
-Little work exists
-for scoring the entire software development organization.
-
-\subsubsection{SOFTWARE QUALITY}
-Quality is tested in \cite{Miguel2014} and a stack of other papers
+    Another measurement of quality can be the cost per defect, also 
+    known as the cost to fix a problem.  As seen in \cite{Jones2013},
+    this measurement has problems because the lowest cost per
+    defect will occur on software with the most problems.  Therefore,
+    the lowest cost per defect is actually the lowest quality as well.
+    Due to this difficulty and others, a number of other models
+    have been created for evaluating the quality of software 
+    \cite{Miguel2014}.  While all of the models have merit
+    in certain situations, the measures of quality must be combined
+    with other measures in order to provide an overall evaluation
+    of a software development organization.
 
 \subsubsection{SOFTWARE ANALYTICS}
-The application of data mining techniques to software engineering can be traced back to the
+
+    One area of research that is focusing on the evaluation 
+    of software development organizations
+    is \textit{software analytics}. 
+    Software analytics is less focused on evaluation
+    and more so on all sorts of analysis of software data.
+    The earliest variants
+    of software analytics were disguised as
+    applications of data mining techniques to software 
+    engineering data in the 
     late 1990s \cite{Ruhe1997,Ebert1999,Goel1997}.   
+    Later the field began to emerge more heavily, but still
+    remained primarily methods of data mining applied to 
+    software engineering \cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. 
+    Finally, The term software intelligence was proposed for the field of study
+    \cite{Hassan2010}, but eventually
+    the term software analytics became the dominant term for referring to the 
+    field of study \cite{Buse10, Zhang2011}.
 
-One area of research that is focusing on the evaluation of software development organizations
-is \textit{software analytics}.  It is less focused on evaluation
-and more so on all sorts of analysis of software data.  Early forms of 
-software analytics were methods of data mining applied to software engineering data
-\cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. The term software intelligence was 
-used \cite{Hassan2010}, but
-the term software analytics has become the common term for referring to the topic \cite{Zhang2011}.
     The goal of software analytics is to extract insights
-from software artifacts to aide practioners in making better decisions regarding software
-development \cite{Zhang2013}.  The three main focus areas of software analytics are:
+    from software artifacts to aide practitioners in making 
+    better decisions regarding software
+    development \cite{Zhang2013}.  The three main focus areas of 
+    software analytics are:
     \begin{description}
-    \item[User Experience] - How can the software enable the user to more easily or quickly 
+        \item[User Experience] - How can the software enable the 
+            user to more easily or quickly 
             accomplish the task at hand?
-    \item[Quality] - How can the number of problems with the software be decreased?
-    \item[Development Productivity] - How can the processes or tools be modified to increase 
+        \item[Quality] - How can the number of problems with 
+            the software be decreased?
+        \item[Development Productivity] - How can the processes
+            or tools be modified to increase 
             the rate at which software is produced? 
     \end{description}
+    The work presented later in this paper will address all three
+    focus areas.
 
@@
     \begin{enumerate}
-    \item ``How much better is my model performing than a naive strategy, such as guessing [\ldots]?''
+        \item ``How much better is my model performing than 
+            a naive strategy, such as guessing [\ldots]?''
         \item ``How practically significant are the results?''
-    \item ``How sensitive are the results to small changes in one or more of the inputs?''
+        \item ``How sensitive are the results to small changes in 
+            one or more of the inputs?''
     \end{enumerate}
-These are 3 important questions that should be addressed when presenting any results in
-software analytics.
+    These are 3 important questions that should be addressed 
+    when presenting any results in software analytics.  The research
+    needs to demonstrate clear advantages for practitioners.
 
-Some of the measurements focus specifically on the source code; analyzing the 
+    One of the software analytic techniques focuses specifically 
+    on the source code; analyzing the 
     complexity, size, and coupling \cite{Tosi2012}. 
+    Letier and Fitzgerald discuss how to choose the 
+    correct tools and techniques to analyze
+    software data \cite{Letier2013}.  A goal model is 
+    produced that matches the data analysis methods
+    with the goals of the software stakeholders. The method does not focus
+    specifically on analysis of the development of software.
 
-Letier and Fitzgerald discuss how to choose the correct tools and techniques to analyze
-software data \cite{Letier2013}.  A goal model is produced that matches the data analysis methods
-with the goals of the software stakeholders.  Again, the method does not focus
-on analysis of development of software.
-
-\textit{Software Development Analytics} is a subfield of software analytics 
-\cite{Menzies2012}.  It focuses on the analytics of the development of software, not
-the overall performance of the software.
-
-Software development produces many value pieces of datum that can be analyzed
+    \textit{Software Development Analytics} is a subfield of 
+    software analytics \cite{Menzies2012}.  It focuses
+    specifically on the 
+    analytics of the development of software, however not
+    the overall performance of the software.  Hassan points out
+    in \cite{Hassan2013} that software analytics needs to go beyond
+    just the developers.  Everyone and everything involved in the 
+    development of software produces some data and that data can be meaningful.
+    The insights from non-developer data has the potential to yield important
+    results as well. 
+    Software development produces many valuable pieces of datum that can be analyzed
     \cite{Marcus2010}. Just a few of the pieces of datum are:
@@
 
-See also \cite{Buse2010} and then \cite{Buse2012} begins to discuss the 
-information that is needed to properly perform software development analytics.
+    All of these techniques are of no use if the correct data
+    is not available.  Therefore, it is important to 
+    identify the information that is needed to properly 
+    perform software development analytics.
+    Unfortunately, there are vast amounts of information that 
+    need to be collected to meet the analytic needs of 
+    developers and managers \cite{Buse2012}.  When the
+    data and tools exists, the analytics should help an
+    organization with the following tasks.
+    \begin{itemize}
+        \item Evaluate a project
+        \item Determine what is and is not working
+        \item Manage Risk
+        \item Anticipate changes
+        \item Evaluate prior decisions
+    \end{itemize}
 
-%%%%%% a brief outline
-the use can be traced back to late 1990s, then techniques of data mining were applied to 
-software engineering data
+    In order to store the data, appropriate tools are needed.  Microsoft
+    is working on developing some tools for the analysis of the development
+    of software \cite{Czerwonka2013,Zhang2013}.  Microsoft has developed
+    StackMine, a postmortem tool for performance debugging, and CODEMINE,
+    a tool for collecting and analyzing software development process data.
+    Both tools provide analytical insight for various aspects of the 
+    software development process, however neither tool covers all aspects
+    of software development.
+    These tools are currently early in development and the adoption of the
+    tools by practitioners is still unknown. One of the reasons for the slow
+    adoption of new tools is the inherent difficulty of producing
+    new tools for the software development process \cite{Spraragen2005}. A 
+    tool that works fantastic for one team might not automatically apply to 
+    another team.  The people creating the tools need to be acutely aware
+    of the needs of the technical practitioners that will be using the
+    tools.
 
-Then it became known as software analytics
-desc software analytics
-
-then describe software dev analytics
-
-then describe how all this analysis requires data, so determining the correct data is important \cite{Buse2012}
-In order to store the data, tools are needed \cite{Czerwonka2013,Zhang2013} not east to create the right tools \cite{Spraragen2005}
-
-then discuss how gamification is an obvious next step \cite{Dubois2013, Jain2013}
-
-the discuss software quality \cite{Jones2013,Boehm2001,Faizan2012,Miguel2014}
+    After the proper tools are in place to collect the necessary
+    data on software development and software analytics are being
+    properly implemented, an obvious next step is the
+    application of gamification to software development. Gamification
+    is ``the process of making activities more game-like'' \cite{Werbach2014}.
+    some of the benefits of gamification are higher productivity, competition,
+    and greater enjoyment.  
+    Prior attempts
+    at gamification of software development focus only on 
+    the computer programming phase \cite{Snipes2013}. Others
+    focus on defining a framework for gamification within
+    the software development process \cite{Jain2013}. There are 
+    even some indications that gamification might help increase
+    software quality \cite{Dubois2013}. 
+    While this work will not focus on gamification, it is important to note
+    that an implementation of an evaluation technique for software
+    development could be implemented simultaneously with a gamification
+    strategy. Both will require new collections of data and new reporting.
 
@@
     specific portions of the software development 
-    lifecycle, namely the development portion.
+    lifecycle, namely the development portion. Plus,
+    there are many tools that need to be created for
+    software analytics to provide all the value
+    that it promises.
 

### 2015-01-03 paper_30_measure.tex
most of the lit review is complete

@@
 Anything can be measured \cite{Hubbard2010}.
+
+A metric can be defined as the science of indirect measurement.
+    The following are some examples of metrics that can be collected 
+    about source code:
+    \begin{itemize}
+        \item SLOC - The number of Source Lines of Code 
+        \item NOM - The Number of Methods per class
+        \item Complexity - A numerical measure of the code complexity,
+            some common examples are McCabe \cite{McCabe1976} and 
+            Halstead \cite{Halstead1977}
+        \item Design - The amount of coupling and cohesion present 
+        in the software code
+        \item Source Code Analysis - Tools that determine whether 
+        code adheres to specified set of rules. Common 
+        examples are PMD and findbugs.
+    \end{itemize}
 

### 2015-01-06 paper_10_intro.tex
new version of PDF and some minor other changes
removed Background and Overview from section 1

@@
 
-\subsection{BACKGROUND}
+%\subsection{OVERVIEW}
 
-    Throughout the history of software development, many values have been 
-    collected and used to measure the effectiveness of software development.
+%    Throughout the history of software development, many values have been 
+%    collected and used to measure the effectiveness of software development.
 
-\subsection{OVERVIEW}
-
-    What is the goal? how will it help?  Expand on the thesis statement here
-    score the overall organization
-    produce a single a number score
-    don't focus too heavily on the source code
+%    What is the goal? how will it help?  Expand on the thesis statement here
+%    score the overall organization
+%    produce a single a number score
+%    don't focus too heavily on the source code
 
@@
     the term software analytics became the dominant term for referring to the 
-    field of study \cite{Buse10, Zhang2011}.
+    field of study \cite{Buse2010, Zhang2011}.
 

### 2015-01-09 paper_20_sdo.tex
new version of PDF and some minor other changes
remove some stuff

@@
 \subsection{THE SOFTWARE DEVELOPMENT LIFECYCLE}
-    For this question, I choose to rewrite that section of the proposal.  This was
-    my favorite question. It forced me to go look back into the history of
-    software development.
-
     The discipline of software engineering has created a workflow for developing
@@
 
-        \begin{figure}
+        \begin{figure}[ht]
             \centering
@@
         \end{figure}%
-        \begin{figure}
+        \begin{figure}[ht]
             \centering
@@
         A modern diagram of the waterfall model can be seen in Figure \ref{fig:waterfall}.
-        \begin{figure}[here]
+        \begin{figure}[ht]
             \centering
@@
 
-Check these book \cite{Jones2009, Jones1996, Lee2003}. This might be similar
-to process mining \cite{vanderAalst2012}.
+Check these book \cite{Jones2009, Jones1996, Lee2003}.
 

### 2015-01-14 paper_10_intro.tex
added overview to chapter 1 references for PMD and findbugs

@@
 
-    The goal of this work is to provide a basis of what data should 
-    be collected by a software development organization, and how that data
-    should be used to formulate a single number representing the 
-    software development score of an organization. A framework to 
-    achieve the score will be presented.  The  score
-    is not to be comparative between organizations, but to 
-    rather form a historical baseline for a specific organization.  Also, a software
-    system to collect, calculate, and report the score will be presented.
+    This work 
+    provides a technique for a software development organization to create
+    a single number score which indicates the overall performance
+    of the organization. The
+    score is based upon data collected for 5 result indicators
+    of a software development organization: quality, availability,
+    satisfaction, schedule, and requirements.  It is not meant
+    to be comparative between organizations, but to 
+    form a historical baseline for a specific organization.
 
-%\subsection{OVERVIEW}
+\subsection{OVERVIEW}
 
-%    Throughout the history of software development, many values have been 
-%    collected and used to measure the effectiveness of software development.
+    Software development organizations are no different than 
+    any other business or organization.  There are: tasks
+    to be completed, goals to achieve (or miss), and measurements
+    to be analyzed.  One difficulty with software development
+    is the varied number and amount of measurements to be used. 
+    It can be difficult to determine the correct activities
+    to measure and the appropriate mechanism to report the measure.
+    This has led organizations to either collect too little information
+    or to collect too much information.  Another problem is the 
+    inconsistency of the reported measures.  It is difficult to compare
+    historical performance if the same measurements are not consistent
+    throughout the recent history of an organization.
 
-%    What is the goal? how will it help?  Expand on the thesis statement here
-%    score the overall organization
-%    produce a single a number score
-%    don't focus too heavily on the source code
+    Software development organizations need a framework to define
+    what measurements should be tracked and how those measurements
+    should be reported.  The MPI framework provides a solid foundation
+    for a consistent evaluation.  It should also provide a broad
+    view of the overall organization.  It is common for software development
+    organizations to measure and focus soley on the source code
+    being produced.  However, a software development organization does more
+    than just produce source code.  There is documentation to be
+    written, testcases to be created, systems to be deployed, and
+    decisions to be made.  The framework provides an evaluation
+    of the overall software development organization.
+
+    The framework will produce a single number score for each of 
+    the five result indicators as well as a single overall score.  
+    It will be able to provide a quick evaluation of the organization.
+    The scores will enable performance to be consistently measured
+    and compared.
+
+    Other attempts at evaluating a software development organization
+    have been presented, but none produce a single number score for
+    the entire effort of the software development organization. 
+    The following are attempts to evaluate all or parts of 
+    software development.
 

### 2015-01-14 paper_30_measure.tex
added overview to chapter 1 references for PMD and findbugs

@@
 
-\section{DATA-DRIVEN SOFTWARE ENGINEERING}
+\section{MEASURING A SDO}
 
@@
         code adheres to specified set of rules. Common 
-        examples are PMD and findbugs.
+        examples are PMD and findbugs \cite{PMD, Findbugs}.
     \end{itemize}
@@
 
-\subsection{RESULT INDICATORS FOR SDOs}
+\subsection{RESULT INDICATORS FOR SDO}
     This section will cover the potential result indicators for an SDO.
 
-\subsection{PERFORMANCE INDICATORS FOR SDOs}
+\subsection{KEY RESULT INDICATORS FOR SDO}
+
+\subsection{PERFORMANCE INDICATORS FOR SDO}
     This section will cover the potential performance indicators for an SDO.
+
+\subsection{KEY PERFORMANCE INDICATORS FOR SDO}
 
@@
 exactly needs to be tracked.  It is also not specific to an SDO and 
-it does produce a single number.
+it does not produce a single number.
 

### 2015-01-21 paper_30_measure.tex
some section changes in chapter 3

@@
         code adheres to specified set of rules. Common 
-        examples are PMD and findbugs \cite{PMD, Findbugs}.
+        examples are PMD and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
     \end{itemize}
@@
 
+\subsection{INDICATORS}
 Performance indicators can be crucial measurements
@@
 
-\subsection{RESULT INDICATORS FOR SDO}
+\subsubsection{RESULT INDICATORS FOR SDO}
     This section will cover the potential result indicators for an SDO.
 
-\subsection{KEY RESULT INDICATORS FOR SDO}
+\subsubsection{KEY RESULT INDICATORS FOR SDO}
 
-\subsection{PERFORMANCE INDICATORS FOR SDO}
+\subsubsection{PERFORMANCE INDICATORS FOR SDO}
     This section will cover the potential performance indicators for an SDO.
 
-\subsection{KEY PERFORMANCE INDICATORS FOR SDO}
+\subsubsection{KEY PERFORMANCE INDICATORS FOR SDO}
 
@@
 A common technique for organization to measure themselves is a balanced scorecard.
-A \textit{balanced scorecard} must contain the following
+A \textit{balanced scorecard} must contain the following six
 characteristics.
-\begin{itemize}
+\begin{enumerate}
   \item Financial 
@@
   \item Learning and Growth
-\end{itemize}
+\end{enumerate}
 
@@
 
-\subsection{POSSIBLE DATA POINTS FOR LEVEL OF EFFORT}
-
-\begin{description}
-    \item[Actual Development Hours] Actual Hours Spent on development
-    \item[Estimated Development Hours]  Initial Hours estimated for a project, this will commonly be different from the actual development hours
-    \item[Source Lines Of Code (SLOC)]  This is count of the total number of lines of source code
-    \item[Modified Lines Of Code] This is a count of the number of modified lines of source code. This number is a sum of the deleted, added, and modified lines of source code.
-\end{description}
-
+\subsection{PROJECT MANAGEMENT MEASUREMENT}
 According to Putnam and Myers in \cite{Putnam2013}, the 5 core measurements for managing software
@@
 
+\subsection{POSSIBLE DATA POINTS FOR LEVEL OF EFFORT}
+
+\begin{description}
+    \item[Actual Development Hours] Actual Hours Spent on development
+    \item[Estimated Development Hours]  Initial Hours estimated for a project, this will commonly be different from the actual development hours
+    \item[Source Lines Of Code (SLOC)]  This is count of the total number of lines of source code
+    \item[Modified Lines Of Code] This is a count of the number of modified lines of source code. This number is a sum of the deleted, added, and modified lines of source code.
+\end{description}
+
 \end{document}

### 2015-01-21 paper_20_sdo.tex
rearrangement for steps of SDLC

@@
 
+The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.
+
+\begin{easylist}[itemize]
+    & Identify the Work/Task/Project
+    && Get Initial Idea 
+    && Obtain Details
+    & Estimate
+    && Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
+    &&Obtain Approval 
+    && Quit or Go Forward
+    & Document Requirements
+    && Identify the Requirements
+    && Detail the Requirements
+    & Design The Software
+    && Find System Integrations
+    && Identify Functional Specs
+    && Detail the Functional Specs
+    & Development of all the tasks in Design and Requirements
+    && Identify the Coding Tasks
+    && Write the Code/Develop the solution
+    && Write the Unit Tests
+    & Test
+    && Create Test Plans and Cases
+    && Run Test Plans and Cases
+    & Deployment
+    && Create Deployment Steps
+    && Run Deployment Steps
+    & Maintenance
+    && Capture Bugs
+    && Survey Users
+\end{easylist}
+
 \subsection{WHAT IS SOFTWARE ENGINEERING?}
@@
 \begin{description}
+
+    \item[App] (Application) - a software system or a collection of other apps, item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
+    \item[Release] - A collection of projects being put in production on a specified date
     \item[SIT]   (Systems Integration Testing) - The initial step of testing

### 2015-01-21 paper_70_case-study.tex
rearrangement for steps of SDLC

@@
 
-These are notes
+\subsection{WITHOUT HISTORICAL DATA}
 
-Application(app) - a software system or a collection of other apps, for example: Wystar is an application but it is a collection of other apps namely WyConnect, WyBatch ...
-Project - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
-Release - A collection of projects being put in production on a specified date
+An MPI calculation with default values.
 
-The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.
+\subsection{WITH HISTORICAL DATA}
 
-1. Identify the Work/Task/Project
-  1. Get Initial Idea
-  2. Obtain Details
-2. Estimate
-  1. Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
-  2. Obtain Approval 
-  3. Quit or Go Forward
-3. Write BRD
-  1. Identify the Requirements
-  2. Detail the Requirements
-4. Write FSD
-  1. Find System Integrations
-  2. Identify Functional Specs
-  3. Detail the Functional Specs
-5. Development of all the tasks in FSD
-  1. Identify the Coding Tasks
-  2. Write the Code/Develop the solution
-  3. Write the Unit Tests
-6. Test
-  1. Create Test Plans and Cases
-  2. Run Test Plans and Cases
-7. Deployment
-  1. Create Deployment Steps
-  2. Run Deployment Steps
-8. Maintenance
-  1. Capture Bugs
-  2. Survey Users
- end of notes
+How to create better formulas with historical data.
 

### 2015-01-21 paper_10_intro.tex
capitalize some table and image names

@@
     should be reported.  The MPI framework provides a solid foundation
-    for a consistent evaluation.  It should also provide a broad
+    for a consistent evaluation.  MPI analyzes the historical performance
+    of an SDO
+    to create a baseline in order to provide a broad
     view of the overall organization.  It is common for software development
@@
     decisions to be made.  The framework provides an evaluation
-    of the overall software development organization.
+    of the overall software development organization, not just the
+    source code.
 
@@
         \includegraphics[scale=.7]{images/cmmi.png}
-        \caption[Characteristics of CMMI]{Characteristics of CMMI, 
+        \caption[CHARACTERISTICS OF CMMI]{Characteristics of CMMI, 
             image adapted from  \cite{Godfrey} }

### 2015-01-21 paper_20_sdo.tex
capitalize some table and image names

@@
             \includegraphics[scale=.5]{images/benington_waterfall.PNG}
-            \caption[Benington's original diagram for producing large software systems]
+            \caption[BENINGTON'S ORIGINAL DIAGRAM FOR PRODUCING LARGE SOFTWARE SYSTEMS]
                     {Benington's original diagram for producing large software 
@@
             \includegraphics[scale=.5]{images/royce_waterfall.PNG}
-            \caption[Royce's version of the waterfall model]
+            \caption[ROYCE'S VERSION OF THE WATERFALL MODEL]
                 {Royce's version of the waterfall model for producing software 
@@
             \includegraphics[scale=.6]{images/waterfall.png}
-            \caption[Modern Waterfall]
+            \caption[MODERN WATERFALL]
                 {Modern Waterfall Diagram, adapted from \cite{Hibbs2009} }
@@
             \includegraphics[scale=.5]{images/spiral_model.png}
-            \caption[Spiral SDLC Model]{Spiral SDLC Model \cite{Boehm2000} }
+            \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
             \label{fig:spiral}

### 2015-01-21 paper_50_sdlc-ae.tex
adding material that had been removed for the proposal
adding some capitol letters to the section headers
most of the lit review is complete
capitalize some table and image names

@@
 
-The SDLC-AE would make gamification of the SDLC attainable.  Prior attempts
-at gamification of the SDLC focus only on the development phase \cite{Dubois2013} \cite{Snipes2013}.
+Once all the SDLC data is collected into a single place, there are many possible applications.  Software analytics
+will be much easier to create and gamification will be much more easily attainable.
 
@@
 \includegraphics[scale=.7]{images/sdlc-ae.png}
-\caption{SDLC Analytic Engine}
+\caption{SDLC ANALYTIC ENGINE}
 \label{fig:sdlc-ae}
@@
 
-\begin{comment}
-    \subsection{Estimation}
+    \subsection{ESTIMATION}
 
@@
 
-    \subsection{Requirements}
+    \subsection{REQUIREMENTS}
     List of: 
@@
 
-    \subsection{Maintenance (Defects)}
+    \subsection{MAINTENANCE (DEFECTS)}
     List of:
@@
 
-    \subsection{Testing}
+    \subsection{TESTING}
 
@@
 
-    \subsection{Development}
+    \subsection{DEVELOPMENT}
 
@@
 
-    \subsection{Implementation}
+    \subsection{IMPLEMENTATION}
 
@@
 
-\end{comment}
-
 \end{document}

### 2015-01-23 paper_20_sdo.tex
updated the PDF output file

@@
     \item[PROD]  (Production) - The software has been released to the final audience.
-    \item[defect] Whenever the output of software does not meet expectations.  It is important to mention that even though defects are typically 
+    \item[defect] ``A software defect is a bug or error that causes
+                software to either stop operating or to produce
+                invalid or unacceptable results'' as quoted from
+            \cite{Jones2009}.  It is important to mention that even though defects are typically 
             found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
@@
 
-            ``
-                A software defect is a bug or error that causes
-                software to either stop operating or to produce
-                invalid or unacceptable results.
-            '' as quoted from
-            \cite{Jones2009}.  Also in here is the 4 severity levels.  Also, current defect removal is only about 85\% and this value should be increased to about 95\%. 
+              Also in here is the 4 severity levels.  Also, current defect removal is only about 85\% and this value should be increased to about 95\%. 
 \end{description}

### 2015-01-26 paper_30_measure.tex
minor changes

@@
 \subsection{INDICATORS}
-Performance indicators can be crucial measurements
-within any business setting, and an SDO is no exception. Many
-SDOs struggle to determine the correct indicators to track and
-how to track them.  
+Indicators can be crucial measurements
+within any business setting, and an SDO is no exception. Determining
+the correct indicators for an organization can
+be difficult.  Software development organizations
 The differences between the indicators will be explored and

### 2015-02-01 paper_10_intro.tex
fix some Typos

@@
     Software Engineering Institute at
-    Carnegie Mellon University. While the CMMI is not specific to software development,
+    Carnegie Mellon University \cite{CMMI}. While the CMMI is not specific to software development,
     it is often applied in software development settings.
@@
     development activities applied to products
-    and services \cite{CMMI}.  The practices covered in 
+    and services.  The practices covered in 
     CMMI-Dev include project management, 
@@
 
-        \item[CMMI MATURITY LEVEL 4 - QUALITATIVELY MANAGED]
+        \item[CMMI MATURITY LEVEL 4 - QUANTITATIVELY MANAGED]
             A maturity level 4 organization has quantitative 
@@
     A visual description of the CMMI maturity levels can be seen in Figure \ref{fig:cmmi}.  
-    While CMMI-Dev does provide an excellent framework for improving a process.  It
+    While CMMI-Dev does provide an excellent framework for improving a process, it
     is wholely focused on process improvement.  It does not provide guidelines

### 2015-02-02 paper_10_intro.tex
more typos fixed

@@
     regarding building or buying software products.  It does not provide 
-    an algorithms to review past performance of estimates and modify the
-    algorithm accordingly.  COCOMO II can be a useful tool for 
+    an algorithm to review and modify past performance 
+    based upon estimates.  COCOMO II can be a useful tool for 
     estimating the time and costs within an SDO,
@@
     or more complex.  Thus, finding a value for quality is easier 
-    than interpreting that value.  Not matter the interpretation,
+    than interpreting that value.  No matter the interpretation,
     the goal is to release the number of problems with the software.
@@
     is ``the process of making activities more game-like'' \cite{Werbach2014}.
-    some of the benefits of gamification are higher productivity, competition,
+    Some of the benefits of gamification are higher productivity, competition,
     and greater enjoyment.  

### 2015-02-03 paper_20_sdo.tex
more typos fixed

@@
 
-\subsection{THE SOFTWARE DEVELOPMENT LIFECYCLE}
+\subsection{THE SOFTWARE DEVELOPMENT LIFE CYCLE}
     The discipline of software engineering has created a workflow for developing
@@
         \cite{Boehm1986, Boehm1988}. 
-        The goal of the spiral mode of software development is very risk-driven.
+        The goal of the spiral model of software development is very risk-driven.
         A software project will start with many small and quick iterations. 

### 2015-02-03 paper_10_intro.tex
minor update to abstract

@@
     software implementation.  More research needs to be done applying
-    process mining to the other process involved with software development,
+    process mining to the other processes involved with software development,
     such as other documentation, testing, and implementation.

### 2015-02-03 paper_20_sdo.tex
increased image size

@@
             \centering
-            \includegraphics[scale=.5]{images/benington_waterfall.PNG}
+            \includegraphics[scale=.7]{images/benington_waterfall.PNG}
             \caption[BENINGTON'S ORIGINAL DIAGRAM FOR PRODUCING LARGE SOFTWARE SYSTEMS]
@@
             \centering
-            \includegraphics[scale=.5]{images/royce_waterfall.PNG}
+            \includegraphics[scale=.7]{images/royce_waterfall.PNG}
             \caption[ROYCE'S VERSION OF THE WATERFALL MODEL]
@@
             \centering
-            \includegraphics[scale=.6]{images/waterfall.png}
+            \includegraphics[scale=.9]{images/waterfall.png}
             \caption[MODERN WATERFALL]
@@
         and the overall process. 
-        \begin{figure}[here]
+        \begin{figure}[ht]
             \centering
-            \includegraphics[scale=.5]{images/spiral_model.png}
+            \includegraphics[scale=.8]{images/spiral_model.png}
             \caption[SPIRAL SDLC MODEL]{Spiral SDLC Model \cite{Boehm2000} }
@@
         Even with the large number of SDLC models currently being used by different SDOs,
-        there is still some commonalities among the models.  The 
+        many ommonalities exist among the models.  The 
         commonalities can be tied back to the steps of waterfall.  All of the models

### 2015-02-04 paper_10_intro.tex
increased image size
adding info about 3 focus areas and 3 questions

@@
 \subsubsection{SOFTWARE ANALYTICS}
+\label{subsub:softwareanalytics}
 
@@
     software analytics are:
-    \begin{description}
-        \item[User Experience] - How can the software enable the 
+    \begin{enumerate}
+        \item \textbf{User Experience} - How can the software enable the 
             user to more easily or quickly 
             accomplish the task at hand?
-        \item[Quality] - How can the number of problems with 
+        \item \textbf{Quality} - How can the number of problems with 
             the software be decreased?
-        \item[Development Productivity] - How can the processes
+        \item \textbf{Development Productivity} - How can the processes
             or tools be modified to increase 
             the rate at which software is produced? 
-    \end{description}
-    The work presented later in this paper will address all three
-    focus areas.
+    \end{enumerate}
 
-    Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
+    Later, Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
     analytics must address:
@@
     when presenting any results in software analytics.  The research
-    needs to demonstrate clear advantages for practitioners.
+    needs to demonstrate clear advantages for practitioners.  The work
+    presented in this work will address both the 3 main focus areas and
+    the 3 important questions of software analytics.
 
@@
 Indicator (MPI).  It will present the essential elements for calculating the MPI, as well
-as the formulas, frameworks, and data necessary to produce the MPI. Chapter 5 provides
+as the formulas, framework, and data necessary to produce the MPI. Chapter 5 provides
 a technological framework for generating and storing the current and historical MPI values.

### 2015-02-04 paper_40_mpi.tex
adding some more papers
capitalize some table and image names
updated the PDF output file
adding info about 3 focus areas and 3 questions

@@
 
-\section{ELEMENTS OF MPI}
+\section{MASTER PERFORMANCE INDICATOR (MPI)}
 
@@
 
-\caption{Availability - Inputs}
+\caption{AVAILABILITY - INPUTS}
 \label{tab:avail}
@@
 
-\caption{Quality - Inputs}
+\caption{QUALITY - INPUTS}
 \label{tab:quality}
@@
 
-\caption{Satisfaction - Inputs}
+\caption{SATISFACTION - INPUTS}
 \label{tab:satisfaction}
@@
 
-    \subsubsection{Overview}
         Delivery of software in a timely manner is an essential part of being a 
@@
 
-\caption{Schedule - Inputs}
+\caption{SCHEDULE - INPUTS}
 \label{tab:sched}
@@
 
-\caption{Requirements - Inputs}
+\caption{REQUIREMENT - INPUTS}
 \label{tab:req}
@@
 
+\subsection{SENSITIVITY OF MPI}
+\label{sub:sensitivity}
+
+For more on sensitivity analysis in statistical modeling, see \cite{Saltelli2000}.
+
+\subsection{IMPORTANCE OF MPI}
+
+Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus areas and 3 important questions for software
+analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how MPI addresses
+each focus area.  
+As can be seen, MPI clearly addresses the 3 main focus areas of software analytics.  MPI does provide
+any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
+the focus areas.
+
+\begin{longtable}{p{3cm}p{11cm}}
+% pairs: absolute number (percentage)
+
+\toprule%
+ \centering%
+ {\bfseries Focus Area}
+ & {\bfseries Why MPI?} \\
+
+\cmidrule[0.4pt](r{0.125em}){1-1}%
+\cmidrule[0.4pt](lr{0.125em}){2-2}%
+% \midrule
+\endhead
+
+User Experience & One of the 5 elements of MPI is satisfaction.
+While not all of the questions focus solely on the user experience, the entire purpose of the survey is to determine if the user is satisfied
+with the software product.
+Does it have the correct features?
+Are new features added in a timely manner?
+Of course, specific survey questions can be created to focus solely on a certain user experience.
+\\
+\myrowcolour%
+Quality & Again, one of the 5 elements specifically focuses on quality.  MPI provides a single number
+to measure quality.  Therefore, it is easy to track changes in quality over time.  MPI does not address
+how to improve the quality, but without a consistent measurement, it would be impossible to determine the change in quality. \\
+Development Productivity & The combination of MPI elements, schedule and requirements, provide an 
+indication of development productivity. The schedule element measures the productivity
+related to estimated schedule. Similarly, the requirement element measures the amount of
+work actually being completed.  \\
+
+\bottomrule
+
+\caption{SOFTWARE ANALYTICS FOCUS AREAS AND MPI}
+\label{tab:focusareas}
+\end{longtable}
+
+\begin{longtable}{p{4cm}p{10cm}}
+% pairs: absolute number (percentage)
+
+\toprule%
+ \centering%
+ {\bfseries Question}
+ & {\bfseries Why MPI?} \\
+
+\cmidrule[0.4pt](r{0.125em}){1-1}%
+\cmidrule[0.4pt](lr{0.125em}){2-2}%
+% \midrule
+\endhead
+
+How much better is my model performing than a naive strategy, such as guessing? & MPI 
+provides consistency which may not exist without it.  Therefore, MPI removes the 
+guesswork of measuring a software development organization. \\
+\myrowcolour%
+How practically significant are the results? &  \\
+How sensitive are the results to small changes in one or more of the inputs? & 
+The question was extensively addressed in section \ref{sub:sensitivity}.  It appears MPI is
+not overly sensitive to small changes in the inputs.\\
+
+\bottomrule
+
+\caption{3 IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND MPI}
+\label{tab:questions}
+\end{longtable}
+
 \end{document}

### 2015-02-04 paper_50_sdlc-ae.tex
adding info about 3 focus areas and 3 questions

@@
 In order for an SDO to properly track the elements of MPI, a data storage system should be available to store the appropriate data.
+A consistent storage system should help to avoid the problem of inaccurate
+data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
+is implemented correctly by allowing limited changes to existing data, it will be able to alliviate
+some of the dishonesty that is currently present in software projects \cite{Rost2011}.
 This storage system will be named the SDLC Analytic Engine (SDLC-AE).

### 2015-02-05 paper_40_mpi.tex
finished tables for 3 focus areas and questions for software analytics

@@
 \myrowcolour%
-How practically significant are the results? &  \\
+How practically significant are the results? & The MPI score is consistent
+and easy to comprehend.  Thus comparison with past performance is quick 
+and simple.  This is a significant advantage for software 
+development organizations. \\
 How sensitive are the results to small changes in one or more of the inputs? & 

### 2015-02-06 paper_20_sdo.tex
adding a reference

@@
     Software engineering has struggled to determine the correct projects to complete \cite{DeMarco2009}.
-    Software projects are typically behind schedule and over budget. Organizations need a better
-    technique to understand the past performance so they can better predict the future performance.
+    Software projects are commonly behind schedule and over budget. Organizations need a better
+    technique to understand the past performance so they can better predict the future performance \cite{Lehtinen2014}.
 

### 2015-02-06 paper_30_measure.tex
added a sentence
adding info about 3 focus areas and 3 questions
fix some more minor typos

@@
 
-Anything can be measured \cite{Hubbard2010}.
+Anything can be measured \cite{Hubbard2010}.  An SDO
+how numerous metrics.
 
@@
         code adheres to specified set of rules. Common 
-        examples are PMD and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
+        examples are PMD\footnote{PMD is a source code analysis product.  It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
     \end{itemize}
@@
 
-A common technique for organization to measure themselves is a balanced scorecard.
+A common technique for organizations to measure themselves is a balanced scorecard.
 A \textit{balanced scorecard} must contain the following six
@@
 Balanced scorecards are great for displaying the important information about
-and organization.  However, a balanced scorecard does not specify what
+an organization.  However, a balanced scorecard does not specify what
 exactly needs to be tracked.  It is also not specific to an SDO and 
@@
 
-\subsection{COMBINING THE MEASURES TO FORM MPI}
+\subsection{COMBINING THE MEASURES}
 

### 2015-02-06 paper_50_sdlc-ae.tex
fix some more minor typos

@@
    All the data necessary to compute MPI needs to be stored in a database.  This section will 
-   layout the structure of tables and relationships necessary to the store all the data
+   lay out the structure of tables and relationships necessary to the store all the data
    within a relational database such as MySQL or PostgreSQL.  Eventually,

### 2015-02-07 paper_40_mpi.tex
fix some more minor typos
adding MPI overview in chapter 4

@@
 Software development organizations struggle to measure overall performance.  
-The Master Performance Indicator (MPI) is an algorithm to provide a single number score for the performance of a software development organization.
-It works by statistically analyzing the past performance of the organization and using that information to score an organization on current and future performance.
-MPI focuses on the following elements of a software development organization: \textit{requirements},  \textit{quality},  \textit{on-schedule},  \textit{availability}, and  \textit{satisfaction}.
-MPI is not meant to be comparative between organizations, but to measure the amount of increase or decrease a single organization exhibits.
-It is possible the concept could be expanded beyond just software development organizations or the previously stated elements.
+        The Master Performance Indicator (MPI) is an algorithm to provide a single 
+        number score to measure the performance of a software development organization. 
+        It works by statistically analyzing the past performance of the 
+        organization and using that information to score an organization 
+        on current performance.  MPI focuses on the following 
+        elements of a software development organization: \textit{quality}, 
+        \textit{availability}, \textit{satisfaction}, \textit{schedule},
+        and \textit{requirements}. A separate MPI
+        score is calculated for each element and 
+        then aggregated together to form an overall 
+        MPI score.   \textbf{MPI is not meant to be comparative between
+        organizations, but to measure the amount of increase or decrease
+        a single organization exhibits across elements}.  MPI is made to be easily 
+        expandable to other elements if desired.
+
+        The scores for MPI will range from -100, indicating the worst 
+        performance, all the way to +100, indicating perfection.
+        A score of 0 is an indication of meeting the basic expectations. 
+        A negative score indicates under-performance and a 
+        positive score indicates over-performance.   Here are some 
+        examples. An MPI score of 35 means the organization is 
+        performing 35\% better than expected.  Conversely, a score 
+        of -15 means an organization is performing 15\% worse than expected.
 
@@
             As long as those 5 features are met, the range can be anything.
-The range of $[-1,1]$ was chosen because it is easy to scale to a different range such as $[-10,10]$ or $[-100,100]$.
+The range of $[-100,100]$ was chosen because it is easy to scale to a different range such as $[-10,10]$ or $[-1,1]$.
 It maybe makes sense to use variables for the range.
-The formulas are designed to fall in the range $[-1,1]$.
+The formulas are designed to fall in the range $[-100,100]$.
 Thus scaling can be applied to obtain values in any appropriate range.
@@
 
-\caption{3 IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND MPI}
+\caption{IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND MPI}
 \label{tab:questions}

### 2015-02-09 paper_40_mpi.tex
adding a variable for scaling

@@
         \item The range of scores must have equal values above and below 0
-                \item The minimum score must equate to the worst possible performance, however that is defined
+        \item The minimum score must equate to the worst possible 
+            performance, however that is defined
         \item Similarily, the maximum score must equate to the best possible performance.  
@@
     As long as those 5 features are met, the range can be anything.  
-The range of $[-100,100]$ was chosen because it is easy to scale to a different range such as $[-10,10]$ or $[-1,1]$.
+    The range of $[-1,1]$ was chosen because it is easy to scale 
+    to a different range such as $[-10,10]$ or $[-100,100]$.  
     It maybe makes sense to use variables for the range.  
@@
     Thus scaling can be applied to obtain values in any appropriate range. 
-
-\subsection{AVAILABILITY}
-All the new requirements and great quality do not matter if the software is not available.  
-The following algorithm will calculate the score of software availability.
-\begin{displaymath}
-   S_{3_i} = \left\{
-     \begin{array}{lr}
-       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
-       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
-     \end{array}
-   \right.
-\end{displaymath} 
-\[
-    S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
-\]
-
-\begin{itemize}
-\item $A_{a_i}$ actual availability for app i
-\item $A_{e_i}$ expected availability for app i
-\end{itemize}
-
-\begin{longtable}{@{}l rr rr}
-% pairs: absolute number (percentage)
-
-\toprule%
- \centering%
- {\bfseries Column Name}
- & {\bfseries Data Type}
- &  \\
-
-\cmidrule[0.4pt](r{0.125em}){1-1}%
-\cmidrule[0.4pt](lr{0.125em}){2-2}%
-\cmidrule[0.4pt](l{0.125em}){3-3}%
-% \midrule
-\endhead
-
-Application ID & String  & Required \\
-\myrowcolour%
-Frequency Date & Date & Required \\
-Uptime & Float & Optional \\
-\myrowcolour%
-Scheduled Downtime & Float & Optional \\
-Unscheduled Downtime & Float  & Optional \\
-\myrowcolour%
-Percent Uptime & Float & Required \\
-Expected Percent Uptime & Float & Required \\
-
-\bottomrule
-
-\caption{AVAILABILITY - INPUTS}
-\label{tab:avail}
-\end{longtable}
+    The scaling is denoted with the variable $k$.  The scale will be the same
+    for all 5 elements.
 
@@
 \end{itemize}
+
+\subsection{AVAILABILITY}
+All the new requirements and great quality do not matter if the software is not available.  
+The following algorithm will calculate the score of software availability.
+\begin{displaymath}
+   S_{3_i} = \left\{
+     \begin{array}{lr}
+       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
+       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
+     \end{array}
+   \right.
+\end{displaymath} 
+\[
+    S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
+\]
+
+\begin{itemize}
+\item $A_{a_i}$ actual availability for app i
+\item $A_{e_i}$ expected availability for app i
+\end{itemize}
+
+\begin{longtable}{@{}l rr rr}
+% pairs: absolute number (percentage)
+
+\toprule%
+ \centering%
+ {\bfseries Column Name}
+ & {\bfseries Data Type}
+ &  \\
+
+\cmidrule[0.4pt](r{0.125em}){1-1}%
+\cmidrule[0.4pt](lr{0.125em}){2-2}%
+\cmidrule[0.4pt](l{0.125em}){3-3}%
+% \midrule
+\endhead
+
+Application ID & String  & Required \\
+\myrowcolour%
+Frequency Date & Date & Required \\
+Uptime & Float & Optional \\
+\myrowcolour%
+Scheduled Downtime & Float & Optional \\
+Unscheduled Downtime & Float  & Optional \\
+\myrowcolour%
+Percent Uptime & Float & Required \\
+Expected Percent Uptime & Float & Required \\
+
+\bottomrule
+
+\caption{AVAILABILITY - INPUTS}
+\label{tab:avail}
+\end{longtable}
 

### 2015-02-09 paper_30_measure.tex
working on quality element

@@
 
-\subsection{POSSIBLE DATA POINTS FOR LEVEL OF EFFORT}
-
-\begin{description}
-    \item[Actual Development Hours] Actual Hours Spent on development
-    \item[Estimated Development Hours]  Initial Hours estimated for a project, this will commonly be different from the actual development hours
-    \item[Source Lines Of Code (SLOC)]  This is count of the total number of lines of source code
-    \item[Modified Lines Of Code] This is a count of the number of modified lines of source code. This number is a sum of the deleted, added, and modified lines of source code.
-\end{description}
-
 \end{document}

### 2015-02-09 paper_40_mpi.tex
working on quality element

@@
 \subsection{QUALITY}
-Quality is arguably the most important part of software development.  Poor quality means time, money, and resources are spent 
-fixing the quality.  One of the key indicators of software quality is defects.  Thus, it is important
-to measure the number of defects associated with a software release.  The following is an algorithm to calculate
+    Measuring quality is a crucial part of accessing 
+    software development results.  
+    Poor quality means time, money, and resources are spent 
+    fixing the problems. As a result, new features are not being
+    created. One of the key indicators of software quality 
+    is defects.  Thus, it is important
+    to measure the number of defects associated with a software 
+    release.  The following is an algorithm to calculate
     the quality score of software being released.
+
+    \subsubsection{QUALITY DATA}
+        In order to properly score the quality of an SDO,
+        certain data needs to be obtained in order to measure
+        performance. Table \ref{tab:qualitydata} identifies
+        the columns of data that will be used to create
+        a score for the quality element of MPI.  
+        Each column is classified as \textit{required} or
+        \textit{optional}.  That is to allow some flexibility
+        in the model for organizations that collect
+        varying amounts of data.
+
+        \begin{longtable}{@{}l rr rr}
+            % pairs: absolute number (percentage)
+
+            \toprule%
+             \centering%
+             {\bfseries Column Name}
+             & {\bfseries Data Type}
+             &  \\
+
+            \cmidrule[0.4pt](r{0.125em}){1-1}%
+            \cmidrule[0.4pt](lr{0.125em}){2-2}%
+            \cmidrule[0.4pt](l{0.125em}){3-3}%
+            % \midrule
+            \endhead
+
+            Application ID & String (factor) & Required \\
+            \myrowcolour%
+            Frequency Date & Date & Required \\
+            Development Effort & Integer & Required \\
+            \myrowcolour%
+            Testing Effort & Integer & Optional \\ 
+            Defects in SIT & Integer & Optional \\ 
+            \myrowcolour%
+            Defects in UAT & Integer  & Optional \\ 
+            Defects in PROD & Integer  & Required \\
+
+            \bottomrule
+
+            \caption{QUALITY DATA NEEDED FOR MPI}
+            \label{tab:qualitydata}
+        \end{longtable}
+
+        The development and testing effort can come from any of 
+        the following choices for effort. 
+        \begin{description}
+            \item[Actual Time] This number is a representation of the 
+                total amount of time spent on a project.  This number
+                can be measured in any unit of time: hours, days, weeks,
+                etc.  Actual time can be applied to development or testing
+                effort.
+            \item[Estimated Time] This number is a representation of the 
+                initial estimated amount of time spent on a project.  This number
+                can be measured in any unit of time: hours, days, weeks,
+                etc.  Estimated time can be applied to development or testing
+                effort.  It is common for the estimated and actual times
+                to be diffent.
+            \item[Source Lines Of Code (SLOC)]  This number is the count of 
+                the total number of lines of source code for a project. 
+                Obviously, 
+                this item only counts as a level of
+                effort for development unless coding in used to generate
+                automated test cases. \footnote{Automated testing is the
+                process of creating software to automatically run tests
+                against other software.  The adoption of automated testing
+                is varied and it is not a solution in all cases 
+                \cite{Ramler2006}. }
+            \item[Modified Lines Of Code] This number is a count of the number 
+                of modified lines of source code. Modified lines is 
+                defined as the number of deleted, added, and modified 
+                lines of source code.  This number is different from above
+                since it does not include all the lines of source code.  Similar
+                to above, this number makes more sense for development effort.
+            \item[Test Cases] A test case is a step or series of steps followed
+                to validate some expected outcome of software.  Organizations
+                will create a number of test cases to be validated for a
+                software system.  The number of such test cases could
+                be used as a level of testing effort.
+        \end{description}
+
+    \subsubsection{QUALITY FORMULA}
+        The first step in creating a score for the quality
+        element is analysis of the historical data.  The historical
+        data is all quality data collected before  a given point
+        in time.  Some common historical cutoffs are the current date
+        or the end of the previous fiscal year.  Then a mathematical
+        model to predict Defects in PROD will be produced.  In statistical
+        terms, the response is \textit{Defects in PROD} and the predictors
+        are: \textit{Defects in UAT}, \textit{Defects in SIT}, 
+        \textit{Testing Effort}, and \textit{Development Effort}.
 
@@
 \end{itemize}
-
-Here are the columns of the data.
-
-\begin{longtable}{@{}l rr rr}
-% pairs: absolute number (percentage)
-
-\toprule%
- \centering%
- {\bfseries Column Name}
- & {\bfseries Data Type}
- &  \\
-
-\cmidrule[0.4pt](r{0.125em}){1-1}%
-\cmidrule[0.4pt](lr{0.125em}){2-2}%
-\cmidrule[0.4pt](l{0.125em}){3-3}%
-% \midrule
-\endhead
-
-Application ID & String (factor) & Required \\
-\myrowcolour%
-Frequency Date & Date & Required \\
-Development Hours & Integer & Required \\
-\myrowcolour%
-Testing Hours & Integer & Optional \\ 
-Defects in SIT & Integer & Optional \\ 
-\myrowcolour%
-Defects in UAT & Integer  & Optional \\ 
-Defects in PROD & Integer  & Required \\
-
-\bottomrule
-
-\caption{QUALITY - INPUTS}
-\label{tab:quality}
-\end{longtable}
 

### 2015-02-10 paper_40_mpi.tex
working on the quality element

@@
     to measure the number of defects associated with a software 
-    release.  The following is an algorithm to calculate
+    release.  The following is the necessary data to collect
+    and an algorithm to calculate
     the quality score of software being released.
@@
         The development and testing effort can come from any of 
-        the following choices for effort. 
+        the following choices for effort. It is possible
+        that other measures will work for effort.
         \begin{description}
@@
         \textit{Testing Effort}, and \textit{Development Effort}.  
+        Some of the following strategies will be employed to find 
+        a reasonable model.
+        \begin{itemize}
+            \item Removal of outliers and/or influential points
+            \item Linear Regression
+            \item Stepwise Regression
+            \item Ridge Regression for suspected multicolinearity
+        \end{itemize}
+
+        Once a model has been found, it will be labeled as $f$ and it
+        will not change.  It serves as the quality baseline for MPI. 
+        All future quality scores will be dependent upon the original
+        $f$.
+
+        After the model $f$ has been determined,
 
@@
 about the most recent release.
-
-Here is the problem for loading the data:
-Given a data file with the above columns, can a regression model be automatically found
-that fits the data?  The regression model will serve as the "target" for future 
-releases.  Here is a list of possible things to automate to get a good model.
-\begin{itemize}
-\item Linear Regression
-\item Stepwise Regression
-\item Ridge Regression for suspected multicolinearity
-\item Removal of outliers
-\end{itemize}
 

### 2015-02-10 paper_40_mpi.tex
working on Chapter 4

@@
     then aggregated together to form an overall 
-    MPI score.   \textbf{MPI is not meant to be comparative between
+    MPI score.  A new MPI score will be calculated based
+    upon the selection of a given time period (weekly, monthly, quarterly).
+    \textbf{MPI is not meant to be comparative between
     organizations, but to measure the amount of increase or decrease
@@
 
-    The scores for MPI will range from -100, indicating the worst 
-    performance, all the way to +100, indicating perfection.
+    The scores for MPI will range from -1, indicating the worst 
+    performance, all the way to +1, indicating perfection.
     A score of 0 is an indication of meeting the basic expectations. 
@@
     positive score indicates over-performance.   Here are some 
-    examples. An MPI score of 35 means the organization is 
+    examples. An MPI score of 0.35 means the organization is 
     performing 35\% better than expected.  Conversely, a score 
-    of -15 means an organization is performing 15\% worse than expected.
+    of -0.15 means an organization is performing 15\% worse than expected.
 
-Here are the attributes of the MPI scoring.
+    Below are the attributes of the MPI scoring.
     \begin{itemize}
@@
 
-\subsection{QUALITY}
+    \subsection{ELEMENTS OF MPI}
+        The MPI score consists of data collected from five
+        different elements of an SDO.  
+        \begin{enumerate}
+            \item Quality
+            \item Availability
+            \item Satisfaction
+            \item Schedule
+            \item Requirements
+        \end{enumerate}
+        These five elements will be outline in the next sections.
+
+        \subsubsection{QUALITY}
             Measuring quality is a crucial part of accessing 
@@
 
-    \subsubsection{QUALITY DATA}
+            \paragraph{QUALITY DATA}
                 In order to properly score the quality of an SDO,
@@
                     Testing Effort & Integer & Optional \\ 
-            Defects in SIT & Integer & Optional \\ 
+                    SIT Defects & Integer & Optional \\ 
                     \myrowcolour%
-            Defects in UAT & Integer  & Optional \\ 
-            Defects in PROD & Integer  & Required \\
+                    UAT Defects & Integer  & Optional \\ 
+                    PROD Defects & Integer  & Required \\
 
@@
 
-    \subsubsection{QUALITY FORMULA}
+            \paragraph{QUALITY FORMULA}
                 The first step in creating a score for the quality
@@
                 or the end of the previous fiscal year.  Then a mathematical
-        model to predict Defects in PROD will be produced.  In statistical
-        terms, the response is \textit{Defects in PROD} and the predictors
-        are: \textit{Defects in UAT}, \textit{Defects in SIT}, 
+                model to predict PROD Defects will be produced.  In statistical
+                terms, the response is \textit{PROD Defects} and the predictors
+                are: \textit{UAT Defects}, \textit{SIT Defects}, 
                 \textit{Testing Effort}, and \textit{Development Effort}.  
@@
                 Once a model has been found, it will be labeled as $f$ and it
-        will not change.  It serves as the quality baseline for MPI. 
+                will not change.  The function $f$ can be the same for all 
+                Application IDs or it can be different for each Application ID
+                or any combination of Application IDs.   It serves as the 
+                quality baseline for MPI. 
                 All future quality scores will be dependent upon the original
-        $f$.
+                $f$.  Once set, the model will not change.
 
-        After the model $f$ has been determined,
+                After the model $f$ has been determined, it is time
+                to calculate the quality score for each application ID
+                within the given time period.  The quality score
+                for each Application ID can be calculated as follows.
 
@@
                      \begin{array}{lr}
-       \text{where } f \geq d_i & : \left[ \frac{f - d_i}{f} \right] \\
-       \text{where } d_i > f  & : \left[ \frac{f-d_i }{6\sigma} \right]
+                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
+                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{6\sigma_i} \times k
                      \end{array}
-   \right]
+                   \right] \text{   , calculate quality score for each app $i$}
                 \end{displaymath} 
+                where
+                \begin{itemize}
+                    \item $S_{1_i}$ is the quality score for Application ID $i$
+                    \item $n$ is the number of Application IDs
+                    \item $d_i$ is the actual PROD defects
+                    \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
+                        \textit{UAT Defects}, \textit{SIT Defects}, \textit{Testing Effort}, 
+                        and \textit{Development Effort}
+                    \item $6\sigma$ 6 times an estimate of the standard deviation of the 
+                        population using function $f_i$ above
+                \end{itemize}
 
                 \[
-    S_{1} = \frac{\sum^n_{i=1} S_{1_i}}{n}
+                    S_{1} = \sum\limits^n_{i=1} w'_i S_{1_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
                 \]
+                where
                 \begin{itemize}
-\item $n$ is the number of apps
-\item $d_i$ is the actual defects
-\item $f(h_i)$ is the function to predict defects based upon hours and other aspects of software development
-\item $6\sigma$ 6 times an estimate of the standard deviation of the population using function $f$ above
+                    \item $S_1$ is the combined quality score for all Application IDs, 
+                    a weighted average
                 \end{itemize}
 
-There are 2 parts here.  First the system needs to be loaded with this data.  Hopefully,
-a file with this data will exist going back a few months or years.  It is also important
-to note that the data load must be optional if an organization does not have existing
-data.  Second, every release (month/year) a new file will be upload with new information
-about the most recent release.
+                Then $S_1$ represents the quality score for that given time period.
 
-\subsection{AVAILABILITY}
+        \subsubsection{AVAILABILITY}
             All the new requirements and great quality do not matter if the software is not available.  
@@
 
-\caption{AVAILABILITY - INPUTS}
+            \caption{AVAILABILITY DATA NEEDED FOR MPI}
             \label{tab:avail}
@@
 
-\subsection{SATISFACTION}
-The satisfaction of the customer is also very important.  The following is an algorithm to calculate the satisfaction of software.
+        \subsubsection{SATISFACTION}
+            The satisfaction of the customer is also very important.  
+            The following is an algorithm to calculate the satisfaction of software.
             \[
@@
 
-\caption{SATISFACTION - INPUTS}
+            \caption{SATISFACTION DATA NEEDED FOR MPI}
             \label{tab:satisfaction}
@@
 
-\subsection{SCHEDULE}
-
+        \subsubsection{SCHEDULE}  
             Delivery of software in a timely manner is an essential part of being a 
@@
 
-    \subsubsection{Formula}
+            \paragraph{SCHEDULE DATA}
+
+                \begin{longtable}{@{}l rr rr}
+                    \toprule%
+                     \centering%
+                     {\bfseries Column Name}
+                     & {\bfseries Data Type}
+                     &  \\
+
+                    \cmidrule[0.4pt](r{0.125em}){1-1}%
+                    \cmidrule[0.4pt](lr{0.125em}){2-2}%
+                    \cmidrule[0.4pt](l{0.125em}){3-3}%
+                    % \midrule
+                    \endhead
+
+                    Application ID & String  & Required \\
+                    \myrowcolour%
+                    Frequency Date & Date & Required \\
+                    Scheduled Start Date & Date & Required \\
+                    \myrowcolour%
+                    Scheduled Finish Date & Date & Required \\
+                    Actual Start Date & Date  & Required \\
+                    \myrowcolour%
+                    Actual Finish Date & Date  & Required \\
+
+                    \bottomrule
+
+                    \caption{SCHEDULE DATA NEEDED FOR MPI}
+                    \label{tab:sched}
+                \end{longtable}
+
+            \paragraph{SCHEDULE FORMULA}
 
@@
 
-    \subsubsection{Example Calculation}
-    \subsubsection{Data and Calculations}
-    \subsubsection{Past Performance}
-    \subsubsection{Process for the Future}
-
-    \subsubsection{ALTERNATE APPROACH}
+            \paragraph{ALTERNATE APPROACH}
                 The best possible score should be achieved
@@
 
-\begin{longtable}{@{}l rr rr}
-% pairs: absolute number (percentage)
+        \subsubsection{REQUIREMENTS}
 
-\toprule%
- \centering%
- {\bfseries Column Name}
- & {\bfseries Data Type}
- &  \\
-
-\cmidrule[0.4pt](r{0.125em}){1-1}%
-\cmidrule[0.4pt](lr{0.125em}){2-2}%
-\cmidrule[0.4pt](l{0.125em}){3-3}%
-% \midrule
-\endhead
-
-Application ID & String  & Required \\
-\myrowcolour%
-Frequency Date & Date & Required \\
-Scheduled Start Date & Date & Required \\
-\myrowcolour%
-Scheduled Finish Date & Date & Required \\
-Actual Start Date & Date  & Required \\
-\myrowcolour%
-Actual Finish Date & Date  & Required \\
-
-\bottomrule
-
-\caption{SCHEDULE - INPUTS}
-\label{tab:sched}
-\end{longtable}
-
-\subsection{REQUIREMENTS}
-Requirements are desired new features or enhancements to a software product.  It is important to know how many requirements
-were scheduled to be completed versus how many actually got completed.  
-\[
-    S_5 = \frac{\sum^n_{i=1}\left( R_{a_i} - R_{e_i} \right)}{n}
-\]
-\begin{itemize}
-\item $R_a$ actual requirements completed for application $i$
-\item $R_e$ expected requirements completed for application $i$
-\end{itemize}
+            \paragraph{REQUIREMENTS DATA}
 
                 \begin{longtable}{@{}l rr rr}
-% pairs: absolute number (percentage)
-
                     \toprule%
@@
 
-\caption{REQUIREMENT - INPUTS}
+                    \caption{REQUIREMENTS DATA NEEDED FOR MPI}
                     \label{tab:req}
@@
 
-\subsection{FINAL MPI SCORE}
-One complete overall score cannot be successful without including information from various aspects of the software development organization.  Therefore, the previous results
+            \paragraph{REQUIREMENTS FORMULA}
+                Requirements are desired new features or enhancements 
+                to a software product.  It is important to know how many requirements
+                were scheduled to be completed versus how many actually got completed.  
+                \[
+                    S_5 = \frac{\sum^n_{i=1}\left( R_{a_i} - R_{e_i} \right)}{n}
+                \]
+                \begin{itemize}
+                    \item $R_a$ actual requirements completed for application $i$
+                    \item $R_e$ expected requirements completed for application $i$
+                \end{itemize}
+
+        \subsubsection{OVERALL MPI SCORE}
+            One complete overall score cannot be successful without including 
+            information from various aspects of the software development 
+            organization.  Therefore, the previous results
             are combined to provide one overall score.
-
             \[
@@
 
+        Some simulations will be run with data from each given distribution.  Then the MPI scores
+        will be analyzed.
         For more on sensitivity analysis in statistical modeling, see \cite{Saltelli2000}.
@@
 
-Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus areas and 3 important questions for software
+        Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus 
+        areas and 3 important questions for software
         analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how MPI addresses

### 2015-02-11 paper_20_sdo.tex
cleaning up references, removing journal abbreviations and spelling out full months
added another Capers Jones book
availability updates

--- 2015-02-03 paper_20_sdo.tex
@@
 
-    Software engineering has struggled to determine the correct projects to complete \cite{DeMarco2009}.
-    Software projects are typically behind schedule and over budget. Organizations need a better
-    technique to understand the past performance so they can better predict the future performance.
+    Software engineering has struggled to determine the correct projects 
+    to complete \cite{DeMarco2009}.
+    Software projects are commonly behind schedule and over budget \cite{Lehtinen2014, 
+    Charette2005,Jorgensen2013,Ichu2012} with nearly 20\% of projects
+    in the United States still failing \cite{Emam2008}. 
+    As of 2015, Software engineering is 
+    still awaiting the professional status of more established fields such
+    as medicine, law, and general engineering \cite{Jones2013b}. 
+    Organizations need a better
+    technique to understand the past performance so they can better 
+    predict the future performance.  Proper measurement will be essential
+    to solidifying software engineering as certified profession.
 

### 2015-02-11 paper_40_mpi.tex
availability updates

@@
             All the new requirements and great quality do not matter if the software is not available.
-            The following algorithm will calculate the score of software availability.
+            All the new features and great quality do not matter if the software is not available.  Thus it
+            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, an SLA is a 
+            contract specifying the amount of time software will be available during a
+            given time period. } and measure 
+            performance against that SLA.  The following section will outline to data needed to properly
+            calculate an SLA and the data needed to calculate the MPI score for availability.
+
+            Special Note: The System ID for availability does not have to be the same
+            as the Application ID for quality or any of the other elements.  Some 
+            organizations have a one-to-one mapping between Applications being developed
+            and systems being deployed.  Others have more complex sceranios that require
+            multiple applications to be combined to form a system.  Then the availability
+            of the system is tracked.
+
+            \paragraph{AVAILABILITY DATA}
+                Table \ref{tab:availdata} identifies the necessary data to calculate
+                the MPI element score for availability.  Notice the three optional 
+                fields: \textit{Uptime}, \textit{Scheduled Downtime}, and 
+                \textit{Unscheduled Downtime}; they are optional because they can be
+                used to calculated the \textit{Percent Uptime}.  The \textit{Percent Uptime}
+                is the important value for the MPI schedule score.  Here are the two common
+                approaches for calculating percent uptime:
+
+                \[
+                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Scheduled Downtime + Unscheduled Downtime}}
+                \]
+                and the alternative method
+                \[
+                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Unscheduled Downtime}}
+                \]
+                The only difference is the removal of scheduled downtime from 
+                the calculation.  The calculation approach is typically specified in
+                the contract associated with the SLA.
+
+                \begin{longtable}{@{}l rr rr}
+                    \toprule%
+                     \centering%
+                     {\bfseries Column Name}
+                     & {\bfseries Data Type}
+                     &  \\
+
+                    \cmidrule[0.4pt](r{0.125em}){1-1}%
+                    \cmidrule[0.4pt](lr{0.125em}){2-2}%
+                    \cmidrule[0.4pt](l{0.125em}){3-3}%
+                    % \midrule
+                    \endhead
+
+                    System ID & String  & Required \\
+                    \myrowcolour%
+                    Frequency Date & Date & Required \\
+                    Uptime & Float & Optional \\
+                    \myrowcolour%
+                    Scheduled Downtime & Float & Optional \\
+                    Unscheduled Downtime & Float  & Optional \\
+                    \myrowcolour%
+                    Percent Uptime & Float & Required \\
+                    Expected Percent Uptime & Float & Required \\
+
+                    \bottomrule
+
+                    \caption{AVAILABILITY DATA NEEDED FOR MPI}
+                    \label{tab:availdata}
+                \end{longtable}
+
+            \paragraph{AVAILABILITY FORMULA}
             \begin{displaymath}
@@
             \end{itemize}
-
-            \begin{longtable}{@{}l rr rr}
-            % pairs: absolute number (percentage)
-
-            \toprule%
-             \centering%
-             {\bfseries Column Name}
-             & {\bfseries Data Type}
-             &  \\
-
-            \cmidrule[0.4pt](r{0.125em}){1-1}%
-            \cmidrule[0.4pt](lr{0.125em}){2-2}%
-            \cmidrule[0.4pt](l{0.125em}){3-3}%
-            % \midrule
-            \endhead
-
-            Application ID & String  & Required \\
-            \myrowcolour%
-            Frequency Date & Date & Required \\
-            Uptime & Float & Optional \\
-            \myrowcolour%
-            Scheduled Downtime & Float & Optional \\
-            Unscheduled Downtime & Float  & Optional \\
-            \myrowcolour%
-            Percent Uptime & Float & Required \\
-            Expected Percent Uptime & Float & Required \\
-
-            \bottomrule
-
-            \caption{AVAILABILITY DATA NEEDED FOR MPI}
-            \label{tab:avail}
-            \end{longtable}
 

### 2015-02-12 paper_40_mpi.tex
finished availability

@@
 
+                Then the overall quality score is calculated as below.
+
                 \[
@@
 
+                The preferred method
                 \[
@@
                 the calculation.  The calculation approach is typically specified in
-                the contract associated with the SLA.
+                the contract associated with the SLA.  Thus, the Percent Uptime is important
+                and it can either be supplied in the data or calculated from the 
+                optional fields.
 
@@
             \paragraph{AVAILABILITY FORMULA}
+                The formula for availability is more straightforward than the quality formula.
+                It does not include any analysis of the historic data.  That lack of historical
+                analysis is avoided since the SLA provides an existing baseline to measure 
+                against.  The following formula is simply a percentage the SLA was exceeded
+                or missed.
+
                 \begin{displaymath}
-               S_{3_i} = \left\{
+                   S_{2_i} = \left\{
                      \begin{array}{lr}
-                   \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
-                   \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
+                       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}}\times k \right] \\
+                       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}}\times k \right]
                      \end{array}
-               \right.
+                   \right. \text{   , calculate availability score for each app $i$}
                 \end{displaymath}
-            \[
-                S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
-            \]
+
+                where
 
                 \begin{itemize}
-            \item $A_{a_i}$ actual availability for app i
-            \item $A_{e_i}$ expected availability for app i
+                    \item $A_{a_i}$ actual availability for System ID $i$
+                    \item $A_{e_i}$ expected availability for System ID $i$
                 \end{itemize}
+
+                Then the overall availability score is calculated as below.
+
+                \[
+                    S_{2} = \sum\limits^n_{i=1} w'_i S_{2_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
+                \]
 

### 2015-02-12 paper_10_intro.tex
adding a reference
minor updates

@@
 
-    One of the software analytic techniques focuses specifically 
+    Lavazza, Morasca, Taibi, and Tosi focus specifically 
     on the source code; analyzing the 
     complexity, size, and coupling \cite{Tosi2012}. 
+    They created a theoretical framework
+    for dynamic measurements instead of traditional static measures.
     Letier and Fitzgerald discuss how to choose the 
@@
 
-    So it has been shown, there exist many attempts to 
+    Overall, there exist many attempts to 
     evaluate portions of the a software development 

### 2015-02-13 paper_20_sdo.tex
working on availability

@@
 
-    \item[App] (Application) - a software system or a collection of other apps, item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
+    \item[App] (Application) - a software system or a collection of other applications 
+    \item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
     \item[Release] - A collection of projects being put in production on a specified date

### 2015-02-13 paper_40_mpi.tex
working on availability

@@
 
-            Special Note: The System ID for availability does not have to be the same
+            Special Note: The Service ID for availability does not have to be the same
             as the Application ID for quality or any of the other elements.  Some 
             organizations have a one-to-one mapping between Applications being developed
-            and systems being deployed.  Others have more complex sceranios that require
-            multiple applications to be combined to form a system.  Then the availability
+            and services being deployed.  Others have more complex sceranios that require
+            multiple applications to be combined to form a service.  Then the availability
             of the system is tracked.
@@
 
-                    System ID & String  & Required \\
+                    Service ID & String  & Required \\
                     \myrowcolour%
@@
         \subsubsection{SATISFACTION}
-            The satisfaction of the customer is also very important.  
-            The following is an algorithm to calculate the satisfaction of software.
-            \[
-                S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
-            \]
+            The satisfaction of users, customers, and/or business partners is 
+            the third element to be measured.  This element is important because 
+            in an established business, retaining customers is less expensive
+            than actracting new customers \cite{Aulet2013}.  
+            Depending upon the type of SDO,
+            the customers may be internal or external to the organization.
+            If one element of MPI was to be rated as the most important, satisfaction
+            would be it.  Without satisfied customers, the rest of the measures do not matter.
+            For example, having a quality
+            application that is always available does not matter if it is not what the customer
+            wants.  Surveys are used to measure satisfaction for MPI.
 
-            \begin{itemize}
-            \item $a_{i j}$ answer to question $j$ for app $i$
-            \item $m$ number of questions with equal weights
-            \item $n$ number of apps
-            \item $min$ minimum score for a question
-            \item $max$ maximum score for a question
-            \end{itemize}
+            \paragraph{SURVEYS}
+                Write possible survey questions here.
+                and explain the issues with surveys, see qualifier
 
+            The questions  are answered on a scale of 1 to 5 with 1 being 
+            \textbf{Strongly Misses Expectations} and 5 being \textbf{Strongly Exceeds
+            Expectations}.
+
+            \paragraph{SATISFACTION DATA}
                 \begin{longtable}{@{}l rr rr}
-            % pairs: absolute number (percentage)
-
                     \toprule%
@@
                     Question Text & String  & Optional \\
-            Application ID & String & Required \\
+                    Respondent ID & String & Optional \\
                     \myrowcolour%
                     Frequency Date & Date & Required \\
-            Response & Integer between min and max  & Required \\
+                    Response & Integer & Required \\
                     \myrowcolour%
                     Response Date & Date & Optional \\
+                    Application ID & String & Optional \\
 
@@
                 \end{longtable}
+
+            \paragraph{SATISFACTION FORMULA}
+
+            The following is an algorithm to calculate the satisfaction of software.
+            \[
+                S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
+            \]
+
+            \begin{itemize}
+            \item $a_{i j}$ answer to question $j$ for app $i$
+            \item $m$ number of questions with equal weights
+            \item $n$ number of apps
+            \item $min$ minimum score for a question
+            \item $max$ maximum score for a question
+            \end{itemize}
 

### 2015-02-14 paper_10_intro.tex
working on SQL

@@
     data on software development and software analytics are being
-    properly implemented, an obvious next step is the
+    p roperly implemented, an obvious next step is the
     application of gamification to software development. Gamification

### 2015-02-14 appendices.tex
a few more updates to the signature page
capitalize titles and rearrange  sections
most of the lit review is complete
minor changes
working on SQL
updating SQL and formatting

@@
 \newpage
+
 %% numbers following sections with A, B, C..
@@
 APPENDIX\\
-~\\
 \end{center}
@@
 
-\section{Case Study Source Code} 
+\section{CASE STUDY SOURCE CODE} 
 \label{app:case}
 
-\subsection{R Code - Quality} 
+%% set appendix to single space for th source code
+\linespread{1.0}
+
+%% options for lists
+\lstset{ %
+  basicstyle=\small,        % the size of the fonts that are used for the code
+  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
+  breaklines=true,                 % sets automatic line breaking
+  commentstyle=\color{ForestGreen},    % comment style
+  frame=single,                    % adds a frame around the code
+  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
+  keywordstyle=\color{blue},       % keyword style
+  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
+  numbersep=5pt,                   % how far the line-numbers are from the code
+  numberstyle=\tiny\color{gray}, % the style that is used for the line-numbers
+  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
+  showstringspaces=false,          % underline spaces within strings only
+  showtabs=false,                  % show tabs within strings adding particular underscores
+  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
+  tabsize=4,                       % sets default tabsize to 2 spaces
+}
+
+\subsection{SQL CODE - DATA TABLES}
+    \lstinputlisting[language=SQL, label=src:rawSQL]{source/raw_tables.sql}
+
+\subsection{SQL CODE - SCORE TABLES}
+    \lstinputlisting[language=SQL, label=src:scoreSQL]{source/score_tables.sql}
+
+\subsection{R CODE - QUALITY} 
 \scriptsize{
@@
 
+\subsection{}
+
 \end{document}

### 2015-02-16 paper_40_mpi.tex
working on SQL
working to add some survey info

@@
             in an established business, retaining customers is less expensive
-            than actracting new customers \cite{Aulet2013}.  
+            than attracting new customers \cite{Aulet2013}.  
             Depending upon the type of SDO,
-            the customers may be internal or external to the organization.
-            If one element of MPI was to be rated as the most important, satisfaction
-            would be it.  Without satisfied customers, the rest of the measures do not matter.
+            the customers may be internal or external to the organization.  For
+            the remainder of this section, the term customer will be used
+            to represent any person who is responsible for guidance, decision-making
+            or use of the software.  The term customer can refer to a: user, paying or nonpaying
+            customer, internal or external business partner, or any other person deemed influential
+            to the development of the software.
+
+            \textit{If one element of MPI was to be rated as the most important, satisfaction
+            would be it.}  
+            Without satisfied customers, the rest of the measures do not matter.
             For example, having a quality
-            application that is always available does not matter if it is not what the customer
-            wants.  Surveys are used to measure satisfaction for MPI.
+            application that is always available does not matter if the
+            application is not what the customer wants.
 
-            \paragraph{SURVEYS}
-                Write possible survey questions here.
-                and explain the issues with surveys, see qualifier
+            Surveys are used to measure satisfaction for MPI.  A series of questions will
+            be presented to all or a subset of the customers.  Any customer that chooses
+            to respond to the survey is considered a respondent.  A respondent can rate
+            questions with a numerical response where the minimum value indicates maximum
+            disagreement and the maximum value indicates
+            the maximum agreement. Common rating scales would be
+            from 1 to 5 or from 1 to 3.  An example survey can be seen in Table 
+            \ref{tab:samplesurvey}.
+
+            \begin{longtable}{@{}l rr rr}
+                \toprule%
+                 \centering%
+                 {\bfseries ID}
+                 & {\bfseries Question}
+                 & {\bfseries Disagree}
+                 & {\bfseries Neutral}
+                 & {\bfseries Agree}  \\
+
+                \cmidrule[0.4pt](r{0.125em}){1-1}%
+                \cmidrule[0.4pt](lr{0.125em}){2-2}%
+                \cmidrule[0.4pt](l{0.125em}){3-3}%
+                \cmidrule[0.4pt](l{0.125em}){4-4}%
+                \cmidrule[0.4pt](l{0.125em}){5-5}%
+                % \midrule
+                \endhead
+
+                1 & I find the software easy to use.  & & & \\
+                \myrowcolour%
+                2 & I would recommend this software to others. & & & \\
+                3 & The software makes me more productive. & & & \\
+                \myrowcolour%
+                4 & I am happy with this software. & & & \\
+
+                \bottomrule
+
+                \caption{SAMPLE SURVEY FOR SATISFACTION}
+                \label{tab:samplesurvey}
+            \end{longtable}
+
+            \paragraph{ISSUES WITH SURVEYS}
+
+                There are 2 cases of surveys that could be used for satisfaction.
+First is when an SDO is part of a larger organization.
+Typically there are a small number of business partners that help to guide and direct the work performed by the SDO.
+In this case, the business partners are the ones offering survey responses and they should all be willing to respond.
+Thus, those business partners represent the entire population, and the surveys should result in a 100\% response rate which is technically a census.
+         The only bias that will be present here is the bias of the business partners and sampling cannot control for that.
+
+       In the other case, end-users will be surveyed for satisfaction.
+Obviously, the entire population cannot be surveyed, so a probability sample should be randomly created.
+Even then, bias will be present.
+First, not all users will respond.
+This is because survey respondents tend to sit at the extremes of either satisfied or dissatisfied.
+Thus the results will tend to indicate that separation.
+Second, even with probability  sampling it is possible to miss entire groups of population members.
+For example consider a banking application such as a savings account, a survey would most likely be presented online and it would have a coverage bias due the exclusion of savings account holders that do not bank online.
+Third, a selection bias can occur when some members of the population have a higher probability of inclusion in the sampling frame than others.
+One example could be a user with multiple savings accounts.
+The selection bias is typically easy to avoid if the bias is identified.
+Weighting is a common solution here.
 
@@
                     Scheduled Finish Date & Date & Required \\
-                    Actual Start Date & Date  & Required \\
+                    Actual Start Date & Date  & Optional \\
                     \myrowcolour%

### 2015-02-16 paper_80_conclusion.tex
capitalize titles and rearrange  sections
working to add some survey info

@@
 
+\section{FUTURE WORK}
+
+Due to the number of issues with surveys.  One area of future work would be indentifying
+a general set of questions that would best fit MPI.  This set would have to include
+the best number of questions, order of questions and wording of questions.  Therefore,
+any new organization would not have to determine their own survey, but rather just use the
+predetermined set of questions.  It would even be advantageous to build a software system to
+handle the survey distribution and collection.  Ideally, the results would automatically be
+inserted into the appropriate database tables for MPI scoring.
+
 % new section
-\section{Conclusions}
+\section{CONCLUSION}
 

### 2015-02-16 paper_40_mpi.tex
a lot more work on satisfaction

@@
 
-            Surveys are used to measure satisfaction for MPI.  A series of questions will
+            Surveys are used to measure satisfaction for MPI.  A series of statements will
             be presented to all or a subset of the customers.  Any customer that chooses
             to respond to the survey is considered a respondent.  A respondent can rate
-            questions with a numerical response where the minimum value indicates maximum
+            statements based upon a Likert Scale\footnote{"The Likert Scale presents 
+            respondents with a series of (attitude) dimensions, which fall along a
+            continuum." \cite{Cowles2015}} with a numerical response where the 
+            minimum value indicates maximum
             disagreement and the maximum value indicates
@@
                  {\bfseries ID}
-                 & {\bfseries Question}
+                 & {\bfseries Statement}
                  & {\bfseries Disagree}
@@
             \paragraph{ISSUES WITH SURVEYS}
+                Surveys present a number of challenges that need to be presented and briefly
+                discussed.  Here are some of the issues that need to be addressed when
+                using surveys.
 
-                There are 2 cases of surveys that could be used for satisfaction.
-First is when an SDO is part of a larger organization.
-Typically there are a small number of business partners that help to guide and direct the work performed by the SDO.
-In this case, the business partners are the ones offering survey responses and they should all be willing to respond.
-Thus, those business partners represent the entire population, and the surveys should result in a 100\% response rate which is technically a census.
-         The only bias that will be present here is the bias of the business partners and sampling cannot control for that.
+                \begin{description}
+                \item[Text] \hfill \\
+                    The specific text used in the questions or statments
+                    is very important.  The text cannot be too vague.  Also, the text
+                    must be clear enough to eliminate misinterpretation. Survey
+                    questions must be complete and not include gaps.  For example, if
+                    an age range is presented, it must include all possible ages.  These
+                    are just some of the difficulties with getting the text correct
+                    in surveys. 
+                \item[Number and Ordering] \hfill \\
+                    The number of questions is important.  Too many questions and the 
+                    respondents will lose interest and begin responding without the
+                    adequate attention needed.  Plus, if the survey is too long there
+                    is the risk of quitting before completion.  A short survey might
+                    not cover the adequate amount of material.  Both short and long
+                    surveys run the risk of providing inaccurate responses.  After
+                    determining the best number of questions, the ordering of the questions
+                    is important.  Previous survey questions can have an unintended 
+                    impact on responses.  Thus, the ordering of questions needs to be
+                    addressed. 
+                \item[Sampling] \hfill \\
+                    Next is the issue of sampling.  Not every customer can be surveyed, so 
+                    sample sets os customers need to be presented with a survery.  
+                    In the case of MPI, there are 2 possible scenarios for sampling.  
+                    \begin{description}
+                    \item[First]
+                    When an SDO is part of a larger organization, there typically is
+                    a small number of business partners that help to guide and 
+                    direct the work performed by the SDO.  In this case, the business 
+                    partners might be the the ones offering survey responses and they 
+                    should all be willing to respond.  Thus, those business partners 
+                    represent the entire population, and the surveys should result in 
+                    a 100\% response rate which is technically a census.  
+                    The only bias that will be present here is the bias of the business 
+                    partners and sampling cannot control for that.
 
-       In the other case, end-users will be surveyed for satisfaction.
-Obviously, the entire population cannot be surveyed, so a probability sample should be randomly created.
-Even then, bias will be present.
-First, not all users will respond.
-This is because survey respondents tend to sit at the extremes of either satisfied or dissatisfied.
-Thus the results will tend to indicate that separation.
-Second, even with probability  sampling it is possible to miss entire groups of population members.
-For example consider a banking application such as a savings account, a survey would most likely be presented online and it would have a coverage bias due the exclusion of savings account holders that do not bank online.
-Third, a selection bias can occur when some members of the population have a higher probability of inclusion in the sampling frame than others.
-One example could be a user with multiple savings accounts.
-The selection bias is typically easy to avoid if the bias is identified.
-Weighting is a common solution here.
+                    \item[Second] End-users will be surveyed for satisfaction. Obviously, the 
+                    entire population cannot be surveyed, so a probability sample should 
+                    be randomly created. Even then, bias will be present.  
+                        \begin{itemize}
+                            \item Not all users will respond.  This is because survey 
+                                respondents tend to sit at the extremes of either 
+                                satisfied or dissatisfied.  Thus the results will tend 
+                                to indicate that separation. 
+                            \item  Even with probability sampling it is possible to miss 
+                                entire groups of population members. For example consider a 
+                                banking application such as a savings account, a survey would 
+                                most likely be presented online and it would have a coverage 
+                                bias due the exclusion of savings account holders that 
+                                do not bank online.
+                            \item A selection bias can occur when some members of the 
+                                population have a higher probability of inclusion in 
+                                the sampling frame than others.  One example could be 
+                                a user with multiple savings accounts.  The selection 
+                                bias is typically easy to avoid if the bias is 
+                                identified.  Weighting is a common solution for selection bias. 
+                        \end{itemize}
 
-            The questions  are answered on a scale of 1 to 5 with 1 being 
-            \textbf{Strongly Misses Expectations} and 5 being \textbf{Strongly Exceeds
-            Expectations}.
+                    \end{description}
+
+                \end{description}
+
+            For more on creating appropriate surveys, see \cite{Snijkers2013} by Snijkers,
+            Haraldsen, Jones, and Willimack. In the book, Snijkers et al. present a framework
+            named generic statistical business process model (GSBPM) for conducting surveys
+            in a business or organizational setting.  GSBPM covers the issues above as well
+            as a few more issues such as response storage and risks.  Also, Cowles and Nelson
+            provide another good resource for preparing and conducting surveys 
+            \cite{Cowles2015}.  They even include an entire chapters on both writing 
+            survey questions and survey errors.
 
             \paragraph{SATISFACTION DATA}
+                Once the surveys have been distributed and the results collected, Table
+                \ref{tab:satisfactiondata} displays the data that needs to be collected 
+                in order to calculate the satisfaction element score for MPI.
                 \begin{longtable}{@{}l rr rr}
@@
                     \caption{SATISFACTION DATA NEEDED FOR MPI}
-                    \label{tab:satisfaction}
+                    \label{tab:satisfactiondata}
                 \end{longtable}
@@
             \paragraph{SATISFACTION FORMULA}
+                After collecting the necessary survey data from Table \ref{tab:satisfactiondata},
+                calculating the score is rather straight forward.
+                The scores for each question are averaged and then those
+                values are averaged together.  If some survey questions
+                are more important than others, the formula could be
+                easily modified to include weighting.
 
-            The following is an algorithm to calculate the satisfaction of software.
+                Mathematically, the following is an algorithm to calculate the 
+                satisfaction element score
+                of MPI.
                 \[

### 2015-02-17 paper_40_mpi.tex
working on the end of chapter 4

@@
         \subsubsection{OVERALL MPI SCORE}
-            One complete overall score cannot be successful without including 
-            information from various aspects of the software development 
-            organization.  Therefore, the previous results
-            are combined to provide one overall score.
+            In order to accomplish the single number score that MPI requires,
+            the 5 element scores must be combined. The combination of the scores
+            is a weighted average.  The weights can be set based upon the 
+            priority of the SDO.  Thus, the overall MPI score is calculated as below.
+
             \[
@@
             \]
+
+    \subsection{CORRELATIONS IN MPI}
+        It is possible that 2 or more of the 5 elements of MPI will be correlated.  This means that
+        one of the elements can be predicted based upon the values of the other elements.  Although
+        it is possible for correlation to occur between any of the elements, the satisfaction element
+        is an obvious element which deserves attention due to the human involvement of the surveys. 
+        If a schedule is missed or an important requirement dropped, that could have a large negative
+        effect on the satisfaction surveys.  The same could be said of quality or availability with regard to 
+        the satisfaction.  However, satisfaction is not the only potentially correlated element.  It is also
+        possible that a decrease in quality could result in unexpected downtime which could have a
+        negative result on availability.  Similarly, if requirements are added, it is possible the schedule
+        will be negatively impacted.  Also, if requirements are dropped, the quality might suffer due
+        to missing functionality.
+
+        It is impossible to know which or if correlations will always exist.  Thus it is necessary to
+        check for correlations after determining element and overall MPI scores.  
+        If correlation is determined, the element should not be dropped but rather be weighted less than
+        the other elements.  This technique keeps the most data available but lessens the importance of
+        the correlated element.
 
@@
 
-    \subsection{IMPORTANCE OF MPI}
+    \subsection{MPI COMPARED}
+
+        \subsubsection{MPI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
 
             Earlier, in the introduction section \ref{subsub:softwareanalytics}, 3 main focus 
-        areas and 3 important questions for software
+            areas  for software
             analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how MPI addresses
             each focus area.  
-        As can be seen, MPI clearly addresses the 3 main focus areas of software analytics.  MPI does provide
+            As can be seen, MPI clearly addresses the 3 main focus areas of software analytics.  MPI does not provide
             any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
@@
             \begin{longtable}{p{3cm}p{11cm}}
-            % pairs: absolute number (percentage)
-
                 \toprule%
@@
             \end{longtable}
+
+        \subsubsection{MPI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
+            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
+            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
+            and a description of how MPI addresses that specific question.  It is clear
+            that MPI addresses the questions.  MPI is a beneficial technique of software
+            analytics when applied to software development organizations.
 

### 2015-02-18 paper_40_mpi.tex
minor updates to the satisfaction formula, broke it into 2 formulas

@@
 
-                Mathematically, the following is an algorithm to calculate the 
-                satisfaction element score
-                of MPI.
+                First the score for each question needs to be calculated.
+
                 \[
-                    S_2 = \frac{\sum^n_{i=1}\left( \frac{\sum^m_{j=1}a_{ij}- \frac{min + max}{2}}{m}  \right)}{n}
+                    S_{3_i} = \sum^n_{i=1}\left( k \times \frac{ \sum^m_{j=1}a_{ij}-\frac{min + max}{2}}{m} \right)
                 \]
@@
                 \begin{itemize}
-                    \item $a_{i j}$ answer to question $j$ for app $i$
-                    \item $m$ number of questions with equal weights
-                    \item $n$ number of apps
+                    \item $a_{ij}$ answer to question $i$ for respondent $j$
+                    \item $n$ number of questions
+                    \item $m$ number of respondents
                     \item $min$ minimum score for a question
@@
                 \end{itemize}
+
+                Then the satisfaction score is calculated as below.  Use a weighted average
+                to combine the question scores.
+
+                \[
+                    S_{3} = \sum\limits^n_{i=1} w'_i S_{3_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
+                \]
 
@@
             not improve.
-
-            The score is based upon the historical deviance of estimates for
-            projects.  The top score of
-            100 will be obtained when the schedule is met exactly.  A historical average 
-            of deviance of schedule will be used to determine an appropriate range
-            of schedule adherence.  A schedule that occurs within that range will be awarded
-            a score of 0 or above, with less deviance being awarded more points.  Schedules
-            that do not fall within the range of deviance will be awarded negative scores, 
-            with a greater deviance resulting in a lower score all the way to -100 which means
-            the package took twice as long as expected or more.
-            For example, a package that takes more than twice as long to deliver than
-            estimated will receive a score of -100.
 

### 2015-02-18 paper_50_sdlc-ae.tex
adding raw tables diagram

--- 2015-02-04 paper_50_sdlc-ae.tex
@@
    All the data necessary to compute MPI needs to be stored in a database.  This section will 
-   layout the structure of tables and relationships necessary to the store all the data
-   within a relational database such as MySQL or PostgreSQL.  Eventually,
-   database diagrams and SQL scripts will be provided in the section.
+   lay out the structure of tables and relationships necessary to the store all the data
+   within a relational database.
+
+   \subsubsection{TABLES FOR RAW MPI DATA}
+
+        The first set of tables that need to be created are tables
+        to store the raw data that is collected.  These tables
+        will line up with the necessary data for each of the 5 elements
+        of MPI.  Figure \ref{fig:raw} provides a visual description
+        of the tables that are needed.  The tables have no relationship
+        with each other since they are raw data.  The primary goal of
+        these tables is to store the raw data in a single database. The
+        5 table names are:
+        \begin{enumerate}
+            \item QUALITY\_RAW
+            \item AVAILABILITY\_RAW
+            \item SATISFACTION\_RAW
+            \item SCHEDULE\_RAW
+            \item REQUIREMENTS\_RAW
+        \end{enumerate}
+        Notice these table names match with the 5 elements of MPI.
+
+       \begin{figure}[ht]
+            \centering
+            \includegraphics[scale=.55]{images/raw_tables.png}
+            \caption{TABLES FOR RAW MPI DATA}
+            \label{fig:raw}
+        \end{figure}%
+
+        Appendix \ref{src:rawSQL} provides the necessary SQL statements to create the 
+        database tables for storing the raw MPI data.  The SQL is written for an Oracle
+        database, but the scripts can be modified to work with another database
+        such as: PostgreSQL, SQL Server, or MySQL.
+
+    \subsubsection{INTERMEDIATE SCORE TABLES FOR MPI}
+
+        Appendix \ref{src:scoreSQL} provides the necessary SQL statements to create the 
+        database tables for storing the intermediate MPI scores.
+
+    \subsubsection{FINAL SCORE TABLES FOR MPI}
+
+        Appendix \ref{src:overallscoreSQL} provides the necessary SQL statements to create the 
+        database tables for storing the final scores for each element and the final 
+        overall MPI scores for each time frequency.
 

### 2015-02-19 paper_40_mpi.tex
working on schedule

@@
 
+            The MPI schedule score provides a numeric value to indicate the amount 
+            schedules are missed or exceeded.  The score provides a cumulative measure
+            of the performance as compared to other months.
+            The score is based upon the historical deviance of estimates for
+            projects.  Projects completing on time will be given a score of 0.
+            Projects finishing early will be rewarded with positive scores increasing toward
+            $k$. Alternatively, 
+            late projects will be given negative scores that approach $-k$ as the projects
+            become more late.
+
             \paragraph{SCHEDULE DATA}
+
+                In order to calculate the schedule score, certain dates
+                need to be present. Table \ref{tab:scheduledata} outlines
+                the necessary data for schedules.  One date is considered
+                optional as it is not used in the MPI calculation, but it
+                is an important date that could be useful for future
+                enhancements.
 
@@
                     \caption{SCHEDULE DATA NEEDED FOR MPI}
-                    \label{tab:sched}
+                    \label{tab:scheduledata}
                 \end{longtable}
@@
             \paragraph{SCHEDULE FORMULA}
-
-                The formula for schedule is based upon past performance.  Of the 422 projects
-                scheduled since June 2013, only 45 projects had an estimated start date, estimated
-                finish date and an actual finish date.  Of those 45 projects; 20 finished exactly on time,
-                9 finished early and 16 finished late.
 

### 2015-02-20 paper_40_mpi.tex
working on schedule

@@
                 is an important date that could be useful for future
-                enhancements.
+                enhancements to MPI.
 
@@
             \paragraph{SCHEDULE FORMULA}
+                Schedule has a clear date for finishing on-time, however
+                there are not clear bounds as to how early or late a project
+                can be delivered.  Thus, the formula for schedule is more involved
+                than availability or satisfaction.  It requires some analysis
+                of the historical data.  The first step of the formula is
+                determining how often projects are early or late, and by how
+                much a project is early or late.  This can be accomplished
+                by looking at the distribution of the data.  Specifically,
+                look at what percentage of the entire project duration the
+                schedule was missed.
+
+            \paragraph{ALTERNATE APPROACH}
+                The best possible score should be achieved
+                when meeting the estimated date exactly.  The maximum score
+                should come from the best estimate.  Then given historical
+                release data, it is easy to determine an 
+                average $\Delta$ between the actual and the estimated.  
+                Finishing a project within that $\Delta$ should result 
+                in a positive score.  Outside the $\Delta$ results in
+                negative scores.  For example, a project releasing
+                one day early or one day late would receive the same score
+                because in both cases the estimate was missed by one day.
 
@@
                 \end{itemize}
-
-            \paragraph{ALTERNATE APPROACH}
-                The best possible score should be achieved
-                when meeting the estimated date exactly.  The maximum score
-                should come from the best estimate.  Then given historical
-                release data, it is easy to determine an 
-                average $\Delta$ between the actual and the estimated.  
-                Finishing a project within that $\Delta$ should result 
-                in a positive score.  Outside the $\Delta$ results in
-                negative scores.  For example, a project releasing
-                one day early or one day late would receive the same score
-                because in both cases the estimate was missed by one day.
 

### 2015-02-21 paper_40_mpi.tex
more schedule work

@@
 
-                    Application ID & String  & Required \\
+                    Project ID & String  & Required \\
                     \myrowcolour%
@@
                 schedule was missed.
+
+                \begin{displaymath}
+                    \Delta_i = \frac{F_{a_i} - F_{s_i}}{ F_{s_i} - B_{s_i} + 1}
+                \end{displaymath}
+                where
+                \begin{itemize}
+                    \item $F_{a_i}$ the actual finish date of project $i$
+                    \item $F_{s_i}$ the scheduled finish date of project $i$
+                    \item $B_{s_i}$ the scheduled beginning date of project $i$
+                    \item $\Delta_i$ the percent the schedule was missed for project $i$
+                \end{itemize}
+
+                Once all the $\Delta_i$'s have been determined, a distribution must
+                be fit to the data.
 

### 2015-02-21 appendices.tex
more SQL updates, new sql file
reworked the end of chapter 2 moved stuff to Appendix A

@@
 
-%%\section{Example Graphics}
+\section{Detailed Steps of the SDLC}
+\label{app:detailedSDLC}
 
-%%\begin{figure}[h!]
-%%\scriptsize
-%%$$
-%%\begin{array}{cc}
-%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
-%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
-%%(a) & (b) \\
-%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
-%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
-%%(c) & (d) \\
-%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png} &
-%%\includegraphics[width=0.2\textwidth]{sdlc-ae.png}\\
-%%(e) & (f) \\
-%%\end{array}
-%%$$
-%%\caption{A graphic in the appendix}
-%%\end{figure}
+    Often times the SDLC contains more than the 5 basic steps of requirements, design,
+    implementation, testing, and  deployment/maintenance.  Those are the high-level
+    phases, but many steps are required to complete each phase.  The following list
+    provides a more detailed version of what needs to be accomplished in the 
+    entire life cycle of software development. These steps do not need 
+    to occur in a sequential fashion.
 
-%% Prints all figures and tables on the page and begins a new page
-%% http://www.astro.rug.nl/~kuijken/latex.html
-%%\clearpage
+    \begin{easylist}[itemize]
+        & Identify the Work/Task/Project
+        && Get Initial Idea 
+        && Obtain Details
+        & Estimate
+        && Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
+        && Obtain Approval 
+        && Quit or Go Forward
+        & Document Requirements
+        && Identify the Requirements
+        && Detail the Requirements
+        & Design The Software
+        && Find System Integrations
+        && Identify Functional Specs
+        && Detail the Functional Specs
+        & Development of all the tasks in Design and Requirements
+        && Identify the Coding Tasks
+        && Write the Code/Develop the solution
+        && Write the Unit Tests
+        & Test
+        && Create Test Plans and Cases
+        && Run Test Plans and Cases
+        & Deployment
+        && Create Deployment Steps
+        && Run Deployment Steps
+        & Maintenance
+        && Capture Bugs
+        && Survey Users
+        & Start Again
+    \end{easylist}
 
@@
     \lstinputlisting[language=SQL, label=src:scoreSQL]{source/score_tables.sql}
+
+\subsection{SQL CODE - FINAL SCORE TABLES}
+    \lstinputlisting[language=SQL, label=src:overallscoreSQL]{source/overall_score_tables.sql}
 

### 2015-02-21 paper_10_intro.tex
reworked the end of chapter 2 moved stuff to Appendix A

@@
     software development.
+
+\subsection{TERMINOLOGY}
+    Like any other business domain, the software engineering field has number
+    of specific terms.  Many of these terms will be used throughout the remainder
+    of the document, so definitions are provided.
+
+    \begin{description}
+
+        \item[Application] - a software system or a collection of other applications 
+        \item[Release] - A collection of projects being put in production on a specified date
+        \item[Project] - A body of work involving zero or more applications in preparation for a release
+        \item[SIT]   (Systems Integration Testing) - The initial step of testing
+            after the development phase of the SDLC.  This is typically 
+            performed by members of the SDO.  It is validation that all the
+            software components function together as expected.
+        \item[UAT]   (User Acceptance Testing) - The final step of testing
+            when a select few members of the user group are invited to
+            validate the software system. Once validation has occured for
+            UAT, the software system is ready to proceed to production
+        \item[PROD]  (Production) - The software has been released to the final audience.
+        \item[defect] ``A software defect is a bug or error that causes
+                    software to either stop operating or to produce
+                    invalid or unacceptable results'' as quoted from Capers Jones
+                \cite{Jones2009}.  It is important to mention that even though defects are typically 
+                found in the computer code, a defect should not be isolated to just code.   
+                A poorly written requirement or missed test cases can 
+                both be considered a defect.  Other common names for a defect 
+                are: bug, error, fault, or ticket.
+    \end{description}
 

### 2015-02-21 paper_20_sdo.tex
reworked the end of chapter 2 moved stuff to Appendix A

--- 2015-02-11 paper_20_sdo.tex
@@
         Even with the large number of SDLC models currently being used by different SDOs,
-        many ommonalities exist among the models.  The 
+        many commonalities exist among the models.  The 
         commonalities can be tied back to the steps of waterfall.  All of the models
@@
         model spends less time in each phase.  The agile models produce less
-        documentation and focus more on the Implemenation phase. Here are
+        documentation and focus more on the implementation phase. Here are
         the common phases in nearly all SDLC models:
@@
                 most expensive and lengthy phase of the software
-                development lifecycle.
+                development life cycle.
         \end{description}
 
-The WHAT of SDLC - These are the steps of SDLC that need to be completed for each project.
-
-\begin{easylist}[itemize]
-    & Identify the Work/Task/Project
-    && Get Initial Idea 
-    && Obtain Details
-    & Estimate
-    && Create an Estimate (What is included? What is the output? days/dollars/hours/reqs)
-    &&Obtain Approval 
-    && Quit or Go Forward
-    & Document Requirements
-    && Identify the Requirements
-    && Detail the Requirements
-    & Design The Software
-    && Find System Integrations
-    && Identify Functional Specs
-    && Detail the Functional Specs
-    & Development of all the tasks in Design and Requirements
-    && Identify the Coding Tasks
-    && Write the Code/Develop the solution
-    && Write the Unit Tests
-    & Test
-    && Create Test Plans and Cases
-    && Run Test Plans and Cases
-    & Deployment
-    && Create Deployment Steps
-    && Run Deployment Steps
-    & Maintenance
-    && Capture Bugs
-    && Survey Users
-\end{easylist}
+        These 5 steps cannot cover everything that needs to be accomplished
+        during a project.  They just provide of rough guideline of what needs
+        to be completed in order to ensure a more successful software release.
+        Appendix \ref{app:detailedSDLC} contains a more detailed list of the
+        tasks necessary to complete the software life cycle.
 
@@
 
-\subsection{TERMINOLOGY}
-
-\begin{description}
-
-    \item[App] (Application) - a software system or a collection of other apps, item[Project] - A body of work involving zero or more apps in preparation for a release, infrastructure upgrades can be a project but no specific app is involved
-    \item[Release] - A collection of projects being put in production on a specified date
-    \item[SIT]   (Systems Integration Testing) - The initial step of testing
-        after the development phase of the SDLC.  This is typically 
-        performed by members of the SDO.  It is validation that all the
-        software components function together as expected.
-    \item[UAT]   (User Acceptance Testing) - The final step of testing
-        when a select few members of the user group are invited to
-        validate the software system. Once validation has occured for
-        UAT, the software system is ready to proceed to production
-    \item[PROD]  (Production) - The software has been released to the final audience.
-    \item[defect] ``A software defect is a bug or error that causes
-                software to either stop operating or to produce
-                invalid or unacceptable results'' as quoted from
-            \cite{Jones2009}.  It is important to mention that even though defects are typically 
-            found in the computer code, a defect should not be isolated to just code.   A poorly written requirement or missed test cases can 
-            both be considered a defect.  Other common names for a defect are: bug, error, fault, or ticket.
-
-              Also in here is the 4 severity levels.  Also, current defect removal is only about 85\% and this value should be increased to about 95\%. 
-\end{description}
-
-Check these book \cite{Jones2009, Jones1996, Lee2003}.
-
 \end{document}

### 2015-02-21 paper_40_mpi.tex
reworked the end of chapter 2 moved stuff to Appendix A

@@
                 Once all the $\Delta_i$'s have been determined, a distribution must
-                be fit to the data.
+                be fit to the data.  The exact distribution is needed for the Cumulative
+                Distribution Function (C.D.F.).  The C.D.F. will be transformed to create
+                the schedule score for MPI. Since all C.D.F. functions fall within the
+                range $[0,1]$, the function needs to be shifted to center around 0, and then
+                doubled to fill the desired range of $[-1,1]$. Thus the MPI schedule score
+                for each project becomes the following.
+
+                \[
+                    S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
+                \]
+
+                Then the overall schedule score is calculated as below.
+
+                \[
+                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
+                \]
 
             \paragraph{ALTERNATE APPROACH}
+                An alternative approach for scoring schedule goes as follows.
                 The best possible score should be achieved
@@
                      \begin{array}{lr}
-                        \text{where } \Delta_i \geq 1 & : -1 \times 100 \\
-                       \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \times 100  \\
-                       \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \times 100
+                        \text{where } \Delta_i \geq 1 & : -1 \times k \\
+                       \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \times k  \\
+                       \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \times k
                      \end{array}
@@
                 \[
-                    S_{4} = \frac{\sum^n_{i=1} S_{4_i}}{n} \text{   , average the schedule scores}
+                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1 \text{   , average the schedule scores}
                 \]
+                where
                 \begin{itemize}
                     \item $n$ is the number of projects
-                    \item $F_{a_i}$ the actual finish date of project i
-                    \item $F_{s_i}$ the scheduled finish date of project i
-                    \item $B_{s_i}$ the scheduled beginning date of project i
+                    \item $F_{a_i}$ the actual finish date of project $i$
+                    \item $F_{s_i}$ the scheduled finish date of project $i$
+                    \item $B_{s_i}$ the scheduled beginning date of project $i$
                     \item $\Delta_i$ the percent the schedule was missed
-                    \item $\bar{\Delta}$ is the average percent RT misses schedules, $\approx 26$
+                    \item $\bar{\Delta}$ is the average percent schedules are missed
                     \item $S_{4_i}$ is the schedule score for project $i$
                 \end{itemize}
-
-%The score can be accomplished with the following 
-%algorithm.
-%\[
-%    S_4 = \frac{\sum^n_{i=1} \left( C_{a_i} - C_{e_i} \right)}{n}
-%\]
-%\begin{itemize}
-%\item $C_a$ actual number of days for application $i$
-%\item $C_e$ estimated number of days for application $i$
-%\end{itemize}
+                Again, this was just an alternate approach to scoring schedule.  It will not be used
+                in the case studies.
 
         \subsubsection{REQUIREMENTS}
+            The requirements of a software development organization are important.
 

### 2015-02-22 appendices.tex
switched references to biblatex

@@
 
-\subsection{}
+\section{ADDITIONAL SDLC DATA NEEDS}
+
+    \subsection{ESTIMATION}
+
+    \begin{itemize}
+    \item Change to Database Structure  
+    \item Modify Database Data    
+    \item Create a New Database, number of new databases  
+    \item Server Configuration Changes Required   
+    \item New Servers Required   
+    \item Number of Team Members Involved  
+    \item Number of (sub)Systems Involved  
+    \item Estimation Date
+    \item Number of Days Allowed
+    \item List of Other Attributes
+    \item Number of Screens Involved 
+    \item Actual Value (hours, days, dollars) 
+    \end{itemize}
+
+    \begin{description}
+        \item[Estimated Dev Hours] - 
+            The number of development hours estimated for a 
+            project, this is just developer hours
+        \item[Estimated Doc Hours] - 
+            The number of documentation hours estimated for a project
+        \item[Estimated Test Hours] - 
+            The number of testing hours estimated for a project
+        \item[Estimated Deployment Hours] - 
+            The number of estimated hours required to 
+            deploy the project
+    \end{description}
+
+    \subsection{REQUIREMENTS}
+    List of: 
+    \begin{description}
+      \item[Title] 
+      \item[Descrition]
+      \item[author]
+      \item[projectID]
+      \item[date]
+      \item[Comments] list of \\
+      \begin{description}
+        \item[date]
+        \item[comment Text]
+        \item[author]
+      \end{description}
+    \end{description}
+
+    \subsection{MAINTENANCE (DEFECTS)}
+    List of:
+    \begin{description}
+      \item[Project] 
+      \item[Release]
+      \item[description]
+      \item[date Entered]
+      \item[Date fixed]
+      \item[Comments] list of \\
+      \begin{description}
+        \item[date]
+        \item[comment Text]
+        \item[author]
+      \end{description}
+    \end{description}
+
+    \subsection{TESTING}
+
+    List of:
+    \begin{description}
+      \item[Project] 
+      \item[Release]
+      \item[title]
+      \item[description]
+      \item[author]
+      \item[Date Started]
+      \item[Date Executed]
+      \item[Status (Pending, pass, fail)]
+      \item[Comments] list of \\
+      \begin{description}
+        \item[date]
+        \item[comment Text]
+        \item[author]
+      \end{description}
+    \end{description}
+
+    \subsection{DEVELOPMENT}
+
+    List of Coding Tasks:
+    \begin{description}
+      \item[Project] 
+      \item[Release]
+      \item[List of Files]
+      \item[author]
+      \item[Date Started]
+      \item[Completion Date]
+      \item[Number of Unit Tests]
+      \item[Lines of Code]
+      \item[Others] See \cite{Jones2009, Jones2012, Rubin2007, Snipes2013}
+    \end{description}
+
+    \subsection{IMPLEMENTATION}
+
+    List of:
+    \begin{description}
+      \item[Project] 
+      \item[Release]
+      \item[date Entered]
+      \item[Date Scheduled]
+      \item[Date Executed]
+      \item[Ordering/Prerequisites]
+      \item[Comments] list of \\
+      \begin{description}
+        \item[date]
+        \item[comment Text]
+        \item[author]
+      \end{description}
+    \end{description}
 

### 2015-02-22 paper_40_mpi.tex
switched references to biblatex

@@
                 Once all the $\Delta_i$'s have been determined, a distribution must
-                be fit to the data.  The exact distribution is needed for the Cumulative
-                Distribution Function (C.D.F.).  The C.D.F. will be transformed to create
+                be fit to the data. There are several techniques for testing the fit
+                of a distribution: histograms, chi-square, Kolmogorov-Smirnov, Shapiro-Wilk,
+                or Anderson-Darling \cite{Damodaran2015,Kutner2003}.
+                The distribution is needed for the Cumulative
+                Distribution Function (C.D.F.). The C.D.F. maps the values
+                to a percentile rank within the distribution \cite{Downey2011}.
+                The C.D.F. will be transformed to create
                 the schedule score for MPI. Since all C.D.F. functions fall within the

### 2015-02-22 paper_50_sdlc-ae.tex
switched references to biblatex

@@
 
-    \subsection{ESTIMATION}
-
-    \begin{itemize}
-    \item Change to Database Structure  
-    \item Modify Database Data    
-    \item Create a New Database, number of new databases  
-    \item Server Configuration Changes Required   
-    \item New Servers Required   
-    \item Number of Team Members Involved  
-    \item Number of (sub)Systems Involved  
-    \item Estimation Date
-    \item Number of Days Allowed
-    \item List of Other Attributes
-    \item Number of Screens Involved 
-    \item Actual Value (hours, days, dollars) 
-    \end{itemize}
-
-    Estimated Dev Hours - The number of development hours estimated for a project, this is just developer hours
-    Estimated Doc Hours - The number of documentation hours estimated for a project
-    Estimated Test Hours - The number of testing hours estimated for a project
-    Estimated Deployment Hours - The number of estimated hours required to deploy the project
-
-    \subsection{REQUIREMENTS}
-    List of: 
-    \begin{description}
-      \item[Title] 
-      \item[Descrition]
-      \item[author]
-      \item[projectID]
-      \item[date]
-      \item[Comments] list of \\
-      \begin{description}
-        \item[date]
-        \item[comment Text]
-        \item[author]
-      \end{description}
-    \end{description}
-
-    \subsection{MAINTENANCE (DEFECTS)}
-    List of:
-    \begin{description}
-      \item[Project] 
-      \item[Release]
-      \item[description]
-      \item[date Entered]
-      \item[Date fixed]
-      \item[Comments] list of \\
-      \begin{description}
-        \item[date]
-        \item[comment Text]
-        \item[author]
-      \end{description}
-    \end{description}
-
-    \subsection{TESTING}
-
-    List of:
-    \begin{description}
-      \item[Project] 
-      \item[Release]
-      \item[title]
-      \item[description]
-      \item[author]
-      \item[Date Started]
-      \item[Date Executed]
-      \item[Status (Pending, pass, fail)]
-      \item[Comments] list of \\
-      \begin{description}
-        \item[date]
-        \item[comment Text]
-        \item[author]
-      \end{description}
-    \end{description}
-
-    \subsection{DEVELOPMENT}
-
-    List of Coding Tasks:
-    \begin{description}
-      \item[Project] 
-      \item[Release]
-      \item[List of Files]
-      \item[author]
-      \item[Date Started]
-      \item[Completion Date]
-      \item[Number of Unit Tests]
-      \item[Lines of Code]
-      \item[Others] See \cite{Jones2009, Jones2012, Rubin2007, Snipes2013}
-    \end{description}
-
-    \subsection{IMPLEMENTATION}
-
-    List of:
-    \begin{description}
-      \item[Project] 
-      \item[Release]
-      \item[date Entered]
-      \item[Date Scheduled]
-      \item[Date Executed]
-      \item[Ordering/Prerequisites]
-      \item[Comments] list of \\
-      \begin{description}
-        \item[date]
-        \item[comment Text]
-        \item[author]
-      \end{description}
-    \end{description}
-
 \end{document}

### 2015-02-23 paper_30_measure.tex
working on the quality element
reworked the end of chapter 2 moved stuff to Appendix A
working on Chapter 3

@@
 
-\section{MEASURING A SDO}
+\section{EVALUATING AN SDO}
 
-Anything can be measured \cite{Hubbard2010}.  An SDO
-how numerous metrics.
+    Anything can be measured \cite{Hubbard2010}.  Thus, an SDO can be 
+    measured.  Proper measurement is crucial for improvement because
+    without a starting point it is impossible to determine progress.
+    Also, consistent reporting is essential for 
+    tracking historical performance.  Many methods are used
+    to measure and evaluate SDOs.  Some of the common ones
+    will be explained in this section.
 
-A metric can be defined as the science of indirect measurement.
+    \subsection{METRICS}
+        A \textit{metric} can be defined as the science of indirect measurement. Metrics
+        are very common in the measurement of SDOs.  
         The following are some examples of metrics that can be collected 
-    about source code:
+        for an SDO. 
         \begin{itemize}
@@
                 code adheres to specified set of rules. Common 
-        examples are PMD\footnote{PMD is a source code analysis product.  It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
+                examples are PMD\footnote{PMD is a source code analysis product.  
+                It is not an acronym.} and FindBugs$^{TM}$ \cite{PMD, Findbugs}.
         \end{itemize}
-
-Data Driven Software Engineering not Data Driven Software Development
+        All these metrics are beneficial, but none of them tell the story of the entire
+        SDO.  Most of the metrics, as seen in the list above, around an SDO focus on 
+        the source code and development phase. 
+        Since metrics are indirect, it can be very difficult match SDO performance with
+        a metric or series of metrics.  Metrics are great for tracking, but decision making
+        based upon metrics is difficult.
 
@@
         be difficult.  Software development organizations
+        are no exception. 
         The differences between the indicators will be explored and
         possible measures for each indicator in an SDO will be
-presented.  The 4 different types of indicators are:
-\begin{description}
-  \item[RI (Result Indicator)] - what has been done
-  \item[KRI (Key Result Indicator)] - how you have done
-  \item[PI (Performance Indicator)] - what to do
-  \item[KPI (Key Performance Indicator)] - what to do to dramatically increase performance
-\end{description}
+        presented.  Indicators are sometimes refered to as 
+        performance measures \cite{parmenter2010}.  The four
+        types of indicators important to an SDO are shown
+        in Table \ref{tab:indicators}.
+
+        \begin{longtable}{@{}l l}
+                \toprule%
+                 \centering%
+                 {\bfseries Performance Measure}
+                 & {\bfseries Description}\\
+
+                \cmidrule[0.4pt](r{0.125em}){1-1}%
+                \cmidrule[0.4pt](lr{0.125em}){2-2}%
+                % \midrule
+                \endhead
+
+                RI (Result Indicator) & What has been done?   \\
+                \myrowcolour%
+                KRI (Key Result Indicator) & How you have done? \\
+                PI (Performance Indicator) & What to do? \\
+                \myrowcolour%
+                KPI (Key Performance Indicator) & How to dramatically increase performance? \\
+
+                \bottomrule
+
+                \caption{SOFTWARE DEFECT SEVERITY LEVELS}
+                \label{tab:indicators}
+            \end{longtable}
 
         More information on the indicators can be found
-in chapter 1 of \cite{parmenter2010}
+        in chapter 1 of 
         as well as \cite{florac1999,kaplan1992}.
@@
         \subsubsection{KEY PERFORMANCE INDICATORS FOR SDO}
+
+        Antolic in \cite{Antolic2008} demostrates some ways to measure KPIs for the  software development process.
 
@@
 
-Antolic in \cite{Antolic2008} demostrates some ways to measure KPIs for the  software development process.
-
     \subsection{MEASURING OTHER ASPECTS OF AN SDO}
@@
         including: deploying software, installing server hardware/software,
-writing documentation, surveying users, and other things.
+        writing documentation, surveying users, research, innovation,
+        education and other common business duties.
 
@@
 
+making decisions based upon historical data.
+
+Data Driven Software Engineering not Data Driven Software Development
+
 \end{document}

### 2015-02-23 paper_40_mpi.tex
working on Chapter 3

@@
             created. One of the key indicators of software quality 
-            is defects.  Thus, it is important
+            is defects.  It is important
             to measure the number of defects associated with a software 
-            release.  The following is the necessary data to collect
-            and an algorithm to calculate
-            the quality score of software being released.
+            release because industry-wide the current defect removal rate is only 
+            about 85\% and this value should be increased to 
+            about 95\% for high quality software \cite{Jones2009}. 
+            Organizations are leaving too many defects unfixed.  If organizations
+            could lower the number of defects, then not as many defects would
+            need to be fixed, which in turn would raise the defect removal rate.
+
+            Another aspect of defects is severity levels.  A severity level indicates
+            the importance of a defect that has been discovered.  Although an
+            organization can choose whatever severity levels they choose, it is
+            common practice to use 5 severity levels \cite{Raynus1999}.  The most 
+            severe level for a defect is 1.  All other levels drop in severity 
+            from that point. Table \ref{tab:severity} describes the 5 levels
+            for defect severity.
+
+            \begin{longtable}{@{}l l}
+                \toprule%
+                 \centering%
+                 {\bfseries Level}
+                 & {\bfseries Description}\\
+
+                \cmidrule[0.4pt](r{0.125em}){1-1}%
+                \cmidrule[0.4pt](lr{0.125em}){2-2}%
+                % \midrule
+                \endhead
+
+                1 & Software is unavailable and no workaround   \\
+                \myrowcolour%
+                2 & Software performance degraded with no workaround \\
+                3 & Software performance degraded but workaround exists \\
+                \myrowcolour%
+                4 & Software functions but a loss of non-critical functionality \\
+                5 & Others: minor cosmetic issue, missing documentation \\
+
+                \bottomrule
+
+                \caption{SOFTWARE DEFECT SEVERITY LEVELS}
+                \label{tab:severity}
+            \end{longtable}
 
@@
                 \end{description}
+
+                Notice the data does not include a severity level.  The severity
+                level should be handled before being stored.  A good technique is
+                to count the defects based upon the weighting scheme
+                in Table \ref{tab:severityweight} \cite{Raynus1999}. For
+                example, finding 1 defect of severity level 5 will result
+                in total count of 1.  However, finding 1 defect of severity
+                level 2 will result in a total count of 15. This strategy helps
+                to standardize the number of defects found.  An organization
+                can alter the values of Table \ref{tab:severityweight} based 
+                upon priorities or use a different technique if desired.  It
+                is just important to get a standard, meaningful number for SIT defects,
+                UAT defects, and PROD defects which manages severity appropriately.
+
+                \begin{longtable}{@{}l rr rr}
+                    % pairs: absolute number (percentage)
+
+                    \toprule%
+                     \centering%
+                     {\bfseries Severity Level}
+                     & {\bfseries Weight} \\
+
+                    \cmidrule[0.4pt](r{0.125em}){1-1}%
+                    \cmidrule[0.4pt](lr{0.125em}){2-2}%
+                    % \midrule
+                    \endhead
+
+                    1 & 30 \\
+                    \myrowcolour%
+                    2 &  15 \\
+                    3 &  5 \\
+                    \myrowcolour%
+                    4 &  2 \\ 
+                    5 &  1 \\
+
+                    \bottomrule
+
+                    \caption{DEFECT SEVERITY LEVEL WEIGHTING}
+                    \label{tab:severityweight}
+                \end{longtable}
 

### 2015-02-24 paper_30_measure.tex
chapter 3 work

@@
 
-\section{EVALUATING AN SDO}
+\section{MEASURING AN SDO}
 
@@
     Also, consistent reporting is essential for 
-    tracking historical performance.  Many methods are used
-    to measure and evaluate SDOs.  Some of the common ones
-    will be explained in this section.
+    tracking historical performance.
+
+    The SDLC, like any process, needs to be properly measured.  In
+    order to accomplish proper measurement, three activities need
+    to occur \cite{florac1999}.
+
+    \begin{itemize}
+        \item Identify Process Issues
+        \item Select And Define Measures
+        \item Integrate with Software Process
+    \end{itemize}
+
+    This work will focus on steps 1 and 2.  The process issue is the overall
+    effectiveness of the SDO.  Section \ref{sec:MPI} will cover step 2 as
+    it relates to an SDO.  Step
+    3 will be different for each SDO, but Section \ref{sec:SDLC-AE} provides
+    a bit of guidance for storing the correct information.  It is up to the
+    specific SDO to determine how and when the information is being stored.
+
+    Many methods have been  used in the past 
+    to measure and evaluate SDOs.  Some of the common methods
+    will be explained in the following sections.
 
     \subsection{METRICS}
-        A \textit{metric} can be defined as the science of indirect measurement. Metrics
+        A \textit{metric} can be defined as a means of telling a complete story
+        for the purpose of improving something \cite{Klubeck2011}.  Metrics are
+        frequently indirect measurements. Metrics
         are very common in the measurement of SDOs.  
@@
         All these metrics are beneficial, but none of them tell the story of the entire
-        SDO.  Most of the metrics, as seen in the list above, around an SDO focus on 
+        SDO.  Most of the metrics, as seen in the list above, for an SDO focus on 
         the source code and development phase. 
@@
         a metric or series of metrics.  Metrics are great for tracking, but decision making
-        based upon metrics is difficult.
+        based upon metrics alone is difficult.  That is why many of the other techniques
+        build upon metrics to provide a more complete overall picture of an SDO.
 
     \subsection{INDICATORS}
+        Another common measurement technique is indicators. An
+        \textit{indicator} is simply a performance measure. 
+        Typically, a number of indicators will be placed
+        together and displayed in some report or on some
+        dashboard. 
         Indicators can be crucial measurements
@@
         the correct indicators for an organization can
-        be difficult.  Software development organizations
-        are no exception. 
+        be difficult, and many organizations incorrectly classify
+        the indicators \cite{parmenter2010}.  
         The differences between the indicators will be explored and
         possible measures for each indicator in an SDO will be
-        presented.  Indicators are sometimes refered to as 
-        performance measures \cite{parmenter2010}.  The four
+        presented.   The four
         types of indicators important to an SDO are shown
@@
 
-        More information on the indicators can be found
-        in chapter 1 of 
-        as well as \cite{florac1999,kaplan1992}.
-
         \subsubsection{RESULT INDICATORS FOR SDO}
-            This section will cover the potential result indicators for an SDO.
+            More to come.
 
         \subsubsection{KEY RESULT INDICATORS FOR SDO}
+            More to come.
 
         \subsubsection{PERFORMANCE INDICATORS FOR SDO}
-            This section will cover the potential performance indicators for an SDO.
+            More to come.
 
         \subsubsection{KEY PERFORMANCE INDICATORS FOR SDO}
+            More to come.
 
-        Antolic in \cite{Antolic2008} demostrates some ways to measure KPIs for the  software development process.
+        Antolic in \cite{Antolic2008} demonstrates some ways to measure KPIs for the  software development process.
 
@@
 
-        A common technique for organizations to measure themselves is a balanced scorecard.
+        A common technique for organizations to measure themselves is a balanced scorecard. \cite{kaplan1992}
         A \textit{balanced scorecard} must contain the following six

### 2015-02-24 paper_30_measure.tex
completed Indicators, working on balanced scorecard

@@
 
-    \begin{itemize}
+    \begin{enumerate}
         \item Identify Process Issues
@@
         \item Integrate with Software Process
-    \end{itemize}
+    \end{enumerate}
 
@@
         for the purpose of improving something \cite{Klubeck2011}.  Metrics are
-        frequently indirect measurements. Metrics
+        frequently indirect measurements and
         are very common in the measurement of SDOs.  
@@
         based upon metrics alone is difficult.  That is why many of the other techniques
-        build upon metrics to provide a more complete overall picture of an SDO.
+        build upon metrics to provide a more complete overall picture of an SDO. Metrics are great starting point, but more is needed to properly 
+        evaluate performance.
 
     \subsection{INDICATORS}
+    \label{sec:indicators}
         Another common measurement technique is indicators. An
@@
 
-                \caption{SOFTWARE DEFECT SEVERITY LEVELS}
+            \caption{INDICATORS}
             \label{tab:indicators}
@@
 
-        \subsubsection{RESULT INDICATORS FOR SDO}
-            More to come.
+        Indicators can be used in just about every organizational
+        setting from businesses to non-profit organizations. They
+        are not unique to SDOs, and the exact indicators to track
+        is very specific to the organization.  The indicators chosen
+        by one organization might not be the same as the indicators
+        chosen by another organization.  The following sections
+        will explain the type of indicators in more detail and provide
+        some examples for an SDO.
 
-        \subsubsection{KEY RESULT INDICATORS FOR SDO}
-            More to come.
+        \subsubsection{RESULT INDICATORS (RI) FOR SDO}
+            \textit{Result Indicators} are performance 
+            measures that summarize activity.  All financial performance
+            measures are result indicators.  Result indicators
+            are measured on a timely basis (daily, weekly, monthly)
+            and are the result of more than one activity.  They do not
+            tell staff what needs to be done to improve the RI. For
+            an SDO, some possible RIs are seen in Table \ref{tab:RI}.
 
-        \subsubsection{PERFORMANCE INDICATORS FOR SDO}
-            More to come.
+            \begin{longtable}{@{}l l}
+                \toprule%
+                 \centering%
+                 {\bfseries Result Indicators} &
+                 \\
 
-        \subsubsection{KEY PERFORMANCE INDICATORS FOR SDO}
-            More to come.
+                \cmidrule[0.4pt](r{0.125em}){1-1}%
+                % \midrule
+                \endhead
 
-        Antolic in \cite{Antolic2008} demonstrates some ways to measure KPIs for the  software development process.
+                Requirements Implemented Per Month  \\
+                \myrowcolour%
+                Monthly SLOC \\
+                New Weekly Users \\
+                \myrowcolour%
+                Monthly Development Hours \\
+                Webpage Views Yesterday \\
+                \myrowcolour%
+                Monthly Development Hours \\
+                Monthly Server Uptime \\
+                \myrowcolour%
+                Quartely Software Sales \\
+
+                \bottomrule
+
+                \caption{RESULT INDICATORS FOR AN SDO}
+                \label{tab:RI}
+            \end{longtable}
+
+        \subsubsection{KEY RESULT INDICATOR (KRI) FOR SDO}
+            \textit{Key Result Indicators} are measures of multiple
+            activities that give a clear picture of whether the
+            organization is traveling in the right direction.  Unfortunately,
+            KRIs are commonly mistaken for KPIs \cite{parmenter2010}.  KRIs
+            do not tell an organization what is needed to improve the 
+            results.  KRIs are highly benefical for high-level management
+            and not necessarily beneficial for staff working directly on 
+            the software.  For
+            an SDO, some possible KRIs are seen in Table \ref{tab:KRI}.
+
+            \begin{longtable}{@{}l l}
+                \toprule%
+                 \centering%
+                 {\bfseries Key Result Indicators} &
+                 \\
+
+                \cmidrule[0.4pt](r{0.125em}){1-1}%
+                % \midrule
+                \endhead
+
+                Customer Satisfaction  \\
+                \myrowcolour%
+                Net Profit \\
+                Money Spent on Fixing Software \\
+                \myrowcolour%
+                \% of New Features vs. Fixes \\
+                Time on Website \\
+                \myrowcolour%
+                \% Servers Meeting the Expected Availability \\
+
+                \bottomrule
+
+                \caption{KEY RESULT INDICATORS FOR AN SDO}
+                \label{tab:KRI}
+            \end{longtable}
+
+        \subsubsection{PERFORMANCE INDICATOR (PI) FOR SDO}
+            \textit{Performance Indicators} are nonfinancial performance measures
+            that help a team align themselves with the organizations 
+            strategy.  These are important to the organizations success, but
+            they are not the key measures that will lead to drastic improvement.  They are specifically tied to a team and all staff understand
+            what actions need to be taken to improve the PI.
+            For an SDO, some possible PIs are seen in Table \ref{tab:PI}.
+
+            \begin{longtable}{@{}l l}
+                \toprule%
+                 \centering%
+                 {\bfseries Performance Indicators} &
+                 \\
+
+                \cmidrule[0.4pt](r{0.125em}){1-1}%
+                % \midrule
+                \endhead
+
+                \% Test Coverage\footnote{Test Coverage is simply the percentage 
+                    of the code that is being tested. Ideally, this 
+                    number would be 100\%, but higher is better.}   \\
+                \myrowcolour%
+                \# of Project Defects from Key Customers  \\
+                Requirements Scheduled for Next Release  \\
+                \myrowcolour%
+                \# of Missed Requirements \\
+                \% of Late Projects \\
+
+                \bottomrule
+
+                \caption{PERFORMANCE INDICATORS FOR AN SDO}
+                \label{tab:PI}
+            \end{longtable}
+
+        \subsubsection{KEY PERFORMANCE INDICATOR (KPI) FOR SDO}
+            \textit{Key Performance Indicators} are performance measures
+            focusing on critical aspects for current and future organizational
+            success.  Notice, KPIs are not focused on historical performance,
+            and they clearly indicate how to drastically increase performance.
+            KPIs allow a team to monitor current performance and 
+            quickly take action to correct future performance.
+            KPIs cover a shorter time frame than KRIs.
+            KPIs consist of the following 7 characteristics \cite{parmenter2010}.
+            \begin{enumerate}
+                \item Not financial
+                \item Measured frequently (hourly, daily, weekly)
+                \item Acted on by CEO\footnote{Chief Executive Officer} 
+                    and/or senior management
+                \item Clearly indicate the action required
+                \item Tie responsibility to a particular team
+                \item Have a significant impact
+                \item Encourage appropriate action
+            \end{enumerate}
+
+            Antolic in \cite{Antolic2008} made one of the earliest attempts
+            to identify and measure the KPIs for an SDO. Antolic's strategy
+            focused around 7 KPIs.
+            \begin{enumerate}
+                \item Schedule Adherence
+                \item Assigned Content Adherence
+                \item Cost Adherence
+                \item Fault slip through
+                \item Trouble report closure rate
+                \item Cost per defect
+            \end{enumerate}
+            However, according to the definition of KPI just presented,
+            they are not really KPIs but instead KRIs.  That is because
+            none of the 7 clearly indicate the action required to 
+            improve the measure.  Also, it is unclear if improving any of
+            the measures will drastically improve performance.
+
+            For an SDO, Table \ref{tab:KPI} identifies some more appropriate
+            KPIs.
+
+            \begin{longtable}{@{}l l}
+                \toprule%
+                 \centering%
+                 {\bfseries Key Performance Indicators} &
+                 \\
+
+                \cmidrule[0.4pt](r{0.125em}){1-1}%
+                % \midrule
+                \endhead
+
+                Projects more than 20\% behind schedule \\
+                \myrowcolour%
+                Servers currently unavailable \\
+                Automated tests failing for more than 24 hours \\
+                \myrowcolour%
+                Projects with test coverage less than 60\% \\
+                Projects with more than 10 SIT defects \\
+                \myrowcolour%
+                Unfixed, high priority PROD defects older than 1 week  \\
+
+                \bottomrule
+
+                \caption{KEY PERFORMANCE INDICATORS FOR AN SDO}
+                \label{tab:KPI}
+            \end{longtable}
 
@@
 
-        A common technique for organizations to measure themselves is a balanced scorecard. \cite{kaplan1992}
-        A \textit{balanced scorecard} must contain the following six
-        characteristics.
+        A common technique for organizations to measure themselves is a 
+        balanced scorecard, first presented by Kaplan and 
+        Norton \cite{kaplan1992}.
+
+        Kaplan and Norton originally identified 4 characteristics
+        for the balanced scorecard, but 
+        A \textit{balanced scorecard} should contain the following six
+        characteristics with the final 2 being optional 
+        as they were presented later by Parmenter \cite{parmenter2010}
+        and are not considered as part of the original balanced
+        scorecard outlined by Kaplan and Norton \cite{kaplan1992,Kaplan2007}.
         \begin{enumerate}
@@
           \item Customer Focus
+          \item Internal Process
+          \item Learning and Growth
+          \item Employee Satisfaction
           \item Environment/Community
-          \item Internal Process
-          \item Employee Satisfaction
-          \item Learning and Growth
         \end{enumerate}
@@
 
-        This info comes from \cite{parmenter2010}.
+        This info comes from .
 

### 2015-02-25 paper_30_measure.tex
mostly done with chapter 3

@@
     \subsection{BALANCED SCORECARD}
+    \label{sec:bsc}
 
-        A common technique for organizations to measure themselves is a 
-        balanced scorecard, first presented by Kaplan and 
-        Norton \cite{kaplan1992}.
+        Developed in 1992 by Robert S. Kaplan and David P. Norton, the 
+        \textit{balanced scorecard}  is a set of measures that
+        give management a quick and comprehensive view of the
+        organization \cite{kaplan1992}.  Originally created as an
+        extension to the already existing financial measures, the
+        balanced scorecard expanded the measures to include: 
+        customer focus, internal process, and learning/growth. 
+        This gave organizations a more comprehensive view that was
+        not strictly financial.  It allows an organization to focus
+        on long-term strategic goals instead of just short-term goals.
+        As a result of the strategic focus, the balance scorecard
+        rapidly gained widespread adoption
+        among businesses \cite{Kaplan2007}.
 
-        Kaplan and Norton originally identified 4 characteristics
-        for the balanced scorecard, but 
-        A \textit{balanced scorecard} should contain the following six
-        characteristics with the final 2 being optional 
-        as they were presented later by Parmenter \cite{parmenter2010}
-        and are not considered as part of the original balanced
-        scorecard outlined by Kaplan and Norton \cite{kaplan1992,Kaplan2007}.
+        In 2010, David Parmenter \cite{parmenter2010} added 2 more
+        characteristics to the balanced scorecard: employee satisfaction
+        and environment/community.  This results in a total of 6 
+        characteristics for the balanced scorecard.
         \begin{enumerate}
@@
           \item Learning and Growth
-          \item Employee Satisfaction
-          \item Environment/Community
+          \item Employee Satisfaction\footnote{\label{ft:bsc} These 2 
+                characteristics are not a part of the original balanced 
+                scorecard presented by Kaplan and Norton in 1992.  
+                They  were added later by Parmenter \cite{parmenter2010}. }
+          \item Environment/Community\textsuperscript{\ref{ft:bsc}}
         \end{enumerate}
 
-        Balanced scorecards are great for displaying the important information about
-        an organization.  However, a balanced scorecard does not specify what
-        exactly needs to be tracked.  It is also not specific to an SDO and 
-        it does not produce a single number.
-
-        This info comes from .
+        Balanced scorecards are great for easily displaying the 
+        important information about
+        an organization.  The downside is a balanced scorecard does not specify what
+        exactly needs to be tracked. It can be very difficult to determine exactly
+        what PIs, RIs, KRIs and/or KPIs to track in a balanced scorecard. 
+        It just specifies 6 broad categories.
+        It is also not specific to an SDO and 
+        it does not produce a single number.  However, any new measurement
+        technique for an organization should be compared with the balanced
+        scorecard.
 
     \subsection{PROJECT MANAGEMENT MEASUREMENT}
-        According to Putnam and Myers in \cite{Putnam2013}, the 5 core measurements for managing software
+    \label{sec:pm}
+        A final strategy to measure an SDO is focused on the aspect of
+        project management. Project management is the guidance
+        applied to a project to ensure an effective and efficient
+        completion.  Proper project management will ensure all steps
+        of the SDLC
+        continue to progress and all obstacles are handled
+        in a timely fashion.  
+        According to Putnam and Myers in \cite{Putnam2013}, 
+        the 5 core measurements for managing software
         projects are:
@@
         \begin{enumerate}
-            \item \textbf{Quantity of function} usually measured in terms of size (such as source lines of code or function points), that ultimately execute on the computer
+            \item \textbf{Quantity of function} usually measured in terms of size (such as source lines of code), that ultimately execute on the computer
             \item \textbf{Productivity} as expressed in terms of the functionality produced for the time and effort expended
@@
         \end{enumerate}
-        However, these measurements don't focus on the entire SDO. They say nothing about the availablity of the software infrastructure or the satisfaction of the users.
 
-        \begin{description}
-          \item[Time] This measurement can be hours, days, weeks, or months.  the time increment does not matter as long as it is consistent.
-          \item[Effort] This measurement is person-months, person-weeks, or person-days.
-          \item[Quality] This measurement is the defect rate (defects per time period).
-          \item[Amount of Work] This measurement has the same units as Effort above. 
-          \item[Process Productivity] look into this a bit further
-          \item[Function Points] find a definition and a comparison with story points
-          \item[Story Points] Look in some agile book
-        \end{description}
+        A \textit{process productivity} number is calculated based entirely
+        off aspects of the SDLC and the 5 core measurements.  It is a number
+        targeted at project teams working on the SDLC.
 
-        Chapter 7 of \cite{Putnam2013} contains some equations to calculate and relate
-        these measures. Those equations will be studied and evaluated.
+    \subsection{A SIMPLER MEASUREMENT}
 
-    \subsection{MEASURING OTHER ASPECTS OF AN SDO}
-
-        It is important to note that software departments do not just
-        develop software.  The department has many other duties
+        It is important to note that SDOs do not just
+        develop software.  An SDO has many other duties
         including: deploying software, installing server hardware/software,
         writing documentation, surveying users, research, innovation,
-        education and other common business duties.
-
-    \subsection{COMBINING THE MEASURES}
+        education and other common business duties.  Thus it is
+        important to measure as many duties as possible.
 
         How can the PIs, RIs, KRIs, and KPIs be combined to form a single
-        value called an MPI (Master Performance Indicator)?  The field
-        of sports analytics also has numerous techniques for combining
-        multiple indicators to produce a single number \cite{Cervone2014}.
-
-making decisions based upon historical data.
-
-Data Driven Software Engineering not Data Driven Software Development
+        value called an MPI (Master Performance Indicator)?
 

### 2015-02-25 paper_40_mpi.tex
chapter 3 work
mostly done with chapter 3

@@
 \section{MASTER PERFORMANCE INDICATOR (MPI)}
+\label{sec:MPI}
 
@@
 
+            \begin{description}
+              \item[Function Points] find a definition and a comparison with story points
+              \item[Story Points] Look in some agile book
+            \end{description}
+
             \paragraph{REQUIREMENTS DATA}
@@
             \begin{longtable}{p{4cm}p{10cm}}
-                % pairs: absolute number (percentage)
 
@@
 
+        \subsubsection{MPI VS. BALANCED SCORECARD}
+            Section \ref{sec:bsc} discusses the characteristics of the 
+            balanced scorecard.  Table \ref{tab:bsc} presents a
+            comparison of the characteristics of a balanced scorecard
+            versus MPI.
+            As the newer 2 characteristics of a balanced scorecard
+            have only existed since 2010 and the adoption is limited,
+            the comparison will only be against the original 4 balanced
+            scorecard characteristics.
+
+             \begin{longtable}{p{3cm}p{1cm}p{10cm}}
+                % pairs: absolute number (percentage)
+
+                \toprule%
+                 \centering%
+                 {\bfseries Balanced Scorecard}
+                 & {\bfseries MPI?} 
+                 & {\bfseries Explanation} \\
+
+                \cmidrule[0.4pt](r{0.125em}){1-1}%
+                \cmidrule[0.4pt](lr{0.125em}){2-2}%
+                \cmidrule[0.4pt](lr{0.125em}){3-3}%
+                % \midrule
+                \endhead
+
+                Financial & No & MPI does not address financial as it is best suited 
+                    for an organization that treats software development as a fixed,
+                    budgeted expense. If the budget is fixed, MPI provides a number
+                    to indicate the amount of value for that fixed budget.  \\
+                \myrowcolour%
+                Customer Focus & Yes & MPI includes a customer survey which is 
+                    completely customer focused.\\
+                Internal Process & Yes & MPI is highly focused on internal processes.
+                    The MPI elements of schedule and requirement are completely
+                    focused on how reality meets the expected process. MPI is
+                    negatively impacted when internal processes are followed. \\
+                \myrowcolour%
+                Learning/Growth & No & MPI does not address this characteristic. \\
+
+                \bottomrule
+
+                \caption{BALANCED SCORECARD VERSUS MPI}
+                \label{tab:bsc}
+            \end{longtable}
+
+        \subsubsection{MPI VS. PROJECT MANAGEMENT MEASUREMENT}
+            Previously in Section \ref{sec:pm}, the project management
+            measurement was presented.   Its greatest limitation is the lack of
+            focus on the entire SDO.  Project management measurement says 
+            nothing about the availability of the software infrastructure
+            or the satisfaction of the users.  It is not near as comprehensive
+            as either the balanced scorecard or MPI. Actually, MPI incorporates
+            the 5 core measurements from project management.
+            Plus, the process productivity
+            number is less suitable for upper management and more
+            suitable for project teams.  Although it does provide a single
+            process productivity number, it is does not have the same focus
+            as MPI.
+
 \end{document}

### 2015-02-25 paper_80_conclusion.tex
mostly done with chapter 3

@@
 inserted into the appropriate database tables for MPI scoring.
+
+As shown in Table \ref{tab:bsc}, MPI is currently not addressing 2 characteristics of the balanced scorecard.  If the SDO does not operate on a fixed budget, MPI could be 
+expanded to include another element for financial data. The challenge arises when
+determining how to relate the SDO performance to finances.  The most likely scenario
+would be a method to either select or predicted the expected software sales
+for a month.  Then every month create an MPI element score that reflects
+how much the expected sales were exceeded or missed.  The other missing
+balanced scorecard characteristic is learning and growth.  Those are very difficult
+to quantitatively measure.  In this case some possible data points might be:
+hours of training, number of training courses, number of employees receiving
+training, number of promotions, or another measure centered around training
+courses and career growth.  Again, once data exists, the problem becomes finding
+a baseline and measuring with respect to that baseline.
 

### 2015-02-26 paper_30_measure.tex
finished chapter 3

@@
         How can the PIs, RIs, KRIs, and KPIs be combined to form a single
-        value called an MPI (Master Performance Indicator)?
+        value called an MPI (Master Performance Indicator)?  If the indicators
+        are targeted for upper management to understand performance, then 
+        KPIs are not the correct indicators.  KPIs are targeted towards
+        immediate action and future performance.  RIs and KRIs are the most
+        beneficial for upper management to gauge how an organization is doing.
+        However, with so many possible RIs and even KRIs, it can be tricky
+        to gain a quick understanding.  The next section will present
+        and explain a technique to combine KRIs into a single number
+        for immediate and  effortless evaluation of an SDO.
 

### 2015-02-26 appendices.tex
adding data files

@@
 \subsection{R CODE - QUALITY}
-\scriptsize{
-\begin{lstlisting}[language=R]
-# Load the Quality data.
-setAs("character","myDate", function(from) as.Date(from, format="%m/%d/%Y") )
-setClass('myDate')
-
-quality_data <- read.csv('quality_data_clean.csv', 
-        colClasses=c('factor','myDate','myDate','numeric','numeric',
-        'numeric','numeric','numeric','numeric','numeric') )
-str(quality_data)
-head(quality_data)
-summary(quality_data)
-
-# Get data prior to 2013
-old_quality_data = quality_data[quality_data$MONTH_DT <= as.Date('2013-12-31') ,]
-str(old_quality_data)
-pairs(old_quality_data[,c('TOTAL_TIX','EST_DEV_RES_HRS')] )
-
-# Separate out large (>1000 hours) and small projects
-large_quality_data = old_quality_data[old_quality_data$EST_DEV_RES_HRS >= 1000,]
-str(large_quality_data)
-largefit <- lm(TOTAL_TIX ~ EST_DEV_RES_HRS + DFTS_CNT_SIT + DFTS_CNT_UAT , 
-        data=large_quality_data)
-summary(largefit)
-largefit_sigma = summary(largefit)$sigma
-pairs(large_quality_data[,c('EST_DEV_RES_HRS','DFTS_CNT_SIT',
-        'DFTS_CNT_UAT','TOTAL_TIX')])
-
-small_quality_data = 
-        old_quality_data[old_quality_data$EST_DEV_RES_HRS < 1000 
-            && old_quality_data$APP != 'App 86' ,]
-str(small_quality_data)
-smallfit <- lm(TOTAL_TIX ~ EST_DEV_RES_HRS + DFTS_CNT_SIT + DFTS_CNT_UAT , 
-        data=small_quality_data)
-summary(smallfit)
-smallfit_sigma = summary(smallfit)$sigma
-pairs(small_quality_data[,c('EST_DEV_RES_HRS','DFTS_CNT_SIT',
-        'DFTS_CNT_UAT','TOTAL_TIX')])
-
-# predict new data  
-new_large_quality_data = 
-        quality_data[quality_data$MONTH_DT > as.Date('2013-12-31') 
-            & quality_data$MONTH_DT < as.Date('2014-12-31') 
-            & quality_data$EST_DEV_RES_HRS >= 1000,]
-new_small_quality_data = 
-        quality_data[quality_data$MONTH_DT > as.Date('2013-12-31') 
-        & quality_data$MONTH_DT < as.Date('2014-12-31') 
-        & quality_data$EST_DEV_RES_HRS < 1000,]
-new_large_quality_data$PREDICTION = 
-        predict(largefit, newdata=new_large_quality_data)
-new_large_quality_data$SCORE = 
-        (new_large_quality_data$PREDICTION - new_large_quality_data$TOTAL_TIX)
-        / (6 * summary(largefit)$sigma)
-new_large_quality_data[,c('APP','MONTH_DT','TOTAL_TIX','PREDICTION', 'SCORE')]
-
-new_small_quality_data$PREDICTION = predict(smallfit, newdata=new_small_quality_data)
-new_small_quality_data$SCORE = 
-        (new_small_quality_data$PREDICTION - new_small_quality_data$TOTAL_TIX)
-        / (6 * summary(smallfit)$sigma)
-new_small_quality_data[,c('APP','MONTH_DT','TOTAL_TIX','PREDICTION', 'SCORE')]
-
-#Combine new data  
-new_quality_data = rbind(new_large_quality_data, new_small_quality_data)
-str(new_quality_data)
-summary(new_quality_data)
-
-aggregate(SCORE ~ MONTH_DT, new_quality_data, mean)
-
-# TODO include
-# numerical summary stats, graphical summaries,
-# dist of variables(hist used for guidance), associations among variables
-\end{lstlisting}}
 

### 2015-02-26 paper_40_mpi.tex
adding data files

@@
     organization and using that information to score an organization 
-    on current performance.  MPI focuses on the following 
-    elements of a software development organization: \textit{quality}, 
-    \textit{availability}, \textit{satisfaction}, \textit{schedule},
-    and \textit{requirements}. A separate MPI
+    on current performance.  MPI is a collection of the following 5 
+    elements, which are actually KRIs,
+    for a software development organization.
+    \textbf{
+    \begin{enumerate}
+        \item Quality
+        \item Availability
+        \item Satisfaction
+        \item Schedule
+        \item Requirements
+    \end{enumerate}
+    }
+    A separate MPI
     score is calculated for each element and 
@@
                 The first step in creating a score for the quality
-                element is analysis of the historical data.  The historical
+                element is analysis of the historical data to create
+                a baseline function.  The historical
                 data is all quality data collected before  a given point
@@
                 or the end of the previous fiscal year.  Then a mathematical
-                model to predict PROD Defects will be produced.  In statistical
+                model, called the \textit{baseline quality function},
+                to predict PROD Defects will be produced.  In statistical
                 terms, the response is \textit{PROD Defects} and the predictors

### 2015-02-26 paper_70_case-study.tex
working on the end of chapter 4
chapter 3 work
mostly done with chapter 3
adding data files

@@
 an SDO within a large financial institution.
-The data collection was from 2008 to present.
-This section will provide the analysis performed and the MPI scores of that data.
-The data is incomplete but that is realistic of most oganizations.
-Currently, the data
-consists of availability, quality, and schedule.  Satisfaction and Requirements are being obtained. An example of the initial analysis is included in \cref{app:case}.
-
-\subsection{WITHOUT HISTORICAL DATA}
-
-An MPI calculation with default values.
+The data collection was from 2007 to January 2015. As would be expected
+in any organization, not all 5 elements have data for the entire duration.
+MPI can still work because the calculations will only include
+the available elements.  This section will provide the analysis performed and the MPI scores of that data.  An example of the initial analysis is included in \cref{app:case}.
 
 \subsection{WITH HISTORICAL DATA}
+    This first case will demonstrate how to calculate the MPI for an
+    organization when historical data is present.  
+    \subsubsection{QUALITY}
+        Luckily, the data for quality goes from October 2007 to January 2015
+        and contains 985 observations.
+        This is important because historical data can be used to create the
+        baseline quality function.  All quality for the years 2007 through 2013
+        will be used as historical data for the purposes of creating
+        the baseline quality function.  
+    \subsubsection{AVAILABILITY}
+    \subsubsection{SATISFACTION}
+    \subsubsection{SCHEDULE}
+    \subsubsection{REQUIREMENTS}
+    \subsubsection{OVERALL}
+        All of the months do not include the same elements.
 
-How to create better formulas with historical data.
+An MPI calculation analyzing historical performance.
+
+%%\subsection{WITHOUT HISTORICAL DATA}
+
+%%An MPI calculation with default values for quality, schedule and requirements.
 

### 2015-02-27 paper_10_intro.tex
switched references to biblatex
completed Indicators, working on balanced scorecard
change name to CRI

@@
     what measurements should be tracked and how those measurements
-    should be reported.  The MPI framework provides a solid foundation
-    for a consistent evaluation.  MPI analyzes the historical performance
+    should be reported.  The Cumulative Result Indicator (CRI)
+    framework provides a solid foundation
+    for a consistent evaluation.  CRI analyzes the historical performance
     of an SDO
@@
 
-    Another promising research area is \textit{process mining}.
+    Another promising research area is \textit{process mining}
+    \cite{vanderAalst2012}.
     As stated by Wil van der Aalst \cite{vanderAalst2011}, 
@@
     development organizations.  Chapter 3 introduces what is meant by the term data-driven
-software engineering. Chapter 4 then provides an explanation of the Master Performance 
-Indicator (MPI).  It will present the essential elements for calculating the MPI, as well
-as the formulas, framework, and data necessary to produce the MPI. Chapter 5 provides
-a technological framework for generating and storing the current and historical MPI values.
-Chapter 6 demostrates how MPI can be implemented in a software development portion of 
+    software engineering. Chapter 4 then provides an explanation of the Cumulative
+    Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
+    as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
+    a technological framework for generating and storing the current and historical CRI values.
+    Chapter 6 demostrates how CRI can be implemented in a software development portion of 
     a large financial institution.  Chapter 7 concludes the dissertation with a summary

### 2015-02-27 paper_30_measure.tex
adding data files
change name to CRI

@@
     This work will focus on steps 1 and 2.  The process issue is the overall
-    effectiveness of the SDO.  Section \ref{sec:MPI} will cover step 2 as
+    effectiveness of the SDO.  Section \ref{sec:CRI} will cover step 2 as
     it relates to an SDO.  Step
@@
         How can the PIs, RIs, KRIs, and KPIs be combined to form a single
-        value called an MPI (Master Performance Indicator)?  If the indicators
+        value called the CRI (Cumulative Result Indicator)?  If the indicators
         are targeted for upper management to understand performance, then 

### 2015-02-27 paper_50_sdlc-ae.tex
chapter 3 work
mostly done with chapter 3
change name to CRI

@@
 \section{SDLC ANALYTIC ENGINE}
+\label{sec:SDLC-AE}
 
-In order for an SDO to properly track the elements of MPI, a data storage system should be available to store the appropriate data.
+In order for an SDO to properly track the elements of CRI, a data storage system should be available to store the appropriate data.
 A consistent storage system should help to avoid the problem of inaccurate
@@
 \subsection{DATABASE STRUCTURE}
-   All the data necessary to compute MPI needs to be stored in a database.  This section will 
+   All the data necessary to compute CRI needs to be stored in a database.  This section will 
    lay out the structure of tables and relationships necessary to the store all the data
@@
 
-   \subsubsection{TABLES FOR RAW MPI DATA}
+   \subsubsection{TABLES FOR RAW CRI DATA}
 
@@
         will line up with the necessary data for each of the 5 elements
-        of MPI.  Figure \ref{fig:raw} provides a visual description
+        of CRI.  Figure \ref{fig:raw} provides a visual description
         of the tables that are needed.  The tables have no relationship
@@
         \end{enumerate}
-        Notice these table names match with the 5 elements of MPI.
+        Notice these table names match with the 5 elements of CRI.
 
@@
             \includegraphics[scale=.55]{images/raw_tables.png}
-            \caption{TABLES FOR RAW MPI DATA}
+            \caption{TABLES FOR RAW CRI DATA}
             \label{fig:raw}
@@
         Appendix \ref{src:rawSQL} provides the necessary SQL statements to create the 
-        database tables for storing the raw MPI data.  The SQL is written for an Oracle
+        database tables for storing the raw CRI data.  The SQL is written for an Oracle
         database, but the scripts can be modified to work with another database
@@
 
-    \subsubsection{INTERMEDIATE SCORE TABLES FOR MPI}
+    \subsubsection{INTERMEDIATE SCORE TABLES FOR CRI}
 
         Appendix \ref{src:scoreSQL} provides the necessary SQL statements to create the 
-        database tables for storing the intermediate MPI scores.
+        database tables for storing the intermediate CRI scores.
 
-    \subsubsection{FINAL SCORE TABLES FOR MPI}
+    \subsubsection{FINAL SCORE TABLES FOR CRI}
 
@@
         database tables for storing the final scores for each element and the final 
-        overall MPI scores for each time frequency.
+        overall CRI scores for each time frequency.
 
@@
     The section will provide the necessary SQL queries to obtain the correct data
-    needed to compute the individual elements of MPI.
+    needed to compute the individual elements of CRI.
 
@@
     This section will provide R scripts to calculate each individual score and the overall 
-    MPI score. The scripts will need to be run every time the data is updated and the MPI
+    CRI score. The scripts will need to be run every time the data is updated and the CRI
     score needs to be recalculated.
 
+making decisions based upon historical data. 
+Data Driven Software Engineering not Data Driven Software Development
+
 \end{document}

### 2015-02-27 paper_60_tooling.tex
adding info about 3 focus areas and 3 questions
change name to CRI

@@
 
-\subsection{SDLC DASHBOARD}
-This maybe needs a name: Project MPI????  The goal of this project is to provide a tool that
-given the 5 files will be able to provide a score for the software department.  It should run 
-as a web application.
-
-This section will provide information to install and run a tool for calculating MPI for an organization.
-\subsubsection{INTRODUCTION}
-\subsubsection{OVERVIEW}
-\subsubsection{INSTALLATION}
-\subsubsection{DATABASE}
-maybe MongoDB, maybe PostgreSQL/MySQL
-\subsubsection{WEBSERVER}
-The software can either run standalone on cloud-hosted platform such as Heroku.  Try using Play Framework 2 with Authenticate.
+% section not used in final dissertation
 

### 2015-02-27 paper_70_case-study.tex
change name to CRI

@@
 in any organization, not all 5 elements have data for the entire duration.
-MPI can still work because the calculations will only include
-the available elements.  This section will provide the analysis performed and the MPI scores of that data.  An example of the initial analysis is included in \cref{app:case}.
+CRI can still work because the calculations will only include
+the available elements.  This section will provide the analysis performed and the CRI scores of that data.  An example of the initial analysis is included in \cref{app:case}.
 
 \subsection{WITH HISTORICAL DATA}
-    This first case will demonstrate how to calculate the MPI for an
+    This first case will demonstrate how to calculate the CRI for an
     organization when historical data is present.  
@@
 
-An MPI calculation analyzing historical performance.
+An CRI calculation analyzing historical performance.
 
@@
 
-%%An MPI calculation with default values for quality, schedule and requirements.
+%%An CRI calculation with default values for quality, schedule and requirements.
 

### 2015-02-27 paper_80_conclusion.tex
change name to CRI

@@
 Due to the number of issues with surveys.  One area of future work would be indentifying
-a general set of questions that would best fit MPI.  This set would have to include
+a general set of questions that would best fit CRI.  This set would have to include
 the best number of questions, order of questions and wording of questions.  Therefore,
@@
 handle the survey distribution and collection.  Ideally, the results would automatically be
-inserted into the appropriate database tables for MPI scoring.
+inserted into the appropriate database tables for CRI scoring.
 
-As shown in Table \ref{tab:bsc}, MPI is currently not addressing 2 characteristics of the balanced scorecard.  If the SDO does not operate on a fixed budget, MPI could be 
+As shown in Table \ref{tab:bsc}, CRI is currently not addressing 2 characteristics of the balanced scorecard.  If the SDO does not operate on a fixed budget, CRI could be 
 expanded to include another element for financial data. The challenge arises when
@@
 would be a method to either select or predicted the expected software sales
-for a month.  Then every month create an MPI element score that reflects
+for a month.  Then every month create an CRI element score that reflects
 how much the expected sales were exceeded or missed.  The other missing
@@
 There are many metrics that can be used to evaluate a Software Development Organization (SDO). 
-Knowing which metrics to use and what they all mean can be a daunting task.  MPI is a
+Knowing which metrics to use and what they all mean can be a daunting task.  CRI is a
 proposed solution to the difficulty of measuring an SDO.
@@
     \item Map the relationship or lack of relationship with a Balanced Scorecard
-    \item Create a Framework to store the necessary data for MPI
-    \item Outline a Process to generate the MPI score
-    \item Provide an example MPI score with real data
+    \item Create a Framework to store the necessary data for CRI
+    \item Outline a Process to generate the CRI score
+    \item Provide an example CRI score with real data
 \end{itemize}

### 2015-02-28 paper_40_cri.tex
file rename to cri

--- 2015-02-26 paper_40_mpi.tex
@@
 
-\section{MASTER PERFORMANCE INDICATOR (MPI)}
-\label{sec:MPI}
+\section{CUMULATIVE RESULT INDICATOR (CRI)}
+\label{sec:CRI}
 
     Software development organizations struggle to measure overall performance.  
-    The Master Performance Indicator (MPI) is an algorithm to provide a single 
+    The Cumulative Result Indicator (CRI) is an algorithm to provide a single 
     number score to measure the performance of a software development organization. 
@@
     organization and using that information to score an organization 
-    on current performance.  MPI is a collection of the following 5 
+    on current performance.  CRI is a collection of the following 5 
     elements, which are actually KRIs,
@@
     }
-    A separate MPI
+    A separate CRI
     score is calculated for each element and 
     then aggregated together to form an overall 
-    MPI score.  A new MPI score will be calculated based
+    CRI score.  A new CRI score will be calculated based
     upon the selection of a given time period (weekly, monthly, quarterly).
-    \textbf{MPI is not meant to be comparative between
+    \textbf{CRI is not meant to be comparative between
     organizations, but to measure the amount of increase or decrease
-    a single organization exhibits across elements}.  MPI is made to be easily 
+    a single organization exhibits across elements}.  CRI is made to be easily 
     expandable to other elements if desired.
 
-    The scores for MPI will range from -1, indicating the worst 
+    The scores for CRI will range from -1, indicating the worst 
     performance, all the way to +1, indicating perfection.
@@
     positive score indicates over-performance.   Here are some 
-    examples. An MPI score of 0.35 means the organization is 
+    examples. An CRI score of 0.35 means the organization is 
     performing 35\% better than expected.  Conversely, a score 
@@
 
-    Below are the attributes of the MPI scoring.
+    Below are the attributes of the CRI scoring.
     \begin{itemize}
@@
 
-    \subsection{ELEMENTS OF MPI}
-        The MPI score consists of data collected from five
+    \subsection{ELEMENTS OF CRI}
+        The CRI score consists of data collected from five
         different elements of an SDO.  
@@
                 the columns of data that will be used to create
-                a score for the quality element of MPI.  
+                a score for the quality element of CRI.  
                 Each column is classified as \textit{required} or
@@
 
-                    \caption{QUALITY DATA NEEDED FOR MPI}
+                    \caption{QUALITY DATA NEEDED FOR CRI}
                     \label{tab:qualitydata}
@@
                 or any combination of Application IDs.   It serves as the 
-                quality baseline for MPI. 
+                quality baseline for CRI. 
                 All future quality scores will be dependent upon the original
@@
             performance against that SLA.  The following section will outline to data needed to properly
-            calculate an SLA and the data needed to calculate the MPI score for availability.
+            calculate an SLA and the data needed to calculate the CRI score for availability.
 
@@
                 Table \ref{tab:availdata} identifies the necessary data to calculate
-                the MPI element score for availability.  Notice the three optional 
+                the CRI element score for availability.  Notice the three optional 
                 fields: \textit{Uptime}, \textit{Scheduled Downtime}, and 
@@
                 used to calculated the \textit{Percent Uptime}.  The \textit{Percent Uptime}
-                is the important value for the MPI schedule score.  Here are the two common
+                is the important value for the CRI schedule score.  Here are the two common
                 approaches for calculating percent uptime:
@@
 
-                    \caption{AVAILABILITY DATA NEEDED FOR MPI}
+                    \caption{AVAILABILITY DATA NEEDED FOR CRI}
                     \label{tab:availdata}
@@
 
-            \textit{If one element of MPI was to be rated as the most important, satisfaction
+            \textit{If one element of CRI was to be rated as the most important, satisfaction
             would be it.}  
@@
 
-            Surveys are used to measure satisfaction for MPI.  A series of statements will
+            Surveys are used to measure satisfaction for CRI.  A series of statements will
             be presented to all or a subset of the customers.  Any customer that chooses
@@
                     sample sets os customers need to be presented with a survery.  
-                    In the case of MPI, there are 2 possible scenarios for sampling.  
+                    In the case of CRI, there are 2 possible scenarios for sampling.  
                     \begin{description}
@@
                 \ref{tab:satisfactiondata} displays the data that needs to be collected 
-                in order to calculate the satisfaction element score for MPI.
+                in order to calculate the satisfaction element score for CRI.
                 \begin{longtable}{@{}l rr rr}
@@
 
-                    \caption{SATISFACTION DATA NEEDED FOR MPI}
+                    \caption{SATISFACTION DATA NEEDED FOR CRI}
                     \label{tab:satisfactiondata}
@@
 
-            The MPI schedule score provides a numeric value to indicate the amount 
+            The CRI schedule score provides a numeric value to indicate the amount 
             schedules are missed or exceeded.  The score provides a cumulative measure
@@
                 the necessary data for schedules.  One date is considered
-                optional as it is not used in the MPI calculation, but it
+                optional as it is not used in the CRI calculation, but it
                 is an important date that could be useful for future
-                enhancements to MPI.
+                enhancements to CRI.
 
@@
 
-                    \caption{SCHEDULE DATA NEEDED FOR MPI}
+                    \caption{SCHEDULE DATA NEEDED FOR CRI}
                     \label{tab:scheduledata}
@@
                 The C.D.F. will be transformed to create
-                the schedule score for MPI. Since all C.D.F. functions fall within the
+                the schedule score for CRI. Since all C.D.F. functions fall within the
                 range $[0,1]$, the function needs to be shifted to center around 0, and then
-                doubled to fill the desired range of $[-1,1]$. Thus the MPI schedule score
+                doubled to fill the desired range of $[-1,1]$. Thus the CRI schedule score
                 for each project becomes the following.
@@
 
-                    \caption{REQUIREMENTS DATA NEEDED FOR MPI}
+                    \caption{REQUIREMENTS DATA NEEDED FOR CRI}
                     \label{tab:req}
@@
 
-        \subsubsection{OVERALL MPI SCORE}
-            In order to accomplish the single number score that MPI requires,
+        \subsubsection{OVERALL CRI SCORE}
+            In order to accomplish the single number score that CRI requires,
             the 5 element scores must be combined. The combination of the scores
             is a weighted average.  The weights can be set based upon the 
-            priority of the SDO.  Thus, the overall MPI score is calculated as below.
+            priority of the SDO.  Thus, the overall CRI score is calculated as below.
 
             \[
-                MPI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
+                CRI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
             \]
 
-    \subsection{CORRELATIONS IN MPI}
-        It is possible that 2 or more of the 5 elements of MPI will be correlated.  This means that
+    \subsection{CORRELATIONS IN CRI}
+        It is possible that 2 or more of the 5 elements of CRI will be correlated.  This means that
         one of the elements can be predicted based upon the values of the other elements.  Although
@@
         It is impossible to know which or if correlations will always exist.  Thus it is necessary to
-        check for correlations after determining element and overall MPI scores.  
+        check for correlations after determining element and overall CRI scores.  
         If correlation is determined, the element should not be dropped but rather be weighted less than
@@
 
-    \subsection{SENSITIVITY OF MPI}
+    \subsection{SENSITIVITY OF CRI}
     \label{sub:sensitivity}
 
-        Some simulations will be run with data from each given distribution.  Then the MPI scores
+        Some simulations will be run with data from each given distribution.  Then the CRI scores
         will be analyzed.
@@
 
-    \subsection{MPI COMPARED}
+    \subsection{CRI COMPARED}
 
-        \subsubsection{MPI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
+        \subsubsection{CRI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
 
@@
             areas  for software
-            analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how MPI addresses
+            analytics were presented.  Table \ref{tab:focusareas} provides a explanation of how CRI addresses
             each focus area.  
-            As can be seen, MPI clearly addresses the 3 main focus areas of software analytics.  MPI does not provide
+            As can be seen, CRI clearly addresses the 3 main focus areas of software analytics.  CRI does not provide
             any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
@@
                  {\bfseries Focus Area}
-                 & {\bfseries Why MPI?} \\
+                 & {\bfseries Why CRI?} \\
 
@@
 
-                User Experience & One of the 5 elements of MPI is satisfaction.
+                User Experience & One of the 5 elements of CRI is satisfaction.
 While not all of the questions focus solely on the user experience, the entire purpose of the survey is to determine if the user is satisfied
@@
                 \myrowcolour%
-                Quality & Again, one of the 5 elements specifically focuses on quality.  MPI provides a single number
-                to measure quality.  Therefore, it is easy to track changes in quality over time.  MPI does not address
+                Quality & Again, one of the 5 elements specifically focuses on quality.  CRI provides a single number
+                to measure quality.  Therefore, it is easy to track changes in quality over time.  CRI does not address
                 how to improve the quality, but without a consistent measurement, it would be impossible to determine the change in quality. \\
-                Development Productivity & The combination of MPI elements, schedule and requirements, provide an 
+                Development Productivity & The combination of CRI elements, schedule and requirements, provide an 
                 indication of development productivity. The schedule element measures the productivity
@@
 
-                \caption{SOFTWARE ANALYTICS FOCUS AREAS AND MPI}
+                \caption{SOFTWARE ANALYTICS FOCUS AREAS AND CRI}
                 \label{tab:focusareas}
@@
 
-        \subsubsection{MPI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
+        \subsubsection{CRI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
             Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
             software analytics must address.  Table \ref{tab:questions} presents the 3 questions
-            and a description of how MPI addresses that specific question.  It is clear
-            that MPI addresses the questions.  MPI is a beneficial technique of software
+            and a description of how CRI addresses that specific question.  It is clear
+            that CRI addresses the questions.  CRI is a beneficial technique of software
             analytics when applied to software development organizations.
@@
                  {\bfseries Question}
-                 & {\bfseries Why MPI?} \\
+                 & {\bfseries Why CRI?} \\
 
@@
 
-                How much better is my model performing than a naive strategy, such as guessing? & MPI 
-                provides consistency which may not exist without it.  Therefore, MPI removes the 
+                How much better is my model performing than a naive strategy, such as guessing? & CRI 
+                provides consistency which may not exist without it.  Therefore, CRI removes the 
                 guesswork of measuring a software development organization. \\
                 \myrowcolour%
-                How practically significant are the results? & The MPI score is consistent
+                How practically significant are the results? & The CRI score is consistent
                 and easy to comprehend.  Thus comparison with past performance is quick 
@@
                 How sensitive are the results to small changes in one or more of the inputs? & 
-                The question was extensively addressed in section \ref{sub:sensitivity}.  It appears MPI is
+                The question was extensively addressed in section \ref{sub:sensitivity}.  It appears CRI is
                 not overly sensitive to small changes in the inputs.\\
@@
 
-                \caption{IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND MPI}
+                \caption{IMPORTANT QUESTIONS FOR SOFTWARE ANALYTICS AND CRI}
                 \label{tab:questions}
@@
 
-        \subsubsection{MPI VS. BALANCED SCORECARD}
+        \subsubsection{CRI VS. BALANCED SCORECARD}
             Section \ref{sec:bsc} discusses the characteristics of the 
@@
             comparison of the characteristics of a balanced scorecard
-            versus MPI.
+            versus CRI.
             As the newer 2 characteristics of a balanced scorecard
@@
                  {\bfseries Balanced Scorecard}
-                 & {\bfseries MPI?} 
+                 & {\bfseries CRI?} 
                  & {\bfseries Explanation} \\
@@
 
-                Financial & No & MPI does not address financial as it is best suited 
+                Financial & No & CRI does not address financial as it is best suited 
                     for an organization that treats software development as a fixed,
-                    budgeted expense. If the budget is fixed, MPI provides a number
+                    budgeted expense. If the budget is fixed, CRI provides a number
                     to indicate the amount of value for that fixed budget.  \\
                 \myrowcolour%
-                Customer Focus & Yes & MPI includes a customer survey which is 
+                Customer Focus & Yes & CRI includes a customer survey which is 
                     completely customer focused.\\
-                Internal Process & Yes & MPI is highly focused on internal processes.
-                    The MPI elements of schedule and requirement are completely
-                    focused on how reality meets the expected process. MPI is
+                Internal Process & Yes & CRI is highly focused on internal processes.
+                    The CRI elements of schedule and requirement are completely
+                    focused on how reality meets the expected process. CRI is
                     negatively impacted when internal processes are followed. \\
                 \myrowcolour%
-                Learning/Growth & No & MPI does not address this characteristic. \\
+                Learning/Growth & No & CRI does not address this characteristic. \\
 
@@
 
-                \caption{BALANCED SCORECARD VERSUS MPI}
+                \caption{BALANCED SCORECARD VERSUS CRI}
                 \label{tab:bsc}
@@
 
-        \subsubsection{MPI VS. PROJECT MANAGEMENT MEASUREMENT}
+        \subsubsection{CRI VS. PROJECT MANAGEMENT MEASUREMENT}
             Previously in Section \ref{sec:pm}, the project management
@@
             or the satisfaction of the users.  It is not near as comprehensive
-            as either the balanced scorecard or MPI. Actually, MPI incorporates
+            as either the balanced scorecard or CRI. Actually, CRI incorporates
             the 5 core measurements from project management.
@@
             process productivity number, it is does not have the same focus
-            as MPI.
+            as CRI.
 

### 2015-02-28 paper_20_sdo.tex
minor changes around the acronym SDO uploaded new output PDF file

@@
 \section{A SOFTWARE DEVELOPMENT ORGANIZATION (SDO)}
-A \textit{Software Development Organization} is any organization or subset of an organization that is responsible
+A \textit{Software Development Organization (SDO)} is any organization or subset of an organization that is responsible
 for the creation, deployment, and maintenance of software.  Many times a software development organization

### 2015-02-28 paper_30_measure.tex
minor changes around the acronym SDO uploaded new output PDF file

@@
 
-        \subsubsection{RESULT INDICATORS (RI) FOR SDO}
+        \subsubsection{RESULT INDICATORS (RI) FOR AN SDO}
             \textit{Result Indicators} are performance 
@@
 
-        \subsubsection{KEY RESULT INDICATOR (KRI) FOR SDO}
+        \subsubsection{KEY RESULT INDICATOR (KRI) FOR AN SDO}
             \textit{Key Result Indicators} are measures of multiple
@@
 
-        \subsubsection{PERFORMANCE INDICATOR (PI) FOR SDO}
+        \subsubsection{PERFORMANCE INDICATOR (PI) FOR AN SDO}
             \textit{Performance Indicators} are nonfinancial performance measures
@@
 
-        \subsubsection{KEY PERFORMANCE INDICATOR (KPI) FOR SDO}
+        \subsubsection{KEY PERFORMANCE INDICATOR (KPI) FOR AN SDO}
             \textit{Key Performance Indicators} are performance measures

### 2015-02-28 paper_40_cri.tex
minor changes around the acronym SDO uploaded new output PDF file

@@
     Software development organizations struggle to measure overall performance.  
-    The Cumulative Result Indicator (CRI) is an algorithm to provide a single 
+    The \textit{Cumulative Result Indicator (CRI)} is an algorithm to provide a single 
     number score to measure the performance of a software development organization. 
@@
             All the new features and great quality do not matter if the software is not available.  Thus it
-            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, an SLA is a 
+            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, the SLA is a 
             contract specifying the amount of time software will be available during a

### 2015-03-01 paper_10_intro.tex
minor changes around the acronym SDO uploaded new output PDF file
some minor typos and proof reading

@@
     for a consistent evaluation.  CRI analyzes the historical performance
-    of an SDO
+    of a Software Development Organization (SDO)
     to create a baseline in order to provide a broad
@@
     larger\footnote{Saying a piece of software is larger can be a 
-    rather arbitrary statement.  Does that mean the software requires 
+    rather arbitrary statement.  It can mean the software requires 
     more computing time, has more lines of code, more documentation, 

### 2015-03-01 paper_30_measure.tex
some minor typos and proof reading

@@
             \begin{enumerate}
-                \item Schedule Adherence
-                \item Assigned Content Adherence
-                \item Cost Adherence
+                \item Schedule adherence
+                \item Assigned content adherence
+                \item Cost adherence
                 \item Fault slip through
@@
           \item Learning and Growth
-          \item Employee Satisfaction\footnote{\label{ft:bsc} These 2 
-                characteristics are not a part of the original balanced 
-                scorecard presented by Kaplan and Norton in 1992.  
-                They  were added later by Parmenter \cite{parmenter2010}. }
+          \item Employee Satisfaction\footnote{\label{ft:bsc} Added 
+          later by Parmenter \cite{parmenter2010}. }
           \item Environment/Community\textsuperscript{\ref{ft:bsc}}

### 2015-03-01 paper_40_cri.tex
some minor typos and proof reading

@@
 
-    As long as those 5 features are met, the range can be anything.  
+    As long as those 5 features are met, the range of scores can be anything.  
     The range of $[-1,1]$ was chosen because it is easy to scale 
     to a different range such as $[-10,10]$ or $[-100,100]$.  
-    It maybe makes sense to use variables for the range.  
-    The formulas are designed to fall in the range $[-100,100]$.  
     Thus scaling can be applied to obtain values in any appropriate range. 
-    The scaling is denoted with the variable $k$.  The scale will be the same
+    The scaling factor is denoted with the variable $k$.  
+    The scale must be the same
     for all 5 elements.
@@
     \subsection{ELEMENTS OF CRI}
-        The CRI score consists of data collected from five
-        different elements of an SDO.  
-        \begin{enumerate}
-            \item Quality
-            \item Availability
-            \item Satisfaction
-            \item Schedule
-            \item Requirements
-        \end{enumerate}
+        Each of the 5 elements of CRI has its own set of data that needs to
+        be collected and a formula for calculating a score. 
         These five elements will be outline in the next sections.
@@
 
-                The preferred method
+                The preferred method:
                 \[
@@
                 \]
-                and the alternative method
+                and the alternative method:
                 \[

### 2015-03-02 paper_50_sdlc-ae.tex
added some database diagrams single space the references
adding some SDLC-AE diagrams

@@
 data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
-is implemented correctly by allowing limited changes to existing data, it will be able to alliviate
+is implemented correctly by allowing limited changes to existing data, it will be able to alleviate
 some of the dishonesty that is currently present in software projects \cite{Rost2011}.
@@
 \begin{figure}[ht]
-\includegraphics[scale=.7]{images/sdlc-ae.png}
+\includegraphics[scale=.6]{images/sdlcae.png}
 \caption{SDLC ANALYTIC ENGINE}
@@
             \label{fig:raw}
-        \end{figure}%
+        \end{figure}
 
@@
 
+       \begin{figure}[ht]
+            \centering
+            \includegraphics[scale=.55]{images/score_tables.png}
+            \caption{TABLES FOR INTERMEDIATE CRI SCORES}
+            \label{fig:score_tables}
+        \end{figure}%
+
     \subsubsection{FINAL SCORE TABLES FOR CRI}
@@
         overall CRI scores for each time frequency.
+
+       \begin{figure}[ht]
+            \centering
+            \includegraphics[scale=.55]{images/final_score_tables.png}
+            \caption{TABLES FOR FINAL CRI SCORES}
+            \label{fig:final_score_tables}
+        \end{figure}
 

### 2015-03-02 paper_10_intro.tex
work on chapter 5, SDLC-AE

@@
 
+    Iqbal, Ureche, Hausenblas, and Tummarello introduced a methodology named
+    Linked Data Driven Software Development (LD2SD) which is a collection
+    of various software artifacts into linked data \cite{Iqbal2009}.  This
+    is one of the original attempts to collect software engineering data.
+    The methodology links version control, discussion forums, and issue tracking
+    data. The result is web-scale integration of data, but the actual
+    benefits are still uncertain.
+
     After the proper tools are in place to collect the necessary

### 2015-03-02 paper_50_sdlc-ae.tex
work on chapter 5, SDLC-AE

@@
 
-In order for an SDO to properly track the elements of CRI, a data storage system should be available to store the appropriate data.
-A consistent storage system should help to avoid the problem of inaccurate
-data caused by numerous manipulations of the existing data \cite{Olson2003}. Plus, if the system
-is implemented correctly by allowing limited changes to existing data, it will be able to alleviate
-some of the dishonesty that is currently present in software projects \cite{Rost2011}.
-This storage system will be named the SDLC Analytic Engine (SDLC-AE).
-Figure \ref{fig:sdlc-ae} provides an overview of the data that could potentially be stored in the SDLC-AE.
+    In order for an SDO to properly track the elements of CRI, a data storage 
+    system should be available to store the appropriate data.  A consistent 
+    storage system should help to avoid the problem of inaccurate
+    data caused by numerous manipulations of the existing data 
+    \cite{Olson2003}. Plus, if the system
+    is implemented correctly by allowing limited changes to existing data, 
+    it will be able to alleviate
+    some of the dishonesty that is currently present in software projects 
+    \cite{Rost2011}. This storage system will be named the SDLC Analytic 
+    Engine (SDLC-AE).
 
-Once all the SDLC data is collected into a single place, there are many possible applications.  Software analytics
+    Once all the SDLC data is collected into a single place, there are 
+    many possible applications.  Software analytics
     will be much easier to create and gamification will be much more easily attainable.  
+    CRI is just one possible application of the SDLC-AE.  Figure \ref{fig:sdlc-ae} 
+    provides an overview of 
+    the data that could potentially be stored in the SDLC-AE as it relates to CRI. The
+    SDLC-AE does not specify how the data is entered, just how the data is stored.
 
     \begin{figure}[ht]
-\includegraphics[scale=.6]{images/sdlcae.png}
+        \includegraphics[scale=.75]{images/sdlcae.png}
         \caption{SDLC ANALYTIC ENGINE}
@@
         lay out the structure of tables and relationships necessary to the store all the data
-   within a relational database.
+        within a relational database.  The SQL\footnote{Structured Query Language (SQL) is 
+        a programming language designed for managing data in relational database 
+        management system.} 
+        is written for an Oracle
+        database, but the scripts can be modified to work with another database
+        such as: PostgreSQL, SQL Server, or MySQL.
 
@@
             Appendix \ref{src:rawSQL} provides the necessary SQL statements to create the 
-        database tables for storing the raw CRI data.  The SQL is written for an Oracle
-        database, but the scripts can be modified to work with another database
-        such as: PostgreSQL, SQL Server, or MySQL.
+            database tables for storing the raw CRI data.
 
         \subsubsection{INTERMEDIATE SCORE TABLES FOR CRI}
+            The next set of tables that need to be created are for the 
+            intermediate level element scores.  These tables hold the
+            element scores at the application\_id, service\_id, and project\_id
+            level.  Figure \ref{fig:score_tables} provides a visual overview
+            of the necessary tables.  Furthermore, these tables also lack
+            relationships between one another because at this point, all the
+            element scores are still being treated independently.  The five
+            table names are:
 
-        Appendix \ref{src:scoreSQL} provides the necessary SQL statements to create the 
-        database tables for storing the intermediate CRI scores.
+            \begin{enumerate}
+                \item QUALITY\_SCORE
+                \item AVAILABILITY\_SCORE
+                \item SATISFACTION\_SCORE
+                \item SCHEDULE\_SCORE
+                \item REQUIREMENTS\_SCORE
+            \end{enumerate}
+            Again, these table names match very closely with the 5 elements of CRI.
 
@@
 
+            Appendix \ref{src:scoreSQL} provides the necessary SQL statements to create the 
+            database tables for storing the intermediate CRI scores.
+
         \subsubsection{FINAL SCORE TABLES FOR CRI}
-
-        Appendix \ref{src:overallscoreSQL} provides the necessary SQL statements to create the 
-        database tables for storing the final scores for each element and the final 
-        overall CRI scores for each time frequency.
+            The final set of tables consists of only two tables.  
+            \begin{enumerate}
+                \item ELEMENT
+                \item CRI\_SCORE
+            \end{enumerate}
+            The first
+            table is the ELEMENT table.  It simply stores the CRI element 
+            (Quality, Availability,Satisfaction,Schedule,Requirements,Overall) and 
+            optional description. The second table is the CRI\_SCORE table.  
+            It stores all the final element scores and the final overall CRI
+            score.  It is related to the ELEMENT table.  Figure 
+            \ref{fig:final_score_tables} provides a visual representation of the 
+            relationship between the 2 tables.
 
@@
 
-\subsection{QUERIES}
-    The section will provide the necessary SQL queries to obtain the correct data
-    needed to compute the individual elements of CRI.
+            Appendix \ref{src:overallscoreSQL} provides the necessary SQL 
+            statements to create the 
+            database tables for storing the final scores for each element and the final 
+            overall CRI scores for each time frequency.
 
-\subsection{COMPUTATIONS}
-    This section will provide R scripts to calculate each individual score and the overall 
-    CRI score. The scripts will need to be run every time the data is updated and the CRI
-    score needs to be recalculated.
-
-making decisions based upon historical data. 
-Data Driven Software Engineering not Data Driven Software Development
+%    \subsection{QUERIES}
+%        The section will provide the necessary SQL queries to obtain the correct data
+%        needed to compute the individual elements of CRI.
+%        
+%    \subsection{COMPUTATIONS}
+%        This section will provide R scripts to calculate each individual score and the overall 
+%        CRI score. The scripts will need to be run every time the data is updated and the CRI
+%        score needs to be recalculated.
 

### 2015-03-02 paper_80_conclusion.tex
some minor typos and proof reading
adding some SDLC-AE diagrams
work on chapter 5, SDLC-AE

@@
 
-As shown in Table \ref{tab:bsc}, CRI is currently not addressing 2 characteristics of the balanced scorecard.  If the SDO does not operate on a fixed budget, CRI could be 
+    As shown in Table \ref{tab:bsc}, CRI is currently not addressing 2 
+    characteristics of the balanced scorecard.  If the SDO does not operate 
+    on a fixed budget, CRI could be 
     expanded to include another element for financial data. The challenge arises when
@@
     a baseline and measuring with respect to that baseline.
+
+    Another area of future work is the expansion of the SDLC-AE to include
+    more artifacts of the SDLC.  The more artifacts and processes that can
+    be collected, the deeper the understanding of the SDLC.  
+    All of the data collection combined with better software analytics
+    could lead to true \textit{data-driven software engineering}. Data-driven
+    software engineering is the application of collecting and analyzing historical
+    information about software engineering artifacts in order to
+    accurately predict the outcomes of software engineering projects. This
+    will lead to more informed decisions about software engineering.  Figure
+    \ref{fig:sdlc-ae-adv} shows an expansion of the previous SDLC-AE diagram.  
+    The new elements are in the unshaded boxes, and they are not exhaustive.
+    Data-driven software engineering should 
+    not to be confused with data-driven programming, in which the computer code
+    describes the data instead of the sequence of opertions \cite{DDP2015}.
+
+    \begin{figure}[ht]
+    \includegraphics[scale=.75]{images/sdlcae-adv.png}
+    \caption{SDLC ANALYTIC ENGINE EXPANSION}
+    \label{fig:sdlc-ae-adv}
+    \end{figure}
+
+    Currently, CRI provides a single method to evaluate past 
+    performance, but it does not
+    provide any guidance around making more informed future decisions. 
+    Some phases are not properly tracked with the initial SDLC-AE and more
+    data can be tracked for the existing phases.
+    Schedules for each of the individual phases of the SDLC need to be tracked,
+    not just the entire project.  Teams need to know how much time is spent
+    in design versus testing.  Also, how much time is required to generate
+    proper test cases?  These are just a couple of examples of expansions
+    to the SDLC-AE.  These and other advancements could lead to greater
+    insights about SDLC phases that are struggling and need improvement.
+    The SDLC-AE could be expanded to have predictive capabilities.
 

### 2015-03-03 paper_70_case-study.tex
adding reference to github
working on Chapter 6

@@
     Data has been collected from the software development processes of
-an SDO within a large financial institution.
-The data collection was from 2007 to January 2015. As would be expected
-in any organization, not all 5 elements have data for the entire duration.
-CRI can still work because the calculations will only include
-the available elements.  This section will provide the analysis performed and the CRI scores of that data.  An example of the initial analysis is included in \cref{app:case}.
+    an SDO within a large financial institution\footnote{All the raw data 
+    files are available at \cite{Swanstrom2015}}.
+    The data collection was from 2007 to January 2015. Only 4 elements had available
+    data, and not all elements had data available for the entire time period.  The
+    elements to be used are: quality, availability, schedule, and requirements.
+    CRI is still effective when not all data is available.
+    The overall CRI score will then be a 
+    weighted average of the available elements. 
+    This section will serve as a guide to preparing the CRI score
+    based upon the available data.
 
     \subsection{WITH HISTORICAL DATA}
-    This first case will demonstrate how to calculate the CRI for an
-    organization when historical data is present.  
+        After the data has been collected, the raw data can be stored in the SDLC
+        if desired.  Then scores for each of the 4 elements can be calculated.
         \subsubsection{QUALITY}
-        Luckily, the data for quality goes from October 2007 to January 2015
+            The first step to dealing with the quality data is a quick
+            analysis of the data.  Table \ref{tab:quality_desc} provides
+            some descriptive statistics for the quality data.
+
+            \begin{longtable}{@{}l rr rrr}
+                \toprule%
+                 \centering%
+                 {\bfseries Column}
+                 & {\bfseries Min}
+                 & {\bfseries Max}
+                 & {\bfseries Median}
+                 & {\bfseries Mean}
+                 & {\bfseries Variance} \\
+
+                \cmidrule[0.2pt](r{0.125em}){1-1}%
+                \cmidrule[0.2pt](lr{0.125em}){2-2}%
+                \cmidrule[0.2pt](l{0.125em}){3-3}%
+                \cmidrule[0.2pt](l{0.125em}){4-4}%
+                \cmidrule[0.2pt](l{0.125em}){5-5}%
+                % \midrule
+                \endhead
+
+                Development Effort & 0 & 26937 & 300 & 1637 & 18383464 \\
+                \myrowcolour%
+                Testing Effort & NA & NA & NA & NA  & NA\\
+                SIT Defects & 0 & 1106 & 1 & 45.86 & 24528 \\
+                \myrowcolour%
+                UAT Defects & 0 & 277 & 0 & 10.28 & 1306 \\
+                PROD Defects & 0 & 1216 & 5 & 51.5 & 20311 \\
+
+                \bottomrule
+
+                \multicolumn{6}{c}{985 obs. from 23 Application IDs from 2007 to 2015} \\
+
+                \caption{QUALITY DATA DESCRIPTIVE STATISTICS}
+                \label{tab:quality_desc}
+            \end{longtable}
+
+            Notice, the data for quality goes from October 2007 to January 2015
             and contains 985 observations.
@@
             will be used as historical data for the purposes of creating
-        the baseline quality function.  
+            the baseline quality function.  Once the historical data is separated,
+            it results in 799 observations to be used for creating the baseline
+            quality function.
+
         \subsubsection{AVAILABILITY}
-    \subsubsection{SATISFACTION}
         \subsubsection{SCHEDULE}

### 2015-03-04 appendices.tex
added some database diagrams single space the references
some minor typos and proof reading
working on case study - quality

@@
 
-\section{Detailed Steps of the SDLC}
+\section{DETAILED STEPS OF THE SDLC}
 \label{app:detailedSDLC}
@@
     phases, but many steps are required to complete each phase.  The following list
-    provides a more detailed version of what needs to be accomplished in the 
+    provides a more detailed list of what needs to be accomplished in the 
     entire life cycle of software development. These steps do not need 
@@
 
-\section{CASE STUDY SOURCE CODE} 
-\label{app:case}
+\section{SDLC-AE SOURCE CODE}
 
-%% set appendix to single space for th source code
+%% set appendix to single space for the source code
 \linespread{1.0}
@@
 
-\subsection{R CODE - QUALITY}
+\section{CASE STUDY SOURCE CODE} 
+\label{app:case}
+
+    \subsection{QUALITY HISTORICAL SOURCE CODE AND ANALYSIS}
+    \label{app:quality-history}
+        \lstinputlisting[language=R]{source/quality.R}
+        The source code for the selected baseline quality function
+        can be seen above. The output for the linear model can be seen below.
+        \lstinputlisting{source/quality_output.txt}
+
+        Some diagnostic plots for the baseline quality function
+        can be seen in Figure \ref{fig:quality-diag}.  The normal probability plot,
+        a.k.a. QQ Plot, shows the errors are not exactly normally distributed, but
+        the baseline quality function had good predictive power as shown by the
+        high $R^2$. The fitted versus
+        residuals plot indicates a lack of heteroscedasticity.  
+        \begin{figure}[ht]
+            \centering
+            \includegraphics[scale=.3]{images/quality_diag.png}
+            \caption{QUALITY DIAGNOSTIC PLOTS}
+            \label{fig:quality-diag}
+        \end{figure}
+
+        Figure \ref{fig:quality-pairs} shows the presence of some
+        possible multicolinearity.  As a result, ridge regression
+        was used to create a model, but the results were very similar
+        to the original baseline quality function. Therefore,
+        ridge regression was not chosen. 
+        \begin{figure}[ht]
+            \centering
+            \includegraphics[scale=.3]{images/quality_pairs.png}
+            \caption{QUALITY PAIRS PLOT OF INDEPENDENT VARIABLES}
+            \label{fig:quality-pairs}
+        \end{figure}
 

### 2015-03-04 paper_70_case-study.tex
working on case study - quality

@@
         if desired.  Then scores for each of the 4 elements can be calculated.
+        For this example, the value of $k$ will be 100 and the time
+        frequency will be monthly.  Thus, scores will fall
+        in the range $[-100,100]$.
         \subsubsection{QUALITY}
@@
             analysis of the data.  Table \ref{tab:quality_desc} provides
-            some descriptive statistics for the quality data.
+            some descriptive statistics for the quality data.  Testing hours
+            were not capture but they are optional, so the analysis can 
+            continue.
 
@@
             This is important because historical data can be used to create the
-            baseline quality function.  All quality for the years 2007 through 2013
+            baseline quality function.  All quality for the years 2007 through 
+            the end of 2013
             will be used as historical data for the purposes of creating
@@
             it results in 799 observations to be used for creating the baseline
-            quality function.
+            quality function.  Figure \ref{fig:quality-plots1} shows scatterplots
+            of PROD\_DFTS versus the independent variables of DEV\_EFF, SIT\_DFTS,
+            and UAT\_DFTS.  It can be seen that some correlations exist between
+            the variables.
+
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[scale=.3]{images/quality_plots1.png}
+                \caption{QUALITY DATA PLOTS: DEPENDENT VS. INDEPENDENT VARIABLES}
+                \label{fig:quality-plots1}
+            \end{figure}
+
+            Figure \ref{fig:quality-plots1} also shows the presence of a possible outlier
+            with 1216 PROD\_DFTS.  That data point is dropped for the remaining analysis.
+            At this point, a simple linear regression model can be fit to the remaining
+            798 observations. At this point, no transformations have been performed
+            on the data.  The linear regression model yields all 3 independent
+            variables as significant and an overall $R^2 = .72$.  The source
+            code and some further analysis can be found in Appendix 
+            \ref{app:quality-history}. It appears to 
+            be a good fit and thus all Application IDs will have the same baseline
+            quality function.  Therefore, $f$ does not need a subscript, and $f$
+            can be seen below.
+
+            \[
+                f = 5.92+ 0.035 \cdot DEV\_EFF - 0.36 \cdot SIT\_DFTS + 1.05 \cdot UAT\_DFTS
+            \]
+
+            Now that $f$ has been determined, the quality scores for each
+            application can be calculated for all the months beyond 2013.
 

### 2015-03-04 source/quality.R

@@ -1,0 +1,69 @@
+### Load the necessary libraries
+library('sense')
+library('ggplot2')
+
+### Load Raw Quality Data
+setAs("character","myDate", 
+      function(from) {as.Date(from, format="%m/%d/%Y")} )
+setClass('myDate')
+
+quality_raw <- read.csv('data/quality_raw.csv', 
+                         colClasses=c('factor',
+                                      'myDate',
+                                      'numeric',
+                                      'numeric',
+                                      'numeric',
+                                      'numeric') )
+
+### Get descriptive statistics
+str(quality_raw)
+summary(quality_raw)
+var(quality_raw)
+
+### Find the Baseline Quality Function
+#### Use data prior to 2014
+history_quality_raw = 
+        quality_raw[quality_raw$MONTH_DT 
+                     <= as.Date('2013-12-31') ,]
+
+#### Create some plots of the historical quality data
+par(mfrow=c(2,2))
+plot(history_quality_raw$DEV_EFF, 
+    history_quality_raw$PROD_DFTS, 
+     xlab='DEV_EFF', ylab='PROD_DFTS', col='steelblue')
+plot(history_quality_raw$SIT_DFTS, 
+    history_quality_raw$PROD_DFTS, 
+     xlab='SIT_DFTS', ylab='PROD_DFTS', col='steelblue')
+plot(history_quality_raw$DEV_EFF, 
+    history_quality_raw$PROD_DFTS, 
+     xlab='UAT_DFTS', ylab='PROD_DFTS', col='steelblue')
+
+
+##### Remove the outlier data point with 1216 PROD_DFTS
+history_quality_clean = history_quality_raw[history_quality_raw$PROD_DFTS < 1000,]
+
+##### create the model after dropping the
+##### data point with over 1000 PROD_DFTS
+baseline_quality_function = lm(PROD_DFTS ~ DEV_EFF + SIT_DFTS + UAT_DFTS, 
+           data=history_quality_clean )
+summary(baseline_quality_function)
+
+par(mfrow=c(1,2))
+qqnorm(baseline_quality_function$resid,col='steelblue')
+qqline(baseline_quality_function$resid,col='steelblue')
+summary(baseline_quality_function)$sigma
+plot(baseline_quality_function$fitted,abs(baseline_quality_function$resid),
+     col='steelblue',
+    main='Fitted vs Resid',
+    xlab='Fitted',
[…]

### 2015-03-04 appendices.tex
finishing quality for case study

@@
 
-    \subsection{QUALITY HISTORICAL SOURCE CODE AND ANALYSIS}
+    \subsection{QUALITY HISTORICAL R CODE AND ANALYSIS}
     \label{app:quality-history}
-        \lstinputlisting[language=R]{source/quality.R}
+        \lstinputlisting[language=R]{source/quality_historical.R}
         The source code for the selected baseline quality function
@@
         \end{figure}
+
+    \subsection{QUALITY SCORES - R CODE}
+        \lstinputlisting[language=R, label=src:quality]{source/quality.R}
 

### 2015-03-04 source/quality_historical.R

@@ -1,0 +1,69 @@
+### Load the necessary libraries
+library('sense')
+library('ggplot2')
+source('barchart.R')
+
+### Load Raw Quality Data
+setAs("character","myDate", 
+      function(from) {as.Date(from, format="%m/%d/%Y")} )
+setClass('myDate')
+
+quality_raw <- read.csv('data/quality_raw.csv', 
+                         colClasses=c('factor',
+                                      'myDate',
+                                      'numeric',
+                                      'numeric',
+                                      'numeric',
+                                      'numeric') )
+
+### Get descriptive statistics
+str(quality_raw)
+summary(quality_raw)
+var(quality_raw)
+
+### Find the Baseline Quality Function
+#### Use data prior to 2014
+history_quality_raw = 
+        quality_raw[quality_raw$MONTH_DT 
+                     <= as.Date('2013-12-31') ,]
+
+#### Create some plots of the historical quality data
+par(mfrow=c(2,2))
+plot(history_quality_raw$DEV_EFF, 
+    history_quality_raw$PROD_DFTS, 
+     xlab='DEV_EFF', ylab='PROD_DFTS', col='steelblue')
+plot(history_quality_raw$SIT_DFTS, 
+    history_quality_raw$PROD_DFTS, 
+     xlab='SIT_DFTS', ylab='PROD_DFTS', col='steelblue')
+plot(history_quality_raw$DEV_EFF, 
+    history_quality_raw$PROD_DFTS, 
+     xlab='UAT_DFTS', ylab='PROD_DFTS', col='steelblue')
+
+##### Remove the outlier data point with 1216 PROD_DFTS
+history_quality_clean = history_quality_raw[history_quality_raw$PROD_DFTS < 1000,]
+
+##### create the model after dropping the
+##### data point with over 1000 PROD_DFTS
+baseline_quality_function = lm(PROD_DFTS ~ DEV_EFF + SIT_DFTS + UAT_DFTS, 
+           data=history_quality_clean )
+summary(baseline_quality_function)
+
+par(mfrow=c(1,2))
+qqnorm(baseline_quality_function$resid,col='steelblue')
+qqline(baseline_quality_function$resid,col='steelblue')
+summary(baseline_quality_function)$sigma
+plot(baseline_quality_function$fitted,abs(baseline_quality_function$resid),
+     col='steelblue',
+    main='Fitted vs Resid',
+    xlab='Fitted',
[…]

### 2015-03-04 paper_40_cri.tex
working on case study - quality
updated case study availability

@@
                         and \textit{Development Effort}
-                    \item $6\sigma$ 6 times an estimate of the standard deviation of the 
-                        population using function $f_i$ above
+                    \item $\sigma^2$ is the estimated variance
                 \end{itemize}
@@
     \subsection{CRI COMPARED}
+        CRI is one way to evaluate an SDO, and it is also a technique of
+        software analytics.  Therefore, it is beneficial to compare CRI
+        with some of the other techniques and guidelines available. The
+        next sections will provide those comparisons.
 

### 2015-03-04 paper_70_case-study.tex
finishing quality for case study
updated case study availability

@@
         frequency will be monthly.  Thus, scores will fall
-        in the range $[-100,100]$.
+        in the range $[-100,100]$.  Also, equal weighting is applied to 
+        all elements and all Project IDs, Application IDs, and System IDs.
         \subsubsection{QUALITY}
@@
             application can be calculated for all the months beyond 2013.
+            Appendix \ref{src:quality} provides the necessary R code to
+            perform the calculations.  Figure \ref{fig:quality-scores} shows
+            the quality scores for 2014 and beyond.  As can be seen, the
+            scores are greatly above expectations.  That is an indication
+            of improved quality over historical performance.
+
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[scale=.3]{images/quality_scores.png}
+                \caption{CRI QUALITY SCORES}
+                \label{fig:quality-scores}
+            \end{figure}
 
         \subsubsection{AVAILABILITY}
+            For the availability data,
+            some descriptive statistics can be seen in 
+            Table \ref{tab:availability_desc}.  The percent uptime
+            was precalculated for this data so uptime, scheduled downtime,
+            and unscheduled downtime are not needed.  Availability
+            does not rely upon analysis of historical data since
+            a known upper and lower bound exist, 1 and 0 respectively.
+
+            \begin{longtable}{@{}l rr rrr}
+                \toprule%
+                 \centering%
+                 {\bfseries Column}
+                 & {\bfseries Min}
+                 & {\bfseries Max}
+                 & {\bfseries Median}
+                 & {\bfseries Mean}
+                 & {\bfseries Variance} \\
+
+                \cmidrule[0.2pt](r{0.125em}){1-1}%
+                \cmidrule[0.2pt](lr{0.125em}){2-2}%
+                \cmidrule[0.2pt](l{0.125em}){3-3}%
+                \cmidrule[0.2pt](l{0.125em}){4-4}%
+                \cmidrule[0.2pt](l{0.125em}){5-5}%
+                % \midrule
+                \endhead
+
+                Percent Uptime & 0 & 1.0 & 1.0 & 0.9745 & 0.023 \\
+                \myrowcolour%
+                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\
+
+                \bottomrule
+
+                \multicolumn{6}{c}{7522 obs. from 83 Application IDs from 2008 to 2015} \\
+
+                \caption{AVAILABILITY DATA DESCRIPTIVE STATISTICS}
+                \label{tab:availability_desc}
+            \end{longtable}
+
+            Since percent uptime has already been calculated and no historical
+            analysis needs to be performed, the calculation of the scores
+            can be performed. 
+            R code to compute the CRI availability scores can be found in Appendix
+            \ref{src:availability}. Figure \ref{fig:availability-scores} displays
+            the CRI availability scores.  As can be seen the scores are all above
+            70.  That is good from a performance standpoint, but it might be an
+            indication that the expected uptimes could be raised.  If expected
+            uptimes are consistently being exceeded, some consideration should
+            be given to increase the expected uptimes.  This shows that
+            organizations, or at least this particular organization, are getting
+            very good at keeping computer systems available.  Therefore,
+            SLAs need to be adjusted to properly reflect the better performance.
+
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[scale=.3]{images/availability_scores.png}
+                \caption{CRI AVAILABILITY SCORES}
+                \label{fig:availability-scores}
+            \end{figure}
+
         \subsubsection{SCHEDULE}

### 2015-03-04 source/availability.R

@@ -1,0 +1,36 @@
+library('sense')
+source('barchart.R')
+
+# Load Data
+# ---------
+#
+# Load the Availability data.
+setAs("character","myDate", 
+      function(from) {as.Date(from, format="%m/%d/%Y")} )
+setClass('myDate')
+
+avail_raw <- read.csv('data/availability_raw.csv',
+                      colClasses=c('factor',
+                                    'myDate',
+                                    'numeric',
+                                    'numeric'))
+
+summary(avail_raw)
+str(avail_raw)
+
+# trim to only 2014 and newer
+avail_data = 
+        avail_data[avail_data$SLA_DATE >= as.Date('2014-01-01') ,]
+
+avail_data$SCORE =  ifelse(
+  avail_data$ACTUAL <= avail_data$EXPECTED,
+  (avail_data$ACTUAL - avail_data$EXPECTED)/avail_data$EXPECTED,
+  (avail_data$ACTUAL - avail_data$EXPECTED)/(1 - avail_data$EXPECTED)
+  )       
+ 
+avail_scores = aggregate(SCORE ~ SLA_DATE, avail_data, mean )
+avail_scores$SLA_DATE = as.yearmon(avail_scores$SLA_DATE, "%Y-%B")
+avail_scores$SCORE = round(100* avail_scores$SCORE, 2)
+
+barchart(avail_scores, main='CRI Availability Scores',
+         ylab='CRI Quality Score',xlab='Month/Year')

### 2015-03-04 source/barchart.R

@@ -1,0 +1,17 @@
+library('ggplot2')
+install.packages('zoo')
+library('zoo')
+library('scales')
+
+barchart <- function(data, main='CRI Scores', xlab='Month', ylab='MPI Score') {
+    
+    ggplot(data, aes(x=as.Date(MONTH_DT), y=SCORE, fill=SCORE)) + 
+      geom_bar(stat = "identity" ) +
+      geom_text(aes(label=round(SCORE, 2), vjust=ifelse(sign(SCORE)>=0, -.4, 1.4)), size=9 ) + 
+      guides(fill=FALSE) +
+      ylim(-100,100) +
+      scale_x_date(labels = date_format("%m/%y"), breaks = date_breaks("month")) +
+      ggtitle(main) +
+      ylab(ylab) +
+      xlab(xlab)
+}

### 2015-03-04 paper_40_cri.tex
update sensitivity description

@@
                     Frequency Date & Date & Required \\
-                    Requirements Scheduled & Integer & Required \\
-                    \myrowcolour%
-                    Actual Requirements Released & Integer  & Required \\
+                    Scheduled Requirements & Integer & Required \\
+                    \myrowcolour%
+                    Actual Requirements & Integer  & Required \\
 
@@
     \label{sub:sensitivity}
-
-        Some simulations will be run with data from each given distribution.  Then the CRI scores
-        will be analyzed.
-        For more on sensitivity analysis in statistical modeling, see \cite{Saltelli2000}.
+        The sensitivity of the formulas should be tested as the scores should not
+        flucate drastically for similar values.  There are 2 possible techniques
+        for testing the sensitivity of the formulas. 
+        \begin{description}
+            \item[First] Given the historical data that has been collected,
+                alter the values by some small random amount.  Then recalculate
+                the CRI element score and compare with the original score.  This
+                technique can be repeated many times in order to verify
+                small changes do not largely affect the score.  Thus, a 
+                formula which is not overly sensitive. 
+            \item[Second] Another technique is to use Monte Carlo methods to 
+                randomly generate input values for the element functions.  
+                This can be done by finding the distributions of the historical
+                data, and randomly selecting from that distribution.  If historical
+                data is not available, then For more on sensitivity analysis 
+                in statistical modeling, see \cite{Saltelli2000}.
+        \end{description}
+
+        .
 

### 2015-03-04 paper_40_cri.tex
defined the requirements element, so finished chapter 4

@@
 
-                Then $S_1$ represents the quality score for that given time period.
+                Then $S_1$ represents the CRI quality score for that given time 
+                frequency.
 
@@
                 \begin{itemize}
+                    \item $S_{2_i}$ is the availability score for System ID $i$
                     \item $A_{a_i}$ actual availability for System ID $i$
@@
                 \]
+                where $S_2$ is the CRI availability score for the time frequency.
 
@@
                 \begin{itemize}
+                    \item $S_{3_i}$ is the satisfaction score for Question ID $i$
                     \item $a_{ij}$ answer to question $i$ for respondent $j$
@@
                 \]
+                where $S_3$ is the CRI satisfaction score for the time frequency.
 
@@
                 \]
+                where
+                \begin{itemize}
+                    \item $S_{4_i}$ is the schedule score for Project ID $i$
+                \end{itemize}
 
@@
                 \]
+                where $S_4$ is the CRI schedule score for the time frequency.
 
@@
                 \end{itemize}
-                Again, this was just an alternate approach to scoring schedule.  It will not be used
-                in the case studies.
+                Again, this was just an alternate approach to scoring schedule.  
+                It will not be used in the case studies.
 
         \subsubsection{REQUIREMENTS}
-            The requirements of a software development organization are important.
-
+            The requirements of an SDO are important. Requirements are desired 
+            new features or enhancements to a software product.  It is important
+            to know how many requirements
+            were scheduled to be completed versus how many actually got completed. 
+            They provide a measurement
+            of the amount of work being completed. However, not all requirements
+            are created equal.  Some requirements can be quickly and easily
+            implemented while other requirements will take much longer.  It
+            is often difficult to know the challenges ahead of time.  Due to
+            this uncertainty, estimating
+            the number of requirements a team can complete in a given time frame can
+            be difficult. Thus, number of requirements is one way to measure 
+            amount of work
+            but there are others.  Here are 3 possible choices in descending
+            order of preference.
             \begin{description}
-              \item[Function Points] find a definition and a comparison with story points
-              \item[Story Points] Look in some agile book
+                \item[Function Points] Function points measure the size of the
+                    software functionality, not the size or time required
+                    to implement the functionality \cite{Jensen2014}.  
+                    If done properly,
+                    function points will provide the most concise measurement
+                    for amount of work being completed. 
+                \item[Story Points] Story points, sometimes just referred to 
+                    as stories, are broken down requirements that can be
+                    completed in an Agile Sprint of 2 to 4 weeks.  A 
+                    story is usually smaller, simpler, and more concise
+                    that a plain requirement. 
+                    Unfortunately, these only apply to an
+                    SDO using the Agile methodology, specifically 
+                    Scrum \cite{Ashmore2014}.
+                \item[Requirements] These are just the requirements as
+                    written by the users or business partners.  Each requirement
+                    can vary greatly from another requirement.  Estimating
+                    number of requirements can be a difficult if not impossible
+                    task.  
             \end{description}
 
+            To summarize, this element is not completely a measurement of requirements
+            but rather a measurment of the work being completed.
+
             \paragraph{REQUIREMENTS DATA}
+                Table \ref{tab:req} specifies the data required to compute
+                a score for the requirements element of CRI.  Again,
+                scheduled requirements and actual requirements can also 
+                be a count of story points or function points.  All of 
+                the columns are required. The data collected is the
+                frequency date and then the number of requirements scheduled
+                to be completed and the actual number of requirements completed.
 
@@
             \paragraph{REQUIREMENTS FORMULA}
-                Requirements are desired new features or enhancements 
-                to a software product.  It is important to know how many requirements
-                were scheduled to be completed versus how many actually got completed.  
+                The requirements formula is the percentage above or below the
+                scheduled number of requirements. Requirements have a nice
+                lower bound of 0 since negative requirements cannot be 
+                completed\footnote{Theoritically, a negative requirement would
+                be considered a defect.}.  Unforntunately, an upper bound
+                does not exist.  The variablity of requirements is not
+                as large as the variability of the number of defects, so
+                a simpler strategy can be used.  For requirements, a 
+                multiplier $b$ will be used to find the upper bound. The
+                number of scheduled requirements should be multiplied by
+                $b$ to obtain the upper bound.  The value of $b$ should
+                be determined by looking at the historical data to make sure
+                no number of completed requirements will exceed $b$ times
+                the number of scheduled requirements. An example will be shown
+                in Section \ref{sec:case-req}. Common choices for $b$ will be 1
+                and 2. Also, the formula will be
+                created to deal with a value going above the upper bound.
+
+                \begin{displaymath}
+                   S_{5_i} = \left\{
+                     \begin{array}{lr}
+                       \text{where } R_{a_i} > b \times R_{s_i} & :  1 \times k \\
+                       \text{where } R_{a_i} \leq R_{s_i} & : \left[ \frac{R_{a_i} - R_{s_i}}{R_{s_i}}\times k \right] \\
+                       \text{where } R_{a_i} > R_{s_i}  & : \left[ \frac{R_{a_i} - R_{s_i} }{b \cdot R_{s_i}}\times k \right]
+                     \end{array}
+                   \right. \text{   , calculate requirements score for each project $i$}
+                \end{displaymath}
+                where
+                \begin{itemize}
+                    \item $S_{5_i}$ is the requirements score for Project ID $i$
+                    \item $R_{a_i}$ actual requirements completed for Project ID $i$
+                    \item $R_{s_i}$ expected requirements completed for Project ID $i$
+                    \item $b$ multiplier to determine the upper bound
+                \end{itemize}
+                Then the requirements score is calculated as below.  
+                Use a weighted average to combine the requirements scores
+                from the Project IDs.
+
                 \[
-                    S_5 = \frac{\sum^n_{i=1}\left( R_{a_i} - R_{e_i} \right)}{n}
+                    S_{5} = \sum\limits^n_{i=1} w'_i S_{5_i} \text{ where }
+                        \sum\limits^n_{i=1} w'_i = 1
                 \]
-                \begin{itemize}
-                    \item $R_a$ actual requirements completed for application $i$
-                    \item $R_e$ expected requirements completed for application $i$
-                \end{itemize}
+
+                where $S_5$ is the CRI requirements score for the time frequency.
 
@@
             \[
-                CRI =\sum\limits^n_{i=1} w_i S_i \text{ where } \sum\limits^n_{i=1} w_i = 1
+                CRI =\sum\limits^n_{i=1} w_i S_i 
+                    \text{ where } \sum\limits^n_{i=1} w_i = 1
             \]
+            where
+            \begin{itemize}
+                \item $CRI$ is the overall CRI score for the time frequency
+            \end{itemize}
+
+            This weighted average allows for a score to be computed even when not
+            all 5 elements are present. Just perform the weighted average with
+            as many elements as present.  This technique allows CRI to implemented
+            before data for all the elements has been collected.  Just begin
+            to average elements as they become accessible.
 

### 2015-03-04 paper_70_case-study.tex
update sensitivity description
defined the requirements element, so finished chapter 4

@@
         \subsubsection{REQUIREMENTS}
+        \label{sec:case-req}
+            There were 15 rows of data that contained 0 for both
+            scheduled and actual
+            \begin{longtable}{@{}l rr rrr}
+                \toprule%
+                 \centering%
+                 {\bfseries Column}
+                 & {\bfseries Min}
+                 & {\bfseries Max}
+                 & {\bfseries Median}
+                 & {\bfseries Mean}
+                 & {\bfseries Variance} \\
+
+                \cmidrule[0.2pt](r{0.125em}){1-1}%
+                \cmidrule[0.2pt](lr{0.125em}){2-2}%
+                \cmidrule[0.2pt](l{0.125em}){3-3}%
+                \cmidrule[0.2pt](l{0.125em}){4-4}%
+                \cmidrule[0.2pt](l{0.125em}){5-5}%
+                % \midrule
+                \endhead
+
+                Scheduled & 0 & 1.0 & 1.0 & 0.9745 & 0.023 \\
+                \myrowcolour%
+                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\
+                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\
+
+                \bottomrule
+
+                \multicolumn{6}{c}{476 obs. from 402 Project IDs from 2010 to 2015} \\
+
+                \caption{REQUIREMENTS DATA DESCRIPTIVE STATISTICS}
+                \label{tab:requirements_desc}
+            \end{longtable}
+
+            The multiplier $b$ is set to 1 because none of the historical performance
+            ever exceeded 25\% more requirements than scheduled. Thus the upper
+            bound is the number of schedule requirements plus $b=1$ times
+            the number of scheduled requirements, for an upper bound of twice
+            the scheduled requirements.
+
         \subsubsection{OVERALL}

### 2015-03-05 appendices.tex
updated case study availability
updated schedule in the case study

@@
             \centering
-            \includegraphics[scale=.3]{images/quality_diag.png}
+            \includegraphics[scale=.25]{images/quality_diag.png}
             \caption{QUALITY DIAGNOSTIC PLOTS}
@@
 
+    \subsection{BAR CHART - R CODE}
+        This is a code for generating a bar chart.  It is used for reporting
+        the scores of all the elements.
+        \lstinputlisting[language=R, label=src:barchart]{source/barchart.R}
+
     \subsection{QUALITY SCORES - R CODE}
         \lstinputlisting[language=R, label=src:quality]{source/quality.R}
+
+    \subsection{AVAILABILITY SCORES - R CODE}
+        \lstinputlisting[language=R, label=src:availability]{source/availability.R}
+
+    \subsection{REQUIREMENTS SCORES - R CODE}
+        \subsubsection{REQUIREMENTS HISTOGRAM}
+        \label{app:requirements-hist}
+            Figure \ref{fig:req-hist} shows a histogram of the data
+            for requirements.  The histogram is based upon the
+            fraction $\frac{Scheduled Requirements}{Actual Requirements}$. The
+            values where the fraction equals 1 have been left out of the histogram.
+            So, the histogram show only the data that did not deliver exactly
+            on the number of requirements. Rarely are more requirements actually 
+            delivered than what was scheduled.  On the opposite side, the histogram
+            bars shrink as they approach zero indicating that it is more common
+            to miss a few requirements than all the requirements.
+
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[scale=.3]{images/req_hist.png}
+                \caption{REQUIREMENTS DATA HISTOGRAM (ACTUAL/SCHEDULED)}
+                \label{fig:req-hist}
+            \end{figure}
+
+        \subsubsection{REQUIREMENTS R CODE}
+        \lstinputlisting[language=R, label=src:requirements]{source/requirements.R}
 

### 2015-03-05 paper_10_intro.tex
updated schedule in the case study

@@
     of the organization. The
-    score is based upon data collected for 5 result indicators
+    score is based upon data collected for 5 key result indicators
     of a software development organization: quality, availability,
@@
     to be comparative between organizations, but to 
-    form a historical baseline for a specific organization.
+    form a historical baseline for a specific organization.  The single
+    number is targeted for upper-level management whom need a quick
+    and simple strategy to evaluate the performance of the organization.
 
@@
 
-    The remainder of this dissertation is divided into 5 chapters.  The next chapter provides
-    an overview of software, software development lifecycles, software engineering, and software
-    development organizations.  Chapter 3 introduces what is meant by the term data-driven
-    software engineering. Chapter 4 then provides an explanation of the Cumulative
+    The remainder of this dissertation is divided into 7 chapters.  Chapter 2 provides
+    an overview of software, software development life cycles, software engineering, and software
+    development organizations.  Chapter 3 introduces some existing techniques for measuring
+    a software development organization. Chapter 4 then provides an explanation of the Cumulative
     Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well
     as the formulas, framework, and data necessary to produce the CRI. Chapter 5 provides
-    a technological framework for generating and storing the current and historical CRI values.
+    a technological framework for storing the current and historical CRI values.
     Chapter 6 demostrates how CRI can be implemented in a software development portion of 
-    a large financial institution.  Chapter 7 concludes the dissertation with a summary
-    of the results and some possible future directions for further enhancements.
+    a large financial institution. Chapter 7 discusses some possible future directions 
+    for further enhancements. Chapter 8 concludes the dissertation with a summary
+    of the results.
 

### 2015-03-05 paper_70_case-study.tex
updated schedule in the case study

@@
         \subsubsection{SCHEDULE}
+            Figure \ref{tab:schedule_desc} displays some descritive statistics
+            for the schedule data.  Since the data is mostly dates, the 
+            descriptive statistics are limited, so extra values were
+            added to the table after removing 4 outliers.  The new values
+            in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
+            Difference (Actual Finish - Schedule Finish), and 
+            $\Delta$ ($frac{\Delta}{\text{Schedule Duration}}$ ).
+
+            \begin{longtable}{@{}l rr rrr}
+                \toprule%
+                 \centering%
+                 {\bfseries Column}
+                 & {\bfseries Min}
+                 & {\bfseries Max}
+                 & {\bfseries Median}
+                 & {\bfseries Mean} \\
+
+                \cmidrule[0.2pt](r{0.125em}){1-1}%
+                \cmidrule[0.2pt](lr{0.125em}){2-2}%
+                \cmidrule[0.2pt](l{0.125em}){3-3}%
+                \cmidrule[0.2pt](l{0.125em}){4-4}%
+                \cmidrule[0.2pt](l{0.125em}){5-5}%
+                % \midrule
+                \endhead
+
+                Scheduled Start & 2013-06-23 & 2015-01-24 & 2014-03-17 & 2014-04-01 \\
+                \myrowcolour%
+                Scheduled Finish & 2014-01-31 & 2015-01-25 & 2014-08-08 & 2014-08-02 \\
+                Actual Start & 2013-01-07 & 2014-10-17 & 2014-01-15  & 2014-02-10 \\
+                \myrowcolour%
+                Actual Finish & 2014-02-20 & 2014-12-31 & 2014-08-31 & 2014-08-11 \\
+                Schedule Duration & 8 & 480 & 92 & 137.7 \\
+                \myrowcolour%
+                Difference & -283 & 149 & 0.0 & -8.919 \\
+                $\Delta$ & -4.75 & 0.6564 & 0.0 & -0.2641 \\
+
+                \bottomrule
+
+                \multicolumn{5}{c}{41 obs. from 40 Project IDs from mid 2013 to 2015} \\
+
+                \caption{SCHEDULE DATA DESCRIPTIVE STATISTICS}
+                \label{tab:schedule_desc}
+            \end{longtable}
+
+            The first task with the schedule data is fitting the data to 
+            a distribution.  Figure \ref{fig:schedule-hist} shows
+            a plot of the histogram of the $\Delta$s and a
+            Cauchy curve with location = 0.0 and scale = 0.057.  The Cauchy
+            distribution appears to be a good fit.
+
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[scale=.25]{images/schedule_hist.png}
+                \caption{SCHEDULE DATA HISTOGRAM WITH CAUCHY}
+                \label{fig:schedule-hist}
+            \end{figure}
+
+            Now that the distribution has been identified, the next step
+            is determining the Cumulative Distribution Function (C.D.F.)
+            for the distribution.  For Cauchy, the general C.D.F. is 
+            given as follows.
+            \[
+                C.D.F. = \frac{1}{\pi}\arctan{\frac{x-x_0}{\gamma}} + \frac{1}{2}
+            \]
+            where 
+            \begin{itemize}
+                \item $x_0$ is the location
+                \item $\gamma$ is the scale
+            \end{itemize}
+
+            Referencing Equation \ref{eq:CDF}, the schedule formula
+            for individual project IDs becomes.
+            \[
+               S_{4_i} = \frac{200}{\pi}\arctan{\left(\frac{\Delta_i}{0.057} \right)} 
+            \]
+
+            The CRI schedule scores can be seen in Figure \ref{fig:schedule-scores}.
+            These scores appear more eratic than the other elements.
+            This difference is due to the small number of releases every month.
+
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[scale=.3]{images/schedule_scores.png}
+                \caption{CRI SCHEDULE SCORES}
+                \label{fig:schedule-scores}
+            \end{figure}
+
         \subsubsection{REQUIREMENTS}
         \label{sec:case-req}
-            There were 15 rows of data that contained 0 for both
-            scheduled and actual
+            The data for requirements is actually counts of story points
+            instead of requirements.  That is because story points
+            are a better choice for counting, since they are more
+            uniform in size than raw requirements.  Also, the data
+            contained 15 rows of data with a 0 for the number of
+            scheduled requirements.  Those 15 rows were removed.
+            Table \ref{tab:requirements_desc} shows some descriptive
+            statistics for the remaining rows. A histogram for the
+            data can be seen in Appendix \ref{app:requirements-hist}.
+
             \begin{longtable}{@{}l rr rrr}
@@
 
-                Scheduled & 0 & 1.0 & 1.0 & 0.9745 & 0.023 \\
+                Scheduled Requirements & 0.5 & 1248 & 75.5 & 136.9 & 31243.89 \\
                 \myrowcolour%
-                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\
-                Expected Percent Uptime & 0.93 & 1.0 & 0.98 & 0.9769  & 0.977\\
+                Actual Requirements & 0 & 1247 & 58 & 123.8 & 30844.75 \\
+                $\frac{Actual Requirements}{Scheduled Requirements}$ & 0 & 1.2364 & 1.0 & 0.8515 & 0.05 \\
 
@@
 
-                \multicolumn{6}{c}{476 obs. from 402 Project IDs from 2010 to 2015} \\
+                \multicolumn{6}{c}{461 obs. from 402 Project IDs from 2010 to 2015} \\
 
@@
 
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[scale=.3]{images/requirements_scores.png}
+                \caption{CRI REQUIREMENTS SCORES}
+                \label{fig:requirements-scores}
+            \end{figure}
+
+            Figure \ref{fig:requirements-scores} displays the CRI requirements
+            scores. The scores are as expected considering the histogram. Many
+            of the projects meet the requirements exactly, and when the requirements
+            are not met, it is usually by a small number.
+            Thus the scores are all 0 or slightly below.
+
         \subsubsection{OVERALL}

### 2015-03-05 source/requirements.R

@@ -1,0 +1,38 @@
+library('sense')
+source('barchart.R')
+
+### Now read in the requirements data
+requirements_raw = read.csv('data/requirements_raw.csv',
+                              colClasses=c('factor',
+                                      'Date',
+                                      'numeric',
+                                      'numeric') )
+
+##### remove rows where COMPLETED and SCHEDULED are both 0
+requirements_clean = requirements_raw[requirements_raw$SCHEDULED != 0, ]
+
+requirements_clean$DIFF = requirements_clean$COMPLETED/requirements_clean$SCHEDULED
+summary(requirements_clean)
+str(requirements_clean)
+var(requirements_clean$SCHEDULED)
+var(requirements_clean$COMPLETED)
+var(requirements_clean$DIFF)
+
+hist(requirements_clean[requirements_clean$DIFF != 1,]$DIFF)
+
+##### Now calculate the requirements CRI score
+##### but only for year 2014 and 2015
+current_requirements = requirements_clean[requirements_clean$MONTH_DT 
+                     > as.Date('2013-12-31'), ]
+current_requirements$MONTH_DT = as.yearmon(as.Date(current_requirements$MONTH_DT), "%Y-%B")
+current_requirements$SCORE = 100*(current_requirements$COMPLETED-current_requirements$SCHEDULED)/current_requirements$SCHEDULED
+
+req_scores = aggregate(SCORE ~ MONTH_DT, current_requirements, mean )
+req_scores$SCORE = round(req_scores$SCORE, 2)
+req_scores
+
+barchart(req_scores, main='CRI Requirements Scores', ylab='CRI Requirements Score',xlab='Month/Year')
+
+
+
+

### 2015-03-05 paper_70_case-study.tex
added overall scores for case study

@@
         \subsubsection{OVERALL}
-            All of the months do not include the same elements.
+            Now it is time to combine the scores for the overall CRI.  Notice
+            the schedule does not have scores for January 2014 or January 2015.
+            Presumably, that is because the SDO within the large financial institution
+            does not schedule projects to be completed in January. Much of the work
+            would need to be completed over Christmas and New Year's Day, but many
+            workers take personal time off of work during that time.  Thus some
+            organizations will schedule appropriately.  CRI is well suited to
+            handle this problem.  Just perform a weighted average over the
+            applicable elements.  In this case study, the weights are all equal,
+            so CRI is just a straight average.  Figure \ref{fig:cri-scores}
+            displays the CRI scores as computed with the source code
+            from Appendix \ref{src:overall}.  The scores are all above 0, so this
+            financial institution is consistently performing better
+            than expected.
 
-    An CRI calculation analyzing historical performance.
+            \begin{figure}[ht]
+                \centering
+                \includegraphics[scale=.3]{images/cri_scores.png}
+                \caption{CRI SCORES}
+                \label{fig:cri-scores}
+            \end{figure}
 

### 2015-03-05 source/barchart.R

@@ -3,7 +3,7 @@ install.packages('zoo')
 library('zoo')
 library('scales')
 
-barchart <- function(data, main='CRI Scores', xlab='Month', ylab='MPI Score') {
+barchart <- function(data, main='CRI Scores', xlab='Month/Year', ylab='CRI Score') {
     
     ggplot(data, aes(x=as.Date(MONTH_DT), y=SCORE, fill=SCORE)) + 
       geom_bar(stat = "identity" ) +

### 2015-03-05 source/overall.R

@@ -1,0 +1,12 @@
+
+### Combine the scores
+# overall
+
+full = merge(x = qual_scores, y = avail_scores, by = "MONTH_DT", all = TRUE)
+full = merge(x = full, y = req_scores, by = "MONTH_DT", all = TRUE)
+full = merge(x = full, y = sched_scores, by = "MONTH_DT", all = TRUE, suffixes='sched')
+
+full$SCORE = apply(full[,seq(2,5)], 1, 
+                   function(x) {sum(x,na.rm=TRUE)/sum(!is.na(x))} )
+
+barchart(full)

### 2015-03-05 source/schedule.R

@@ -1,0 +1,52 @@
+source('barchart.R')
+
+## Load the Schedule data.
+setAs("character","myDate", function(from) {as.Date(from, format="%m/%d/%Y")} )
+setClass('myDate')
+
+schedule_raw <- read.csv('data/schedule_raw.csv',
+                      colClasses=c('factor',
+                                   'myDate',
+                                   'myDate',
+                                   'myDate',
+                                   'myDate',
+                                   'myDate'))
+summary(schedule_raw)
+str(schedule_raw)
+
+#### Clean up data by removing all rows with 
+#### schedule start, schedule end, and actual end
+clean_sched_data = schedule_raw[ !is.na(schedule_raw$ACTUAL_FINISH) & !is.na(schedule_raw$SCHED_START) & !is.na(schedule_raw$SCHED_FINISH),]
+
+#### Find the estimated duration, 
+#### and the delta from the estimated finish 
+#### and percent
+clean_sched_data$EST_DUR = as.numeric(clean_sched_data$SCHED_FINISH - clean_sched_data$SCHED_START+1)
+clean_sched_data$DELTA = as.numeric(clean_sched_data$SCHED_FINISH - clean_sched_data$ACTUAL_FINISH )
+clean_sched_data$PERCENT_DELTA = clean_sched_data$DELTA/clean_sched_data$EST_DUR
+
+#### Remove some of the outlier data
+clean_sched_data = clean_sched_data[abs(clean_sched_data$PERCENT_DELTA) < 20 , ]
+summary(clean_sched_data)
+str(clean_sched_data)
+
+### Fit a Distribution to the data
+
+location = median(clean_sched_data$PERCENT_DELTA)
+scale = IQR(clean_sched_data$PERCENT_DELTA)/2
+c(location, scale)
+h = hist(clean_sched_data$PERCENT_DELTA, breaks = 70, prob=TRUE, ylim=c(0,6), main='Histogram of Schedule Data')
+x=seq(-5,5,length=200)
+curve(dcauchy(x, location, scale ), 
+          col="darkblue", lwd=2, add=TRUE)
+
+### Now find the CRI scores
+sched_data = clean_sched_data
+sched_data$SCORE = (200/pi)*atan(sched_data$PERCENT_DELTA /scale)
+sched_data$MONTH_DT = as.yearmon(sched_data$ACTUAL_FINISH, "%Y-%B")
[…]

### 2015-03-06 paper_70_case-study.tex
updated sensitivity analysis and conclusion added latest PDF file

@@
 
-    \subsection{WITH HISTORICAL DATA}
     After the data has been collected, the raw data can be stored in the SDLC
@@
     all elements and all Project IDs, Application IDs, and System IDs.
-        \subsubsection{QUALITY}
+
+    \subsection{QUALITY}
         The first step to dealing with the quality data is a quick
@@
 
-        \subsubsection{AVAILABILITY}
+    \subsection{AVAILABILITY}
         For the availability data,
@@
 
-        \subsubsection{SCHEDULE}
+    \subsection{SCHEDULE}
         Figure \ref{tab:schedule_desc} displays some descritive statistics
@@
 
-        \subsubsection{REQUIREMENTS}
+    \subsection{REQUIREMENTS}
     \label{sec:case-req}
@@
 
-        \subsubsection{OVERALL}
+    \subsection{OVERALL}
         Now it is time to combine the scores for the overall CRI.  Notice
@@
 
-%%\subsection{WITHOUT HISTORICAL DATA}
+    \subsection{CORRELATION AND SENSITIVITY}
+        Based upon the graphs for the elements scores, there does not
+        appear to be any correlation.  None of the graphs
+        rise and fall during the same intervals.  The missing element,
+        satisfaction, is the most likely element to exhibit correlation,
+        so the 4 elements analyzed here remain independent.
 
-%%An CRI calculation with default values for quality, schedule and requirements.
+        To check the sensitivity of the CRI formula, the first method
+        from Section \ref{sub:sensitivity} is used.  Small random
+        values were added to the input values of the formulas. 
+        Then the new values were used to calculated the element scores 
+        at the respective Application ID or Project ID level.  Finally
+        the new CRI element scores were compared with the previous
+        scores from the unaltered data.  The goal is to show small
+        changes in the input values result in small changes to the 
+        CRI element score.  Figure \ref{fig:sensitivity} shows
+        histograms of the new scores compared with the previous scores.
+        None of the formulas exhibit too much sensitivity as the 
+        histograms all indicate most of the score changes are small,
+        as seen by the high peak of the histograms.
+
+        \begin{figure}[ht]
+            \centering
+            \includegraphics[scale=.3]{images/sensitivity.png}
+            \caption{CRI SENSITIVITY ANALYSIS}
+            \label{fig:sensitivity}
+        \end{figure}
+
+        The random values added were based on the standard 
+        deviations of the values in the column.
+        Quality and Requirements used the standard deviation of the
+        matching Application ID or Project ID.  This slight difference
+        is due to the wide variation of standard deviations between
+        Application IDs for Quality and Project IDs for Requirements. 
+        Table \ref{tab:sensitivity} shows the columns that were
+        altered for each element.
+
+        \begin{longtable}{@{}l rr rrr}
+            \toprule%
+             \centering%
+             {\bfseries CRI Element}
+             & {\bfseries Columns Altered } \\
+
+            \cmidrule[0.2pt](r{0.125em}){1-1}%
+            \cmidrule[0.2pt](lr{0.125em}){2-2}%
+            % \midrule
+            \endhead
+
+            Quality  & Development Effort, SIT Defects, UAT Defects \\
+            \myrowcolour%
+            Availability & Percent Uptime \\
+            Schedule &  $\frac{\text{Schedule Finish - Actual Finish}}
+                    {\text{Scheduled Finish - Scheduled Start}}$ \\
+            \myrowcolour%
+            Requirements & Actual Requirements Released \\
+
+            \bottomrule
+
+            \multicolumn{6}{c}{461 obs. from 402 Project IDs from 2010 to 2015} \\
+
+            \caption{CRI SENSITIVITY ANALYSIS}
+            \label{tab:sensitivity}
+        \end{longtable}
 

### 2015-03-06 paper_80_conclusion.tex
updated sensitivity analysis and conclusion added latest PDF file

@@
 
-There are many metrics that can be used to evaluate a Software Development Organization (SDO). 
-Knowing which metrics to use and what they all mean can be a daunting task.  CRI is a
-proposed solution to the difficulty of measuring an SDO.
+    There are many metrics that can be used to evaluate a Software
+    Development Organization (SDO). The entire SDO needs to be measured 
+    and analyzed properly, not just the development portion. 
+    Knowing which metrics to use and what they all mean can be a daunting task.  
+    This work identified the Cumulative Result Indicator (CRI) which is a
+    proposed solution to the difficulty of measuring an SDO by creating a
+    single number score for upper-level management to use to quickly gauge
+    performance.
 
-Upon completion, this work shall identify:
+    The following have all been provided in this work.
     \begin{itemize}
-    \item Define \textbf{What} characteristics should be measured for an SDO
-    \item Define \textbf{How} to measure those characteristics
-    \item Map the relationship or lack of relationship with a Balanced Scorecard
-    \item Create a Framework to store the necessary data for CRI
-    \item Outline a Process to generate the CRI score
-    \item Provide an example CRI score with real data
+        \item CRI defines what 5 elements of an SDO should be measured.
+            Result indicators are included for quality, availability, satisfaction,
+            schedule, and requirements. 
+        \item CRI defines what data needs to be collected to create a 
+            score for the 5 elements.
+        \item CRI defines the formulas to create a score for the 5 elements.
+        \item A process was outlined to generate the CRI score.
+        \item An SDLC-AE was designed which includes a storage 
+            framework for the necessary CRI data.
+        \item A comparison with existing SDO evaluation techniques was presented.
+        \item Finally, an example CRI score was calculated with data provided by
+            an SDO organization within a large financial institution.
     \end{itemize}
 
-An entire software development organization (SDO) needs to be measured and analyzed properly, not just the development portion.
-This document has provided an overview of what indicators need to be measured for an SDO, and how those indicators can be combined to form a single number indicating the performance score of a software development organization.
-Also, a framework to store this data was discussed.
+    Now SDOs have a technique to consistently measure performance over time.  CRI
+    should help upper-level management identify the areas of the organization
+    that need attention and those that do not.  CRI should save time required to 
+    evaluate the performance since the result is a single number.
 

### 2015-03-06 source/quality.R

@@ -1,69 +1,25 @@
-### Load the necessary libraries
-library('sense')
-library('ggplot2')
-
-### Load Raw Quality Data
-setAs("character","myDate", 
-      function(from) {as.Date(from, format="%m/%d/%Y")} )
-setClass('myDate')
-
-quality_raw <- read.csv('data/quality_raw.csv', 
-                         colClasses=c('factor',
-                                      'myDate',
-                                      'numeric',
-                                      'numeric',
-                                      'numeric',
-                                      'numeric') )
-
-### Get descriptive statistics
-str(quality_raw)
-summary(quality_raw)
-var(quality_raw)
-
-### Find the Baseline Quality Function
-#### Use data prior to 2014
-history_quality_raw = 
+### Now calculate the Quality scores
+#### Get data for 2014 and newer
+current_quality = 
         quality_raw[quality_raw$MONTH_DT 
-                     <= as.Date('2013-12-31') ,]
+                     > as.Date('2013-12-31') ,]
 
-#### Create some plots of the historical quality data
-par(mfrow=c(2,2))
-plot(history_quality_raw$DEV_EFF, 
-    history_quality_raw$PROD_DFTS, 
-     xlab='DEV_EFF', ylab='PROD_DFTS', col='steelblue')
-plot(history_quality_raw$SIT_DFTS, 
-    history_quality_raw$PROD_DFTS, 
-     xlab='SIT_DFTS', ylab='PROD_DFTS', col='steelblue')
-plot(history_quality_raw$DEV_EFF, 
-    history_quality_raw$PROD_DFTS, 
-     xlab='UAT_DFTS', ylab='PROD_DFTS', col='steelblue')
+current_quality$PREDICTION = 
+        predict(baseline_quality_function, newdata=current_quality)
+current_quality$SCORE = 100 * 
+        ifelse(current_quality$PREDICTION 
+               >= current_quality$PROD_DFTS,
+                  (current_quality$PREDICTION 
+                    - current_quality$PROD_DFTS)
+                    /current_quality$PREDICTION,
+                  (current_quality$PREDICTION 
+                    - current_quality$PROD_DFTS)
+                    /(summary(baseline_quality_function)$sigma^2)
+                                     )
 
[…]

### 2015-03-06 source/quality_historical.R

@@ -1,8 +1,3 @@
-### Load the necessary libraries
-library('sense')
-library('ggplot2')
-source('barchart.R')
-
 ### Load Raw Quality Data
 setAs("character","myDate", 
       function(from) {as.Date(from, format="%m/%d/%Y")} )
@@ -38,6 +33,7 @@ plot(history_quality_raw$SIT_DFTS,
 plot(history_quality_raw$DEV_EFF, 
     history_quality_raw$PROD_DFTS, 
      xlab='UAT_DFTS', ylab='PROD_DFTS', col='steelblue')
+
 
 ##### Remove the outlier data point with 1216 PROD_DFTS
 history_quality_clean = history_quality_raw[history_quality_raw$PROD_DFTS < 1000,]

### 2015-03-07 paper_40_cri.tex
updated schedule in the case study
updated sensitivity analysis and conclusion added latest PDF file
rearranged some figures so they appear more inline with the appropriate content

@@
                        \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
-                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{6\sigma_i} \times k
+                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{\sigma_i^2} \times k
                      \end{array}
@@
                     \item $n$ is the number of Application IDs
-                    \item $d_i$ is the actual PROD defects
+                    \item $d_i$ is the actual PROD defects for Application ID $i$
                     \item $f_i$ is the function to predict PROD defects for Application $i$ based upon 
@@
                         and \textit{Development Effort}
-                    \item $\sigma^2$ is the estimated variance
+                    \item $\sigma_i^2$ is the estimated variance for Application $i$
                 \end{itemize}
@@
 
-                \[
+                \begin{equation}
+                \label{eq:CDF}
                     S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
-                \]
+                \end{equation}
                 where
@@
     \subsection{SENSITIVITY OF CRI}
-    \label{sub:sensitivity}
+    \label{sec:sensitivity}
         The sensitivity of the formulas should be tested as the scores should not
@@
                 How sensitive are the results to small changes in one or more of the inputs? & 
-                The question was extensively addressed in section \ref{sub:sensitivity}.  It appears CRI is
+                The question was extensively addressed in section \ref{sec:sensitivity}.  It appears CRI is
                 not overly sensitive to small changes in the inputs.\\

### 2015-03-07 paper_50_sdlc-ae.tex
rearranged some figures so they appear more inline with the appropriate content

@@
 
+    \begin{figure}[hbt]
+        \includegraphics[scale=.75]{images/sdlcae.png}
+        \caption{SDLC ANALYTIC ENGINE}
+        \label{fig:sdlc-ae}
+    \end{figure}
+
     Once all the SDLC data is collected into a single place, there are 
@@
     SDLC-AE does not specify how the data is entered, just how the data is stored.
-
-    \begin{figure}[ht]
-        \includegraphics[scale=.75]{images/sdlcae.png}
-        \caption{SDLC ANALYTIC ENGINE}
-        \label{fig:sdlc-ae}
-    \end{figure}
 
@@
             to store the raw data that is collected.  These tables
-            will line up with the necessary data for each of the 5 elements
+            will match up with the necessary data for each of the 5 elements
             of CRI.  Figure \ref{fig:raw} provides a visual description
@@
             with each other since they are raw data.  The primary goal of
-            these tables is to store the raw data in a single database. The
+            these tables is to store the raw data in a single location. The
             5 table names are:
@@
 
-           \begin{figure}[ht]
+           \begin{figure}[htb]
                 \centering
-                \includegraphics[scale=.55]{images/raw_tables.png}
+                \includegraphics[scale=.52]{images/raw_tables.png}
                 \caption{TABLES FOR RAW CRI DATA}
@@
 
-           \begin{figure}[ht]
+           \begin{figure}[htb]
                 \centering
-                \includegraphics[scale=.55]{images/score_tables.png}
+                \includegraphics[scale=.52]{images/score_tables.png}
                 \caption{TABLES FOR INTERMEDIATE CRI SCORES}
@@
 
-           \begin{figure}[ht]
+           \begin{figure}[hbt]
                 \centering
-                \includegraphics[scale=.55]{images/final_score_tables.png}
+                \includegraphics[scale=.52]{images/final_score_tables.png}
                 \caption{TABLES FOR FINAL CRI SCORES}
@@
 
-%    \subsection{QUERIES}
-%        The section will provide the necessary SQL queries to obtain the correct data
-%        needed to compute the individual elements of CRI.
-%        
-%    \subsection{COMPUTATIONS}
-%        This section will provide R scripts to calculate each individual score and the overall 
-%        CRI score. The scripts will need to be run every time the data is updated and the CRI
-%        score needs to be recalculated.
-
 \end{document}

### 2015-03-07 paper_70_case-study.tex
rearranged some figures so they appear more inline with the appropriate content

@@
 
-        \begin{figure}[ht]
+        \begin{figure}[htb]
             \centering
@@
         \ref{src:availability}. Figure \ref{fig:availability-scores} displays
-        the CRI availability scores.  As can be seen the scores are all above
-        70.  That is good from a performance standpoint, but it might be an
+        the CRI availability scores.
+
+        \begin{figure}[htb]
+            \centering
+            \includegraphics[scale=.3]{images/availability_scores.png}
+            \caption{CRI AVAILABILITY SCORES}
+            \label{fig:availability-scores}
+        \end{figure}
+
+        As can be seen in Figure  \ref{fig:availability-scores}
+        the scores are all above 70 which
+        is good from a performance standpoint, but it might be an
         indication that the expected uptimes could be raised.  If expected
@@
         SLAs need to be adjusted to properly reflect the better performance.
-
-        \begin{figure}[ht]
-            \centering
-            \includegraphics[scale=.3]{images/availability_scores.png}
-            \caption{CRI AVAILABILITY SCORES}
-            \label{fig:availability-scores}
-        \end{figure}
 
@@
     \subsection{OVERALL}
-        Now it is time to combine the scores for the overall CRI.  Notice
-        the schedule does not have scores for January 2014 or January 2015.
+        Now it is time to combine the scores for the overall CRI.
+        Schedule does not have scores for January 2014 or January 2015.
         Presumably, that is because the SDO within the large financial institution
@@
         applicable elements.  In this case study, the weights are all equal,
-        so CRI is just a straight average.  Figure \ref{fig:cri-scores}
-        displays the CRI scores as computed with the source code
-        from Appendix \ref{src:overall}.  The scores are all above 0, so this
-        financial institution is consistently performing better
-        than expected.
+        so CRI is just a straight average.
 
-        \begin{figure}[ht]
+        \begin{figure}[htb]
             \centering
@@
 
-    \subsection{CORRELATION AND SENSITIVITY}
-        Based upon the graphs for the elements scores, there does not
-        appear to be any correlation.  None of the graphs
-        rise and fall during the same intervals.  The missing element,
-        satisfaction, is the most likely element to exhibit correlation,
-        so the 4 elements analyzed here remain independent.
+        Figure \ref{fig:cri-scores}
+        displays the CRI scores as computed with the source code
+        from Appendix \ref{src:overall}.  The scores are all above 0, so this
+        financial institution has performed consistently better
+        than expected.
+
+    \subsection{SENSITIVITY AND CORRELATION}
 
         To check the sensitivity of the CRI formula, the first method
-        from Section \ref{sub:sensitivity} is used.  Small random
+        from Section \ref{sec:sensitivity} is used.  Small random
         values were added to the input values of the formulas. 
@@
 
-        \begin{longtable}{@{}l rr rrr}
+        \begin{longtable}{@{}l r}
             \toprule%
@@
             \cmidrule[0.2pt](r{0.125em}){1-1}%
-            \cmidrule[0.2pt](lr{0.125em}){2-2}%
+            \cmidrule[0.2pt](r{0.125em}){2-2}%
             % \midrule
@@
 
-            \multicolumn{6}{c}{461 obs. from 402 Project IDs from 2010 to 2015} \\
-
             \caption{CRI SENSITIVITY ANALYSIS}
@@
 
+        The columns were altered by adding
+        random noise from a normal distribution with mean 0 and standard
+        deviation as explained above.  The only exception to the normal
+        distribution was for the schedule element.  The schedule element
+        drew its noise from a Cauchy distribution with location and scale
+        as defined when determining the distribution of the schedule data.
+        That Cauchy distribution can be seen with the histogram in 
+        Figure \ref{fig:schedule-hist}.
+
+        Based upon the graphs for the elements scores, there does not
+        appear to be any correlation.  None of the graphs
+        rise and fall during the same intervals.  The missing element,
+        satisfaction, is the most likely element to exhibit correlation,
+        so the 4 elements analyzed here remain independent.
+
 \end{document}

### 2015-03-08 paper_10_intro.tex
use SDO everywhere instead of software development organization

@@
     This work 
-    provides a technique for a software development organization to create
+    provides a technique for a Software Development Organization (SDO) to create
     a single number score which indicates the overall performance
@@
     score is based upon data collected for 5 key result indicators
-    of a software development organization: quality, availability,
+    of an SDO: quality, availability,
     satisfaction, schedule, and requirements.  It is not meant
@@
 
-    Software development organizations are no different than 
+    An SDO is no different than 
     any other business or organization.  There are: tasks
@@
 
-    Software development organizations need a framework to define
+    SDOs need a framework to define
     what measurements should be tracked and how those measurements
@@
     for a consistent evaluation.  CRI analyzes the historical performance
-    of a Software Development Organization (SDO)
+    of an SDO
     to create a baseline in order to provide a broad
@@
     organizations to measure and focus soley on the source code
-    being produced.  However, a software development organization does more
+    being produced.  However, an SDO does more
     than just produce source code.  There is documentation to be
@@
     decisions to be made.  The framework provides an evaluation
-    of the overall software development organization, not just the
+    of the overall SDO, not just the
     source code.
@@
 
-    Other attempts at evaluating a software development organization
+    Other attempts at evaluating an SDO
     have been presented, but none produce a single number score for
-    the entire effort of the software development organization. 
+    the entire effort of the SDO. 
     The following are attempts to evaluate all or parts of 
@@
     development data, it has not yet been applied to the entirety 
-    of a software development organization. It also does not
+    of an SDO. It also does not
     focus on the results of the organization.  It focuses
@@
     Little work exists
-    for scoring the entire software development organization.
+    for scoring the entire SDO.
 
@@
     with other measures in order to provide an overall evaluation
-    of a software development organization.
+    of an SDO.
 
@@
     One area of research that is focusing on the evaluation 
-    of software development organizations
+    of SDOs
     is \textit{software analytics}. 
@@
     development organizations.  Chapter 3 introduces some existing techniques for measuring
-    a software development organization. Chapter 4 then provides an explanation of the Cumulative
+    an SDO. Chapter 4 then provides an explanation of the Cumulative
     Result Indicator (CRI).  It will present the essential elements for calculating the CRI, as well

### 2015-03-08 paper_20_sdo.tex
work on chapter 5, SDLC-AE
use SDO everywhere instead of software development organization

@@
 A \textit{Software Development Organization (SDO)} is any organization or subset of an organization that is responsible
-for the creation, deployment, and maintenance of software.  Many times a software development organization
-is a company that produces software.  Other times, a software development organization is contained
+for the creation, deployment, and maintenance of software.  Many times an SDO
+is a company that produces software.  Other times, an SDO is contained
 within the Information Technology department of a larger organization. Some of the job roles
@@
 \subsection{WHAT IS SOFTWARE ENGINEERING?}
+\label{sec:swe}
     \textit{Software Engineering} as a term dates back to the 

### 2015-03-08 paper_40_cri.tex
use SDO everywhere instead of software development organization

@@
 
-    Software development organizations struggle to measure overall performance.  
+    SDOs struggle to measure overall performance.  
     The \textit{Cumulative Result Indicator (CRI)} is an algorithm to provide a single 
-    number score to measure the performance of a software development organization. 
+    number score to measure the performance of an SDO. 
     It works by statistically analyzing the past performance of the 
@@
     elements, which are actually KRIs,
-    for a software development organization.
+    for an SDO.
     \textbf{
@@
             that CRI addresses the questions.  CRI is a beneficial technique of software
-            analytics when applied to software development organizations.
+            analytics when applied to SDOs.
 
@@
                 provides consistency which may not exist without it.  Therefore, CRI removes the 
-                guesswork of measuring a software development organization. \\
+                guesswork of measuring an SDO. \\
                 \myrowcolour%

### 2015-03-08 paper_10_intro.tex
added abbreviations page

@@
     This work 
-    provides a technique for a Software Development Organization (SDO) to create
+    provides a technique for a Software Development Organization (SDO)
+    \nomenclature{SDO}{Software Development Organization}to create
     a single number score which indicates the overall performance
@@
     should be reported.  The Cumulative Result Indicator (CRI)
+    \nomenclature{CRI}{Cumulative Result Indicator}
     framework provides a solid foundation
@@
             software components function together as expected.
+            \nomenclature{SIT}{Systems Integration Testing} 
         \item[UAT] (User Acceptance Testing) - The final step of testing
@@
             UAT, the software system is ready to proceed to production
-        \item[PROD]  (Production) - The software has been released to the final audience.
+            \nomenclature{UAT}{User Acceptance Testing} 
+        \item[PROD] (Production) - The software has been released to the 
+        final audience. \nomenclature{PROD}{Production} 
         \item[defect] ``A software defect is a bug or error that causes
@@
 \subsection{CMMI}
-    The Capability Maturity Model Integration (CMMI) is one of the most 
+    The Capability Maturity Model Integration (CMMI)
+    \nomenclature{CMMI}{Capability Maturity Model Integration} is one of the most 
     widely acknowledged models for process 
@@
     be the ``new software engineering'' 
-    \cite{Jacobson2014}.  The authors rightfully claim that 
+    \cite{Jacobson2014}. 
+    \nomenclature{SEMAT}{Software Engineering Method and Theory}
+    The authors rightfully claim that 
     software engineering lacks

### 2015-03-08 paper_20_sdo.tex
added abbreviations page

@@
 
-\section{A SOFTWARE DEVELOPMENT ORGANIZATION (SDO)}
+\section{A SOFTWARE DEVELOPMENT ORGANIZATION}
 A \textit{Software Development Organization (SDO)} is any organization or subset of an organization that is responsible
@@
     software.  
-    This workflow is called the \textit{Software Development Life Cycle (SDLC)}.
+    This workflow is called the \textit{Software Development Life Cycle (SDLC)}
+    \nomenclature{SDLC}{Software Development Life Cycle}.
     SDLC can be defined as \cite{Ruparelia2010}:
@@
     1968 North Atlantic Treaty Organization (NATO) conference \cite{Tsui2013, Naur1969}. Over the 
-    years many definitions have been provided.  IEEE provides a definition that encompasses many of the
-    other definitions.  IEEE ISO610.12 defines software engineering as, 
+    years many definitions have been provided.  Institute of Electrical 
+    and Electronics Engineers (IEEE) provides a definition that encompasses 
+    many of the other definitions.
+    \nomenclature{IEEE}{Institute of Electrical and Electronics Engineers}
+    IEEE ISO610.12 defines software engineering as, 
     ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''

### 2015-03-08 paper_30_measure.tex
added abbreviations page

@@
             \item SLOC - The number of Source Lines of Code 
+                \nomenclature{SLOC}{Source Lines Of Code}
             \item NOM - The Number of Methods per class
+                \nomenclature{NOM}{Number of Methods}
             \item Complexity - A numerical measure of the code complexity,
@@
         presented.   The four
-        types of indicators important to an SDO are shown
+        categories of indicators important to an SDO are shown
         in Table \ref{tab:indicators}.
+
+        \nomenclature{RI}{Result Indicator}
+        \nomenclature{KRI}{Key Result Indicator}
+        \nomenclature{PI}{Performance Indicator}
+        \nomenclature{KPI}{Key Performance Indicator}
 
@@
                 \item Acted on by CEO\footnote{Chief Executive Officer} 
-                    and/or senior management
+                    and/or upper-level management 
+                    \nomenclature{CEO}{Chief Executive Officer}
                 \item Clearly indicate the action required

### 2015-03-08 paper_40_cri.tex
added abbreviations page

@@
     upon the selection of a given time period (weekly, monthly, quarterly).
-    \textbf{CRI is not meant to be comparative between
+    CRI is not meant to be comparative between
     organizations, but to measure the amount of increase or decrease
-    a single organization exhibits across elements}.  CRI is made to be easily 
+    a single organization exhibits across elements.  CRI is made to be easily 
     expandable to other elements if desired.
@@
                         to be diffent.
-                    \item[Source Lines Of Code (SLOC)]  This number is the count of 
+                    \item[SLOC]  This number is the count of 
                         the total number of lines of source code for a project. 

### 2015-03-08 paper_50_sdlc-ae.tex
added abbreviations page

@@
     \cite{Rost2011}. This storage system will be named the SDLC Analytic 
-    Engine (SDLC-AE).
+    Engine (SDLC-AE). \nomenclature{SDLC-AE}{SDLC Analytic Engine}
 
@@
         a programming language designed for managing data in relational database 
-        management system.} 
+        management system.\nomenclature{SQL}{Structured Query Language}} 
         is written for an Oracle

### 2015-03-09 abstract.tex
minor update to abstract
change name to CRI
updates to abstract

@@
 The primary goal of this work is to provide a general framework for what a software development organization
-should measure and how to report on those measurements.  The focus is scoring of the entire
-organization and not just the development efforts.  The secondary goal of this work is to provide
-a software implementation of that framework.
+should measure and how to report on those measurements.  The focus is providing a single number
+to represnet the entire
+organization and not just the development efforts.  That single number is considered the CRI score. The secondary goal of this work is to provide
+a framework for storing the necessary data.
 

### 2015-03-15 abstract.tex
typo
update abstract

@@
 should measure and how to report on those measurements.  The focus is providing a single number
-to represnet the entire
-organization and not just the development efforts.  That single number is considered the CRI score. The secondary goal of this work is to provide
+to represent the entire
+organization and not just the development efforts.  That single number is considered the 
+Cumulative Result Indicator (CRI) score. The secondary goal of this work is to provide
 a framework for storing the necessary data.

### 2015-03-18 paper_10_intro.tex
updates the chapter 1 this work to this dissertation

@@
 
-    This work 
+    This dissertation 
     provides a technique for a Software Development Organization (SDO)
@@
     view of the overall organization.  It is common for software development
-    organizations to measure and focus soley on the source code
+    organizations to measure and focus solely on the source code
     being produced.  However, an SDO does more
     than just produce source code.  There is documentation to be
-    written, testcases to be created, systems to be deployed, and
+    written, test cases to be created, systems to be deployed, and
     decisions to be made.  The framework provides an evaluation
@@
             when a select few members of the user group are invited to
-            validate the software system. Once validation has occured for
+            validate the software system. Once validation has occurred for
             UAT, the software system is ready to proceed to production
@@
             A maturity level 1 organization consists of an
-                adhoc and chaotic processes.  While working
+                impromptu and chaotic process.  While working
                 products are still produced, the results are 
@@
     While CMMI-Dev does provide an excellent framework for improving a process, it
-    is wholely focused on process improvement.  It does not provide guidelines
+    is entirely focused on process improvement.  It does not provide guidelines
     for evaluating the final product.  
@@
     Points are positive or negative based upon the 
-    presense of various techniques. A couple example techniques are: 
+    presence of various techniques. A couple of example techniques are: 
     automated source code analysis and continuous integration.  The end 
@@
     While the result is a single number score, it does not account for the 
-    entirety of the software development lifecycle.
+    entirety of the software development life cycle.
 
@@
     cost of a software project.  The original version developed in 1981 was
-    focused on mainframe and batch processing.  An unpdated version, named
+    focused on mainframe and batch processing.  An updated version, named
     COCOMO II, was created by Boehm in 1995 to be more flexible for newer 
@@
     It provides no information regarding the rest of the 
-    software development lifecycle.  Also, the primary output of Sextant 
+    software development life cycle.  Also, the primary output of Sextant 
     is visual graphs.  While these graphs do provide
@@
     However, the measures on source code only explain part of the 
-    software development lifecycle.
+    software development life cycle.
 
@@
     needs to demonstrate clear advantages for practitioners.  The work
-    presented in this work will address both the 3 main focus areas and
+    presented in this dissertation will address both the 3 main focus areas and
     the 3 important questions of software analytics.
@@
     data on software development and software analytics are being
-    p roperly implemented, an obvious next step is the
+    properly implemented, an obvious next step is the
     application of gamification to software development. Gamification
@@
     software quality \cite{Dubois2013}. 
-    While this work will not focus on gamification, it is important to note
+    While this dissertation will not focus on gamification, it is important to note
     that an implementation of an evaluation technique for software
@@
     specific portions of the software development 
-    lifecycle, namely the development portion. Plus,
+    life cycle, namely the development portion. Plus,
     there are many tools that need to be created for
@@
     a technological framework for storing the current and historical CRI values.
-    Chapter 6 demostrates how CRI can be implemented in a software development portion of 
+    Chapter 6 demonstrates how CRI can be implemented in a software development portion of 
     a large financial institution. Chapter 7 discusses some possible future directions 

### 2015-03-18 paper_20_sdo.tex
updates the chapter 1 this work to this dissertation

@@
 "Software is not just the programs but also all associated documentation and configuration data which is needed to make these programs operate correctly."
-This is the definition used for the remainder of this work.
+This is the definition used for the remainder of this dissertation.
 

### 2015-03-18 paper_80_conclusion.tex
updates the chapter 1 this work to this dissertation

@@
     Knowing which metrics to use and what they all mean can be a daunting task.  
-    This work identified the Cumulative Result Indicator (CRI) which is a
+    This dissertation identified the Cumulative Result Indicator (CRI) which is a
     proposed solution to the difficulty of measuring an SDO by creating a
@@
 
-    The following have all been provided in this work.
+    The following have all been provided in this dissertation.
     \begin{itemize}

### 2015-03-18 paper_20_sdo.tex
updates through chapter 4

@@
         without risking too much time or effort in any single iteration.
-        Sprial requires a very adaptive management approach
+        Spiral requires a very adaptive management approach
         as well as flexibility of the key stakeholders \cite{Ruparelia2010}.
@@
                 necessary infrastructure and involved software systems
-                must be identified. This phase can serve as a roadmap for the 
+                must be identified. This phase can serve as a guideline for the 
                 remaining phases. If done properly, this phase can greatly 

### 2015-03-18 paper_30_measure.tex
updates the chapter 1 this work to this dissertation
updates through chapter 4

@@
         \item Select And Define Measures
-        \item Integrate with Software Process
+        \item Integrate with the Software Process
     \end{enumerate}
 
-    This work will focus on steps 1 and 2.  The process issue is the overall
+    This dissertation will focus on steps 1 and 2.  The process issue is the overall
     effectiveness of the SDO.  Section \ref{sec:CRI} will cover step 2 as
@@
             do not tell an organization what is needed to improve the 
-            results.  KRIs are highly benefical for high-level management
+            results.  KRIs are highly beneficial for high-level management
             and not necessarily beneficial for staff working directly on 
@@
         \subsubsection{PERFORMANCE INDICATOR (PI) FOR AN SDO}
-            \textit{Performance Indicators} are nonfinancial performance measures
+            \textit{Performance Indicators} are non-financial performance measures
             that help a team align themselves with the organizations 
@@
         A \textit{process productivity} number is calculated based entirely
-        off aspects of the SDLC and the 5 core measurements.  It is a number
+        on aspects of the SDLC and the 5 core measurements.  It is a number
         targeted at project teams working on the SDLC.

### 2015-03-18 paper_40_cri.tex
updates through chapter 4

@@
     A score of 0 is an indication of meeting the basic expectations. 
-    A negative score indicates under-performance and a 
-    positive score indicates over-performance.   Here are some 
+    A negative score indicates worse-than-expected performance and a 
+    positive score indicates better-than-expected performance.   Here are some 
     examples. An CRI score of 0.35 means the organization is 
@@
             performance, however that is defined
-        \item Similarily, the maximum score must equate to the best possible performance.  
+        \item Similarly, the maximum score must equate to the best possible performance.  
         \item A score of 0 must be average (or expected) performance
@@
         Each of the 5 elements of CRI has its own set of data that needs to
-        be collected and a formula for calculating a score. 
-        These five elements will be outline in the next sections.
+        be collected and formula for calculating a score. 
+        These five elements will be outlined in the next sections.
 
@@
                 Each column is classified as \textit{required} or
-                \textit{optional}.  That is to allow some flexibility
+                \textit{optional}.  This is to allow some flexibility
                 in the model for organizations that collect
@@
                         effort.  It is common for the estimated and actual times
-                        to be diffent.
+                        to be different.
                     \item[SLOC]  This number is the count of 
@@
                 \textit{Testing Effort}, and \textit{Development Effort}.  
-                Some of the following strategies will be employed to find 
-                a reasonable model.
+                Some of the following strategies to find  
+                a reasonable model include:
                 \begin{itemize}
@@
                     \item $S_{1_i}$ is the quality score for Application ID $i$
+                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                     \item $n$ is the number of Application IDs
@@
                 \[
-                    S_{1} = \sum\limits^n_{i=1} w'_i S_{1_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
+                    S_{1} = \sum\limits^n_{i=1} w_i S_{1_i}
                 \]
@@
                     a weighted average
+                    \item $w_i > 0$ for all $i$
+                    \item $\sum\limits^n_{i=1} w_i = 1$
                 \end{itemize}
@@
             All the new requirements and great quality do not matter if the software is not available.
-            All the new features and great quality do not matter if the software is not available.  Thus it
+            Thus it
             is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, the SLA is a 
@@
             given time period. } and measure 
-            performance against that SLA.  The following section will outline to data needed to properly
-            calculate an SLA and the data needed to calculate the CRI score for availability.
+            performance against that SLA.  The following section will outline the data needed to properly
+            calculate an SLA and to calculate the CRI score for availability.
 
@@
             organizations have a one-to-one mapping between Applications being developed
-            and services being deployed.  Others have more complex sceranios that require
+            and services being deployed.  Others have more complex scenarios that require
             multiple applications to be combined to form a service.  Then the availability
@@
                 \textit{Unscheduled Downtime}; they are optional because they can be
-                used to calculated the \textit{Percent Uptime}.  The \textit{Percent Uptime}
+                used to calculate the \textit{Percent Uptime}.  The \textit{Percent Uptime}
                 is the important value for the CRI schedule score.  Here are the two common
@@
                     \item $S_{2_i}$ is the availability score for System ID $i$
+                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                     \item $A_{a_i}$ actual availability for System ID $i$
@@
                 \[
-                    S_{2} = \sum\limits^n_{i=1} w'_i S_{2_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
+                    S_{2} = \sum\limits^n_{i=1} w_i S_{2_i} 
                 \]
-                where $S_2$ is the CRI availability score for the time frequency.
+                where
+                \begin{itemize}
+                    \item $S_2$ is the combined availability score for all Service IDs, 
+                    a weighted average
+                    \item $w_i > 0$ for all $i$
+                    \item $\sum\limits^n_{i=1} w_i = 1$
+                \end{itemize}
+
+                Then $S_2$ represents the CRI availability score for that given time 
+                frequency.
 
@@
                 \item[Text] \hfill \\
-                    The specific text used in the questions or statments
+                    The specific text used in the questions or statements
                     is very important.  The text cannot be too vague.  Also, the text
@@
                     Next is the issue of sampling.  Not every customer can be surveyed, so 
-                    sample sets os customers need to be presented with a survery.  
+                    sample sets of customers need to be presented with a survey.  
                     In the case of CRI, there are 2 possible scenarios for sampling.  
@@
             For more on creating appropriate surveys, see \cite{Snijkers2013} by Snijkers,
-            Haraldsen, Jones, and Willimack. In the book, Snijkers et al. present a framework
+            Haraldsen, Jones, and Willimack. They present a framework
             named generic statistical business process model (GSBPM) for conducting surveys
@@
             provide another good resource for preparing and conducting surveys 
-            \cite{Cowles2015}.  They even include an entire chapters on both writing 
+            \cite{Cowles2015}.  They even include entire chapters on both writing 
             survey questions and survey errors.
@@
                     \item $S_{3_i}$ is the satisfaction score for Question ID $i$
+                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                     \item $a_{ij}$ answer to question $i$ for respondent $j$
@@
                 \[
-                    S_{3} = \sum\limits^n_{i=1} w'_i S_{3_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
+                    S_{3} = \sum\limits^n_{i=1} w_i S_{3_i}
                 \]
-                where $S_3$ is the CRI satisfaction score for the time frequency.
+                where
+                \begin{itemize}
+                    \item $S_3$ is the combined satisfaction score for all Questions IDs, 
+                    a weighted average
+                    \item $w_i > 0$ for all $i$
+                    \item $\sum\limits^n_{i=1} w_i = 1$
+                \end{itemize}
+
+                Then $S_3$ represents the CRI satisfaction score for that given time 
+                frequency.
 
@@
                     \item $B_{s_i}$ the scheduled beginning date of project $i$
-                    \item $\Delta_i$ the percent the schedule was missed for project $i$
+                    \item $\Delta_i$ the proportion the schedule was missed for project $i$
                 \end{itemize}
@@
                 The distribution is needed for the Cumulative
-                Distribution Function (C.D.F.). The C.D.F. maps the values
+                Distribution Function (CDF) 
+                \nomenclature{CDF}{Cumulative Distribution Function}. 
+                The CDF maps the values
                 to a percentile rank within the distribution \cite{Downey2011}.
-                The C.D.F. will be transformed to create
-                the schedule score for CRI. Since all C.D.F. functions fall within the
+                The CDF will be transformed to create
+                the schedule score for CRI. Since all CDF functions fall within the
                 range $[0,1]$, the function needs to be shifted to center around 0, and then
@@
                 \label{eq:CDF}
-                    S_{4_i} = 2k \cdot (C.D.F.(\Delta_i) - \frac{1}{2})
+                    S_{4_i} = 2k \cdot (CDF(\Delta_i) - \frac{1}{2})
                 \end{equation}
@@
                     \item $S_{4_i}$ is the schedule score for Project ID $i$
+                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                 \end{itemize}
@@
                 \[
-                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1
+                    S_{4} = \sum\limits^n_{i=1} w_i S_{4_i}
                 \]
-                where $S_4$ is the CRI schedule score for the time frequency.
+                where
+                \begin{itemize}
+                    \item $S_4$ is the combined schedule score for all Project IDs, 
+                    a weighted average
+                    \item $w_i > 0$ for all $i$
+                    \item $\sum\limits^n_{i=1} w_i = 1$
+                \end{itemize}
+
+                Then $S_4$ represents the CRI schedule score for that given time 
+                frequency.
 
@@
 
-                Find the average of the $\Delta_i$'s.  This is the average percent of a missed
+                Find the average of the $\Delta_i$'s.  This is the average proportion of a missed
                 schedule.  
@@
 
-                After the $\bar{\Delta}$ is calculated, the following formulas are used to create the schedule scores
+                After $\bar{\Delta}$ is calculated, the following formulas are used to create the schedule scores
                 for each project and then the averaged schedule score.
@@
                 \[
-                    S_{4} = \sum\limits^n_{i=1} w'_i S_{4_i} \text{ where } \sum\limits^n_{i=1} w'_i = 1 \text{   , average the schedule scores}
+                    S_{4} = \sum\limits^n_{i=1} w_i S_{4_i} 
                 \]
@@
                 \begin{itemize}
+                    \item $S_4$ is the combined schedule score for all Project IDs, 
+                    a weighted average
+                    \item $k$ scaling factor to produce results in the range $[-k,k]$
+                    \item $w_i > 0$ for all $i$
+                    \item $\sum\limits^n_{i=1} w_i = 1$
                     \item $n$ is the number of projects
@@
                 \end{itemize}
+                Then $S_4$ represents the CRI schedule score for that given time 
+                frequency.
                 Again, this was just an alternate approach to scoring schedule.  
@@
             To summarize, this element is not completely a measurement of requirements
-            but rather a measurment of the work being completed.
+            but rather a measurement of the work being completed.
 
@@
                 completed\footnote{Theoritically, a negative requirement would
-                be considered a defect.}.  Unforntunately, an upper bound
-                does not exist.  The variablity of requirements is not
+                be considered a defect.}.  Unfortunately, an upper bound
+                does not exist.  The variability of requirements is not
                 as large as the variability of the number of defects, so
@@
                     \item $S_{5_i}$ is the requirements score for Project ID $i$
+                    \item $k$ scaling factor to produce results in the range $[-k,k]$
                     \item $R_{a_i}$ actual requirements completed for Project ID $i$
@@
                 \[
-                    S_{5} = \sum\limits^n_{i=1} w'_i S_{5_i} \text{ where }
-                        \sum\limits^n_{i=1} w'_i = 1
+                    S_{5} = \sum\limits^n_{i=1} w_i S_{5_i} 
                 \]
-
-                where $S_5$ is the CRI requirements score for the time frequency.
+                where
+                \begin{itemize}
+                    \item $S_5$ is the combined requirements score for all Project IDs, 
+                    a weighted average
+                    \item $w_i > 0$ for all $i$
+                    \item $\sum\limits^n_{i=1} w_i = 1$
+                \end{itemize}
+
+                Then $S_5$ represents the CRI requirements score for that given time 
+                frequency.
 
@@
         check for correlations after determining element and overall CRI scores.  
-        If correlation is determined, the element should not be dropped but rather be weighted less than
-        the other elements.  This technique keeps the most data available but lessens the importance of
+        If an element is determined to be correlated with another element, neither element should be dropped,
+        but rather one of the elements should be weighted less than
+        the other correlated element.  
+        This technique keeps the most data available but lessens the importance of
         the correlated element.
@@
         The sensitivity of the formulas should be tested as the scores should not
-        flucate drastically for similar values.  There are 2 possible techniques
+        fluctuate drastically for similar values.  There are 2 possible techniques
         for testing the sensitivity of the formulas. 
@@
                 data, and randomly selecting from that distribution.  If historical
-                data is not available, then For more on sensitivity analysis 
-                in statistical modeling, see \cite{Saltelli2000}.
+                data is not available, then the normal distribution can be used.
+                See \cite{Saltelli2000} for more information on sensitivity analysis 
+                in statistical modeling.
         \end{description}
@@
 
-        \subsubsection{CRI VS. FOCUS AREAS OF SOFTWARE ANALYTICS}
+        \subsubsection{CRI VS. IMPORTANT QUESTIONS OF SOFTWARE ANALYTICS}
             Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
@@
                 How sensitive are the results to small changes in one or more of the inputs? & 
-                The question was extensively addressed in section \ref{sec:sensitivity}.  It appears CRI is
+                The question was extensively addressed in section \ref{sec:sensitivity}. CRI is
                 not overly sensitive to small changes in the inputs.\\

### 2015-03-18 appendices.tex
added overall scores for case study
some more modifications and include CRI element scatterplot matrix

@@
 
-    Often times the SDLC contains more than the 5 basic steps of requirements, design,
+    The SDLC often contains more than the 5 basic steps of requirements, design,
     implementation, testing, and  deployment/maintenance.  Those are the high-level
@@
 \label{app:case}
+    A full set of the source code and applicable output is available 
+    at \cite{Swanstrom2015s}.
 
@@
 
+    \subsection{SCHEDULE SCORES - R CODE}
+        \lstinputlisting[language=R, label=src:schedule]{source/schedule.R}
+
     \subsection{REQUIREMENTS SCORES - R CODE}
@@
         \lstinputlisting[language=R, label=src:requirements]{source/requirements.R}
+
+    \subsection{OVERALL SCORES - R CODE}
+        \lstinputlisting[language=R, label=src:overall]{source/overall.R}
 

### 2015-03-18 paper_50_sdlc-ae.tex
some more modifications and include CRI element scatterplot matrix

--- 2015-03-07 paper_50_sdlc-ae.tex
@@
         a programming language designed for managing data in relational database 
-        management system.} 
+        management system.\nomenclature{SQL}{Structured Query Language}} 
         is written for an Oracle
-        database, but the scripts can be modified to work with another database
+        database, but the scripts can be modified to work with other databases
         such as: PostgreSQL, SQL Server, or MySQL.

### 2015-03-18 paper_70_case-study.tex
updates through chapter 4
some more modifications and include CRI element scatterplot matrix

@@
         some descriptive statistics for the quality data.  Testing hours
-        were not capture but they are optional, so the analysis can 
+        were not captured, but they are optional, so the analysis can 
         continue.
@@
             \cmidrule[0.2pt](l{0.125em}){5-5}%
+            \cmidrule[0.2pt](l{0.125em}){6-6}%
             % \midrule
@@
             \centering
-            \includegraphics[scale=.3]{images/quality_plots1.png}
+            \includegraphics[scale=.25]{images/quality_plots1.png}
             \caption{QUALITY DATA PLOTS: DEPENDENT VS. INDEPENDENT VARIABLES}
@@
         Table \ref{tab:availability_desc}.  The percent uptime
-        was precalculated for this data so uptime, scheduled downtime,
+        was previously calculated for this data so uptime, scheduled downtime,
         and unscheduled downtime are not needed.  Availability
@@
         a known upper and lower bound exist, 1 and 0 respectively.
+
+        The numbers in Table \ref{tab:availability_desc} indicate
+        the values are very near 1.  This is expected as SDOs
+        set SLA uptime values near 1, and even strive to meet
+        an uptime of 1.  An uptime of 1 means the system was
+        available the entire time period.  Thus numbers for uptime
+        near 1 are highly desirable for an SDO expecting
+        to score well for availability.
 
@@
 
-        \begin{figure}[htb]
+        \begin{figure}[hb]
             \centering
@@
     \subsection{SCHEDULE}
-        Figure \ref{tab:schedule_desc} displays some descritive statistics
+        Figure \ref{tab:schedule_desc} displays some descriptive statistics
         for the schedule data.  Since the data is mostly dates, the 
@@
         Difference (Actual Finish - Schedule Finish), and 
-        $\Delta$ ($frac{\Delta}{\text{Schedule Duration}}$ ).
+        $\Delta$ ($\frac{\text{Difference}}{\text{Schedule Duration}}$ ).
 
@@
         Now that the distribution has been identified, the next step
-        is determining the Cumulative Distribution Function (C.D.F.)
-        for the distribution.  For Cauchy, the general C.D.F. is 
+        is determining the CDF
+        for the distribution.  For Cauchy, the general CDF is 
         given as follows.
         \[
-            C.D.F. = \frac{1}{\pi}\arctan{\frac{x-x_0}{\gamma}} + \frac{1}{2}
+            CDF(x) = \frac{1}{\pi}\arctan{\frac{x-x_0}{\gamma}} + \frac{1}{2}
         \]
@@
         The CRI schedule scores can be seen in Figure \ref{fig:schedule-scores}.
-        These scores appear more eratic than the other elements.
+        These scores appear more erratic than the other elements.
         This difference is due to the small number of releases every month.
@@
 
-        Based upon the graphs for the elements scores, there does not
-        appear to be any correlation.  None of the graphs
-        rise and fall during the same intervals.  The missing element,
+        Figure \ref{fig:correlation_cri} shows a scatterplot matrix
+        for the individual element scores.  No correlation appears
+        to exist between any of the elements. The missing element,
         satisfaction, is the most likely element to exhibit correlation,
@@
 
+        \begin{figure}[htb]
+            \centering
+            \includegraphics[scale=.3]{images/correlation.png}
+            \caption{SCATTERPLOT MATRIX OF CRI ELEMENT SCORES}
+            \label{fig:correlation_cri}
+        \end{figure}
+
 \end{document}

### 2015-03-18 paper_80_conclusion.tex
some more modifications and include CRI element scatterplot matrix

@@
 
-    Due to the number of issues with surveys.  One area of future work would be indentifying
+    Due to the number of issues with surveys.  One area of future work would be identifying
     a general set of questions that would best fit CRI.  This set would have to include
@@
     determining how to relate the SDO performance to finances.  The most likely scenario
-    would be a method to either select or predicted the expected software sales
+    would be a method to either select or predict the expected software sales
     for a month.  Then every month create an CRI element score that reflects
     how much the expected sales were exceeded or missed.  The other missing
-    balanced scorecard characteristic is learning and growth.  Those are very difficult
+    balanced scorecard characteristic is learning and growth.  These are very difficult
     to quantitatively measure.  In this case some possible data points might be:
@@
     not to be confused with data-driven programming, in which the computer code
-    describes the data instead of the sequence of opertions \cite{DDP2015}.
+    describes the data instead of the sequence of operations \cite{DDP2015}.
 
@@
     not just the entire project.  Teams need to know how much time is spent
-    in design versus testing.  Also, how much time is required to generate
-    proper test cases?  These are just a couple of examples of expansions
+    in design versus testing.  Consideration should also be given to the amount
+    of time required to generate
+    proper test cases.  These are just a couple of examples of expansions
     to the SDLC-AE.  These and other advancements could lead to greater
@@
     Now SDOs have a technique to consistently measure performance over time.  CRI
-    should help upper-level management identify the areas of the organization
-    that need attention and those that do not.  CRI should save time required to 
-    evaluate the performance since the result is a single number.
+    will help upper-level management identify the areas of the organization
+    that need attention and those that do not.  CRI will save time required to 
+    evaluate performance since the result is a single number.
 

### 2015-03-18 source/overall.R

@@ -2,9 +2,13 @@
 ### Combine the scores
 # overall
 
-full = merge(x = qual_scores, y = avail_scores, by = "MONTH_DT", all = TRUE)
-full = merge(x = full, y = req_scores, by = "MONTH_DT", all = TRUE)
-full = merge(x = full, y = sched_scores, by = "MONTH_DT", all = TRUE, suffixes='sched')
+# overall
+
+full = merge(x = qual_scores, y = avail_scores, by = "MONTH_DT", all = TRUE, suffixes=c('_QUAL','_AVAIL'))
+full = merge(x = full, y = sched_scores, by = "MONTH_DT", all = TRUE, suffixes='_SCHED' )
+colnames(full)[4] = 'SCORE_SCHED'
+full = merge(x = full, y = req_scores, by = "MONTH_DT", all = TRUE, suffixes=c('','_REQ') )
+colnames(full)[5] = 'SCORE_REQ'
 
 full$SCORE = apply(full[,seq(2,5)], 1, 
                    function(x) {sum(x,na.rm=TRUE)/sum(!is.na(x))} )

### 2015-03-20 paper_10_intro.tex
updates through chapter 4
make testcase one word

@@
     provides a technique for a Software Development Organization (SDO)
-    \nomenclature{SDO}{Software Development Organization}to create
+    \nomenclature{SDO}{Software Development Organization} to create
     a single number score which indicates the overall performance
@@
     form a historical baseline for a specific organization.  The single
-    number is targeted for upper-level management whom need a quick
+    number is targeted for upper-level management who need a quick
     and simple strategy to evaluate the performance of the organization.
@@
     than just produce source code.  There is documentation to be
-    written, test cases to be created, systems to be deployed, and
+    written, testcases to be created, systems to be deployed, and
     decisions to be made.  The framework provides an evaluation
@@
 \subsection{TERMINOLOGY}
-    Like any other business domain, the software engineering field has number
+    Like any other business domain, the software engineering field has a number
     of specific terms.  Many of these terms will be used throughout the remainder
@@
                 found in the computer code, a defect should not be isolated to just code.   
-                A poorly written requirement or missed test cases can 
+                A poorly written requirement or missed testcases can 
                 both be considered a defect.  Other common names for a defect 
@@
     specified, and they include the 
-    existence of a number of process areas.  The 5 maturity 
+    existence of a number of process areas.  The five maturity 
     levels and the process areas are specified as follows.

### 2015-03-20 paper_40_cri.tex
some more modifications and include CRI element scatterplot matrix
make testcase one word

@@
                         effort for development unless coding in used to generate
-                        automated test cases. \footnote{Automated testing is the
+                        automated testcases. \footnote{Automated testing is the
                         process of creating software to automatically run tests
@@
                         to above, this number makes more sense for development effort.
-                    \item[Test Cases] A test case is a step or series of steps followed
+                    \item[Testcases] A testcase is a step or series of steps followed
                         to validate some expected outcome of software.  Organizations
-                        will create a number of test cases to be validated for a
-                        software system.  The number of such test cases could
+                        will create a number of testcases to be validated for a
+                        software system.  The number of such testcases could
                         be used as a level of testing effort.
@@
                 and it can either be supplied in the data or calculated from the 
-                optional fields.
+                optional fields. For the purposes of this dissertation, the percent
+                uptime should be handled in decimal form and not as a percent out of 100.
 

### 2015-03-20 paper_10_intro.tex
grammar updates to chapter 1

@@
     of the organization. The
-    score is based upon data collected for 5 key result indicators
+    score is based upon data collected for five key result indicators
     of an SDO: quality, availability,
@@
     source code.  More complex code results in more maintenance efforts and
-    more chances for problems. A couple of numerical measures for the 
+    more chances for problems. Some numerical measures for the 
     complexity of source code have been created.  The most common examples
@@
 
-    Later, Martin Shepperd in \cite{Hassan2013} identified 3 important questions that software
+    Later, Martin Shepperd in \cite{Hassan2013} identified three important questions that software
     analytics must address:
@@
     \end{enumerate}
-    These are 3 important questions that should be addressed 
+    These are three important questions that should be addressed 
     when presenting any results in software analytics.  The research
     needs to demonstrate clear advantages for practitioners.  The work
-    presented in this dissertation will address both the 3 main focus areas and
-    the 3 important questions of software analytics.
+    presented in this dissertation will address both the three main focus areas and
+    the three important questions of software analytics.
 
@@
     is ``the process of making activities more game-like'' \cite{Werbach2014}.
-    Some of the benefits of gamification are higher productivity, competition,
+    Some of the benefits of gamification are higher productivity, added competition,
     and greater enjoyment.  
@@
     Overall, there exist many attempts to 
-    evaluate portions of the a software development 
-    organization.  None of the the attempts provide
+    evaluate portions of an SDO.  None of the attempts provide
     a single number score for the entirety of the 
@@
 
-    The remainder of this dissertation is divided into 7 chapters.  Chapter 2 provides
+    The remainder of this dissertation is divided into seven chapters.  Chapter 2 provides
     an overview of software, software development life cycles, software engineering, and software

### 2015-03-20 appendices.tex
more grammatical fixes updates to lists in the appendix

@@
 
-    The SDLC often contains more than the 5 basic steps of requirements, design,
+    The SDLC often contains more than the five basic steps of requirements, design,
     implementation, testing, and  deployment/maintenance.  Those are the high-level
@@
         can be seen in Figure \ref{fig:quality-diag}.  The normal probability plot,
-        a.k.a. QQ Plot, shows the errors are not exactly normally distributed, but
+        a.k.a. Q-Q Plot, shows the errors are not exactly normally distributed, but
         the baseline quality function had good predictive power as shown by the
@@
 
+    This appendix describes some additional SDLC attributes that could be tracked to help improve
+    estimation.  The SDLC-AE could be expanded to include the following.
+
     \subsection{ESTIMATION}
 
-    \begin{itemize}
-    \item Change to Database Structure  
-    \item Modify Database Data    
-    \item Create a New Database, number of new databases  
-    \item Server Configuration Changes Required   
-    \item New Servers Required   
-    \item Number of Team Members Involved  
-    \item Number of (sub)Systems Involved  
-    \item Estimation Date
-    \item Number of Days Allowed
-    \item List of Other Attributes
-    \item Number of Screens Involved 
-    \item Actual Value (hours, days, dollars) 
-    \end{itemize}
-
-    \begin{description}
-        \item[Estimated Dev Hours] - 
+        The following are additional data points that could be tracked for project estimation.
+        \begin{easylist}[itemize]
+            & Change to Database Structure  
+            & Modify Database Data    
+            & Create a New Database, number of new databases  
+            & Server Configuration Changes Required   
+            & New Servers Required   
+            & Number of People Involved  
+            & Number of (sub)Systems Involved  
+            & Estimation Date
+            & Number of Days Allowed
+            & List of Other Attributes
+            & Number of Screens Involved 
+            & Actual Values (hours, days, dollars) 
+            & Estimated Values
+            && Estimated Dev Hours: 
                 The number of development hours estimated for a 
                 project, this is just developer hours
-        \item[Estimated Doc Hours] - 
+            && Estimated Doc Hours: 
                 The number of documentation hours estimated for a project
-        \item[Estimated Test Hours] - 
+            && Estimated Test Hours:
                 The number of testing hours estimated for a project
-        \item[Estimated Deployment Hours] - 
+            && Estimated Deployment Hours: 
                 The number of estimated hours required to 
                 deploy the project
-    \end{description}
+        \end{easylist}
 
     \subsection{REQUIREMENTS}
-    List of: 
-    \begin{description}
-      \item[Title] 
-      \item[Descrition]
-      \item[author]
-      \item[projectID]
-      \item[date]
-      \item[Comments] list of \\
-      \begin{description}
-        \item[date]
-        \item[comment Text]
-        \item[author]
-      \end{description}
-    \end{description}
 
-    \subsection{MAINTENANCE (DEFECTS)}
-    List of:
-    \begin{description}
-      \item[Project] 
-      \item[Release]
-      \item[description]
-      \item[date Entered]
-      \item[Date fixed]
-      \item[Comments] list of \\
-      \begin{description}
-        \item[date]
-        \item[comment Text]
-        \item[author]
-      \end{description}
-    \end{description}
-
-    \subsection{TESTING}
-
-    List of:
-    \begin{description}
-      \item[Project] 
-      \item[Release]
-      \item[title]
-      \item[description]
-      \item[author]
-      \item[Date Started]
-      \item[Date Executed]
-      \item[Status (Pending, pass, fail)]
-      \item[Comments] list of \\
-      \begin{description}
-        \item[date]
-        \item[comment Text]
-        \item[author]
-      \end{description}
-    \end{description}
+        The following are additional data points that could be tracked for the requirements phase of an
+        SDLC project.
+        \begin{easylist}[itemize]
+            & Title
+            & Description
+            & Author
+            & Project
+            & Date
+            & Comments
+            &&  Date
+            &&  Comment text
+            &&  Author
+        \end{easylist}
 
@@
 
-    List of Coding Tasks:
-    \begin{description}
-      \item[Project] 
-      \item[Release]
-      \item[List of Files]
-      \item[author]
-      \item[Date Started]
-      \item[Completion Date]
-      \item[Number of Unit Tests]
-      \item[Lines of Code]
-      \item[Others] See \cite{Jones2009, Jones2012, Rubin2007, Snipes2013}
-    \end{description}
+        The following are additional data points that could be tracked for the development phase of an
+        SDLC project.
+        \begin{easylist}[itemize]
+            & Project
+            & Release
+            & List of files
+            & Author
+            & Date started
+            & Completion date
+            & Number of unit tests
+            & Lines of code
+            & Percentage of automated test coverage
+            & Others
+        \end{easylist}
+
+    \subsection{TESTING}
+        The following are additional data points that could be tracked during, before, and after the
+        testing phase of an SDLC project.
+        \begin{easylist}[itemize]
+            & Project
+            & Release
+            & Title
+            & description]
+            & Author]
+            & Date started
+            & Date executed
+            & Status (pending, pass, fail)
+            & Comments 
+            && Date
+            && Comment text
+            && Author
+        \end{easylist}
 
@@
 
-    List of:
-    \begin{description}
-      \item[Project] 
-      \item[Release]
-      \item[date Entered]
-      \item[Date Scheduled]
-      \item[Date Executed]
-      \item[Ordering/Prerequisites]
-      \item[Comments] list of \\
-      \begin{description}
-        \item[date]
-        \item[comment Text]
-        \item[author]
-      \end{description}
-    \end{description}
+        The following are additional data points that could be tracked for the implementation of a project.
+        \begin{easylist}[itemize]
+            & Project
+            & Release
+            & date Entered
+            & Date Scheduled
+            & Date Executed
+            & Ordering/Prerequisites
+            & Comments
+            && date
+            && Comment text
+            && Author
+        \end{easylist}
+
+    \subsection{MAINTENANCE (DEFECTS)}
+
+        The following are additional data points that could be tracked for maintenance of a project.
+        \begin{easylist}[itemize]
+            & Project
+            & Release
+            & Description
+            & Date Entered
+            & Date fixed
+            & Comments
+            && Date
+            && Comment text
+            && Author
+        \end{easylist}
 

### 2015-03-20 paper_10_intro.tex
more grammatical fixes updates to lists in the appendix

@@
     endeavours. The three parts to the kernel are:
-    \begin{description}
-        \item[Measurement] - There must exist a means to 
-            determine the health and progress of an endeavour
-        \item[Categorization]-  The activities must progress 
-            through categories during an endeavour
-        \item[Competencies] - Specific competencies will 
+    \begin{enumerate}
+        \item \textbf{Measurement} - There must exist a means to 
+            determine the health and progress of an endeavour.
+        \item \textbf{Categorization} -  The activities must progress 
+            through categories during an endeavour.
+        \item \textbf{Competencies} - Specific competencies will 
             be required for completing activities
-    \end{description}
+    \end{enumerate}
 

### 2015-03-20 paper_30_measure.tex
more grammatical fixes updates to lists in the appendix

@@
         All these metrics are beneficial, but none of them tell the story of the entire
-        SDO.  Most of the metrics, as seen in the list above, for an SDO focus on 
+        SDO.  Most of the metrics for an SDO, as seen in the list above, focus on 
         the source code and development phase. 
-        Since metrics are indirect, it can be very difficult match SDO performance with
+        Since metrics are indirect, it can be very difficult to match SDO performance with
         a metric or series of metrics.  Metrics are great for tracking, but decision making
         based upon metrics alone is difficult.  That is why many of the other techniques
-        build upon metrics to provide a more complete overall picture of an SDO. Metrics are great starting point, but more is needed to properly 
+        build upon metrics to provide a more complete overall picture of an SDO. Metrics are a great starting point, but more is needed to properly 
         evaluate performance.
@@
         are not unique to SDOs, and the exact indicators to track
-        is very specific to the organization.  The indicators chosen
+        are very specific to the organization.  The indicators chosen
         by one organization might not be the same as the indicators
@@
             KPIs cover a shorter time frame than KRIs.
-            KPIs consist of the following 7 characteristics \cite{parmenter2010}.
+            KPIs consist of the following seven characteristics \cite{parmenter2010}.
             \begin{enumerate}
@@
             to identify and measure the KPIs for an SDO. Antolic's strategy
-            focused around 7 KPIs.
+            focused around six KPIs.
             \begin{enumerate}
@@
             they are not really KPIs but instead KRIs.  That is because
-            none of the 7 clearly indicate the action required to 
+            none of the six clearly indicate the action required to 
             improve the measure.  Also, it is unclear if improving any of
@@
 
-        In 2010, David Parmenter \cite{parmenter2010} added 2 more
+        In 2010, David Parmenter \cite{parmenter2010} added two more
         characteristics to the balanced scorecard: employee satisfaction
-        and environment/community.  This results in a total of 6 
+        and environment/community.  This results in a total of six 
         characteristics for the balanced scorecard.
@@
         what PIs, RIs, KRIs and/or KPIs to track in a balanced scorecard. 
-        It just specifies 6 broad categories.
+        It specifies six broad categories.
         It is also not specific to an SDO and 
@@
         According to Putnam and Myers in \cite{Putnam2013}, 
-        the 5 core measurements for managing software
+        the five core measurements for managing software
         projects are:
@@
         \begin{enumerate}
-            \item \textbf{Quantity of function} usually measured in terms of size (such as source lines of code), that ultimately execute on the computer
-            \item \textbf{Productivity} as expressed in terms of the functionality produced for the time and effort expended
-            \item \textbf{Time} the duration of the project in calendar months
-            \item \textbf{Effort} the amount of work expended in person-months
-            \item \textbf{Reliability} as expressed in terms of defect rate (or its reciprocal, mean time to defect)
+            \item \textbf{Quantity of function} - usually measured in terms of size (such as source lines of code), that ultimately execute on the computer
+            \item \textbf{Productivity} - as expressed in terms of the functionality produced for the time and effort expended
+            \item \textbf{Time} - the duration of the project in calendar months
+            \item \textbf{Effort} - the amount of work expended in person-months
+            \item \textbf{Reliability} - as expressed in terms of defect rate (or its reciprocal, mean time to defect)
         \end{enumerate}
@@
         A \textit{process productivity} number is calculated based entirely
-        on aspects of the SDLC and the 5 core measurements.  It is a number
+        on aspects of the SDLC and the five core measurements.  It is a number
         targeted at project teams working on the SDLC.

### 2015-03-20 paper_40_cri.tex
more grammatical fixes updates to lists in the appendix

@@
     organization and using that information to score an organization 
-    on current performance.  CRI is a collection of the following 5 
+    on current performance.  CRI is a collection of the following five 
     elements, which are actually KRIs,
@@
     The scale must be the same
-    for all 5 elements.
+    for all five elements.
 
     \subsection{ELEMENTS OF CRI}
-        Each of the 5 elements of CRI has its own set of data that needs to
+        Each of the five elements of CRI has its own set of data that needs to
         be collected and formula for calculating a score. 
@@
             organization can choose whatever severity levels they choose, it is
-            common practice to use 5 severity levels \cite{Raynus1999}.  The most 
+            common practice to use five severity levels \cite{Raynus1999}.  The most 
             severe level for a defect is 1.  All other levels drop in severity 
-            from that point. Table \ref{tab:severity} describes the 5 levels
+            from that point. Table \ref{tab:severity} describes the five levels
             for defect severity.
@@
                 in Table \ref{tab:severityweight} \cite{Raynus1999}. For
-                example, finding 1 defect of severity level 5 will result
-                in total count of 1.  However, finding 1 defect of severity
+                example, finding one defect of severity level 5 will result
+                in a total count of one.  However, finding one defect of severity
                 level 2 will result in a total count of 15. This strategy helps
@@
                 upon priorities or use a different technique if desired.  It
-                is just important to get a standard, meaningful number for SIT defects,
+                is important to establish a standard, meaningful number for SIT defects,
                 UAT defects, and PROD defects which manages severity appropriately.
@@
                     sample sets of customers need to be presented with a survey.  
-                    In the case of CRI, there are 2 possible scenarios for sampling.  
-                    \begin{description}
-                    \item[First]
-                    When an SDO is part of a larger organization, there typically is
+                    In the case of CRI, there are two possible scenarios for sampling.  
+                    \begin{enumerate}
+                        \item When an SDO is part of a larger organization, there typically is
                         a small number of business partners that help to guide and 
@@
 
-                    \item[Second] End-users will be surveyed for satisfaction. Obviously, the 
+                        \item End-users will be surveyed for satisfaction. Obviously, the 
                         entire population cannot be surveyed, so a probability sample should 
@@
                                 banking application such as a savings account, a survey would 
-                                most likely be presented online and it would have a coverage 
-                                bias due the exclusion of savings account holders that 
+                                most likely be presented online, and it would have a coverage 
+                                bias due to the exclusion of savings account holders that 
                                 do not bank online.
@@
 
-                    \end{description}
+                    \end{enumerate}
 
@@
                 After collecting the necessary survey data from Table \ref{tab:satisfactiondata},
-                calculating the score is rather straight forward.
+                calculating the score is rather straightforward.
                 The scores for each question are averaged and then those
@@
             the number of requirements a team can complete in a given time frame can
-            be difficult. Thus, number of requirements is one way to measure 
+            be difficult. Thus, the number of requirements is one way to measure 
             amount of work
-            but there are others.  Here are 3 possible choices in descending
+            but there are others.  Here are three possible choices in descending
             order of preference.
-            \begin{description}
-                \item[Function Points] Function points measure the size of the
+            \begin{enumerate}
+                \item \textbf{Function Points} - Function points measure the size of the
                     software functionality, not the size or time required
@@
                     for amount of work being completed. 
-                \item[Story Points] Story points, sometimes just referred to 
+                \item \textbf{Story Points} - Story points, sometimes just referred to 
                     as stories, are broken down requirements that can be
-                    completed in an Agile Sprint of 2 to 4 weeks.  A 
+                    completed in an Agile Sprint of two to four weeks.  A 
                     story is usually smaller, simpler, and more concise
@@
                     Scrum \cite{Ashmore2014}.
-                \item[Requirements] These are just the requirements as
+                \item \textbf{Requirements} - These are just the requirements as
                     written by the users or business partners.  Each requirement
@@
                     task.  
-            \end{description}
+            \end{enumerate}
 
@@
                 lower bound of 0 since negative requirements cannot be 
-                completed\footnote{Theoritically, a negative requirement would
+                completed\footnote{Theoretically, a negative requirement would
                 be considered a defect.}.  Unfortunately, an upper bound
@@
             In order to accomplish the single number score that CRI requires,
-            the 5 element scores must be combined. The combination of the scores
+            the five element scores must be combined. The combination of the scores
             is a weighted average.  The weights can be set based upon the 
@@
             This weighted average allows for a score to be computed even when not
-            all 5 elements are present. Just perform the weighted average with
+            all five elements are present. Just perform the weighted average with
             as many elements as present.  This technique allows CRI to implemented
@@
     \subsection{CORRELATIONS IN CRI}
-        It is possible that 2 or more of the 5 elements of CRI will be correlated.  This means that
+        It is possible that two or more of the five elements of CRI will be correlated.  This means that
         one of the elements can be predicted based upon the values of the other elements.  Although
@@
         The sensitivity of the formulas should be tested as the scores should not
-        fluctuate drastically for similar values.  There are 2 possible techniques
+        fluctuate drastically for similar values.  There are two possible techniques
         for testing the sensitivity of the formulas. 
-        \begin{description}
-            \item[First] Given the historical data that has been collected,
+        \begin{enumerate}
+            \item Given the historical data that has been collected,
                 alter the values by some small random amount.  Then recalculate
@@
                 formula which is not overly sensitive. 
-            \item[Second] Another technique is to use Monte Carlo methods to 
+            \item Another technique is to use Monte Carlo methods to 
                 randomly generate input values for the element functions.  
@@
                 in statistical modeling.
-        \end{description}
+        \end{enumerate}
 
@@
             each focus area.  
-            As can be seen, CRI clearly addresses the 3 main focus areas of software analytics.  CRI does not provide
+            As can be seen, CRI clearly addresses the three main focus areas of software analytics.  CRI does not provide
             any mechanisms for improving the focus areas, but it provides a consistent mechanism to measure
@@
 
-                User Experience & One of the 5 elements of CRI is satisfaction.
+                User Experience & One of the five elements of CRI is satisfaction.
 While not all of the questions focus solely on the user experience, the entire purpose of the survey is to determine if the user is satisfied
@@
                 \myrowcolour%
-                Quality & Again, one of the 5 elements specifically focuses on quality.  CRI provides a single number
+                Quality & Again, one of the five elements specifically focuses on quality.  CRI provides a single number
                 to measure quality.  Therefore, it is easy to track changes in quality over time.  CRI does not address
@@
         \subsubsection{CRI VS. IMPORTANT QUESTIONS OF SOFTWARE ANALYTICS}
-            Also, section \ref{subsub:softwareanalytics} mentions 3 important questions that
-            software analytics must address.  Table \ref{tab:questions} presents the 3 questions
+            Also, section \ref{subsub:softwareanalytics} mentions three important questions that
+            software analytics must address.  Table \ref{tab:questions} presents the three questions
             and a description of how CRI addresses that specific question.  It is clear
@@
             versus CRI.
-            As the newer 2 characteristics of a balanced scorecard
+            As the newer two characteristics of a balanced scorecard
             have only existed since 2010 and the adoption is limited,
-            the comparison will only be against the original 4 balanced
+            the comparison will only be against the original four balanced
             scorecard characteristics.
@@
             as either the balanced scorecard or CRI. Actually, CRI incorporates
-            the 5 core measurements from project management.
+            the five core measurements from project management.
             Plus, the process productivity

### 2015-03-20 paper_50_sdlc-ae.tex
more grammatical fixes updates to lists in the appendix

@@
         All the data necessary to compute CRI needs to be stored in a database.  This section will 
-        lay out the structure of tables and relationships necessary to the store all the data
+        lay out the structure of tables and relationships necessary to store all the data
         within a relational database.  The SQL\footnote{Structured Query Language (SQL) is 
@@
             to store the raw data that is collected.  These tables
-            will match up with the necessary data for each of the 5 elements
+            will match up with the necessary data for each of the five elements
             of CRI.  Figure \ref{fig:raw} provides a visual description
@@
             these tables is to store the raw data in a single location. The
-            5 table names are:
+            five table names are:
             \begin{enumerate}
@@
             \end{enumerate}
-            Notice these table names match with the 5 elements of CRI.
+            Notice these table names match with the five elements of CRI.
 
@@
             \end{enumerate}
-            Again, these table names match very closely with the 5 elements of CRI.
+            Again, these table names match very closely with the five elements of CRI.
 
@@
             table is the ELEMENT table.  It simply stores the CRI element 
-            (Quality, Availability,Satisfaction,Schedule,Requirements,Overall) and 
-            optional description. The second table is the CRI\_SCORE table.  
+            (Quality, Availability, Satisfaction, Schedule, Requirements, Overall) and 
+            an optional description. The second table is the CRI\_SCORE table.  
             It stores all the final element scores and the final overall CRI
@@
             \ref{fig:final_score_tables} provides a visual representation of the 
-            relationship between the 2 tables.
+            relationship between the two tables.
 

### 2015-03-20 paper_70_case-study.tex
more grammatical fixes updates to lists in the appendix

@@
     \subsection{QUALITY}
-        The first step to dealing with the quality data is a quick
+        The first step for dealing with the quality data is a quick
         analysis of the data.  Table \ref{tab:quality_desc} provides
@@
         descriptive statistics are limited, so extra values were
-        added to the table after removing 4 outliers.  The new values
+        added to the table after removing four outliers.  The new values
         in the table are: Schedule Duration (Scheduled Finish - Scheduled Start),
@@
         satisfaction, is the most likely element to exhibit correlation,
-        so the 4 elements analyzed here remain independent.
+        so the four elements analyzed here remain independent.
 

### 2015-03-20 paper_80_conclusion.tex
make testcase one word
more grammatical fixes updates to lists in the appendix

@@
 
-    As shown in Table \ref{tab:bsc}, CRI is currently not addressing 2 
+    As shown in Table \ref{tab:bsc}, CRI is currently not addressing two 
     characteristics of the balanced scorecard.  If the SDO does not operate 
@@
     of time required to generate
-    proper test cases.  These are just a couple of examples of expansions
+    proper testcases.  These are just a couple of examples of expansions
     to the SDLC-AE.  These and other advancements could lead to greater
@@
 
-    There are many metrics that can be used to evaluate a Software
-    Development Organization (SDO). The entire SDO needs to be measured 
+    There are many metrics that can be used to evaluate an SDO. 
+    The entire SDO needs to be measured 
     and analyzed properly, not just the development portion. 
@@
     \begin{itemize}
-        \item CRI defines what 5 elements of an SDO should be measured.
+        \item CRI defines what five elements of an SDO should be measured.
             Result indicators are included for quality, availability, satisfaction,
@@
         \item CRI defines what data needs to be collected to create a 
-            score for the 5 elements.
-        \item CRI defines the formulas to create a score for the 5 elements.
+            score for the five elements.
+        \item CRI defines the formulas to create a score for the five elements.
         \item A process was outlined to generate the CRI score.

### 2015-03-20 acknowledgements.tex
a few more updates to the signature page
added quotes back in
final format check, added latest PDF

@@
 ACKNOWLEDGEMENTS\\
-~\\
 \end{center}
@@
 
-I would also like to acknowledge numerous other people for providing
-guidance and support during the process.
-I will only use first names, but you know who you are. Thank you to: Jess, Chris, Clay, 
-Bob, Todd, Leslie, Mike, and Ralph.
+Next, I would like to thank my advisor, Dr. Gary Hatfield, for the encouragement and guidance
+along the way.  Also, thank you to Clay, Jess, and Chris for helping me formulate 
+the initial idea.
+
+Finally, I would like to thank my Mom for providing a 
+final grammatical proof-reading of the dissertation.
 

### 2015-03-20 appendices.tex
final format check, added latest PDF

@@
             for requirements.  The histogram is based upon the
-            fraction $\frac{Scheduled Requirements}{Actual Requirements}$. The
-            values where the fraction equals 1 have been left out of the histogram.
+            fraction, $\frac{Scheduled Requirements}{Actual Requirements}$. The
+            values where the fraction equals one have been left out of the histogram.
             So, the histogram show only the data that did not deliver exactly
@@
         \begin{easylist}[itemize]
-            & Change to Database Structure  
-            & Modify Database Data    
-            & Create a New Database, number of new databases  
-            & Server Configuration Changes Required   
-            & New Servers Required   
-            & Number of People Involved  
-            & Number of (sub)Systems Involved  
-            & Estimation Date
-            & Number of Days Allowed
-            & List of Other Attributes
-            & Number of Screens Involved 
-            & Actual Values (hours, days, dollars) 
-            & Estimated Values
-            && Estimated Dev Hours: 
+            & Change to database structure  
+            & Modify database data    
+            & Create a new database, number of new databases  
+            & Server configuration changes required   
+            & New servers required   
+            & Number of people involved  
+            & Number of (sub)systems involved  
+            & Estimation date
+            & Number of days allowed
+            & List of other attributes
+            & Number of screens involved 
+            & Actual values (hours, days, dollars) 
+            & Estimated values
+            && Estimated development hours: 
                 The number of development hours estimated for a 
                 project, this is just developer hours
-            && Estimated Doc Hours: 
+            && Estimated documentation hours: 
                 The number of documentation hours estimated for a project
-            && Estimated Test Hours:
+            && Estimated testing hours:
                 The number of testing hours estimated for a project
-            && Estimated Deployment Hours: 
+            && Estimated deployment hours: 
                 The number of estimated hours required to 

### 2015-03-20 paper_10_intro.tex
final format check, added latest PDF

@@
         final audience. \nomenclature{PROD}{Production} 
-        \item[defect] ``A software defect is a bug or error that causes
+        \item[Defect] - ``A software defect is a bug or error that causes
                     software to either stop operating or to produce
@@
         \item \textbf{Competencies} - Specific competencies will 
-            be required for completing activities
+            be required for completing activities.
     \end{enumerate}

### 2015-03-20 paper_20_sdo.tex
more grammatical fixes updates to lists in the appendix
final format check, added latest PDF

@@
 Software is more than just computer programs. According to Ian Sommerville \cite{Sommerville2001}, 
-"Software is not just the programs but also all associated documentation and configuration data which is needed to make these programs operate correctly."
+``Software is not just the programs but also all associated documentation and configuration data which is needed to make these programs operate correctly.''
 This is the definition used for the remainder of this dissertation.
@@
         documentation and focus more on the implementation phase. Here are
-        the common phases in nearly all SDLC models:
+        the five common phases in nearly all SDLC models:
         \begin{description}
@@
 
-        These 5 steps cannot cover everything that needs to be accomplished
+        These five steps cannot cover everything that needs to be accomplished
         during a project.  They just provide of rough guideline of what needs

### 2015-03-20 paper_70_case-study.tex
final format check, added latest PDF

@@
             \centering
-            \includegraphics[scale=.3]{images/quality_scores.png}
+            \includegraphics[scale=.28]{images/quality_scores.png}
             \caption{CRI QUALITY SCORES}
@@
 
-        \begin{figure}[hb]
+        \begin{figure}[htb]
             \centering
-            \includegraphics[scale=.3]{images/availability_scores.png}
+            \includegraphics[scale=.28]{images/availability_scores.png}
             \caption{CRI AVAILABILITY SCORES}
@@
             \centering
-            \includegraphics[scale=.3]{images/schedule_scores.png}
+            \includegraphics[scale=.28]{images/schedule_scores.png}
             \caption{CRI SCHEDULE SCORES}
@@
 
-        \begin{figure}[htb]
+        \begin{figure}[hbt]
             \centering
-            \includegraphics[scale=.3]{images/requirements_scores.png}
+            \includegraphics[scale=.28]{images/requirements_scores.png}
             \caption{CRI REQUIREMENTS SCORES}
@@
         applicable elements.  In this case study, the weights are all equal,
-        so CRI is just a straight average.
+        so CRI is a straight average.
 
-        \begin{figure}[htb]
+        \begin{figure}[hbt]
             \centering
-            \includegraphics[scale=.3]{images/cri_scores.png}
+            \includegraphics[scale=.28]{images/cri_scores.png}
             \caption{CRI SCORES}
@@
 
-        \begin{figure}[htb]
+        \begin{figure}[hbt]
             \centering
-            \includegraphics[scale=.3]{images/sensitivity.png}
+            \includegraphics[scale=.25]{images/sensitivity.png}
             \caption{CRI SENSITIVITY ANALYSIS}
@@
         Figure \ref{fig:correlation_cri} shows a scatterplot matrix
-        for the individual element scores.  No correlation appears
+        for the individual element scores.  There
+        is no clear upper or downward trend in any of the graphs.
+        Therefore, no correlation appears
         to exist between any of the elements. The missing element,
-        satisfaction, is the most likely element to exhibit correlation,
-        so the four elements analyzed here remain independent.
+        satisfaction, is the most likely element to exhibit correlation. 
+        That is because lower scores on the other four elements
+        will likely result in 
+        decreased survey scores, which will result in lower satisfaction
+        scores.  Anyhow, the four elements analyzed here remain independent.
 
@@
             \centering
-            \includegraphics[scale=.3]{images/correlation.png}
+            \includegraphics[scale=.25]{images/correlation.png}
             \caption{SCATTERPLOT MATRIX OF CRI ELEMENT SCORES}

### 2015-04-06 paper_10_intro.tex
final updates before format check

@@
 
-        \item[Application] - a software system or a collection of other applications 
+        \item[Application] - A software system or a collection of other applications 
         \item[Release] - A collection of projects being put in production on a specified date
@@
     Points are positive or negative based upon the 
-    presence of various techniques. A couple of example techniques are: 
+    presence of various techniques. Two examples of such techniques are: 
     automated source code analysis and continuous integration.  The end 
@@
     readily available in today's systems.''  Creating software involves
-    a vast amount of processes.  Numerous logs of raw data are collected.  
+    many processes.  Numerous logs of raw data are collected.  
     One application of process mining in the area of software development
@@
     than interpreting that value.  No matter the interpretation,
-    the goal is to release the number of problems with the software.
+    the goal is to decrease the number of problems with the software.
     Top 10 lists have been created for techniques to remove problems
@@
     software engineering \cite{Kaner2004,Xie2009,Taylor2010,Halkidi2011}. 
-    Finally, The term software intelligence was proposed for the field of study
+    The term software intelligence was proposed for the field of study
     \cite{Hassan2010}, but eventually
@@
     developers and managers \cite{Buse2012}.  When the
-    data and tools exists, the analytics should help an
+    data and tools exist, the analytics should help an
     organization with the following tasks.
@@
         \item Determine what is and is not working
-        \item Manage Risk
+        \item Manage risk
         \item Anticipate changes

### 2015-04-06 paper_20_sdo.tex
final updates before format check

@@
     IEEE ISO610.12 defines software engineering as, 
-    ''The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
+    ``The application of a systematic, disciplined, quantifiable approach to the development, operation, and maintenance of software''
     \cite{Ieee1990}.

### 2015-04-06 paper_40_cri.tex
final format check, added latest PDF
final updates before format check

@@
     A negative score indicates worse-than-expected performance and a 
-    positive score indicates better-than-expected performance.   Here are some 
-    examples. An CRI score of 0.35 means the organization is 
+    positive score indicates better-than-expected performance.   For
+    example, a CRI score of 0.35 means the organization is 
     performing 35\% better than expected.  Conversely, a score 
-    of -0.15 means an organization is performing 15\% worse than expected.
+    of $-0.15$ means an organization is performing 15\% worse than expected.
 
@@
     \begin{itemize}
-        \item The range of scores must have equal values above and below 0
+        \item The range of scores must have equal values above and below 0.
         \item The minimum score must equate to the worst possible 
-            performance, however that is defined
+            performance, however that is defined.
         \item Similarly, the maximum score must equate to the best possible performance.  
-        \item A score of 0 must be average (or expected) performance
-        \item All individual elements must have the same scoring range
+        \item A score of 0 must be average (or expected) performance.
+        \item All individual elements must have the same scoring range.
     \end{itemize}
@@
 
-                1 & Software is unavailable and no workaround   \\
+                1 & Software is unavailable with no workaround   \\
                 \myrowcolour%
@@
                      \begin{array}{lr}
-                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \times k  \\
-                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{\sigma_i^2} \times k
-                     \end{array}
-                   \right] \text{   , calculate quality score for each app $i$}
+                       \text{where } f_i \geq d_i & :  \frac{f_i - d_i}{f_i} \cdot k  \\
+                       \text{where } d_i > f_i  & : \frac{f_i-d_i }{\sigma_i^2} \cdot k
+                     \end{array} \right.
+                   \text{   , calculate quality score for each app $i$}
                 \end{displaymath} 
@@
                     \item $S_{1_i}$ is the quality score for Application ID $i$
-                    \item $k$ scaling factor to produce results in the range $[-k,k]$
+                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                     \item $n$ is the number of Application IDs
@@
                      \begin{array}{lr}
-                       \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}}\times k \right] \\
-                       \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}}\times k \right]
+                       \text{where } A_{a_i} \leq A_{e_i} & : \frac{A_{a_i} - A_{e_i}}{A_{e_i}}\cdot k  \\
+                       \text{where } A_{a_i} > A_{e_i}  & : \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}}\cdot k
                      \end{array}
-                   \right. \text{   , calculate availability score for each app $i$}
+                   \right. \text{   , calculate availability score for each sys $i$}
                 \end{displaymath}
@@
                     \item $S_{2_i}$ is the availability score for System ID $i$
-                    \item $k$ scaling factor to produce results in the range $[-k,k]$
-                    \item $A_{a_i}$ actual availability for System ID $i$
-                    \item $A_{e_i}$ expected availability for System ID $i$
+                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
+                    \item $A_{a_i}$ is the actual availability for System ID $i$
+                    \item $A_{e_i}$ is the expected availability for System ID $i$
                 \end{itemize}
@@
                 \[
-                    S_{3_i} = \sum^n_{i=1}\left( k \times \frac{ \sum^m_{j=1}a_{ij}-\frac{min + max}{2}}{m} \right)
+                    S_{3_i} = k \cdot \frac{ \sum^m_{j=1}(\frac{2a_{ij}-min-max}{max-min})}{m}
                 \]
@@
                     \item $S_{3_i}$ is the satisfaction score for Question ID $i$
-                    \item $k$ scaling factor to produce results in the range $[-k,k]$
-                    \item $a_{ij}$ answer to question $i$ for respondent $j$
-                    \item $n$ number of questions
-                    \item $m$ number of respondents
-                    \item $min$ minimum score for a question
-                    \item $max$ maximum score for a question
+                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
+                    \item $a_{ij}$ is the answer to question $i$ for respondent $j$
+                    \item $n$ is the number of questions
+                    \item $m$ is the number of respondents
+                    \item $min$ is the minimum score for a question
+                    \item $max$ is the maximum score for a question
                 \end{itemize}
@@
                 Then the satisfaction score is calculated as below.  Use a weighted average
-                to combine the question scores.
+                to combine the question scores:
 
@@
                     \item $w_i > 0$ for all $i$
-                    \item $\sum\limits^n_{i=1} w_i = 1$
+                    \item $\sum\limits^n_{i=1} w_i = 1$.
                 \end{itemize}
@@
                 \begin{itemize}
-                    \item $F_{a_i}$ the actual finish date of project $i$
-                    \item $F_{s_i}$ the scheduled finish date of project $i$
-                    \item $B_{s_i}$ the scheduled beginning date of project $i$
-                    \item $\Delta_i$ the proportion the schedule was missed for project $i$
+                    \item $F_{a_i}$ is the actual finish date of project $i$
+                    \item $F_{s_i}$ is the scheduled finish date of project $i$
+                    \item $B_{s_i}$ is the scheduled beginning date of project $i$
+                    \item $\Delta_i$ is the proportion the schedule was missed for project $i$
                 \end{itemize}
@@
 
-                \begin{equation}
+                \[
                 \label{eq:CDF}
-                    S_{4_i} = 2k \cdot (CDF(\Delta_i) - \frac{1}{2})
-                \end{equation}
+                    S_{4_i} = 2k \cdot \left(CDF(\Delta_i) - \frac{1}{2} \right)
+                \]
                 where
@@
                     \item $S_{4_i}$ is the schedule score for Project ID $i$
-                    \item $k$ scaling factor to produce results in the range $[-k,k]$
+                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                 \end{itemize}
@@
                      \begin{array}{lr}
-                        \text{where } \Delta_i \geq 1 & : -1 \times k \\
-                       \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \times k  \\
-                       \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \times k
+                        \text{where } \Delta_i \geq 1 & : -1 \cdot k \\
+                       \text{where }  \Delta_i \leq \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{\bar{\Delta}}   \cdot k  \\
+                       \text{where } \Delta_i > \bar{\Delta} & : \frac{\bar{\Delta} - \Delta_i}{1 - \bar{\Delta}} \cdot k
                      \end{array}
-                   \right] \text{   , calculate schedule score for each project $i$}
+                   \right. \text{   , calculate schedule score for each project $i$}
                 \end{displaymath}
@@
                     a weighted average
-                    \item $k$ scaling factor to produce results in the range $[-k,k]$
+                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
                     \item $w_i > 0$ for all $i$
@@
                     \item $n$ is the number of projects
-                    \item $F_{a_i}$ the actual finish date of project $i$
-                    \item $F_{s_i}$ the scheduled finish date of project $i$
-                    \item $B_{s_i}$ the scheduled beginning date of project $i$
-                    \item $\Delta_i$ the percent the schedule was missed
+                    \item $F_{a_i}$ is the actual finish date of project $i$
+                    \item $F_{s_i}$ is the scheduled finish date of project $i$
+                    \item $B_{s_i}$ is the scheduled beginning date of project $i$
+                    \item $\Delta_i$ is the percent the schedule was missed
                     \item $\bar{\Delta}$ is the average percent schedules are missed
@@
                      \begin{array}{lr}
-                       \text{where } R_{a_i} > b \times R_{s_i} & :  1 \times k \\
-                       \text{where } R_{a_i} \leq R_{s_i} & : \left[ \frac{R_{a_i} - R_{s_i}}{R_{s_i}}\times k \right] \\
-                       \text{where } R_{a_i} > R_{s_i}  & : \left[ \frac{R_{a_i} - R_{s_i} }{b \cdot R_{s_i}}\times k \right]
+                       \text{where } R_{a_i} > b \cdot R_{s_i} & :  1 \cdot k \\
+                       \text{where } R_{a_i} \leq R_{s_i} & : \frac{R_{a_i} - R_{s_i}}{R_{s_i}}\cdot k \\
+                       \text{where } R_{a_i} > R_{s_i}  & : \frac{R_{a_i} - R_{s_i} }{b \cdot R_{s_i}}\cdot k
                      \end{array}
@@
                     \item $S_{5_i}$ is the requirements score for Project ID $i$
-                    \item $k$ scaling factor to produce results in the range $[-k,k]$
-                    \item $R_{a_i}$ actual requirements completed for Project ID $i$
-                    \item $R_{s_i}$ expected requirements completed for Project ID $i$
-                    \item $b$ multiplier to determine the upper bound
+                    \item $k$ is the scaling factor to produce results in the range $[-k,k]$
+                    \item $R_{a_i}$ is the actual requirements completed for Project ID $i$
+                    \item $R_{s_i}$ is the expected requirements completed for Project ID $i$
+                    \item $b$ is the multiplier to determine the upper bound
                 \end{itemize}
@@
             all five elements are present. Just perform the weighted average with
-            as many elements as present.  This technique allows CRI to implemented
+            as many elements as present.  This technique allows CRI to be implemented
             before data for all the elements has been collected.  Just begin

### 2015-04-07 signature.tex
minor changes to signature page
formatting changes to title page and signature page

@@
 \yourtitle
-\vspace{0.5in}
 \end{center}
@@
 \par This dissertation is approved as a creditable and independent investigation by a 
-candidate for the Doctor of Philosophy degree and is acceptable for 
+candidate for the Doctor of Philosophy in \yourmajor \ degree and is acceptable for 
 meeting the dissertation requirements for this degree. Acceptance of this does not imply 
@@
 
-\vspace{1.5in}
-
 \singlespacing
 
-\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
-\hspace*{194bp}\youradvisor\\
-\hspace*{\fill}Dissertation Advisor \hspace*{47bp}Date
+\begin{textblock}{8.5}(2.7,5.875)
 
-\vspace{1in}
+\underline{\hspace{4.2in}}\\
+\youradvisor\\
+Dissertation Advisor \hspace{2.3in}Date
 
-\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
-\hspace*{194bp}\departmenthead\\
-\hspace*{\fill}Head, Math and Statistics \hspace*{40bp}Date
+\vspace{.75in}
 
-\vspace{1in}
+\underline{\hspace{4.2in}}\\
+\departmenthead\\
+Head, Department of Mathematics and Statistics \hspace{0.27in}Date
 
-\hspace*{\fill}\underline{$~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~$}\\
-\hspace*{194bp}Dean, Graduate School \hspace*{54bp}Date
+\vspace{.5in}
+
+\underline{\hspace{4.2in}}\\
+Dean, Graduate School \hspace{2.12in}Date
+
+\end{textblock}
 \end{document}

### 2015-04-13 signature.tex
move up quotes on dedication page, format changes on signature page

@@
 \youradvisor\\
-Dissertation Advisor \hspace{2.3in}Date
+Dissertation Advisor \hspace{2.43in}Date
 
@@
 \departmenthead\\
-Head, Department of Mathematics and Statistics \hspace{0.27in}Date
+Head, Department of Mathematics and Statistics \hspace{0.6in}Date
 
@@
 \underline{\hspace{4.2in}}\\
-Dean, Graduate School \hspace{2.12in}Date
+Dean, Graduate School \hspace{2.27in}Date
 
